### 2021-02-17 paper/sample-acmsmall-conf.tex
Started paper folder

\documentclass[acmsmall,screen,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2021}
\acmYear{2021}
\acmDOI{???}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[JCDL '21]{JCDL '21: Joint Conference on
  Digital Libraries}{September 27--30, 2021}{????, USA}
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  %June 03--05, 2018, Woodstock, NY}
%\acmPrice{15.00}
%\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Automated Metadata Generation for Biological Specimen Image Collections}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Joel Pepper}
\email{jcp353@drexel.edu}
%\orcid{1234-5678-9012}
\author{David Breen}
\author{Jane Greenberg}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Pepper, Breen and Greenberg}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002951.10002952.10003219.10003215</concept_id>
       <concept_desc>Information systems~Extraction, transformation and loading</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Extraction, transformation and loading}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{bioinformatics, metadata}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{fish}
  \caption{Fish prediction}
  \Description{Fish prediction}
  \label{fig:fish}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
Text
\section{Background}
Text
\subsection{Related Work}
Text
\section{Objectives}
Text
\section{Data Analysis}
Text
\section{Discussion}
Text
\section{Conclusion}
Text

\pagebreak{}

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[acmsmall]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-acmsmall-conf.tex'.

### 2021-02-18 paper/sample-acmsmall-conf.tex
Testing

@@
-\documentclass[acmsmall,screen,review]{acmart}
+%\documentclass[acmsmall,screen,review]{acmart}
+\documentclass[acmconf,screen,review]{acmart}
+\usepackage{todonotes}
 
@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
+  A clear\todo{test} and well-documented \LaTeX\ document is presented as an
   article formatted for publication by ACM in a conference proceedings
@@
 \section{Introduction}
-Text
+Text~\ref{demo-intro}~\todo{Liney}
 \section{Background}
-Text
+Text~\todo[noline]{Do this}
 \subsection{Related Work}
@@
 \section{Discussion}
-Text
+Text \textit{texty text}~\cite{Lamport:LaTeX}
 \section{Conclusion}
-Text
+Text \textbf{text}
 
@@
 
-\section{Introduction}
+\section{Introduction}~\label{demo-intro}
 ACM's consolidated article template, introduced in 2017, provides a

### 2021-02-25 gen_metadata.py
Set up to loop over fish and eye pairings

@@ -41,7 +41,7 @@ def gen_metadata(file_path):
     cfg.merge_from_file("config/mask_rcnn_R_50_FPN_3x.yaml")
     cfg.MODEL.ROI_HEADS.NUM_CLASSES = 5
     cfg.MODEL.WEIGHTS = os.path.join(cfg.OUTPUT_DIR, "model_final.pth")
-    cfg.MODEL.ROI_HEADS.SCORE_THRESH_TEST = 0.05
+    cfg.MODEL.ROI_HEADS.SCORE_THRESH_TEST = 0.3
     predictor = DefaultPredictor(cfg)
     im = cv2.imread(file_path)
     metadata = Metadata(evaluator_type='coco', image_root='.',
@@ -59,20 +59,19 @@ def gen_metadata(file_path):
     for i in range(1, 5):
         temp = insts.pred_classes==i
         selector += temp.cumsum(axis=0).cumsum(axis=0) == 1
-    try:
-        fish = insts[insts.pred_classes==0][0]
+    fish = insts[insts.pred_classes==0]
+    if len(fish):
         results['fish'] = [{}]
-    except:
+    else:
         fish = None
-    results['is_fish'] = bool(fish)
+    results['has_fish'] = bool(fish)
     try:
         ruler = insts[insts.pred_classes==1][0]
-        print(ruler)
         ruler_bbox = list(ruler.pred_boxes.tensor.cpu().numpy()[0])
         results['ruler_bbox'] = [round(x) for x in ruler_bbox]
     except:
         ruler = None
-    results['is_ruler'] = bool(ruler)
+    results['has_ruler'] = bool(ruler)
     try:
         two = insts[insts.pred_classes==3][0]
     except:
@@ -84,45 +83,66 @@ def gen_metadata(file_path):
     if ruler and two and three:
         scale = calc_scale(two, three)
         results['scale'] = scale
+    visualizer = Visualizer(im[:, :, ::-1], metadata=metadata, scale=1.0)
+    vis = visualizer.draw_instance_predictions(insts[selector].to('cpu'))
+    os.makedirs('images', exist_ok=True)
+    file_name = file_path.split('/')[-1]
+    print(file_name)
+    cv2.imwrite(f'images/gen_mask_prediction_{file_name}',
+            vis.get_image()[:, :, ::-1])
     if fish:
         try:
-            eye = insts[insts.pred_classes==2][0]
+            eyes = insts[insts.pred_classes==2]
         except:
[…]

### 2021-02-25 gen_metadata.py
Fixed flood filling corner issue

@@ -44,6 +44,7 @@ def gen_metadata(file_path):
     cfg.MODEL.ROI_HEADS.SCORE_THRESH_TEST = 0.3
     predictor = DefaultPredictor(cfg)
     im = cv2.imread(file_path)
+    im_gray = cv2.imread(file_path, cv2.IMREAD_GRAYSCALE)
     metadata = Metadata(evaluator_type='coco', image_root='.',
             json_file='',
             name='metadata',
@@ -108,9 +109,19 @@ def gen_metadata(file_path):
             results['fish_count'] = len(insts[(insts.pred_classes==0).
                 logical_and(insts.scores > 0.3)])
 
-            bbox, mask = gen_mask(
-                    fish.pred_boxes.tensor.cpu().numpy().astype('float64')[i],
-                    file_path, file_name)
+            bbox_d = [round(x) for x in curr_fish.pred_boxes.tensor.cpu().
+                    numpy().astype('float64')[0]]
+            im_crop = im_gray[bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
+            f_bbox_crop = curr_fish.pred_masks[0].cpu().numpy()\
+                    [bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
+            fground = im_crop.reshape(-1)[f_bbox_crop.reshape(-1)]
+            bground = im_crop.reshape(-1)[np.invert(f_bbox_crop.reshape(-1))]
+            sign = -1 if np.mean(bground) > np.mean(fground) else 1
+            #print(np.std(fground))
+            #print(np.std(bground))
+            #print(len(curr_fish.pred_masks[0].cpu().numpy().reshape(-1)))
+            bbox, mask = gen_mask(bbox_d, file_path, file_name,
+                    val=np.mean(bground) + sign * np.std(bground) * 2)
             results['fish'][i]['bbox'] = list(bbox)
             #results['mask'] = mask.astype('uint8').tolist()
 
@@ -173,7 +184,7 @@ def calc_scale(two, three):
     #print(f'Pixels/cm: {scale}')
     return scale
 
-def gen_mask(bbox, file_path, file_name):
+def gen_mask(bbox, file_path, file_name, val=None):
     l = round(bbox[0])
     r = round(bbox[2])
     t = round(bbox[1])
@@ -189,7 +200,10 @@ def gen_mask(bbox, file_path, file_name):
[…]

### 2021-02-25 gen_metadata.py
Foreground background info added to output

@@ -117,11 +117,33 @@ def gen_metadata(file_path):
             fground = im_crop.reshape(-1)[f_bbox_crop.reshape(-1)]
             bground = im_crop.reshape(-1)[np.invert(f_bbox_crop.reshape(-1))]
             sign = -1 if np.mean(bground) > np.mean(fground) else 1
-            #print(np.std(fground))
-            #print(np.std(bground))
+            #print(np.mean(fground))
+            #print(np.mean(bground))
             #print(len(curr_fish.pred_masks[0].cpu().numpy().reshape(-1)))
             bbox, mask = gen_mask(bbox_d, file_path, file_name,
                     val=np.mean(bground) + sign * np.std(bground) * 2)
+            bbox_d = bbox
+            im_crop = im_gray[bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
+            f_bbox_crop = curr_fish.pred_masks[0].cpu().numpy()\
+                    [bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
+            fground = im_crop.reshape(-1)[f_bbox_crop.reshape(-1)]
+            bground = im_crop.reshape(-1)[np.invert(f_bbox_crop.reshape(-1))]
+            sign = -1 if np.mean(bground) > np.mean(fground) else 1
+            #print(np.mean(fground))
+            #print(np.mean(bground))
+            #im_crop = im_gray[bbox[1]:bbox[3],bbox[0]:bbox[2]]
+            #mask_crop = mask[bbox[1]:bbox[3],bbox[0]:bbox[2]]
+            #print(im_gray)
+            #print(mask_crop)
+            #exit(0)
+            #fground = im_crop.reshape(-1)[mask_crop.reshape(-1)]
+            #bground = im_crop.reshape(-1)[np.invert(mask_crop.reshape(-1))]
+            results['fish'][i]['foreground'] = {}
+            results['fish'][i]['foreground']['mean'] = np.mean(fground)
+            results['fish'][i]['foreground']['std'] = np.std(fground)
+            results['fish'][i]['background'] = {}
+            results['fish'][i]['background']['mean'] = np.mean(bground)
+            results['fish'][i]['background']['std'] = np.std(bground)
             results['fish'][i]['bbox'] = list(bbox)
             #results['mask'] = mask.astype('uint8').tolist()
 

### 2021-02-25 gen_metadata.py
Fish scale done, seems fairly accurate

@@ -101,6 +101,8 @@ def gen_metadata(file_path):
             if eyes:
                 eye_ols = [overlap(curr_fish, eyes[j]) for j in
                         range(len(eyes))]
+                # TODO: Add pred score as a secondary key in event there are
+                #       more than one 1.0 overlap eyes
                 max_ind = max(range(len(eye_ols)), key=eye_ols.__getitem__)
                 eye = eyes[max_ind]
             else:
@@ -117,9 +119,6 @@ def gen_metadata(file_path):
             fground = im_crop.reshape(-1)[f_bbox_crop.reshape(-1)]
             bground = im_crop.reshape(-1)[np.invert(f_bbox_crop.reshape(-1))]
             sign = -1 if np.mean(bground) > np.mean(fground) else 1
-            #print(np.mean(fground))
-            #print(np.mean(bground))
-            #print(len(curr_fish.pred_masks[0].cpu().numpy().reshape(-1)))
             bbox, mask = gen_mask(bbox_d, file_path, file_name,
                     val=np.mean(bground) + sign * np.std(bground) * 2)
             bbox_d = bbox
@@ -128,16 +127,6 @@ def gen_metadata(file_path):
                     [bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
             fground = im_crop.reshape(-1)[f_bbox_crop.reshape(-1)]
             bground = im_crop.reshape(-1)[np.invert(f_bbox_crop.reshape(-1))]
-            sign = -1 if np.mean(bground) > np.mean(fground) else 1
-            #print(np.mean(fground))
-            #print(np.mean(bground))
-            #im_crop = im_gray[bbox[1]:bbox[3],bbox[0]:bbox[2]]
-            #mask_crop = mask[bbox[1]:bbox[3],bbox[0]:bbox[2]]
-            #print(im_gray)
-            #print(mask_crop)
-            #exit(0)
-            #fground = im_crop.reshape(-1)[mask_crop.reshape(-1)]
-            #bground = im_crop.reshape(-1)[np.invert(mask_crop.reshape(-1))]
             results['fish'][i]['foreground'] = {}
             results['fish'][i]['foreground']['mean'] = np.mean(fground)
             results['fish'][i]['foreground']['std'] = np.std(fground)
@@ -145,15 +134,20 @@ def gen_metadata(file_path):
             results['fish'][i]['background']['mean'] = np.mean(bground)
             results['fish'][i]['background']['std'] = np.std(bground)
[…]

### 2021-02-26 gen_metadata.py
Attempt at batch processing w/ output file

@@ -1,3 +1,5 @@
+import math
+import json
 import sys
 import os
 from multiprocessing import Pool
@@ -88,7 +90,7 @@ def gen_metadata(file_path):
     vis = visualizer.draw_instance_predictions(insts[selector].to('cpu'))
     os.makedirs('images', exist_ok=True)
     file_name = file_path.split('/')[-1]
-    print(file_name)
+    #print(file_name)
     cv2.imwrite(f'images/gen_mask_prediction_{file_name}',
             vis.get_image()[:, :, ::-1])
     if fish:
@@ -157,8 +159,39 @@ def gen_metadata(file_path):
                     results['fish'][i]['side'] = 'left'
                 else:
                     results['fish'][i]['side'] = 'right'
+                results['fish'][i]['clock_value'] = clock_value(evec)
             results['fish'][i]['primary_axis'] = list(evec)
-    pprint.pprint(results)
+    #pprint.pprint(results)
+    return {file_name: results}
+
+def angle(vec1, vec2):
+    return math.acos(vec1.dot(vec2) / (np.linalg.norm(vec1) *
+        np.linalg.norm(vec2)))
+
+def clock_value(evec):
+    if evec[0] < 0:
+        if evec[1] < 0:
+            comp = np.array([0,-1])
+            start = 6
+        else:
+            comp = np.array([-1,0])
+            start = 9
+    else:
+        if evec[1] < 0:
+            comp = np.array([1,0])
+            start = 3
+        else:
+            comp = np.array([0,0])
+            start = 0
+    ang = angle(comp, evec)
+    clock = start + ang
+    if clock > 11.5:
+        clock = 12
+    elif clock < 0.5:
+        clock = 12
+    elif clock >= 0.5 and clock < 1.0:
+        clock = 1
+    return round(clock)
 
 def fish_length(mask, centroid, evec, scale):
     m1 = evec[1] / evec[0]
@@ -302,5 +335,17 @@ def shrink_bbox(mask):
 
     return (cmin, rmin, cmax, rmax)
 
+def main():
+    direct = sys.argv[1]
+    files = [os.path.join(direct, f) for f in direct]
+    with Pool() as p:
+        results = p.map(gen_metadata, files)
+    output = {}
+    for i in results:
+        output[i.keys()[0]]: i.values()[0]
+    with open('metadata.json', 'w') as f:
+        json.dump(output, f)
+
 if __name__ == '__main__':
-    gen_metadata(sys.argv[1])
+    #gen_metadata(sys.argv[1])
+    main()

### 2021-02-26 gen_metadata.py
Pool causing problems but runs single threaded

@@ -90,7 +90,7 @@ def gen_metadata(file_path):
     vis = visualizer.draw_instance_predictions(insts[selector].to('cpu'))
     os.makedirs('images', exist_ok=True)
     file_name = file_path.split('/')[-1]
-    #print(file_name)
+    print(file_name)
     cv2.imwrite(f'images/gen_mask_prediction_{file_name}',
             vis.get_image()[:, :, ::-1])
     if fish:
@@ -121,8 +121,11 @@ def gen_metadata(file_path):
             fground = im_crop.reshape(-1)[f_bbox_crop.reshape(-1)]
             bground = im_crop.reshape(-1)[np.invert(f_bbox_crop.reshape(-1))]
             sign = -1 if np.mean(bground) > np.mean(fground) else 1
-            bbox, mask = gen_mask(bbox_d, file_path, file_name,
-                    val=np.mean(bground) + sign * np.std(bground) * 2)
+            try:
+                bbox, mask = gen_mask(bbox_d, file_path, file_name,
+                        val=np.mean(bground) + sign * np.std(bground) * 2)
+            except:
+                return {file_name: {'errored': True}}
             bbox_d = bbox
             im_crop = im_gray[bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
             f_bbox_crop = curr_fish.pred_masks[0].cpu().numpy()\
@@ -337,12 +340,14 @@ def shrink_bbox(mask):
 
 def main():
     direct = sys.argv[1]
-    files = [os.path.join(direct, f) for f in direct]
-    with Pool() as p:
+    files = [entry.path for entry in os.scandir(direct)]
+    print(files)
+    with Pool(2) as p:
         results = p.map(gen_metadata, files)
+    #results = map(gen_metadata, files)
     output = {}
     for i in results:
-        output[i.keys()[0]]: i.values()[0]
+        output[list(i.keys())[0]]: list(i.values())[0]
     with open('metadata.json', 'w') as f:
         json.dump(output, f)
 

### 2021-02-26 gen_metadata.py
Runs in batch or single

@@ -90,7 +90,7 @@ def gen_metadata(file_path):
     vis = visualizer.draw_instance_predictions(insts[selector].to('cpu'))
     os.makedirs('images', exist_ok=True)
     file_name = file_path.split('/')[-1]
-    print(file_name)
+    #print(file_name)
     cv2.imwrite(f'images/gen_mask_prediction_{file_name}',
             vis.get_image()[:, :, ::-1])
     if fish:
@@ -139,18 +139,15 @@ def gen_metadata(file_path):
             results['fish'][i]['background']['mean'] = np.mean(bground)
             results['fish'][i]['background']['std'] = np.std(bground)
             results['fish'][i]['bbox'] = list(bbox)
-            #results['fish'][i]['mask'] = mask.astype('uint8').tolist()
+            results['fish'][i]['mask'] = mask.astype('uint8').tolist()
             results['fish'][i]['mask'] = '[...]'
 
             centroid, evec = pca(mask)
             if scale:
                 results['fish'][i]['length'] = fish_length(mask, centroid,
                         evec, scale)
-            results['fish'][i]['centroid'] = list(centroid)
+            results['fish'][i]['centroid'] = centroid.tolist()
             if eye:
-                #print(fish)
-                #print(overlap(fish[i], eye))
-                #exit(0)
                 eye_center = [round(x) for x in
                         eye.pred_boxes.get_centers()[i].cpu().numpy()]
                 results['fish'][i]['eye_center'] = list(eye_center)
@@ -162,7 +159,7 @@ def gen_metadata(file_path):
                     results['fish'][i]['side'] = 'left'
                 else:
                     results['fish'][i]['side'] = 'right'
-                results['fish'][i]['clock_value'] = clock_value(evec)
+                results['fish'][i]['clock_value'] = clock_value(evec, file_name)
             results['fish'][i]['primary_axis'] = list(evec)
     #pprint.pprint(results)
     return {file_name: results}
@@ -171,9 +168,10 @@ def angle(vec1, vec2):
     return math.acos(vec1.dot(vec2) / (np.linalg.norm(vec1) *
         np.linalg.norm(vec2)))
 
-def clock_value(evec):
+def clock_value(evec, file_name):
     if evec[0] < 0:
         if evec[1] < 0:
+            print(file_name)
             comp = np.array([0,-1])
             start = 6
         else:
@@ -192,8 +190,7 @@ def clock_value(evec):
[…]

### 2021-02-26 validate.py

@@ -1,0 +1,40 @@
+import json
+import pandas as pd
+import numpy as np
+import os
+
+df = pd.read_csv('/home/HDD/bgnn_data/image_quality_metadata_20210208.csv')
+results = json.load(open('metadata.json'))
+
+#one=set(os.listdir('/home/HDD/bgnn_data/full_imgs/'))
+#two=set(df.image_name)
+#inter=list(one&two)
+
+#np.random.seed(1)
+#values = np.unique(np.random.randint(len(inter), size=100))
+#for i in values:
+    #print(inter[i])
+#exit(0)
+
+counter = 0
+right = 0
+errored = 0
+for i in results.keys():
+    counter += 1
+    me = results[i]
+    #print(me)
+    if not 'errored' in me.keys():
+        yasin = df[df.image_name == i].iloc[0]
+        if me['has_fish']:
+            if me['fish'][0]['has_eye']:
+                right += me['fish'][0]['clock_value'] == yasin.specimen_angled
+                print(f"{i}: {me['fish'][0]['clock_value']}, {yasin.specimen_angled}")
+            else:
+                errored += 1
+        #print(me['fish']==)
+    else:
+        errored += 1
+print(f'Right: {right}')
+print(f'Failed: {errored}')
+print(f'Total: {counter}')
+print(f'Percent Right: {right / counter}')

### 2021-02-26 gen_metadata.py
Working fairly well

@@ -90,7 +90,7 @@ def gen_metadata(file_path):
     vis = visualizer.draw_instance_predictions(insts[selector].to('cpu'))
     os.makedirs('images', exist_ok=True)
     file_name = file_path.split('/')[-1]
-    #print(file_name)
+    print(file_name)
     cv2.imwrite(f'images/gen_mask_prediction_{file_name}',
             vis.get_image()[:, :, ::-1])
     if fish:
@@ -154,7 +154,10 @@ def gen_metadata(file_path):
                 dist1 = distance(centroid, eye_center + evec)
                 dist2 = distance(centroid, eye_center - evec)
                 if dist2 > dist1:
+                    #print("HERE")
+                    #print(evec)
                     evec *= -1
+                    #print(evec)
                 if evec[0] <= 0.0:
                     results['fish'][i]['side'] = 'left'
                 else:
@@ -171,7 +174,7 @@ def angle(vec1, vec2):
 def clock_value(evec, file_name):
     if evec[0] < 0:
         if evec[1] < 0:
-            print(file_name)
+            #print(file_name)
             comp = np.array([0,-1])
             start = 6
         else:
@@ -190,7 +193,7 @@ def clock_value(evec, file_name):
         clock = 12
     elif clock < 0.5:
         clock = 12
-    print(clock)
+    #print(evec)
     return round(clock)
 
 def fish_length(mask, centroid, evec, scale):
@@ -239,9 +242,14 @@ def pca(img):
 
     cov = np.cov(coords)
     evals, evecs = np.linalg.eig(cov)
+    if evals[0] > evals[1]:
+        evec = evecs[0]
+    else:
+        evec = evecs[1]
 
-    sort_indices = np.argsort(evals)[::-1]
-    return (np.array(centroid), evecs[:, sort_indices[0]])
+    #sort_indices = np.argsort(evals)[::-1]
+    #return (np.array(centroid), evecs[:, sort_indices[0]])
+    return (np.array(centroid), evec)
 
 def distance(pt1, pt2):
     return np.sqrt((pt1[0] - pt2[0])**2 + (pt1[1] - pt2[1])**2)

### 2021-03-16 gen_metadata.py
May have fixed adaptive thresholding

@@ -117,37 +117,30 @@ def gen_metadata(file_path):
             results['fish_count'] = len(insts[(insts.pred_classes==0).
                 logical_and(insts.scores > 0.3)])
 
-            bbox_d = [round(x) for x in curr_fish.pred_boxes.tensor.cpu().
-                    numpy().astype('float64')[0]]
-            im_crop = im_gray[bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
-            f_bbox_crop = curr_fish.pred_masks[0].cpu().numpy()\
-                    [bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
-            fground = im_crop.reshape(-1)[f_bbox_crop.reshape(-1)]
-            bground = im_crop.reshape(-1)[np.invert(f_bbox_crop.reshape(-1))]
-            mean_b = np.mean(bground)
-            mean_f = np.mean(fground)
-            flipped = mean_b < mean_f
-            val = (mean_b + mean_f) / 2
-            if flipped:
-                val -= val * VAL_SCALE_FAC
-            else:
-                val += val * VAL_SCALE_FAC
-            val = min(max(1, val), 254)
             #try:
-            bbox, mask = gen_mask(bbox_d, file_path, file_name,
-                    im_gray, val, flipped=flipped)
+            bbox = [round(x) for x in curr_fish.pred_boxes.tensor.cpu().
+                      numpy().astype('float64')[0]]
+            im_crop = im_gray[bbox[1]:bbox[3],bbox[0]:bbox[2]]
+            detectron_mask = curr_fish.pred_masks[0].cpu().numpy()\
+                    [bbox[1]:bbox[3],bbox[0]:bbox[2]]
+            val = adaptive_threshold(bbox, im_gray, detectron_mask)
+            bbox, mask = gen_mask(bbox, file_path, file_name, im_gray, val)
             #except:
                 #return {file_name: {'errored': True}}
             if not np.count_nonzero(mask):
                 print('Mask failed: {file_name}')
                 results['errored'] = True
             else:
-                bbox_d = bbox
-                im_crop = im_gray[bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
-                f_bbox_crop = curr_fish.pred_masks[0].cpu().numpy()\
[…]

### 2021-03-17 gen_metadata.py
Runs validation for batch generated metadata

@@ -10,8 +10,10 @@ from PIL import Image
 from functools import partial
 import matplotlib.pyplot as plt
 import pprint
+from copy import copy
 
 import torch
+#torch.multiprocessing.set_start_method('forkserver')
 
 import pycocotools
 import detectron2.structures as structures
@@ -38,15 +40,19 @@ from skimage import filters
 from skimage.morphology import flood_fill
 from random import shuffle
 
-VAL_SCALE_FAC = 0.3
+VAL_SCALE_FAC = 0.0
 
-def gen_metadata(file_path):
+def init_model():
     cfg = get_cfg()
     cfg.merge_from_file("config/mask_rcnn_R_50_FPN_3x.yaml")
     cfg.MODEL.ROI_HEADS.NUM_CLASSES = 5
     cfg.MODEL.WEIGHTS = os.path.join(cfg.OUTPUT_DIR, "model_final.pth")
     cfg.MODEL.ROI_HEADS.SCORE_THRESH_TEST = 0.3
     predictor = DefaultPredictor(cfg)
+    return predictor
+
+def gen_metadata(file_path):
+    predictor = init_model()
     im = cv2.imread(file_path)
     im_gray = cv2.imread(file_path, cv2.IMREAD_GRAYSCALE)
     metadata = Metadata(evaluator_type='coco', image_root='.',
@@ -65,8 +71,11 @@ def gen_metadata(file_path):
         temp = insts.pred_classes==i
         selector += temp.cumsum(axis=0).cumsum(axis=0) == 1
     fish = insts[insts.pred_classes==0]
+    #print(fish)
     if len(fish):
-        results['fish'] = [{}]
+        results['fish'] = []
+        for _ in range(len(fish)):
+            results['fish'].append({})
     else:
         fish = None
     results['has_fish'] = bool(fish)
@@ -95,7 +104,7 @@ def gen_metadata(file_path):
     os.makedirs('images', exist_ok=True)
     file_name = file_path.split('/')[-1]
     print(file_name)
-    cv2.imwrite(f'images/gen_mask_prediction_{file_name}.jpg',
+    cv2.imwrite(f'images/gen_mask_prediction_{file_name}.png',
             vis.get_image()[:, :, ::-1])
     if fish:
         try:
@@ -121,10 +130,10 @@ def gen_metadata(file_path):
             bbox = [round(x) for x in curr_fish.pred_boxes.tensor.cpu().
[…]

### 2021-03-17 validate.py

@@ -26,15 +26,26 @@ for i in results.keys():
     me = results[i]
     #print(me)
     if not 'errored' in me.keys():
-        yasin = df[df.image_name == i].iloc[0]
+        all_yasin = df[df.image_name == i]
+        all_yasin = all_yasin[~all_yasin['specimen_angled'].isnull()]
+        #all_yasin = all_yasin[not all_yasin.specimen_angled.isnull()]
+        #print(all_yasin.specimen_angled)
+        #yasin = df[df.image_name == i].iloc[0]
+        angle = np.mean(all_yasin['specimen_angled'])
+        #print(angle)
+        angle = round(angle)
         if me['has_fish']:
             if me['fish'][0]['has_eye']:
                 val = int(me['fish'][0]['clock_value'])
-                print(yasin)
-                exit(0)
-                right += val >= round(yasin.specimen_angled - 1) and\
-                        val <= round(yasin.specimen_angled + 1)
-                print(f"{i}: {me['fish'][0]['clock_value']}, {yasin.specimen_angled}")
+                #print(yasin)
+                #exit(0)
+                right += val >= (angle - 1) and\
+                        val <= (angle + 1)
+                #right += val >= round(yasin.specimen_angled - 1) and\
+                #        val <= round(yasin.specimen_angled + 1)
+                if not (val >= (angle - 1) and val <= (angle + 1)):
+                    #print(f"{i}: {me['fish'][0]['clock_value']}, {yasin.specimen_angled}")
+                    print(f"{i}: {me['fish'][0]['clock_value']}, {angle}")
             else:
                 no_eye += 1
                 print(f'{i}: No eye')

### 2021-03-17 paper/paper.tex
Renamed
Commented stuff out, made new bib file
Changed section headings. Started the bib file

--- 2021-02-18 paper/sample-acmsmall-conf.tex
@@
 \usepackage{todonotes}
-
+\usepackage{comment}
 %%
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Automated Metadata Generation for Biological Specimen Image Collections}
+\title{Automated Metadata Generation for Fish Specimen Image Collections}
 
@@
 %\orcid{1234-5678-9012}
+\author{Jane Greenberg}
 \author{David Breen}
-\author{Jane Greenberg}
+\orcid{0002-1376-5008}
 \affiliation{%
@@
 Text~\ref{demo-intro}~\todo{Liney}
-\section{Background}
+
+\section{Related Work}
 Text~\todo[noline]{Do this}
-\subsection{Related Work}
+\subsection{History of Quality Metadata}
+\subsection{Fish Image Analysis}
+
+\cite{BockAlexander2018TITE}
+\cite{KonovalovD2017RDfA}
+\cite{Williams:2020:UIF}
+
+\section{Methods}
 Text
-\section{Objectives}
-Text
-\section{Data Analysis}
+\section{Results}
 Text
 \section{Discussion}
-Text \textit{texty text}~\cite{Lamport:LaTeX}
+Text \textit{texty text}%~\cite{Lamport:LaTeX}
 \section{Conclusion}
@@
 
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{paper}
+
+\begin{comment}
 \pagebreak{}
-
 \section{Introduction}~\label{demo-intro}
@@
   \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
+  %\includegraphics[width=\linewidth]{sample-franklin}
   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
@@
 %% the bibliography file.
+
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{paper}
 
@@
 
+\end{comment}
+
 \end{document}

### 2021-03-23 paper/paper.tex
Updates from Overleaf

@@
 \section{Introduction}
-Text~\ref{demo-intro}~\todo{Liney}
+
+\ref{demo-intro}~\todo{Sentences I didn't use: Over the last few decades, cyberinfrastructure development, advances in digitization, and the open science tenor, have helped support global access to natural history.
+OR
+Global access to natural history collections has accelerated over the last few decades to advances in cyberinfrastructure, digitization, and the general open science tenor}
+
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collection.
+In the U.S., programs, such as the National Science Foundation’s initial Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for well over [nearly?] a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital transformation of data and images for millions of biological specimens.
+These resources are globally available through a wide range of portals and digital libraries for researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
+Significant challenges surface; however, when researchers seek to apply computational methods, due to both image quality and metadata.
+(As researchers seek to apply computational methods, and explore AI, significant challenges surface..)
+
+Unfortunately, potential scientific advances are hindered [by image quality] as well as [more so?] the lack of high-quality and pertinent metadata associated with the image collections.
+Many specimen collections include Darwin Core metadata, detailing specimen taxon, geographic location, and several other descriptive aspects.
+Additionally, some digitization efforts record technical metadata, detailing imaging specifications.
+While these types of metadata are helpful for a human examining several images at a time, they are insufficient for researchers seeking to apply computational methods to examine thousands of images to determine if, for instance, a dorsal fin of a specific fish has a different shape.
+Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
+Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
+
+As a step towards improving metadata in specimen research image collections, members of the Metadata Research Center, Drexel University, have been developing methods to automatically analyze fish images and extract a set of important features [metadata].
+The research is being conducted as part of Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploits machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
+Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement.
+This paper reports on our research examining a set of [add numbers] images drawn from the Illinois Natural History Survey (INHS) Collection.
+The following section of this paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods.
+Next, the results are presented, followed by a discussion.
+The conclusion highlights key findings and identifies next steps.
 
@@
 Text~\todo[noline]{Do this}
-\subsection{History of Quality Metadata}
+\subsection{Metadata for Image Collection}
+Metadata development is intertwined with the development of digital technology.
+A wide range of metadata standards are applicable to metadata supporting image description as well as technical aspects, and have been used in a range of image repositories.
+Examples of Descriptive schemes include X, y, z...
+Examples of technical schemes include...
+The use varies across communities, and application technique is primarily manual.
+Research evaluating such schemes XXX, show XXX.
+
+Natural history collections generally use a sub-set of such standards.
+Darwin Core, a globally adopted standard overseen by the Taxonomic Data Working Group (TDWG).
+[Jane continue here on some of this, and then with preservation/image quality less]
+
+\subsection{Metadata genberation?}
+
 \subsection{Fish Image Analysis}

### 2021-03-24 gen_metadata.py
Tweaks to script

@@ -130,7 +130,7 @@ def gen_metadata(file_path):
             bbox = [round(x) for x in curr_fish.pred_boxes.tensor.cpu().
                       numpy().astype('float64')[0]]
             im_crop = im_gray[bbox[1]:bbox[3],bbox[0]:bbox[2]]
-            detectron_mask = curr_fish.pred_masks[0].cpu().numpy()
+            detectron_mask = curr_fish.pred_masks[i].cpu().numpy()
             val = adaptive_threshold(bbox, im_gray)
             bbox, mask = gen_mask(bbox, file_path, file_name, im_gray, val,
                     detectron_mask, index=i)
@@ -277,7 +277,7 @@ def clock_value(evec, file_name):
             start = 3
         else:
             comp = np.array([0,1])
-            start = 0
+            start = 6
     ang = angle(comp, evec)
     #print(ang)
     clock = start + (ang / (2 * math.pi) * 12)
@@ -483,10 +483,18 @@ def shrink_bbox(mask):
 
     return (cmin, rmin, cmax, rmax)
 
+def gen_metadata_safe(file_path):
+    try:
+        return gen_metadata(file_path)
+    except Exception as e:
+        print(f'{file_path}: Errored out ({e})')
+        return {file_path: {'errored': True}}
+
+
 def main():
     direct = sys.argv[1]
     if os.path.isdir(direct):
-        files = [entry.path for entry in os.scandir(direct)][:1000]
+        files = [entry.path for entry in os.scandir(direct)]
     else:
         files = [direct]
     #print(files)
@@ -494,7 +502,7 @@ def main():
     #f = partial(gen_metadata, predictor)
     with Pool(4) as p:
         #results = map(gen_metadata, files)
-        results = p.map(gen_metadata, files)
+        results = p.map(gen_metadata_safe, files)
     #results = map(gen_metadata, files)
     output = {}
     for i in results:

### 2021-03-24 validate.py

@@ -21,6 +21,7 @@ right = 0
 no_eye = 0
 no_fish = 0
 errored = 0
+wrong_wrong = 0
 for i in results.keys():
     counter += 1
     me = results[i]
@@ -39,8 +40,10 @@ for i in results.keys():
                 val = int(me['fish'][0]['clock_value'])
                 #print(yasin)
                 #exit(0)
-                right += val >= (angle - 1) and\
+                check = val >= (angle - 1) and\
                         val <= (angle + 1)
+                right += check
+                wrong_wrong += 1 if not check else 0
                 #right += val >= round(yasin.specimen_angled - 1) and\
                 #        val <= round(yasin.specimen_angled + 1)
                 if not (val >= (angle - 1) and val <= (angle + 1)):
@@ -60,6 +63,7 @@ print(f'\nRight: {right}')
 print(f'Errored: {errored}')
 print(f'No eye: {no_eye}')
 print(f'No fish: {no_fish}')
+print(f'Wrong wrong: {wrong_wrong}')
 print(f'Total: {counter}')
 print(f'Percent right: {right / counter}')
 print(f'Percent right that didn\'t error: {right / (counter - no_eye - no_fish - errored)}')

### 2021-03-24 paper/paper.tex
Updates from Overleaf
First draft Pixel Analysis section

@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Pepper, Breen and Greenberg}
+\renewcommand{\shortauthors}{Pepper, Greenberg and Breen}
 
@@
 
-\subsection{Metadata genberation?}
+\subsection{Metadata generation?}
 
@@
 \section{Methods}
-Text
+
+\subsection{Detectron}
+\subsection{Pixel Analysis}
+The masks and bounding boxes produced by \verb|detectron| are generally quite good, although they are almost never perfect.
+They almost always either include additional background as part of the fish, or clip part(s) of the fish outside the bounding box.
+To solve this shortcoming, we utilize pixel analysis methods commonly found in image informatics.
+
+The first calculation in the pixel analysis process is determining the cutoff intensity between what constitutes the foreground (i.e.\ the fish) and background of the image.
+Initially, we base this off the bounding box and mask generated by \verb|detectron|.
+Specimen images are read in as gray scale, and pixels in the image are treated as unsigned integers between 0 and 255.
+Otsu thresholding is used to get an initial cutoff value between foreground and background.
+\todo{Put in another sentence or two about Otsu} While this value occasionally generates an accurate mask as is, most of the time the contrast between foreground and background is not great enough and much of the lighter parts of the fish (such as its tail fin) are marked as background.
+
+To overcome this, the threshold value needs either scaled up or down depending on if the background is lighter or darker than the fish.
+For our current dataset, the background is always lighter (i.e.\ closer to 255), so the threshold value needs scaled up to include more of the image as foreground.
+Precisely how much to scale this value by is difficult to determine.
+For optimal results it is dependent on the level of contrast between the background and foreground, which can be affected by both how washed out the image is and how light or dark the pigmentation of the fish is.
+To take this into account, we measure the mean intensity of the foreground and background, then use these intensity values and the difference between them to scale the threshold value.
+Even with these values in hand it is not entirely clear how to scale the threshold, but we have found\ldots{}\todo{This is still somewhat indeterminate, need to pick a definitive technique, I've tried a few}
+
+While thresholding has the potential to generate better masks than a neural network (when provided an initial approximate bounding box), it also introduces considerable noise.
+Single or small groups of errant pixels can be marked as foreground depending on the consistency of the background, and interior pixels of the fish (especially around the fins) can be marked as background.
+To be useful for generating an accurate bounding box and for subsequent computational analysis, the mask must consist of one single ``blob'' over the fish the contains no holes, and no other pixels disconnected from this blob can be marked as foreground.
+
+To accomplish this, we apply an iterative process of flood filling from all the foreground pixels in the image until a blob is generated that is large enough to constitute the fish.
+This is another metaparameter, but greater than 10\% of the current bounding box has masked the specimen in all observed cases.
+Once the fish's blob is found, noise then needs removed.
+This is done by flood filling from each of the corner of the bounding box where the specimen is not present (all four corners in the overwhelming majority of cases), then taking the inverse of the result.
+The fish mask is excluded from these corner flood fills, so this process removes all noise from both the background and foreground of the image leaving only a close mask over the fish itself.
+
+With an accurate mask generated, it is then necessary to check whether the bounding box needs expanded or shrunk along any edges.
+Expansion is done first, buy checking whether any edge intersects with any of the foreground mask pixels.
+If one does, it is expanded out by 1 pixel.
+If any edges are expanded, the whole the process, masking and expansion process is repeated to account for any changes in average intensities.
+Once no edges contain foreground pixels, the mask is the shrunk.
+This process is more efficient as all that is required is to shrink each edge by one up until the point they contain one or more foreground pixels.
+Once the shrinkage step is accomplished, the final mask and bounding box have been generated.
+\subsection{Metadata Generation}
 \section{Results}

### 2021-03-24 paper/paper.tex
Properties table

@@
 %\documentclass[acmsmall,screen,review]{acmart}
-\documentclass[acmconf,screen,review]{acmart}
+%\documentclass[acmconf,screen,review]{acmart}
+\documentclass[screen,review]{acmart}
 \usepackage{todonotes}
 \usepackage{comment}
+%\usepackage{booktabs}
 %%
@@
 
-\ref{demo-intro}~\todo{Sentences I didn't use: Over the last few decades, cyberinfrastructure development, advances in digitization, and the open science tenor, have helped support global access to natural history.
-OR
+\todo{Sentences I didn't use: Over the last few decades, cyberinfrastructure development, advances in digitization, and the open science tenor, have helped support global access to natural history. OR
 Global access to natural history collections has accelerated over the last few decades to advances in cyberinfrastructure, digitization, and the general open science tenor}
@@
 \subsection{Metadata Generation}
+Including what has already been discussed, the following metadata properties are being currently being generated:
+\begin{table}[H]
+    \centering
+    \caption{Metadata properties}
+    \label{tab:properties}
+    \begin{tabular}{cccp{0.5\linewidth}}
+        \toprule
+        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
+        \midrule
+        \verb|has_fish| & Overall & Boolean & Whether a fish was found in the image.\\
+        \verb|fish_count| & Overall & Integer & The quantity of fish present.\\
+        \verb|has_ruler| & Overall & Boolean & Whether a ruler was found in the image.\\
+        \verb|ruler_bbox| & Overall & 4 Tuple & The bounding box of the ruler (if found).\\
+        \verb|scale| & Overall & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
+        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
+        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
+        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
+        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of what define the bounding box for a fish.\\
+        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
+        \verb|primary_axis| & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
+        \verb|clock_value| & Per Fish & Integer & A fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
+        \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish an 0's and 1's.\\
+        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
+        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
+        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
+        \verb|side| & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
+      \bottomrule
+\end{tabular}
+\end{table}
+\subsection{Consideration}
+Just gonna throw some caveats in here, might be its own section might not
+\begin{itemize}
+    \item Program falls back to using detectron mask and bbox for metadata generation in the event the mask generation/pixel analysis fails.
+Failure is defined as never finding a cohesive flood filled mask that covers more than 10\% of the detectron bbox initially.
+Can provide a statistic on how often this occurs.
+\end{itemize}
 \section{Results}

### 2021-03-24 gen_metadata.py

@@ -377,17 +377,11 @@ def gen_mask(bbox, file_path, file_name, im_gray, val, detectron_mask,
     done = False
     im_crop = im_gray[t:b,l:r]
     while not done:
-        #print(f'val: {val}')
         done = True
         arr0 = np.array(im.crop(bbox))
         bb_size = arr0.size
 
-
-        #if val is None:
-        #print(val)
         val = filters.threshold_otsu(arr0)
-        #print(val)
-        #arr1 = np.where(check(arr0, val, flipped), 1, 0).astype(np.uint8)
         arr1 = np.where(arr0 < val, 1, 0).astype(np.uint8)
         indicies = list(zip(*np.where(arr1 == 1)))
         shuffle(indicies)
@@ -406,13 +400,7 @@ def gen_mask(bbox, file_path, file_name, im_gray, val, detectron_mask,
                         temp = flood_fill(temp, (i, j), 2)
                 arr1 = np.where(temp != 2, 1, 0).astype(np.uint8)
                 break
-        #print(np.count_nonzero(arr1))
         arr3 = np.full(shape, 0).astype(np.uint8)
-        #print(arr1.shape)
-        #print(shape)
-        #print(f'{t}:{b},{l}:{r}')
-        #print(np.count_nonzero(arr1))
-        #print('=====')
         arr3[t:b,l:r] = arr1
         #im_crop = im_gray[t:b,l:r]
         #fground = im_crop.reshape(-1)[arr1.reshape(-1)]
@@ -450,7 +438,6 @@ def gen_mask(bbox, file_path, file_name, im_gray, val, detectron_mask,
             done = True
         bbox = (l,t,r,b)
         #val = adaptive_threshold(bbox, im_gray)
-    #print(list(arr1.reshape(-1)))
     if np.count_nonzero(arr1) / bb_size < .1:
         print(f'{file_name}: Using detectron mask and bbox')
         arr3 = detectron_mask.astype('uint8')

### 2021-03-24 paper/paper.tex
Metadata gen methods section drafted

@@
 \usepackage{comment}
-%\usepackage{booktabs}
 %%
@@
 \acmYear{2021}
-\acmDOI{???}
+\acmDOI{}
 
@@
 \acmConference[JCDL '21]{JCDL '21: Joint Conference on
-  Digital Libraries}{September 27--30, 2021}{????, USA}
+  Digital Libraries}{September 27--30, 2021}{Urbana--Champaign, Illinois, USA}
 %\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
@@
 Including what has already been discussed, the following metadata properties are being currently being generated:
+
 \begin{table}[H]
@@
         \midrule
-        \verb|has_fish| & Overall & Boolean & Whether a fish was found in the image.\\
-        \verb|fish_count| & Overall & Integer & The quantity of fish present.\\
-        \verb|has_ruler| & Overall & Boolean & Whether a ruler was found in the image.\\
-        \verb|ruler_bbox| & Overall & 4 Tuple & The bounding box of the ruler (if found).\\
-        \verb|scale| & Overall & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
+        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
+        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
+        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
+        \verb|scale| & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of what define the bounding box for a fish.\\
         \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
@@
         \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
-        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of what define the bounding box for a fish.\\
         \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
@@
         \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
-        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish an 0's and 1's.\\
+        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
         \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
@@
 \end{table}
+
+\verb|has_fish|, \verb|fish_count|, \verb|has_ruler|, \verb|ruler_bbox|, \verb|background.*|, \verb|foreground.*|, \verb|bbox|, \verb|mask|, \verb|score|, and \verb|has_eye| have already been discussed.
+The remaining properties are determined as follows:
+\subsubsection{centroid and eye\_center}
+Centroids are provided for masks/bounding boxes generated by \verb|detectron|, and since we do not recalculate the mask of fish eyes we can use that value directly for \verb|eye_center|.
+
+Since we recalculate the mask of the fish, we must recalculate its centroid as well. This can be done via
+\begin{equation}
+    (\bar{x}, \bar{y}) = (\mathrm{round}(\frac{M_{10}}{M_{00}}), \mathrm{round}(\frac{M_{01}}{M_{00}}))
+\end{equation}
+where \(M_{00}\) is the pixel area of the fish's blob, \(M_{10}\) is the sum of all the \(x\) values of blob pixels, and \(M_{01}\) is the sum of all the \(y\) values of blob pixels.
+\subsubsection{side}
+Determining which \verb|side| of the fish is visible is predicated on finding its eye.
+If an eye is found, the sign of the \(x\) component of the vector from the centroid of the fish to the centroid of the eye specifies which side is up: negative for left and positive for right.
+This assumes the fish was photographed vertically, which is essentially always the case for all image collections our group has worked on.
+\subsubsection{primary\_axis and clock\_value}
+The \verb|primary_axis| of a fish can be calculated by taking the covariance\todo{I could explain this in more detail if necessary} of its blob in \(x\) and \(y\), which yields its principle eigenvector.
+This can be directly assigned to the property.
+If an eye is present, we specify this axis in the direction of the eye in relation to the fish's centroid.
+
+Our team encoded this information as a ``clock value'' between 1 and 12 when recording it by hand.
+To convert \verb|principal_axis| to \verb|clock|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish is angles into relative to its centroid.
+Depending on this quadrant, we then dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\) which correspond to 9, 6, 3 and ``0'' o'clock respectively.
+The resulting radian value is then converted to a polar displacement in clock value space, and added to the comparative clock value used in the dot product.
+This then gives the fish's clock value from 0 to \(11.\overline{9}\).
+Before recording as \verb|clock| in the output, the value is rounded to the nearest integer, and in the event of a 0 final result it is replaced with 12.
+\subsubsection{scale and length}
+\(\frac{\mathrm{pixels}}{\mathrm{inch}}\) can be calculated by measuring the distance between the digits 2 and 3 found on the ruler by \verb|detectron|.
+Converting this to \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) gives the \verb|scale| metadata property as reported in the output.
+
+For the fish \verb|length| property, it is necessary to determine the furthest points from the centroid of the fish in each direction.
+Since fish are normally measured in a straight line from their snout down the middle of their trunk, we project every pixel onto the major axis of the fish (as a line through its centroid) before checking the distance.
+This projection is done by intersecting the line through the point along the tangent of the principal axis and the aforementioned centroid--principal axis line.
+After checking every pixel, measuring the distance between the two furthest projected points gives the length of the fish in pixels.
+Multiplying this by \verb|scale| gives the fish \verb|length| in centimeters.
 \subsection{Consideration}

### 2021-03-24 gen_metadata.py

@@ -277,7 +277,7 @@ def clock_value(evec, file_name):
             start = 3
         else:
             comp = np.array([0,1])
-            start = 6
+            start = 0
     ang = angle(comp, evec)
     #print(ang)
     clock = start + (ang / (2 * math.pi) * 12)

### 2021-03-25 paper/paper.tex
Wrote something in every section of methods

@@
 Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
-Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
+Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.~\cite{Leipzig2021.01.28.428644}\todo{Throwing in Jeremy's paper somewhere}
 
@@
 \section{Methods}
+Our process for metadata generation can be broken into 3 steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image informatics analysis at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.
 
 \subsection{Detectron}
+A prerequisite task to addressing any more advanced metadata property determination is finding specimens (and other relevant objects) within collection images.
+Object detection has been an incredibly active field of study in recent years,~\cite{zou2019object} and has resulted in a number of well tested purpose built architectures.
+We elected to use Facebook AI Research's \verb|detectron| tool~\cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture~\cite{he2018mask}, for object detection in our project.
+
+\verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format dataset.
+It is able to handle an arbitrary number of object classes, and can classify an arbitrary number of object within a given sample.
+For our project, we are currently using it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers.
 \subsection{Pixel Analysis}

### 2021-03-25 paper/paper.tex
Attempts at improving efficiency and adaptive threshold

@@
 Our team encoded this information as a ``clock value'' between 1 and 12 when recording it by hand.
-To convert \verb|principal_axis| to \verb|clock|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish is angles into relative to its centroid.
+To convert \verb|principal_axis| to \verb|clock_value|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish is angles into relative to its centroid.
 Depending on this quadrant, we then dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\) which correspond to 9, 6, 3 and ``0'' o'clock respectively.
@@
 This then gives the fish's clock value from 0 to \(11.\overline{9}\).
-Before recording as \verb|clock| in the output, the value is rounded to the nearest integer, and in the event of a 0 final result it is replaced with 12.
+Before recording as \verb|clock_value| in the output, the value is rounded to the nearest integer, and in the event of a 0 final result it is replaced with 12.
 \subsubsection{scale and length}

### 2021-03-25 gen_metadata.py

@@ -2,7 +2,7 @@ import math
 import json
 import sys
 import os
-from multiprocessing import Pool
+from torch.multiprocessing import Pool
 import pandas as pd
 import numpy as np
 import nrrd
@@ -40,7 +40,7 @@ from skimage import filters
 from skimage.morphology import flood_fill
 from random import shuffle
 
-VAL_SCALE_FAC = 0.0
+VAL_SCALE_FAC = 0.3
 
 def init_model():
     cfg = get_cfg()
@@ -130,7 +130,7 @@ def gen_metadata(file_path):
             bbox = [round(x) for x in curr_fish.pred_boxes.tensor.cpu().
                       numpy().astype('float64')[0]]
             im_crop = im_gray[bbox[1]:bbox[3],bbox[0]:bbox[2]]
-            detectron_mask = curr_fish.pred_masks[i].cpu().numpy()
+            detectron_mask = curr_fish.pred_masks[0].cpu().numpy()
             val = adaptive_threshold(bbox, im_gray)
             bbox, mask = gen_mask(bbox, file_path, file_name, im_gray, val,
                     detectron_mask, index=i)
@@ -201,19 +201,19 @@ def adaptive_threshold(bbox, im_gray):
     #bbox_d = [round(x) for x in curr_fish.pred_boxes.tensor.cpu().
             #numpy().astype('float64')[0]]
     im_crop = im_gray[bbox[1]:bbox[3],bbox[0]:bbox[2]]
-    val = filters.threshold_otsu(im_crop) * 1.13
+    val = filters.threshold_otsu(im_crop)
     mask = np.where(im_crop > val, 1, 0).astype(np.uint8)
     #f_bbox_crop = curr_fish.pred_masks[0].cpu().numpy()\
             #[bbox_d[1]:bbox_d[3],bbox_d[0]:bbox_d[2]]
     flat_mask = mask.reshape(-1)
-    fground = im_crop.reshape(-1)[np.where(flat_mask)]
+    #fground = im_crop.reshape(-1)[np.where(flat_mask)]
     bground = im_crop.reshape(-1)[np.where(np.logical_not(flat_mask))]
     mean_b = np.mean(bground)
-    mean_f = np.mean(fground)
+    #mean_f = np.mean(fground)
     #print(f'b: {mean_b} | f: {mean_f}')
     #flipped = mean_b < mean_f
     flipped = False
-    diff = abs(mean_b - mean_f)
[…]

### 2021-03-25 gen_metadata.py
Hopefully final fine tunning on gen_metadata.py before publish

@@ -40,7 +40,7 @@ from skimage import filters
 from skimage.morphology import flood_fill
 from random import shuffle
 
-VAL_SCALE_FAC = 0.3
+VAL_SCALE_FAC = 0.5
 
 def init_model():
     cfg = get_cfg()
@@ -132,8 +132,8 @@ def gen_metadata(file_path):
             im_crop = im_gray[bbox[1]:bbox[3],bbox[0]:bbox[2]]
             detectron_mask = curr_fish.pred_masks[0].cpu().numpy()
             val = adaptive_threshold(bbox, im_gray)
-            bbox, mask = gen_mask(bbox, file_path, file_name, im_gray, val,
-                    detectron_mask, index=i)
+            bbox, mask, pixel_anal_failed = gen_mask(bbox, file_path,
+                    file_name, im_gray, val, detectron_mask, index=i)
             #except:
                 #return {file_name: {'errored': True}}
             if not np.count_nonzero(mask):
@@ -157,7 +157,8 @@ def gen_metadata(file_path):
                 results['fish'][i]['background']['mean'] = np.mean(bground)
                 results['fish'][i]['background']['std'] = np.std(bground)
                 results['fish'][i]['bbox'] = list(bbox)
-                results['fish'][i]['mask'] = mask.astype('uint8').tolist()
+                results['fish'][i]['pixel_analysis_failed'] = pixel_anal_failed
+                #results['fish'][i]['mask'] = mask.astype('uint8').tolist()
                 results['fish'][i]['mask'] = '[...]'
 
                 centroid, evec = pca(mask)
@@ -183,7 +184,8 @@ def gen_metadata(file_path):
                         results['fish'][i]['side'] = 'right'
                     x_mid = int(bbox[0] + (bbox[2] - bbox[0]) / 2)
                     y_mid = int(bbox[1] + (bbox[3] - bbox[1]) / 2)
-                    snout_vec = find_snout_vec(np.array([x_mid, y_mid]), eye_center, mask)
+                    #snout_vec = find_snout_vec(np.array([x_mid, y_mid]), eye_center, mask)
+                    snout_vec = evec
                     if snout_vec is None:
                         results['fish'][i]['clock_value'] =\
                                 clock_value(evec,file_name)
@@ -263,23 +265,24 @@ def angle(vec1, vec2):
     return math.acos(vec1.dot(vec2) / (np.linalg.norm(vec1) * np.linalg.norm(vec2)))
 
[…]

### 2021-03-25 paper/paper.tex
Hopefully final fine tunning on gen_metadata.py before publish
Put results in as plain text

@@
 \acmConference[JCDL '21]{JCDL '21: Joint Conference on
-  Digital Libraries}{September 27--30, 2021}{Urbana--Champaign, Illinois, USA}
+  Digital Libraries, September 27--30, 2021, Urbana--Champaign, Illinois, USA}
 %\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
@@
 \email{jcp353@drexel.edu}
-%\orcid{1234-5678-9012}
+\orcid{0002-1601-8729}
 \author{Jane Greenberg}
@@
 For our project, we are currently using it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers.
+
+Placeholder\todo{A paragraph about training will go here}
 \subsection{Pixel Analysis}
@@
 \section{Results}
-Text
+\begin{verbatim}
+What I think should be the final results:
+
+Right: 6956
+Errored: 0
+No eye: 246
+No fish: 10
+Wrong wrong: 35
+Total: 7247
+Percent right: 0.959845453291017
+Percent right that didn't error: 0.9949935631526248
+
+-----------------------
+
+My hand checking of the ''wrong wrong'' fish:
+
+INHS_FISH_101109.jpg: 9, 11, I'm wrong although it's fairly curved
+INHS_FISH_56818.jpg: 4, 2, I'm wrong although there's a tag that is likely messing things up
+INHS_FISH_57607.jpg: 3, 9, I'm wrong
+INHS_FISH_57001.jpg: 4, 2, I'm wrong although there's a tag that is likely messing things up
+INHS_FISH_63953.jpg: 3, 9, I'm wrong
+INHS_FISH_51100.jpg: 3, 9, I'm wrong
+INHS_FISH_80528.jpg: 3, 8, I'm wrong
+INHS_FISH_6370.jpg: 3, 9, I'm wrong
+INHS_FISH_54157.jpg: 9, 7, I'm arguably wrong although it's very curved
+INHS_FISH_80987.jpg: 9, 3, I'm wrong although this one is a fairly atypical image
+
+INHS_FISH_58647.jpg: 9, 7, I'm right
+INHS_FISH_8415.jpg: 9, 6, I'm right
+INHS_FISH_5041.jpg: 9, 11, very curved averages to about 9
+INHS_FISH_52821.jpg: 9, 7, I'm arguably right although the fish is damaged and its head points to ~7
+INHS_FISH_6696.jpg: 9, 7, I'm right
+INHS_FISH_75252.jpg: 9, 6, I'm right
+INHS_FISH_79498.jpg: 9, 6, I'm right
+INHS_FISH_45744.jpg: 9, 5, I'm right
+INHS_FISH_47579.jpg: 9, 6, I'm right
+INHS_FISH_64599.jpg: 9, 6, I'm right
+INHS_FISH_74550.jpg: 9, 5, I'm right
+INHS_FISH_101664.jpg: 9, 6, I'm right
+INHS_FISH_100861.jpg: 9, 6, I'm right
+INHS_FISH_60589.jpg: 3, 9, I'm right
+INHS_FISH_53469.jpg: 9, 1, I'm right
+INHS_FISH_44694.jpg: 9, 6, I'm right
+INHS_FISH_54921.jpg: 9, 6, I'm right
+INHS_FISH_44645.jpg: 10, 8, I'm right
+INHS_FISH_50459.jpg: 9, 11, I'm right although the fish is damaged and its head points to ~11
+INHS_FISH_68061.jpg: 9, 6, I'm right
+INHS_FISH_74716.jpg: 9, 6, I'm right
+INHS_FISH_80976.jpg: 9, 6, I'm right
+INHS_FISH_57977.jpg: 9, 6, I'm right
+INHS_FISH_45377.jpg: 9, 6, I'm right
+INHS_FISH_47142.jpg: 9, 6, I'm right
+
+Verdict: For only 10 of the 35 am I actually wrong and all of those are either curved, atypical
+images with tags, or something on the wrong side was detected as an eye (so the clock value is backwards).
+
+\end{verbatim}
 \section{Discussion}

### 2021-03-25 paper/paper.tex
Added more data and small tweaks

@@
 
-Placeholder\todo{A paragraph about training will go here}
+\begin{verbatim}
+|  category  | #instances   |  category  | #instances   |  category  | #instances   |
+|:----------:|:-------------|:----------:|:-------------|:----------:|:-------------|
+|    fish    | 297          |   ruler    | 1496         |    eye     | 456          |
+|    two     | 100          |   three    | 100          |            |              |
+|   total    | 2449         |            |              |            |              |
+
+Iterations: 100,000
+
+Initial: {"data_time": 0.004866079999999329, "fast_rcnn/cls_accuracy": 0.115234375,
+"fast_rcnn/false_negative": 0.1686291000841043,
+"fast_rcnn/fg_cls_accuracy": 0.2782012195121951, "iteration": 5, "loss_box_reg": 0.40475407242774963,
+"loss_cls": 1.8559419512748718, "loss_mask": 0.6982034742832184, "loss_rpn_cls": 0.05218731239438057,
+"loss_rpn_loc": 0.007734265644103289, "lr": 0.00011990000000000001, "mask_rcnn/accuracy": 0.2920252418802887,
+"mask_rcnn/false_negative": 0.9506743610216735, "mask_rcnn/false_positive": 0.2467277275646746,
+"roi_head/num_bg_samples": 115.0, "roi_head/num_fg_samples": 13.0, "rpn/num_neg_anchors": 251.25,
+"rpn/num_pos_anchors": 4.75, "time": 0.2812129614999961, "total_loss": 2.9480794025585055}
+
+Final: {"data_time": 0.006645713496254757, "eta_seconds": 0.0, "fast_rcnn/cls_accuracy": 0.984375,
+"fast_rcnn/false_negative": 0.0, "fast_rcnn/fg_cls_accuracy": 1.0, "iteration": 99999,
+"loss_box_reg": 0.054501257836818695, "loss_cls": 0.03908616118133068, "loss_mask": 0.06379510834813118,
+"loss_rpn_cls": 0.0010549294238444418, "loss_rpn_loc": 0.005114196799695492, "lr": 0.02,
+"mask_rcnn/accuracy": 0.9722937165937804, "mask_rcnn/false_negative": 0.012800597698663846,
+"mask_rcnn/false_positive": 0.05609636495338312, "roi_head/num_bg_samples": 115.75,
+"roi_head/num_fg_samples": 12.25, "rpn/num_neg_anchors": 246.5, "rpn/num_pos_anchors": 9.5,
+"time": 0.3563086399990425, "total_loss": 0.15775199318886735}
+\end{verbatim}\todo{Training details, will turn this into a paragraph on how model is created}
 \subsection{Pixel Analysis}
@@
 To take this into account, we measure the mean intensity of the foreground and background, then use these intensity values and the difference between them to scale the threshold value.
-Even with these values in hand it is not entirely clear how to scale the threshold, but we have found\ldots{}\todo{This is still somewhat indeterminate, need to pick a definitive technique, I've tried a few}
+Even with these values in hand it is not entirely clear how to scale the threshold.
+We scaled the threshold value by 50\% of the difference between the mean of the background and the original threshold value, which captures most of fish's fins in most cases without also masking parts of the background.
 
@@
         \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
+        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish.
+If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
         \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
@@
 
+Pixel analysis failed: 0.036336004421110804
+
+-----------------------
+
 My hand checking of the ''wrong wrong'' fish:
-
+               My guess, Yasin spreadsheet
 INHS_FISH_101109.jpg: 9, 11, I'm wrong although it's fairly curved

### 2021-03-25 paper/paper.tex
Updates from Overleaf
Wrote training paragraph and table

@@
 \subsection{Metadata for Image Collection}
+\todo{Wasn't looking for a citation but stumbled upon this paper: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0207636}, might be worth a skim}
 Metadata development is intertwined with the development of digital technology.
@@
 
+\section{Goal and Objectives}
+
 \section{Methods}
@@
 
+Our training dataset consisted of the following number of instances for each class:
+
+\begin{table}[H]
+    \centering
+    \caption{Training dataset}
+    \label{tab:dataset}
+    \begin{tabular}{cc}
+        \toprule
+        \textbf{Class} & \textbf{Number of Instances}\\
+        \midrule
+        Fish & 297\\
+        Ruler & 1496\\
+        Eye & 456\\
+        Two & 100\\
+        Three & 100\\
+      \bottomrule
+\end{tabular}
+\end{table}
+
+All of the training data was labeled by hand using \verb|makesense.ai|.~\cite{make-sense} While the ultimate goal of the project is to generalize to images from a variety of specimen collections, we have thus far focused only on images from the INHS\ Fish Collection.~\cite{INHS} Using \verb|detectron|'s default training scheme, the model was trained for \(100,000\) epochs.
+All instance types were included in a single object detection model.
+The total loss\todo{Find and specify which loss function was used} began at \(2.948\) and ended at \(0.158\) for the training data.
+
+\begin{comment}
 \begin{verbatim}
@@
 "time": 0.3563086399990425, "total_loss": 0.15775199318886735}
-\end{verbatim}\todo{Training details, will turn this into a paragraph on how model is created}
+\end{verbatim}
+\end{comment}
 \subsection{Pixel Analysis}
@@
 \end{verbatim}
+
+\todo{Randomly verify a sampling of length values}
+
 \section{Discussion}
 Text \textit{texty text}%~\cite{Lamport:LaTeX}
+\subsection{Future Work}
 \section{Conclusion}

### 2021-03-26 paper/paper.tex
Updates from Overleaf

@@
 \author{Jane Greenberg}
+\orcid{0001-7819-5360}
+\affiliation{%
+  \institution{Drexel University}
+  \streetaddress{3675 Market St}
+  \city{Philadelphia}
+  \state{Pennsylvania}
+  \country{USA}
+  \postcode{19104}
+}
+\author{Yasin Bakis}
+\orcid{0001-6144-9440}
+\author{Henry Bart Jr.}
+\orcid{0002-5662-9444}
+\affiliation{
+  \institution{Tulane University}
+  \city{New Orleans}
+  \state{Louisiana}
+  \country{USA}
+}
 \author{David Breen}
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Pepper, Greenberg and Breen}
+\renewcommand{\shortauthors}{Pepper, Greenberg, Bakis, Bart and Breen}
 
@@
 \subsection{Future Work}
+\begin{itemize}
+    \item Further fine tuning of pixel analysis (e.g.\ thresholding on different regions of the bbox)
+    \item Generalizing ruler reading
+    \item Training on a progressively larger number of image collections to hopefully gain reasonable generality for the whole class of fish specimen images
+    \item Adding things like seahorses and eels
+    \item Fitting a ``spine'' to specimen
+\end{itemize}
 \section{Conclusion}

### 2021-03-26 paper/paper.tex
Started results section

@@
 \begin{abstract}
-  A clear\todo{test} and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down} Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+One area of considerable activity is the digitization of the biological specimens that have been collected worldwide by museums and other research institutions.
+The scanning of these specimen collections and the placement of the resulting images into easily accessible repositories on the Internet is enabling new scientific studies based on the previously unavailable data.
+Unfortunately, potential scientific advances are hindered by the lack of high-quality and pertinent metadata associated with the image collections.
+Metadata is required to search the repositories for the imaged specimens needed for a particular study.
+Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
+Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
+
+As a step towards improving metadata in specimen research image collections, our team has been developing methods for automatically analyzing fish images to extract a variety of important features.
+These fish specimens are being studied for a larger project titled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in the form of specimen images, phylogenies and anatomy ontologies.
+Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.
+
+Metadata is often unavailable, sparse or incorrect within specimen image repositories, but is vital for subsequent machine learning, analysis and scientific discovery.
+Our goal is to develop image metadata generation methods that both support the novel machine learning research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
+A longer term goal is to extend the image analysis methods for computing specific quantitative features in support of specific biological investigations.
+For example, we are able to automatically measure the length of a fish specimen.
+Associating these measurements with location and acquisition date may provide insights into the influence of habitat factors on fish development/health.
+Since it is prohibitively expensive for scientists to manually gather this data, we are also interested in applying our tools to images of other species stored in a variety of repositories (e.g.
+iDigBio).
+The technical challenges in achieving a broader usage of our approach mostly involve training new classifiers for different types of species, learning to segment and read annotation tags, and generalizing our classifier to find and interpret different types of rulers.
+This presentation will report on our current efforts to automatically generate metadata for fish specimen images and offer thoughts on how to extend these techniques for other specimen image collections.
 \end{abstract}
@@
 \section{Related Work}
-Text~\todo[noline]{Do this}
+\textbf{Todo}
 \subsection{Metadata for Image Collection}
@@
 \section{Methods}
-Our process for metadata generation can be broken into 3 steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image informatics analysis at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.
+Our process for metadata generation can be broken into 3 steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image informatics analysis at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.\todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images.
+Not sure where I want to put it yet so just leaving it as a todo}
 
@@
 \section{Results}
+Technicians employed by our team have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{Leipzig2021.01.28.428644} for a large number of INHS images.
+\(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images.
+Of these \(8,398\) images, \(7,247\) were both not part of the \verb|detectron| training set and meet our current admissibility criteria for what \verb|detectron| and the pixel analysis process can reliably handle.
+We ran the metadata extraction program on these \(7,247\) images.
+
+Our automated process currently generates 7 of the 22 core metadata properties: \verb|if_fish| (\verb|has_fish|), \verb|fish_number| (\verb|fish_count|), \verb|if_ruler| (\verb|has_ruler|), \verb|specimen_angled| (\verb|clock_value|), \verb|specimen_view| (\verb|side|), \verb|brightness| (derived from \verb|background.mean| and \verb|foreground.mean|), and \verb|if_background_uniform| (\verb|background.std|).
+In addition, our process also calculates bounding boxes and fish lengths in centimeters.\todo{Talk more about what we can and can't verify and how}
+
+All images in the INHS dataset contain exactly one fish. \textbf{Todo}: if\_fish and fish\_count results
+
+\textbf{Todo}: Ruler results
+
+\textbf{Todo}: Side results
+
+\textbf{Todo}: Clock value results
+
+\textbf{Todo}: Brightness/uniformity results? I can try to do this but I need to set up the infrastructure, we probably need to discuss a plan of action for this.
+
+\textbf{Todo}: Bounding box results
+
+\textbf{Todo}: Scale results
+\begin{comment}
 \begin{verbatim}
@@
 \end{verbatim}
-
-\todo{Randomly verify a sampling of length values}
+\end{comment}
 
 \section{Discussion}
-Text \textit{texty text}%~\cite{Lamport:LaTeX}
+\textbf{Todo}
 \subsection{Future Work}
@@
 \section{Conclusion}
-Text \textbf{text}
+\textbf{Todo}
 

### 2021-03-26 paper/paper.tex
Probably done for the night

@@
 }
-\author{Yasin Bakis}
+\author{Yasin Baki\c{s}}
 \orcid{0001-6144-9440}
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Pepper, Greenberg, Bakis, Bart and Breen}
+\renewcommand{\shortauthors}{Pepper, Greenberg, Baki\c{s}, Bart and Breen}
 
@@
 \begin{abstract}
-    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down} Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down.
+Also, we need to decide what to do for the ``teaser image''.} Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
 One area of considerable activity is the digitization of the biological specimens that have been collected worldwide by museums and other research institutions.
@@
 The technical challenges in achieving a broader usage of our approach mostly involve training new classifiers for different types of species, learning to segment and read annotation tags, and generalizing our classifier to find and interpret different types of rulers.
-This presentation will report on our current efforts to automatically generate metadata for fish specimen images and offer thoughts on how to extend these techniques for other specimen image collections.
+This presentation will report on our current efforts to automatically generate metadata for fish specimen images and offer thoughts on how to extend these techniques for other specimen image collections.\todo{Need to figure out what to actually do for this CCS stuff (\url{http://dl.acm.org/ccs.cfm}) and also the key words}
 \end{abstract}
@@
 Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
-Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.~\cite{Leipzig2021.01.28.428644}\todo{Throwing in Jeremy's paper somewhere}
+Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
 
@@
 Once the shrinkage step is accomplished, the final mask and bounding box have been generated.
+
+\subsubsection{Fallback} The pixel analysis process occasionally fails.
+This can occur if certain flood fill operations behave unexpectedly, or if the image is too washed out or otherwise atypical for the thresholding process to work correctly.
+In the event this happens, the original mask and bounding box generated by \verb|detectron| is used for metadata generation.
 \subsection{Metadata Generation}
@@
 Multiplying this by \verb|scale| gives the fish \verb|length| in centimeters.
+\begin{comment}
 \subsection{Consideration}
@@
 \end{itemize}
+\end{comment}
 \section{Results}
@@
 Our automated process currently generates 7 of the 22 core metadata properties: \verb|if_fish| (\verb|has_fish|), \verb|fish_number| (\verb|fish_count|), \verb|if_ruler| (\verb|has_ruler|), \verb|specimen_angled| (\verb|clock_value|), \verb|specimen_view| (\verb|side|), \verb|brightness| (derived from \verb|background.mean| and \verb|foreground.mean|), and \verb|if_background_uniform| (\verb|background.std|).
-In addition, our process also calculates bounding boxes and fish lengths in centimeters.\todo{Talk more about what we can and can't verify and how}
+In addition, our process also calculates bounding boxes and fish lengths in centimeters.\todo{Talk more about what we can and can't verify and how.
+Also, need to fit the percent of the time pixel analysis failed in here somewhere.}
 

### 2021-03-26 paper/paper.tex
Started to edit abstract.

@@
 \begin{abstract}
-    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down.
-Also, we need to decide what to do for the ``teaser image''.} Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down. Also, we need to decide what to do for the ``teaser image''.} 
+    Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
 One area of considerable activity is the digitization of the biological specimens that have been collected worldwide by museums and other research institutions.
@@
 
+ Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions; thus producing large image collections.
+Metadata is often unavailable, sparse or incorrect within these specimen image repositories, but is vital for subsequent machine learning, analysis and scientific discovery.
 As a step towards improving metadata in specimen research image collections, our team has been developing methods for automatically analyzing fish images to extract a variety of important features.
@@
 Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.
+Our goal is to develop image metadata generation methods that both support the novel machine learning research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
+A longer term goal is to extend the image analysis methods for computing specific quantitative features in support of specific biological investigations.
 
@@
   \includegraphics[width=\textwidth]{fish}
-  \caption{Fish prediction}
+  \caption{Fish prediction. Not sure such a big image should go here.  I'll think about a more succinct figure.}
   \Description{Fish prediction}

### 2021-03-26 paper/paper.tex
Worked on abstract, Intro and CCS

--- 2021-03-26 paper/paper.tex
@@
 \begin{abstract}
-    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down.
-Also, we need to decide what to do for the ``teaser image''.} Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+%%    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down. Also, we need to decide what to do for the ``teaser image''.} 
+%    Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
 One area of considerable activity is the digitization of the biological specimens that have been collected worldwide by museums and other research institutions.
@@
 
-As a step towards improving metadata in specimen research image collections, our team has been developing methods for automatically analyzing fish images to extract a variety of important features.
-These fish specimens are being studied for a larger project titled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in the form of specimen images, phylogenies and anatomy ontologies.
+ Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.
+The metadata that is vital for subsequent machine learning, analysis and
+scientific discovery based on these specimen image repositories
+is often unavailable, sparse or incorrect.
+As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features.
+These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies.
 Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.
-
-Metadata is often unavailable, sparse or incorrect within specimen image repositories, but is vital for subsequent machine learning, analysis and scientific discovery.
+Our goal is to develop image metadata generation methods that both support
+the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
+A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
+
+% Metadata is often unavailable, sparse or incorrect within specimen image repositories, but is vital for subsequent machine learning, analysis and scientific discovery.
 Our goal is to develop image metadata generation methods that both support the novel machine learning research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
@@
 The technical challenges in achieving a broader usage of our approach mostly involve training new classifiers for different types of species, learning to segment and read annotation tags, and generalizing our classifier to find and interpret different types of rulers.
-This presentation will report on our current efforts to automatically generate metadata for fish specimen images and offer thoughts on how to extend these techniques for other specimen image collections.\todo{Need to figure out what to actually do for this CCS stuff (\url{http://dl.acm.org/ccs.cfm}) and also the key words}
+This presentation will report on our current efforts to automatically generate metadata for fish specimen images and offer thoughts on how to extend these techniques for other specimen image collections.
 \end{abstract}
@@
 %%
+% \todo{Need to figure out what to actually do for this CCS stuff (\url{http://dl.acm.org/ccs.cfm}) and also the key words}
 \begin{CCSXML}
@@
    </concept>
+   <concept>
+        <concept_id>10010147.10010178</concept_id>
+	<concept_desc>Computing methodologies~Artificial intelligence~Computer Vision</concept_desc>
+	<concept_significance>500</concept_significance>
+    </concept>
 </ccs2012>
@@
 \ccsdesc[500]{Information systems~Extraction, transformation and loading}
+\ccsdesc[500]{Computing methodologies~Artificial intelligence}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{bioinformatics, metadata}
+\keywords{bioinformatics, metadata, image analysis, applied machine learning}
 
@@
 
-Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collection.
-In the U.S., programs, such as the National Science Foundation’s initial Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for well over [nearly?] a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital transformation of data and images for millions of biological specimens.
+Over the last several decades, given the trends towards open science,
+advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections.
+In the U.S., programs, such as the National Science Foundation’s former
+Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
+nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of
+data and images for millions of biological specimens.
 These resources are globally available through a wide range of portals and digital libraries for researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
-Significant challenges surface; however, when researchers seek to apply computational methods, due to both image quality and metadata.
-(As researchers seek to apply computational methods, and explore AI, significant challenges surface..)
-
-Unfortunately, potential scientific advances are hindered [by image quality] as well as [more so?] the lack of high-quality and pertinent metadata associated with the image collections.
-Many specimen collections include Darwin Core metadata, detailing specimen taxon, geographic location, and several other descriptive aspects.
-Additionally, some digitization efforts record technical metadata, detailing imaging specifications.
-While these types of metadata are helpful for a human examining several images at a time, they are insufficient for researchers seeking to apply computational methods to examine thousands of images to determine if, for instance, a dorsal fin of a specific fish has a different shape.
-Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
+Significant challenges surface, however, when researchers seek to apply computational methods to these data items,
+due to both image quality and metadata issues.
+% (As researchers seek to apply computational methods, and explore AI, significant challenges surface..)
+
+Unfortunately, potential scientific advances are hindered by image quality
+problems and the lack of accurate and pertinent metadata
+associated with the image collections.
+Poor quality images, e.g. with low contrast, inadequate lighting, out of
+focus, cluttered visual arrangements, provide inadequate input for automated
+image analysis and machine learning algorithms and lead to inferior
+computational results.
+In order to perform quantitative morphometric analysis of the specimens,
+the physical scale of the images (pixels/inch) is needed; thus
+requiring the ability to identify and measure rulers in the images.
+Many specimen collections do include Darwin Core metadata, detailing
+specimen taxon, geographic location, and several other descriptive aspects.
+Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
+human examining several images at a time, they are insufficient for researchers seeking to apply computational methods to examine thousands of images
+to determine if, for instance, a specific fish grows to different lengths
+in different ecosystems.
+
+Since the digital collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
 Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
-
-As a step towards improving metadata in specimen research image collections, members of the Metadata Research Center, Drexel University, have been developing methods to automatically analyze fish images and extract a set of important features [metadata].
-The research is being conducted as part of Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploits machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
-Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement.
-This paper reports on our research examining a set of [add numbers] images drawn from the Illinois Natural History Survey (INHS) Collection.
-The following section of this paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods.
+As a step towards improving metadata in specimen research image collections, members of the Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
+extract a set of data features that provide important metadata about the
+digital specimen.
+The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
+Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata such as fish quantity and location within images, fish orientation, and
+image scaling based on ruler identification and measurement. Image scaling
+allows us to compute quantitative features about the fish specimens, such
+as their length and area.
+In order to test and validate our methods, we applied them to a set of 7,247
+images drawn from the Illinois Natural History Survey (INHS) Collection.
+The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods.
 Next, the results are presented, followed by a discussion.

### 2021-03-27 paper/paper.tex
Adding fish image analysis references.

@@
 allows us to compute quantitative features about the fish specimens, such
-as their length and area.
-In order to test and validate our methods, we applied them to a set of 7,247
+as their length and area.  In order to test and validate our methods, they
+were  applied to a set of 7,247
 images drawn from the Illinois Natural History Survey (INHS) Collection.
@@
 
-\cite{BockAlexander2018TITE}
-\cite{KonovalovD2017RDfA}
-\cite{Williams:2020:UIF}
+Bock 2018 \cite{BockAlexander2018TITE},
+Konovalov 2017 \cite{KonovalovD2017RDfA},
+Williams 2020 \cite{Williams:2020:UIF},
+Hao 2015 \cite{Hao2015TheMO},
+Lalabadi 2020 \cite{Lalabadi2020FishFC},
+Wang 2015 \cite{Huihui2015StudyOT},
+Saberioon 2017 \cite{Saberioon2017ApplicationOM},
+Tappi 2017 \cite{Tappi2017ComputerVS},
+Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
+Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
+Bernardo 2020 \cite{Bernardo2020FishQI},
+Konovalov 2018 \cite{Konovalov2018AutomaticSO},
+Konovalov 2019 \cite{Konovalov2019AutomaticWE},
+Lugatiman 2019 \cite{Lugatiman2019TunaMF},
+Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
+Petrov 2020 \cite{Petrov2020Overview},
+G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
+Miranda 2017 \cite{MIRANDA201741},
+Zion 2000 \cite{Zion2000InvivoFS},
+Zion 2012 \cite{Zion2012ReviewTU}.
 

### 2021-03-27 paper/paper.tex
Added more refs to paper and bibtex file.

--- 2021-03-26 paper/paper.tex
@@
 
-\cite{BockAlexander2018TITE}
-\cite{KonovalovD2017RDfA}
-\cite{Williams:2020:UIF}
+Bock 2018 \cite{BockAlexander2018TITE},
+Konovalov 2017 \cite{KonovalovD2017RDfA},
+Williams 2020 \cite{Williams:2020:UIF},
+Hao 2015 \cite{Hao2015TheMO},
+Lalabadi 2020 \cite{Lalabadi2020FishFC},
+Wang 2015 \cite{Huihui2015StudyOT},
+Saberioon 2017 \cite{Saberioon2017ApplicationOM},
+Tappi 2017 \cite{Tappi2017ComputerVS},
+Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
+Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
+Bernardo 2020 \cite{Bernardo2020FishQI},
+Konovalov 2018 \cite{Konovalov2018AutomaticSO},
+Konovalov 2019 \cite{Konovalov2019AutomaticWE},
+Lugatiman 2019 \cite{Lugatiman2019TunaMF},
+Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
+Petrov 2020 \cite{Petrov2020Overview},
+G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
+Miranda 2017 \cite{MIRANDA201741},
+Zion 2000 \cite{Zion2000InvivoFS},
+Zion 2012 \cite{Zion2012ReviewTU},
+Dowlati 2012 \cite{Dowlati2012ApplicationOM},
+Balaban 2010 \cite{Balaban2010UsingIA},
+Alsmadi 2010 \cite{Alsmadi2010FishRB},
+Isimen 2014 \cite{Iscimen2014ImageAM},
+Iqbal 2021 \cite{Iqbal2021AutomaticFS},
+Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
+Sung 2017 \cite{Sung2017VisionBR},
+Sharmin 2019 \cite{Sharmin2019MVB},
+Salman 2016 \cite{Salman2016FishSC},
+Sung 2020 \cite{Sung2020AutomaticGF},
+Xu 2021 \cite{Xu2021TransferLA},
+Banan 2020 \cite{Banan2020DeepLA}
 

### 2021-03-27 paper/paper.tex
Updates from Overleaf

@@
 \begin{teaserfigure}
-  \includegraphics[width=\textwidth]{fish}
-  \caption{Fish prediction. Not sure such a big image should go here.  I'll think about a more succinct figure.}
-  \Description{Fish prediction}
+  \centering
+  \begin{subfigure}%{.5\linewidth}
+  \includegraphics[width=.49\textwidth]{images/teaser1}
+  \end{subfigure}
+  \begin{subfigure}%{.5\linewidth}
+  \includegraphics[width=.49\textwidth]{images/teaser2}
+  \end{subfigure}
+  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
+  \Description{Fish predictions}
   \label{fig:fish}
@@
 A prerequisite task to addressing any more advanced metadata property determination is finding specimens (and other relevant objects) within collection images.
-Object detection has been an incredibly active field of study in recent years,~\cite{zou2019object} and has resulted in a number of well tested purpose built architectures.
-We elected to use Facebook AI Research's \verb|detectron| tool~\cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture~\cite{he2018mask}, for object detection in our project.
-
-\verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format dataset.
-It is able to handle an arbitrary number of object classes, and can classify an arbitrary number of object within a given sample.
+Object detection has been an incredibly active field of study in recent years,~\cite{zou2019object} and has resulted in a number of well tested, purpose built architectures.
+We elected to use Facebook AI Research's \verb|detectron| tool,~\cite{wu2019detectron2} and specifically its implementation of the Mask R-CNN architecture,~\cite{he2018mask} for object detection in our project.
+
+\verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format datasets.
+It is able to handle an arbitrary number of object classes, and can classify an arbitrary number of object within a given image.
 For our project, we are currently using it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers.
@@
 \begin{itemize}
-    \item Further fine tuning of pixel analysis (e.g.\ thresholding on different regions of the bbox)
-    \item Generalizing ruler reading
-    \item Training on a progressively larger number of image collections to hopefully gain reasonable generality for the whole class of fish specimen images
-    \item Adding things like seahorses and eels
-    \item Fitting a ``spine'' to specimen
+    \item Further fine tuning of pixel analysis (e.g.\ thresholding on different regions of the bbox).
+    \item Generalizing ruler reading.
+    \item Training on a progressively larger number of image collections to hopefully gain reasonable generality for the whole class of fish specimen images.
+    \item Adding things like seahorses and eels.
+    \item Fitting a ``spine'' to specimen.
+    \item Attempt to address tags that overlap fish?
+If nothing else could add a ``tag'' class and either try to exclude those pixels from the pixel analysis of the fish, or just use detectron bbox if a tag intersects with a specimen.
 \end{itemize}

### 2021-03-27 paper/paper.tex
Added all raw results (no tables or pictures yet)
Also updated validate.py to show a few more things

@@
   \centering
-  \begin{subfigure}%{.5\linewidth}
   \includegraphics[width=.49\textwidth]{images/teaser1}
-  \end{subfigure}
-  \begin{subfigure}%{.5\linewidth}
   \includegraphics[width=.49\textwidth]{images/teaser2}
-  \end{subfigure}
   \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
@@
 
-\section{Goal and Objectives}
+\section{Goals and Objectives}
 
@@
 \(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images.
-Of these \(8,398\) images, \(7,247\) were both not part of the \verb|detectron| training set and meet our current admissibility criteria for what \verb|detectron| and the pixel analysis process can reliably handle.
-We ran the metadata extraction program on these \(7,247\) images.
+Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and meet our current admissibility criteria for what \verb|detectron| and the pixel analysis process can reliably handle.
+We ran the metadata extraction program on these \(7,244\) images.
 
 Our automated process currently generates 7 of the 22 core metadata properties: \verb|if_fish| (\verb|has_fish|), \verb|fish_number| (\verb|fish_count|), \verb|if_ruler| (\verb|has_ruler|), \verb|specimen_angled| (\verb|clock_value|), \verb|specimen_view| (\verb|side|), \verb|brightness| (derived from \verb|background.mean| and \verb|foreground.mean|), and \verb|if_background_uniform| (\verb|background.std|).
-In addition, our process also calculates bounding boxes and fish lengths in centimeters.\todo{Talk more about what we can and can't verify and how.
-Also, need to fit the percent of the time pixel analysis failed in here somewhere.}
-
-All images in the INHS dataset contain exactly one fish. \textbf{Todo}: if\_fish and fish\_count results
-
-\textbf{Todo}: Ruler results
-
-\textbf{Todo}: Side results
-
-\textbf{Todo}: Clock value results
-
-\textbf{Todo}: Brightness/uniformity results? I can try to do this but I need to set up the infrastructure, we probably need to discuss a plan of action for this.
-
-\textbf{Todo}: Bounding box results
-
-\textbf{Todo}: Scale results
+In addition, our process also calculates bounding boxes and fish lengths in centimeters.\todo{Talk more about what we can and can't verify and how.}
+
+\subsection{Fish Detection}
+All images in the INHS dataset contain exactly one fish.
+For \(7,209\) of the specimen images, one fish was detected.
+For 25 of the images, 2 fish were detected, 3 fish were detected for 3 images, and for 7 images no fish were found.
+In the case of greater than 1 fish, 9 of the 28 contained tags which overlapped the fish and were themselves labeled as a second fish.
+Of the remaining 17, \verb|detectron| erroneously labeled the fish as two separate fish objects, or labeled a subsection of the fish a second time.
+
+\subsection{Ruler Detection}
+For all but 2 of the \(7,244\) images \verb|detectron| was able to find the ruler.\todo{Not sure if I can phrase it that way or not since I haven't looked at all the images to see if the ruler itself was found or something else was labeled a ruler} For an additional 56 images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed.
+
+\subsection{Side Detection}
+For 246 of the images \verb|detectron| was unable to find a fish eye. Of the remaining \(6,998\) images where it did, the correct side (\verb|left| or \verb|right|) was detected in all but 6 cases.
+
+\subsection{Clock Value}
+Clock position values were successfully generated for \(6,991\) of the images. Of those, all but 10 were within \(\pm{}1\) of the correct result.
+
+\subsection{Brightness/Uniformity Results?}
+\textbf{Todo}: I can try to do this but I need to set up the infrastructure, we probably need to discuss a plan of action for this.
+
+\subsection{Bounding Box}
+Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found.
+All but 263 of these were generated via pixel analysis, with those 263 falling back to the original \verb|detectron| bounding box.
+\textbf{Todo}: Anything more than this is going to need hand checked.
+
+\subsection{Length}
+Fish lengths were calculated for \(7,179\) of the images. \textbf{Todo}: Anything more than this is going to need hand checked.
 \begin{comment}

### 2021-03-27 validate.py

@@ -22,6 +22,9 @@ no_eye = 0
 no_fish = 0
 errored = 0
 wrong_wrong = 0
+side_wrong = 0
+length_calced = 0
+bbox = 0
 for i in results.keys():
     counter += 1
     me = results[i]
@@ -36,6 +39,10 @@ for i in results.keys():
         #print(angle)
         angle = round(angle)
         if me['has_fish']:
+            if 'bbox' in me['fish'][0].keys():
+                bbox += 1
+            if 'length' in me['fish'][0].keys():
+                length_calced += 1
             if me['fish'][0]['has_eye']:
                 val = int(me['fish'][0]['clock_value'])
                 #print(yasin)
@@ -46,9 +53,14 @@ for i in results.keys():
                 wrong_wrong += 1 if not check else 0
                 #right += val >= round(yasin.specimen_angled - 1) and\
                 #        val <= round(yasin.specimen_angled + 1)
-                if not (val >= (angle - 1) and val <= (angle + 1)):
+                #if not (val >= (angle - 1) and val <= (angle + 1)):
                     #print(f"{i}: {me['fish'][0]['clock_value']}, {yasin.specimen_angled}")
-                    print(f"{i}: {me['fish'][0]['clock_value']}, {angle}")
+                    #print(f"{i}: {me['fish'][0]['clock_value']}, {angle}")
+                mes = me['fish'][0]['side']
+                yasins = all_yasin.iloc[0].specimen_viewing
+                if yasins.find(mes) < 0:
+                    side_wrong += 1
+                    print(f'{i}: Side wrong | {mes} | {yasins}')
             else:
                 no_eye += 1
                 print(f'{i}: No eye')
@@ -67,3 +79,6 @@ print(f'Wrong wrong: {wrong_wrong}')
 print(f'Total: {counter}')
 print(f'Percent right: {right / counter}')
 print(f'Percent right that didn\'t error: {right / (counter - no_eye - no_fish - errored)}')
+print(f'\nSide wrong: {side_wrong}')
+print(f'Length calculated: {length_calced}')
+print(f'Bbox calculated: {bbox}')

### 2021-03-28 paper/paper.tex
Updates from Overleaf
Added more Fish Image refs
Cropped teaser pix

@@
   \centering
-  \includegraphics[width=.49\textwidth]{images/teaser1}
-  \includegraphics[width=.49\textwidth]{images/teaser2}
+  \includegraphics[width=.45\textwidth]{images/teaser1_crop}
+  \hspace{4mm}
+  \includegraphics[width=.45\textwidth]{images/teaser2_crop}
   \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
@@
 The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
-Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata such as fish quantity and location within images, fish orientation, and
+Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
 image scaling based on ruler identification and measurement. Image scaling
@@
 
+Fish Classification\newline
+Alsmadi 2010 \cite{Alsmadi2010FishRB},
+Alsmadi 2019 \cite{Alsmadi2019RFE},
+Hasija 2017 \cite{Hasija2017FishSC},
+Hu 2012 \cite{HuJing2012Fscb},
+Iqbal 2021 \cite{Iqbal2021AutomaticFS},
+Iscimen 2014 \cite{Iscimen2014ImageAM},
+Iscimen 2015 \cite{Iscimen2015ClassificationOF},
+
+Orientation, Size and Weight and Shape\newline
+Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
+Balaban 2010 \cite{Balaban2010UsingIA},
+Wang 2015 \cite{Huihui2015StudyOT},
+Hao 2015 \cite{Hao2015TheMO},
+
+Fish Quality\newline
+Bernardo 2020 \cite{Bernardo2020FishQI},
+Dowlati 2012 \cite{Dowlati2012ApplicationOM},
+
+3D Segmentation from microCT\newline
 Bock 2018 \cite{BockAlexander2018TITE},
+
+Computer Vision Overviews to Fish\newline
+G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
+
 Konovalov 2017 \cite{KonovalovD2017RDfA},
 Williams 2020 \cite{Williams:2020:UIF},
-Hao 2015 \cite{Hao2015TheMO},
 Lalabadi 2020 \cite{Lalabadi2020FishFC},
-Wang 2015 \cite{Huihui2015StudyOT},
 Saberioon 2017 \cite{Saberioon2017ApplicationOM},
@@
 Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
-Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
-Bernardo 2020 \cite{Bernardo2020FishQI},
 Konovalov 2018 \cite{Konovalov2018AutomaticSO},
@@
 Petrov 2020 \cite{Petrov2020Overview},
-G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
 Miranda 2017 \cite{MIRANDA201741},
@@
 Zion 2012 \cite{Zion2012ReviewTU},
-Dowlati 2012 \cite{Dowlati2012ApplicationOM},
-Balaban 2010 \cite{Balaban2010UsingIA},
-Alsmadi 2010 \cite{Alsmadi2010FishRB},
-Isimen 2014 \cite{Iscimen2014ImageAM},
-Iqbal 2021 \cite{Iqbal2021AutomaticFS},
 Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
@@
 Xu 2021 \cite{Xu2021TransferLA},
-Banan 2020 \cite{Banan2020DeepLA}
+Banan 2020 \cite{Banan2020Deep,LA}
+Kinjo 2014 \cite{KinjoAtsushi2014Scoi},
+Ogunlana 2015 \cite{Ogunlana2015FCU},
+Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
+Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
+Shah 2019 \cite{Shah2019FishPakFS},
+Li 2014 \cite{Li2014IdentificationOF}
 

### 2021-03-28 paper/paper.tex
Committing to pull
Tweaking Fish Image Analysis section and .bib entries

@@
 %%
-% \todo{Need to figure out what to actually do for this CCS stuff (\url{http://dl.acm.org/ccs.cfm}) and also the key words}
 \begin{CCSXML}
@@
 Iscimen 2015 \cite{Iscimen2015ClassificationOF},
+Kinjo 2014 \cite{KinjoAtsushi2014Scoi},
+Li 2014 \cite{Li2014IdentificationOF}
 
@@
 Hao 2015 \cite{Hao2015TheMO},
+Konovalov 2018 \cite{Konovalov2018AutomaticSO},
+Konovalov 2019 \cite{Konovalov2019AutomaticWE},
+
+Ruler Detection\newline
+Konovalov 2017 \cite{KonovalovD2017RDfA},
 
@@
 Dowlati 2012 \cite{Dowlati2012ApplicationOM},
+Lalabadi 2020 \cite{Lalabadi2020FishFC},
 
@@
 
-Computer Vision Overviews to Fish\newline
+Computer Vision Overviews Related to Fish\newline
 G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
 
-Konovalov 2017 \cite{KonovalovD2017RDfA},
 Williams 2020 \cite{Williams:2020:UIF},
-Lalabadi 2020 \cite{Lalabadi2020FishFC},
 Saberioon 2017 \cite{Saberioon2017ApplicationOM},
@@
 Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
-Konovalov 2018 \cite{Konovalov2018AutomaticSO},
-Konovalov 2019 \cite{Konovalov2019AutomaticWE},
 Lugatiman 2019 \cite{Lugatiman2019TunaMF},
@@
 Banan 2020 \cite{Banan2020Deep,LA}
-Kinjo 2014 \cite{KinjoAtsushi2014Scoi},
 Ogunlana 2015 \cite{Ogunlana2015FCU},
@@
 Shah 2019 \cite{Shah2019FishPakFS},
-Li 2014 \cite{Li2014IdentificationOF}
 
@@
 \section{Discussion}
-\textbf{Todo}
+\textbf{Todo}: Will need some sort of intro/framing paragraph
+\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
+\subsubsection{Object Detection}
+\begin{itemize}
+    \item Worked fairly well all things considered
+    \item Talk about which fish failed
+    \item Talk about which rulers failed
+\end{itemize}
+\subsubsection{Side Detection}
+
+\subsubsection{Clock Value}
+
+\subsubsection{Brightness?}
+
+\subsubsection{Bounding Box}
+
+\subsubsection{Length}
+
 \subsection{Future Work}

### 2021-03-28 paper/paper.tex
Added a lot of images and more discussion

@@
 Computer Vision Overviews Related to Fish\newline
-G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
+G{\"u}m{\"u}\c{s} 2011 \cite{Gm2011MachineVA},
 
@@
 Xu 2021 \cite{Xu2021TransferLA},
-Banan 2020 \cite{Banan2020Deep,LA}
+Banan 2020 \cite{Banan2020DeepLA}
 Ogunlana 2015 \cite{Ogunlana2015FCU},
@@
 \subsection{Clock Value}
-Clock position values were successfully generated for \(6,991\) of the images. Of those, all but 10 were within \(\pm{}1\) of the correct result.
+Clock position values were successfully generated for \(6,991\) of the images. Of those, all but 8 were within \(\pm{}1\) of the correct result.
 
@@
 
-\subsection{Bounding Box}
+\subsection{Mask and Bounding Box}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/011196_pred}
+  \includegraphics[width=0.49\linewidth]{images/011196_mask}
+  \includegraphics[width=0.49\linewidth]{images/52399_pred}
+  \includegraphics[width=0.49\linewidth]{images/52399_mask}
+  \includegraphics[width=0.49\linewidth]{images/56885_pred}
+  \includegraphics[width=0.49\linewidth]{images/56885_mask}
+  \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}
+  \Description{Bounding box and mask examples}
+\end{figure}
 Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found.
@@
 \subsubsection{Object Detection}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/none1}
+  \includegraphics[width=0.49\linewidth]{images/double1}
+  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
+  \Description{Mislabeled eye on a catfish}
+\end{figure}
+
 \begin{itemize}
@@
 \subsubsection{Side Detection}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
+  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
+  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
+  \Description{Mislabeled eye on a catfish}
+\end{figure}
+For all 6 of the cases where an eye was detected but the \verb|side| value was wrong, a spot on the wrong side of the fish was labeled as the most likely eye within the bounding box of the fish.
+There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
+For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than than the human error rate.
 
 \subsubsection{Clock Value}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/curved1}
+  %\includegraphics[width=0.49\linewidth]{images/}
+  \caption{An example of a heavily curved specimen.}
+  \Description{Mislabeled eye on a catfish}
+\end{figure}
+Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).For 25 of those the human generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
+Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value.
+The other 6 were values of 3 instead of 9 or vice versa that resulted from a mislabeled eye as discussed in the previous section.
+A small number of images (such as on the right in Figure~\ref{fig:fish}) have tags that overlap with the fish.
+These tags were light enough that they were correctly labeled as background by the pixel analysis.
+
+\subsubsection{Mask and Bounding Box}
 
 \subsubsection{Brightness?}
-
-\subsubsection{Bounding Box}
 
@@
     \item Fitting a ``spine'' to specimen.
-    \item Attempt to address tags that overlap fish?
-If nothing else could add a ``tag'' class and either try to exclude those pixels from the pixel analysis of the fish, or just use detectron bbox if a tag intersects with a specimen.
 \end{itemize}
@@
 \bibliography{paper}
+
+%\begin{figure}[H]
+%  \centering
+%  \includegraphics[width=\linewidth]{images/}
+%  \caption{}
+%  \Description{}
+%\end{figure}
 

### 2021-03-29 paper/fishImageAnalysisAbs.tex
Partial results for Previous Work section.

\subsection{Fish Image Analysis}

Image analysis has been utilized to examine and process images of fish
for well over two decades \cite{Zion2000InvivoFS}. It is an important
application of technology both for marine science, in the study of aquatic
habitats and ecosystems, and for food the industry, in the development
of automated fish sorting and grading systems, as well as fisheries
management. The main focus of
these computational analyses has been the recognition and classification 
of the fish present in an image.

\textbf{Fish Recognition and Classification}\newline
Alsmadi 2010 \cite{Alsmadi2010FishRB},
 our aim was to recognize an isolated pattern of interest in the image based on the combination between robust features extraction. Where depend on size and shape measurements, that were extracted by measuring the distance and geometrical measurements.

Alsmadi 2019 \cite{Alsmadi2019RFE},
Based on feature selection and combination theory between major extracted features, this study attempts to establish a system that could recognize fish object within the image utilizing texture, anchor points, and statistical measurements. Then, a generic fish classification is executed with the application of an innovative classification evaluation through a meta-heuristic algorithm known as Memetic Algorithm (Genetic Algorithm with Simulated Annealing) with back-propagation algorithm (MA-B Classifier).

Hasija 2017 \cite{Hasija2017FishSC},
This paper proposes a novel method based on an improved image-set matching approach, which makes use of Graph-Embedding Discriminant Analysis. In contrast to the state-of-the-art methods, which operate on single input images, our method makes, use of explicit image set matching which renders it robust computationally.

Hu 2012 \cite{HuJing2012Fscb},
This paper presents a novel method of classifying species of fish based on color and texture features and using a multi-class support vector machine (MSVM). Fish images were acquired and sent by smartphone

Iqbal 2021 \cite{Iqbal2021AutomaticFS},
In this paper, we presented an automated system for identification and classification of fish species. It helps the marine biologists to have greater understanding of the fish species and their habitats. The proposed model is based on deep convolutional neural networks. It uses a reduced version of AlexNet model comprises of four convolutional layers and two fully connected layers. A comparison is presented against the other deep learning models such as AlexNet and VGGNet. The four parameters are considered that is number of convolu- tional layers and number of fully-connected layers, number of iterations to achieve 100% accuracy on training data, batch size and dropout layer. The results show that the proposed and modified AlexNet model with less number of layers has achieved the testing accuracy of 90.48% while the original AlexNet model achieved 86.65% over the untrained bench- mark fish dataset. The inclusion of dropout layer has enhanced the overall performance of our proposed model. It contain less training images, less memory and it is also less compu- tational complex.

Li 2014 \cite{Li2014IdentificationOF}
Abstract - For more fish varieties, to the subsequent processing and marketing, which is necessary to classify the types of fish.This study is based on image processing technology to classify the types of fish, four fish to make use of the existing image acquisition device for collecting samples, through the MATLAB software for image preprocessing, such as fish gray, binarization, image enhancement, contour extraction to extract the 11 feature parameters of four fish species, such as using the principal component analysis (PCA) to 11 characteristic parameters for dimension reduction, this study took four principal component.Then use SPSS software to establish fisher and mahalanobis distance model, the combination of four principal component reuse component to build a model to classify the four different kinds of fish.Through SPSS software simulation and identification results show that the average recognition rate of 96.67%, which can be well applied to the fish species identification technology.

Banan 2020 \cite{Banan2020DeepLA}
Hence, in this study, a deep learning neural network as a smart, real-time and non-destructive method was developed and applied to automate the identification of four economically important carp species namely common carp (Cyprinus carpio), grass carp (Ctenopharingodon idella), bighead carp (Hypophtalmichthys nobilis) and silver carp (Hypophthalmichthys molitrix). The obtained results proved that our approach, evaluated through 5-fold cross-validation, achieved the highest possible accuracy of 100 %. The achieved high level of classification accuracy was due to the ability of the suggested deep model to build a hierarchy of self-learned features, which was in accordance with the hierarchy of these fish’s identification keys. In conclusion, the proposed convolutional neural network (CNN)-based method has a single and generic trained architecture with promising performance for fish species identification.

Ogunlana 2015 \cite{Ogunlana2015FCU},
In this paper, a Support Vector Machine (SVM)-based technique for the elimination of the limitations of some existing techniques and improved classification of fish species is proposed. The technique is based on the shape features of fish that was divided into two subsets with the first comprising 76 fish as training set while the second comprises of 74 fish as testing set. The body and the five fin lengths; namely anal, caudal, dorsal, pelvic and pectoral were extracted in centimeter (cm). Results based on the new technique show a classification accuracy of 78.59%, which is significantly higher than what obtained for ANN, KNN and K-mean clustering-based algorithms.

Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
This paper proposes five different schemes for automatic classification of fish species. These schemes make the species recognition based on image sample ana- lysis. Different techniques have been combined for build- ing the classifiers: three feature extraction techniques (PCA, SIFT and SIFT ? VLAD ? PCA), three data clustering algorithms (aiNet, ARIA and k-means) and three input classifiers (k-NN, SIFT class. and k-means class) are tested. When compared to common methodologies, which are based on human observation, it is believed that these schemes are able to provide significant improvement in time and financial resources spent in classification. Two datasets have been considered: (1) a dataset with image samples of six fish species which are perfectly conserved in formaldehyde solution, and; (2) a dataset composed of images of four fish species in real-world conditions (in vivo). The five proposed schemes have been evaluated
in both datasets, and a ranking for the methods has been derived for each one.

Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
We are studying image-based fish identification. Most of traditional approaches used a fish image which was easy to extract a fish region with a white background or uniform background for automatic processing. This research adapted an approach to give several points by manual operation by the user. The proposed approach is able to accept the fish image in the complicated background taken on the rocky place. Furthermore, to investigate the efficient features for fish recognition, we defined various features, such as, shape features, local features, and six kinds of texture features. We collected 129 species under various photography conditions, and the proposed method was carried out to it. As the results, it was confirmed that a combination features with geometric features and BoVW models obtained the highest recognition accuracy.

Salman 2016 \cite{Salman2016FishSC},
Underwater video and digital still cameras are rapidly being adopted by marine scientists and managers as a tool for non-destructively quantifying and measuring the relative abundance, cover and size of marine fauna and flora. Imagery recorded of fish can be time consuming and costly to process and analyze manually. For this reason, there is great interest in automatic classification, counting, and measurement of fish. Uncon- strained underwater scenes are highly variable due to changes in light intensity, changes in fish orientation due to movement, a variety of background habitats which sometimes also move, and most importantly simi- larity in shape and patterns among fish of different species. This poses a great challenge for image/video processing techniques to accurately differentiate between classes or species of fish to perform automatic clas- sification. We present a machine learning approach, which is suitable for solving this challenge. We demon- strate the use of a convolution neural network model in a hierarchical feature combination setup to learn species-dependent visual features of fish that are unique, yet abstract and robust against environmental and intra-and inter-species variability. This approach avoids the need for explicitly extracting features from raw images of the fish using several fragmented image processing techniques. As a result, we achieve a single and generic trained architecture with favorable performance even for sample images of fish species that have not been used in training. Using the LifeCLEF14 and LifeCLEF15 benchmark fish datasets, we have demonstrated results with a correct classification rate of more than 90%.

Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
This paper proposed an automated fish species identification system based on a modified crow search optimization algorithm. Median filtering is applied for image smoothing and removing noise through reducing the variation of intensities between the neighbors. Then, a k-mean clustering algorithm is used to segment the fish image into multiple segments. Shape-based and texture-based feature extraction process for classification is presented. A new modified binary version of crow search algorithm is proposed to reduce the data dimensionality of the extracted features. Finally, support vector machine and decision trees are implemented for classification and the fish species are classified based on either their class including Actinopterygii and Chondrichthyes or based on their order. Total of 270 images with different species, classes and orders are used for evaluation of the proposed system. The experimental results show that the proposed system achieves the highest classification accuracy compared to state-of-the-art algorithms. Also, the results show that the overall fish species identification system obtains on average of 10 folds, 96% classification accuracy for classification based on class and 74% for classification based on fish order.

Sharmin 2019 \cite{Sharmin2019MVB},
the new generation people of Bangladesh lacks the knowledge of local freshwater fish. For this problem, a solution has been found with the collaboration of vision-based technology. As a solution, a machine-vision based local freshwater fish recognition system is presented that can be proceed with an image of fish captured with a mobile or handheld device and recognize the fish in order to introduce the fish. To demonstrate the utility of the proposed expert system, several experiments are performed. At first, a set of fourteen features, which consists of four types of features, are presented. Then the color image has been converted into gray-scale image and the gray-scale histogram is formed. Image segmentation takes place using histogram-based method and then the features are extracted. PCA is used for decreasing the feature numbers. Three classifiers are used for recognizing fish, where SVM gives the highest accuracy showing a value of 94.2%.

Sung 2017 \cite{Sung2017VisionBR},
Underwater vision has specific characteristics such as high attenuation of lights, severe noise and haze in the images. For real-time fish detection using underwater vision, this paper proposes convolutional neural network based techniques based on You Only Look Once algorithm. Actual fish video images were used to evaluate the reliability and accuracy of the proposed method. As a result, the network recorded 93% classification accuracy, 0.634 intersection over union between predicted bounding box and ground truth, and 16.7 frames per second of fish detection. It also outperforms another fish detector using sliding window algorithm and classifier trained with histogram of oriented gradient features and support vector machine.

Xu 2021 \cite{Xu2021TransferLA},
Scientific studies on species identification in fish have considerable significance in aquatic ecosystems and quality evaluation. The morphological differences between different fish species are obvious. Machine learning methods use artificial prior knowledge to extract fish features, which is time-consuming, laborious, and subjective. Recently, deep learning-based identification of fish species has been widely used. However, fish species identification still faces many challenges due to the small scale of fish samples and the imbalance of the number of categories. For example, the model is prone to being overfitted, and the performance of the classifier is biased to the fish species of most samples. To solve the above problems, this paper proposes a fish species identification approach based on SE-ResNet152 and class-balanced focal loss. First, visualization analysis and image preprocessing of fish datasets are carried out. Second, the SE-ResNet152 model is constructed as a generalized feature extractor and is migrated to the target dataset. Finally, we apply the class-balanced focal loss function to train the SE-ResNet152 model, and realize fish species identification on three fish image views (body, head, and scale). The proposed method was tested on the Fish-Pak public dataset and achieved 98.80%, 96.67%, and 91.25% accuracy on the three fish image views, respectively. To ensure the superior performance of the proposed method, we performed an experimental comparison with other methods involving SENet154, DenseNet121, ResNet18, ResNet152, VGG16, cross-entropy, and focal loss. Comprehensive empirical analyses reveal that the proposed method achieves good performance on the three fish image views and outperforms common methods.

Zion 2000 \cite{Zion2000InvivoFS},
An image-processing algorithm, applied to images of common carp (Cyprinus carpio), St. Peter’s fish (Oreochromis sp.) and grey mullet (Mugil cephalus), successfully discriminated among the species. Fish images were acquired while they were swimming in an aquarium with their side to the camera. The algorithm was based on the method of moment-invariants (MI) coupled with geometrical considerations and was, therefore, insensitive to fish size, two-dimensional orientation and location in the camera’s field of view. One hundred and forty three images (47 grey mullet, 43 St. Peter’s fish and 53 carp images) were acquired and divided into two sets: 20 grey mullet, 20 St. Peter’s fish and 20 carp images in one set and the rest of the images in the other set. Each of these two sets was used as a training set for selection of feature thresholds, which were then applied to the other set as a test case (two-fold cross-validation test). Fish species identification reached 100, 91 and 91% for grey mullet, carp and St. Peter’s fish, respectively. To the best of our knowledge this is the first report on successful discrimination among fish species in vivo.

\textbf{Orientation, Length, Size, Weight and Shape}\newline
Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
Fish processing in small and medium fish supplying centers requires an intelligent system to operate on different sizes. Therefore, an image processing algorithm was developed to extract the proper head and belly cutting points according to the trout dimensions. The algorithm detects the fish orientation and location of pectoral, anal, pelvic, and caudal fins. In this study, each of the trout images was divided into slices along its length in order to segment the fins and extract cutting points. The channel ‘B’ of RGB color space was considered in both initial segmentation and fin detection stages among the examined channels of RGB, HSV, and L*a*b* color spaces. The back-belly and head-tail sides were detected with an accuracy of 100% based on gray intensity values and head to tail ratio, respectively. Furthermore, performing an analysis of variance (ANOVA) resulted in an F-value of 64.82 among the fins. Conducting a t-test among the mean intensity values of the fins and non-fin regions of channel ‘B’ resulted in the highest distinction with t-values of 90.30, 78.07, 74.28, and 86.01 with p < 0.01 for the pectoral, pelvic, anal, and caudal fins paired with the corresponding non-fin region, respectively. The results showed that the selected ‘B’ channel is the adequate one for fin segmentation. The fin detection process showed an overall sensitivity, specificity, and accuracy of 86.05%, 99.97%, and 99.87%, respectively. By solving the line determination error in 8.24% and the extra object error in 4.12% of the samples, the overall fin identification accuracy was 100%. Finally, after extracting the fin regions, the start point of the pectoral fin and the end point of the anal fin will be applied in the trout processing system as the head and belly cutting points, respectively.

Balaban 2010 \cite{Balaban2010UsingIA},
After harvesting , salmon is sorted by species, size, and quality. This is generally manually done by op-erators. Automation would bring repeatability, objectivity, and record-keeping capabilities to these tasks. Machinevision (MV) and image analysis have been used in sorting many agricultural products. Four salmon species weretested: pink (Oncorhynchus gorbuscha), red (Oncorhynchus nerka), silver (Oncorhynchus kisutch), and chum (On-corhynchus keta). A total of 60 whole fish from each species were first weighed, then placed in a light box to taketheir picture. Weight compared with view area as well as length and width correlations were developed. In additionthe effect of “hump” development (see text) of pink salmon on this correlation was investigated. It was possible topredict the weight of a salmon by view area, regardless of species, and regardless of the development of a humpfor pinks. Within pink salmon there was a small but insignificant difference between predictive equations for theweight of “regular” fish and “humpy” fish. Machine vision can accurately predict the weight of whole salmon forsorting.

Hao 2015 \cite{Hao2015TheMO}, A REVIEW
This study reviewed the methods of fish size measurement through machine vision. Length and area are important information that can help fishers manage fish scientifically and conveniently. This information could be used to calculate the volume and weight according to their relation; other information could also be calculated. Machine vision is more effective, economical and faster than traditional methods.

Konovalov 2017 \cite{KonovalovD2017RDfA},
Fast and low cost image collection and processing is often required in aquaculture farms for quality/size attributes and breeding programs. For example, the absolute physical dimensions of fish (in millimeters or inches) could be estimated from electronic images. The absolute scale of the photographed fish is often unknown or requires additional hardware, data- collection and/or management overheads. One cost and time effective solution is to capture the absolute scale (in pixels-per- millimeter or dots-per-inch) by including a measuring ruler in the photographed scene. To assist that type of workflow, we designed a relatively simple image-processing algorithm that automatically located a sufficiently large section of the ruler in a given image. The algorithm utilized the Fast Fourier Transform and was designed to be free from adjustable parameters and therefore did not require training or calibration. The algorithm was tested on 445 images of Barramundi (Asian sea bass, Lates calcarifer), where a millimeter-graded ruler was included in each image. The algorithm achieved precision of 98% (on the original, 10, 20, 70, 80 90 degree rotated images) and 95-96% on 40, 50, 60 degree rotated images. \newline
Konovalov 2018 \cite{Konovalov2018AutomaticSO},
In aquaculture breeding programs where large numbers of fish need to be rapidly phenotyped, the absolute physical dimensions of fish (in millimeters or inches) are often required to be extracted from electronic images in order to measure the size of the fish. While it is possible to infer the length of the fish in pixels, the absolute scale of the image (in pixels-per-millimeter or dots-per- inch) is largely unknown without a reference grid, or requires additional hardware, data collection and/or record-keeping management overheads. One cost and time effective solution is to capture the absolute scale by including a measuring ruler in the photographed scene and from which a computer program can automatically identify the scale of the photo and calculate fish morphometric measurements. To assist such workflow, this study developed an algorithm that automatically detects a ruler in a given image, and automatically extracts its scale as distance (in fractional number of pixels) betw􏱜􏱜􏰬 􏰦􏱬􏱜 􏰪􏰣􏰴􏱜􏰪􏰱􏰤 􏱼􏰪􏲂􏱙􏰣􏲂􏰦􏲋􏱟􏰬 􏰨􏲂􏰪􏲀􏰤. The algorithm was applied to 445 publicly available images of barramundi or Asian seabass (Lates calcarifer), where a millimeter-graded ruler was included in each image. Convolutional Neural Network (CNN) was trained to segment the images into ruler, background, fish and label sections. Then the distance-extraction algorithm was applied to the ruler section of the images. The false-negative rate was less than 2%, where the ruler graduation distances could not be extracted in only 2-6 (out of 445) images even when the test images were rotated up to 90 degrees. The mean absolute relative error (MARE) of the inferred distances was 1-2%.\newline
Konovalov 2019 \cite{Konovalov2019AutomaticWE},
Approximately 2,500 weights and corresponding images of harvested Lates calcarifer (Asian seabass or barra- mundi) were collected at three different locations in Queensland, Australia. Two instances of the LinkNet-34 segmentation Convo- lutional Neural Network (CNN) were trained. The first one was trained on 200 manually segmented fish masks with excluded fins and tails. The second was trained on 100 whole-fish masks. The two CNNs were applied to the rest of the images and yielded automatically segmented masks. The one-factor and two-factor simple mathematical weight-from-area models were fitted on 1072 area-weight pairs from the first two locations, where area values were extracted from the automatically segmented masks. When applied to 1,400 test images (from the third location), the one- factor whole-fish mask model achieved the best mean absolute percentage error (MAPE), MAPE = 4.36%. Direct weight-from- image regression CNNs were also trained, where the no-fins based CNN performed best on the test images with MAPE = 4.28%.

\textbf{Fish Quality}\newline
Lalabadi 2020 \cite{Lalabadi2020FishFC},
Developing new techniques to determine fish freshness and quality can enhance nutritional value of the overall household food basket. In this research, digital image analysis was utilized to assess the freshness of rainbow trout fish by tracing the color attributes of its eyes and gills. The image data were collected from left and right eyes and gills in a 10-day ice-storage duration, and color components were extracted in RGB, HSV, and L*a*b* color spaces. Analysis of variance revealed that the RGB components of both eyes and gills had a significant change towards getting brighter during the ice-storage. Feature extraction was fulfilled from the color spaces, and then artificial neural networks (ANNs) and support vector machines (SVMs) were applied for classification of the ice-storage durations. The overall accuracies of the developed models demonstrated that the ANN somewhat outperformed the SVM for both the extracted features from the eyes and gills. Moreover, the gills’ features could describe the variance in the storage durations more efficiently than those extracted from the eyes. Finally, it was concluded that the applied colorimetric system along with the developing models could be employed as a successful non-destructive approach for evaluation of fish freshness.

Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
In the current research, the potential of a novel method based on the artificial neural network was investigated to diagnose the freshness of common carp (Cyprinus carpio) during ice storage. Fish as an aquaculture product has high nutrients and low-fat content. So, people have consumed it as a safe and high-value foodstuff in their daily diet. Investigation of fish freshness is proposed as a significant issue in the aquaculture industry since fish spoils rapidly. The applied system of this study is comprised of the following steps: First, images of samples were captured and the pre-processing operation was done on the images. Then, particular channels including R, G, B, H, S, I, L*, a*, and b* were computed. Next, feature extraction was performed to obtain 6 types of texture features from each channel. Afterward, the hybrid Artificial Bee Colony-Artificial Neural Network (ABC-ANN) algorithm was applied to select the best features. Finally, the Support Vector Machine (SVM), K-Nearest Neighbor (K-NN) and Artificial Neural Network (ANN) algorithms as the most common methods were used to classify fish images. The best performance of the K-NN classifier was calculated in the k = 8 neighborhood size with the accuracy of 90.48. The best kernel function for the SVM algorithm was polynomial with C, sigma, and accuracy of 1, 2 and 91.52 percent, respectively. In this system, the input layer has consisted of 22 neurons based on the feature selection operation and 4 classes including most fresh, fresh, fairly fresh and spoiled have been used as the number of output layer. At the end, the best results of the MLP networks were achieved by LM learning algorithm and 6 neurons in the hidden layer with the 22–10–4 topology and accuracy of 93.01 percent. The achieved results demonstrate the high performance of the ANN classifier for evaluation of common carp freshness during ice storage as a rapid, accurate, non-destructive, real-time and automated method. It shows the potential of computer vision method in combination with artificial neural networks as an intelligent technique for evaluation of fish freshness.

Tappi 2017 \cite{Tappi2017ComputerVS},
The evaluation of fish freshness can be per- formed using chemical, sensory and physical methods. Besides sensory methods, several instrumental techniques have been applied with the objective of replacing sensory assessment. The aim of this study was to set up and test objective physical methods mainly based on computer vision system (CVS) to assess red mullet (Mullus barba- tus) freshness evolution during 10 days of storage, at two different storage temperatures (0 and 4 °C). To check the effectiveness of the purposed physical methods, CVS fea- tures (loss in the epidermis pigmentation, development of gill mucus and eye concavity index) and firmness have been compared with chemical trimethylamine content and sensory (QIM) attribute scores. As expected, fish degrada- tion was faster at the higher temperature. Instrumental tex- ture evaluation of fish by penetration test enabled to detect distinctive firmness changes due to onset and resolution of rigor mortis, and the successive tenderization phenomenon. Among CVS parameters, the epidermis pigmentation loss, and particularly the eye shape modification (eye concavity index) evidenced a high sensibility for the estimation of fresh red mullet quality loss, as a function of the two differ- ent storage conditions, and a good agreement with trimeth- ylamine content and QIM response evolution.

\textbf{Computer Vision Overviews Related to Fish}\newline
Saberioon 2017 \cite{Saberioon2017ApplicationOM}, A decent, somewhat 
recent overview.

\textbf{Unbending a Fish}\newline
Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
Williams 2020 \cite{Williams:2020:UIF},

\textbf{Not Used}\newline
(Kinda vague. More about food, then fish, G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA}),
(In Turkish, Iscimen 2014 \cite{Iscimen2014ImageAM},
Iscimen 2015 \cite{Iscimen2015ClassificationOF}),
(Not based on images (sonar?) Kinjo 2014 \cite{KinjoAtsushi2014Scoi}),
(Too basic, Wang 2015 \cite{Huihui2015StudyOT}),
(Not so interesting, a very engineered, constrained imaging set up, Miranda 2017 \cite{MIRANDA201741}),

(A review of all types of sensing systems for quality checkin, Bernardo 2020 \cite{Bernardo2020FishQI}),
(Another review, but in Trends in Analytical Chemistry. I think we can
skip it. To so technical, Dowlati 2012 \cite{Dowlati2012ApplicationOM}),

(Simple industrial system. Computing length, Sung 2020 \cite{Sung2020AutomaticGF}),
(It's 3D. Don't want to go there, Bock 2018 \cite{BockAlexander2018TITE}),

(A review that is not quite focused enough, Petrov 2020 \cite{Petrov2020Overview}),
(Don't have access to it, and I have a newer review, Zion 2012 \cite{Zion2012ReviewTU}),

### 2021-03-29 paper/paper.tex
Partial results for Previous Work section.

--- 2021-03-28 paper/paper.tex
@@
 
+Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS},
+
 \subsection{Metadata generation?}
@@
 
-Fish Classification\newline
-Alsmadi 2010 \cite{Alsmadi2010FishRB},
+Image analysis has been utilized to examine and process images of fish
+for well over two decades \cite{Zion2000InvivoFS,Saberioon2017ApplicationOM}. It is an important
+application of technology both for marine science, in the study of aquatic
+species, habitats and ecosystems, and for food the industry, in the
+development of automated fish sorting and grading systems, as well as
+fisheries management. Many of these computational analyses focus on
+the recognition and classification 
+of the fish present in an image.  The computational methods employed for
+fish image analysis followed the general trends in the field.
+Hu et al.~\cite{HuJing2012Fscb} presented a method of classifying species
+of fish based on color and texture features and used a multi-class support
+vector machine (MSVM) \cite{Vapnik1999AOS}.
+Li and Hong \cite{Li2014IdentificationOF} computed eleven shape and color
+features from fish images that were distilled down to four, using Principal
+Component Analysis, and derived a linear model from these four features
+that could discriminate between four different fishes.
+%  Kinda unimpressive. Let's leave out.
+% Saitoh \cite{Saitoh2015ImagebasedFR}
+% utilized a Random Forest method \cite{Breiman2001RF} on manually-derived
+% geometric, Bag of visual words (BoVW) and color features 
+Rodrigues et al.~\cite{RodriguesMarcoT.A2015Ecda} explored several
+combinations of features extraction, input classifiers and clustering
+algorithms to produce a method that could distinguish between 10 different
+types of fish with a 92\% accuracy.
+%  Again, not too impressive. Let's leave out.
+% Ogunlana 2015 \cite{Ogunlana2015FCU},
+% In this paper, a Support Vector Machine (SVM)-based technique for the elimination of the limitations of some existing techniques and improved classification of fish species is proposed.
+The technique is based on the shape features of fish that was divided into two subsets with the first comprising 76 fish as training set while the second comprises of 74 fish as testing set.
+The body and the five fin lengths; namely anal, caudal, dorsal, pelvic and pectoral were extracted in centimeter (cm).
+Results based on the new technique show a classification accuracy of 78.59%, which is significantly higher than what obtained for ANN, KNN and K-mean clustering-based algorithms.
+Salman et al.~\cite{Salman2016FishSC} employed a deep Convolution Neural
+Networks (CNN) \cite{LeCun2004LMG} together with classification based on
+K-Nearest Neighbor and Support Vector Machines trained on the features
+extracted by the CNN in supervised deep learning. They achieved 90\%
+accuracy on challenging underwater digital images.
+Sung 2017 \cite{Sung2017VisionBR},
+Underwater vision has specific characteristics such as high attenuation of lights, severe noise and haze in the images.
+For real-time fish detection using underwater vision, this paper proposes convolutional neural network based techniques based on You Only Look Once algorithm.
+Actual fish video images were used to evaluate the reliability and accuracy of the proposed method.
+As a result, the network recorded 93% classification accuracy, 0.634 intersection over union between predicted bounding box and ground truth, and 16.7 frames per second of fish detection.
+It also outperforms another fish detector using sliding window algorithm and classifier trained with histogram of oriented gradient features and support vector machine.
+Hasija 2017 \cite{Hasija2017FishSC},
+This paper proposes a novel method based on an improved image-set matching approach, which makes use of Graph-Embedding Discriminant Analysis.
+In contrast to the state-of-the-art methods, which operate on single input images, our method makes, use of explicit image set matching which renders it robust computationally.
+Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
+This paper proposed an automated fish species identification system based on a modified crow search optimization algorithm.
+Median filtering is applied for image smoothing and removing noise through reducing the variation of intensities between the neighbors.
+Then, a k-mean clustering algorithm is used to segment the fish image into multiple segments.
+Shape-based and texture-based feature extraction process for classification is presented.
+A new modified binary version of crow search algorithm is proposed to reduce the data dimensionality of the extracted features.
+Finally, support vector machine and decision trees are implemented for classification and the fish species are classified based on either their class including Actinopterygii and Chondrichthyes or based on their order.
+Total of 270 images with different species, classes and orders are used for evaluation of the proposed system.
+The experimental results show that the proposed system achieves the highest classification accuracy compared to state-of-the-art algorithms.
+Also, the results show that the overall fish species identification system obtains on average of 10 folds, 96% classification accuracy for classification based on class and 74% for classification based on fish order.
 Alsmadi 2019 \cite{Alsmadi2019RFE},
-Hasija 2017 \cite{Hasija2017FishSC},
-Hu 2012 \cite{HuJing2012Fscb},
+Based on feature selection and combination theory between major extracted features, this study attempts to establish a system that could recognize fish object within the image utilizing texture, anchor points, and statistical measurements.
+Then, a generic fish classification is executed with the application of an innovative classification evaluation through a meta-heuristic algorithm known as Memetic Algorithm (Genetic Algorithm with Simulated Annealing) with back-propagation algorithm (MA-B Classifier).
+Sharmin 2019 \cite{Sharmin2019MVB},
+the new generation people of Bangladesh lacks the knowledge of local freshwater fish.
+For this problem, a solution has been found with the collaboration of vision-based technology.
+As a solution, a machine-vision based local freshwater fish recognition system is presented that can be proceed with an image of fish captured with a mobile or handheld device and recognize the fish in order to introduce the fish.
+To demonstrate the utility of the proposed expert system, several experiments are performed.
+At first, a set of fourteen features, which consists of four types of features, are presented.
+Then the color image has been converted into gray-scale image and the gray-scale histogram is formed.
+Image segmentation takes place using histogram-based method and then the features are extracted.
+PCA is used for decreasing the feature numbers.
+Three classifiers are used for recognizing fish, where SVM gives the highest accuracy showing a value of 94.2%.
+Banan 2020 \cite{Banan2020DeepLA}
+Hence, in this study, a deep learning neural network as a smart, real-time and non-destructive method was developed and applied to automate the identification of four economically important carp species namely common carp (Cyprinus carpio), grass carp (Ctenopharingodon idella), bighead carp (Hypophtalmichthys nobilis) and silver carp (Hypophthalmichthys molitrix).
+The obtained results proved that our approach, evaluated through 5-fold cross-validation, achieved the highest possible accuracy of 100 %.
+The achieved high level of classification accuracy was due to the ability of the suggested deep model to build a hierarchy of self-learned features, which was in accordance with the hierarchy of these fish’s identification keys.
+In conclusion, the proposed convolutional neural network (CNN)-based method has a single and generic trained architecture with promising performance for fish species identification.
 Iqbal 2021 \cite{Iqbal2021AutomaticFS},
-Iscimen 2014 \cite{Iscimen2014ImageAM},
-Iscimen 2015 \cite{Iscimen2015ClassificationOF},
-Kinjo 2014 \cite{KinjoAtsushi2014Scoi},
-Li 2014 \cite{Li2014IdentificationOF}
-
-Orientation, Size and Weight and Shape\newline
+In this paper, we presented an automated system for identification and classification of fish species.
+It helps the marine biologists to have greater understanding of the fish species and their habitats.
+The proposed model is based on deep convolutional neural networks.
+It uses a reduced version of AlexNet model comprises of four convolutional layers and two fully connected layers.
+A comparison is presented against the other deep learning models such as AlexNet and VGGNet.
+The four parameters are considered that is number of convolu- tional layers and number of fully-connected layers, number of iterations to achieve 100% accuracy on training data, batch size and dropout layer.
+The results show that the proposed and modified AlexNet model with less number of layers has achieved the testing accuracy of 90.48% while the original AlexNet model achieved 86.65% over the untrained bench- mark fish dataset.
+The inclusion of dropout layer has enhanced the overall performance of our proposed model.
+It contain less training images, less memory and it is also less compu- tational complex.
+Xu 2021 \cite{Xu2021TransferLA},
+Scientific studies on species identification in fish have considerable significance in aquatic ecosystems and quality evaluation.
+The morphological differences between different fish species are obvious.
+Machine learning methods use artificial prior knowledge to extract fish features, which is time-consuming, laborious, and subjective.
+Recently, deep learning-based identification of fish species has been widely used.
+However, fish species identification still faces many challenges due to the small scale of fish samples and the imbalance of the number of categories.
+For example, the model is prone to being overfitted, and the performance of the classifier is biased to the fish species of most samples.
+To solve the above problems, this paper proposes a fish species identification approach based on SE-ResNet152 and class-balanced focal loss.
+First, visualization analysis and image preprocessing of fish datasets are carried out.
+Second, the SE-ResNet152 model is constructed as a generalized feature extractor and is migrated to the target dataset.
+Finally, we apply the class-balanced focal loss function to train the SE-ResNet152 model, and realize fish species identification on three fish image views (body, head, and scale).
+The proposed method was tested on the Fish-Pak public dataset and achieved 98.80%, 96.67%, and 91.25% accuracy on the three fish image views, respectively.
+To ensure the superior performance of the proposed method, we performed an experimental comparison with other methods involving SENet154, DenseNet121, ResNet18, ResNet152, VGG16, cross-entropy, and focal loss.
+Comprehensive empirical analyses reveal that the proposed method achieves good performance on the three fish image views and outperforms common methods.
+
+\textbf{Orientation, Length, Size, Weight and Shape}\newline
 Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
+Fish processing in small and medium fish supplying centers requires an intelligent system to operate on different sizes.
+Therefore, an image processing algorithm was developed to extract the proper head and belly cutting points according to the trout dimensions.
+The algorithm detects the fish orientation and location of pectoral, anal, pelvic, and caudal fins.
+In this study, each of the trout images was divided into slices along its length in order to segment the fins and extract cutting points.
+The channel ‘B’ of RGB color space was considered in both initial segmentation and fin detection stages among the examined channels of RGB, HSV, and L*a*b* color spaces.
+The back-belly and head-tail sides were detected with an accuracy of 100% based on gray intensity values and head to tail ratio, respectively.
+Furthermore, performing an analysis of variance (ANOVA) resulted in an F-value of 64.82 among the fins.
+Conducting a t-test among the mean intensity values of the fins and non-fin regions of channel ‘B’ resulted in the highest distinction with t-values of 90.30, 78.07, 74.28, and 86.01 with p < 0.01 for the pectoral, pelvic, anal, and caudal fins paired with the corresponding non-fin region, respectively.
+The results showed that the selected ‘B’ channel is the adequate one for fin segmentation.
+The fin detection process showed an overall sensitivity, specificity, and accuracy of 86.05%, 99.97%, and 99.87%, respectively.
+By solving the line determination error in 8.24% and the extra object error in 4.12% of the samples, the overall fin identification accuracy was 100%.
+Finally, after extracting the fin regions, the start point of the pectoral fin and the end point of the anal fin will be applied in the trout processing system as the head and belly cutting points, respectively.
+
 Balaban 2010 \cite{Balaban2010UsingIA},
-Wang 2015 \cite{Huihui2015StudyOT},
-Hao 2015 \cite{Hao2015TheMO},
+After harvesting , salmon is sorted by species, size, and quality.
+This is generally manually done by op-erators.
+Automation would bring repeatability, objectivity, and record-keeping capabilities to these tasks.
+Machinevision (MV) and image analysis have been used in sorting many agricultural products.
+Four salmon species weretested: pink (Oncorhynchus gorbuscha), red (Oncorhynchus nerka), silver (Oncorhynchus kisutch), and chum (On-corhynchus keta).
+A total of 60 whole fish from each species were first weighed, then placed in a light box to taketheir picture.
+Weight compared with view area as well as length and width correlations were developed.
+In additionthe effect of “hump” development (see text) of pink salmon on this correlation was investigated.
+It was possible topredict the weight of a salmon by view area, regardless of species, and regardless of the development of a humpfor pinks.
+Within pink salmon there was a small but insignificant difference between predictive equations for theweight of “regular” fish and “humpy” fish.
+Machine vision can accurately predict the weight of whole salmon forsorting.
+
+Hao 2015 \cite{Hao2015TheMO}, A REVIEW
+This study reviewed the methods of fish size measurement through machine vision.
+Length and area are important information that can help fishers manage fish scientifically and conveniently.
+This information could be used to calculate the volume and weight according to their relation; other information could also be calculated.
+Machine vision is more effective, economical and faster than traditional methods.
+
+Konovalov 2017 \cite{KonovalovD2017RDfA},
+Fast and low cost image collection and processing is often required in aquaculture farms for quality/size attributes and breeding programs.
+For example, the absolute physical dimensions of fish (in millimeters or inches) could be estimated from electronic images.
+The absolute scale of the photographed fish is often unknown or requires additional hardware, data- collection and/or management overheads.
+One cost and time effective solution is to capture the absolute scale (in pixels-per- millimeter or dots-per-inch) by including a measuring ruler in the photographed scene.
+To assist that type of workflow, we designed a relatively simple image-processing algorithm that automatically located a sufficiently large section of the ruler in a given image.
+The algorithm utilized the Fast Fourier Transform and was designed to be free from adjustable parameters and therefore did not require training or calibration.
+The algorithm was tested on 445 images of Barramundi (Asian sea bass, Lates calcarifer), where a millimeter-graded ruler was included in each image.
+The algorithm achieved precision of 98% (on the original, 10, 20, 70, 80 90 degree rotated images) and 95-96% on 40, 50, 60 degree rotated images.
+\newline
 Konovalov 2018 \cite{Konovalov2018AutomaticSO},
+In aquaculture breeding programs where large numbers of fish need to be rapidly phenotyped, the absolute physical dimensions of fish (in millimeters or inches) are often required to be extracted from electronic images in order to measure the size of the fish.
+While it is possible to infer the length of the fish in pixels, the absolute scale of the image (in pixels-per-millimeter or dots-per- inch) is largely unknown without a reference grid, or requires additional hardware, data collection and/or record-keeping management overheads.
+One cost and time effective solution is to capture the absolute scale by including a measuring ruler in the photographed scene and from which a computer program can automatically identify the scale of the photo and calculate fish morphometric measurements.
+To assist such workflow, this study developed an algorithm that automatically detects a ruler in a given image, and automatically extracts its scale as distance (in fractional number of pixels) betw.
+The algorithm was applied to 445 publicly available images of barramundi or Asian seabass (Lates calcarifer), where a millimeter-graded ruler was included in each image.
+Convolutional Neural Network (CNN) was trained to segment the images into ruler, background, fish and label sections.
+Then the distance-extraction algorithm was applied to the ruler section of the images.
+The false-negative rate was less than 2%, where the ruler graduation distances could not be extracted in only 2-6 (out of 445) images even when the test images were rotated up to 90 degrees.
+The mean absolute relative error (MARE) of the inferred distances was 1-2%.\newline
 Konovalov 2019 \cite{Konovalov2019AutomaticWE},
-
-Ruler Detection\newline
-Konovalov 2017 \cite{KonovalovD2017RDfA},
-
-Fish Quality\newline
-Bernardo 2020 \cite{Bernardo2020FishQI},
-Dowlati 2012 \cite{Dowlati2012ApplicationOM},
+Approximately 2,500 weights and corresponding images of harvested Lates calcarifer (Asian seabass or barra- mundi) were collected at three different locations in Queensland, Australia.
+Two instances of the LinkNet-34 segmentation Convo- lutional Neural Network (CNN) were trained.
+The first one was trained on 200 manually segmented fish masks with excluded fins and tails.
+The second was trained on 100 whole-fish masks.
+The two CNNs were applied to the rest of the images and yielded automatically segmented masks.
+The one-factor and two-factor simple mathematical weight-from-area models were fitted on 1072 area-weight pairs from the first two locations, where area values were extracted from the automatically segmented masks.
+When applied to 1,400 test images (from the third location), the one- factor whole-fish mask model achieved the best mean absolute percentage error (MAPE), MAPE = 4.36%.
+Direct weight-from- image regression CNNs were also trained, where the no-fins based CNN performed best on the test images with MAPE = 4.28%.
+
+\textbf{Fish Quality}\newline
 Lalabadi 2020 \cite{Lalabadi2020FishFC},
-
-3D Segmentation from microCT\newline
-Bock 2018 \cite{BockAlexander2018TITE},
-
-Computer Vision Overviews Related to Fish\newline
-G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
-
+Developing new techniques to determine fish freshness and quality can enhance nutritional value of the overall household food basket.
+In this research, digital image analysis was utilized to assess the freshness of rainbow trout fish by tracing the color attributes of its eyes and gills.
+The image data were collected from left and right eyes and gills in a 10-day ice-storage duration, and color components were extracted in RGB, HSV, and L*a*b* color spaces.
+Analysis of variance revealed that the RGB components of both eyes and gills had a significant change towards getting brighter during the ice-storage.
+Feature extraction was fulfilled from the color spaces, and then artificial neural networks (ANNs) and support vector machines (SVMs) were applied for classification of the ice-storage durations.
+The overall accuracies of the developed models demonstrated that the ANN somewhat outperformed the SVM for both the extracted features from the eyes and gills.
+Moreover, the gills’ features could describe the variance in the storage durations more efficiently than those extracted from the eyes.
+Finally, it was concluded that the applied colorimetric system along with the developing models could be employed as a successful non-destructive approach for evaluation of fish freshness.
+
+Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
+In the current research, the potential of a novel method based on the artificial neural network was investigated to diagnose the freshness of common carp (Cyprinus carpio) during ice storage.
+Fish as an aquaculture product has high nutrients and low-fat content.
+So, people have consumed it as a safe and high-value foodstuff in their daily diet.
+Investigation of fish freshness is proposed as a significant issue in the aquaculture industry since fish spoils rapidly.
+The applied system of this study is comprised of the following steps: First, images of samples were captured and the pre-processing operation was done on the images.
+Then, particular channels including R, G, B, H, S, I, L*, a*, and b* were computed.
+Next, feature extraction was performed to obtain 6 types of texture features from each channel.
+Afterward, the hybrid Artificial Bee Colony-Artificial Neural Network (ABC-ANN) algorithm was applied to select the best features.
+Finally, the Support Vector Machine (SVM), K-Nearest Neighbor (K-NN) and Artificial Neural Network (ANN) algorithms as the most common methods were used to classify fish images.
+The best performance of the K-NN classifier was calculated in the k = 8 neighborhood size with the accuracy of 90.48.
+The best kernel function for the SVM algorithm was polynomial with C, sigma, and accuracy of 1, 2 and 91.52 percent, respectively.
+In this system, the input layer has consisted of 22 neurons based on the feature selection operation and 4 classes including most fresh, fresh, fairly fresh and spoiled have been used as the number of output layer.
+At the end, the best results of the MLP networks were achieved by LM learning algorithm and 6 neurons in the hidden layer with the 22–10–4 topology and accuracy of 93.01 percent.
+The achieved results demonstrate the high performance of the ANN classifier for evaluation of common carp freshness during ice storage as a rapid, accurate, non-destructive, real-time and automated method.
+It shows the potential of computer vision method in combination with artificial neural networks as an intelligent technique for evaluation of fish freshness.
+
+Tappi 2017 \cite{Tappi2017ComputerVS},
+The evaluation of fish freshness can be per- formed using chemical, sensory and physical methods.
+Besides sensory methods, several instrumental techniques have been applied with the objective of replacing sensory assessment.
+The aim of this study was to set up and test objective physical methods mainly based on computer vision system (CVS) to assess red mullet (Mullus barba- tus) freshness evolution during 10 days of storage, at two different storage temperatures (0 and 4 °C).
+To check the effectiveness of the purposed physical methods, CVS fea- tures (loss in the epidermis pigmentation, development of gill mucus and eye concavity index) and firmness have been compared with chemical trimethylamine content and sensory (QIM) attribute scores.
+As expected, fish degrada- tion was faster at the higher temperature.
+Instrumental tex- ture evaluation of fish by penetration test enabled to detect distinctive firmness changes due to onset and resolution of rigor mortis, and the successive tenderization phenomenon.
+Among CVS parameters, the epidermis pigmentation loss, and particularly the eye shape modification (eye concavity index) evidenced a high sensibility for the estimation of fresh red mullet quality loss, as a function of the two differ- ent storage conditions, and a good agreement with trimeth- ylamine content and QIM response evolution.
+
+\textbf{Unbending a Fish}\newline
+Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
 Williams 2020 \cite{Williams:2020:UIF},
-Saberioon 2017 \cite{Saberioon2017ApplicationOM},
-Tappi 2017 \cite{Tappi2017ComputerVS},
-Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
-Lugatiman 2019 \cite{Lugatiman2019TunaMF},
-Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
-Petrov 2020 \cite{Petrov2020Overview},
-Miranda 2017 \cite{MIRANDA201741},
-Zion 2000 \cite{Zion2000InvivoFS},
-Zion 2012 \cite{Zion2012ReviewTU},
-Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
-Sung 2017 \cite{Sung2017VisionBR},
-Sharmin 2019 \cite{Sharmin2019MVB},
-Salman 2016 \cite{Salman2016FishSC},
-Sung 2020 \cite{Sung2020AutomaticGF},
-Xu 2021 \cite{Xu2021TransferLA},
-Banan 2020 \cite{Banan2020Deep,LA}
-Ogunlana 2015 \cite{Ogunlana2015FCU},
-Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
-Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
-Shah 2019 \cite{Shah2019FishPakFS},
 

### 2021-03-29 paper/paper.tex

@@
 
+3D Segmentation from microCT\newline
+Bock 2018 \cite{BockAlexander2018TITE},
+
+Computer Vision Overviews Related to Fish\newline
+G{\"u}m{\"u}\c{s} 2011 \cite{Gm2011MachineVA},
+
 Tappi 2017 \cite{Tappi2017ComputerVS},
@@
 Among CVS parameters, the epidermis pigmentation loss, and particularly the eye shape modification (eye concavity index) evidenced a high sensibility for the estimation of fresh red mullet quality loss, as a function of the two differ- ent storage conditions, and a good agreement with trimeth- ylamine content and QIM response evolution.
+Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
+Lugatiman 2019 \cite{Lugatiman2019TunaMF},
+Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
+Petrov 2020 \cite{Petrov2020Overview},
+Miranda 2017 \cite{MIRANDA201741},
+Zion 2000 \cite{Zion2000InvivoFS},
+Zion 2012 \cite{Zion2012ReviewTU},
+Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
+Sung 2017 \cite{Sung2017VisionBR},
+Sharmin 2019 \cite{Sharmin2019MVB},
+Salman 2016 \cite{Salman2016FishSC},
+Sung 2020 \cite{Sung2020AutomaticGF},
+Xu 2021 \cite{Xu2021TransferLA},
+Banan 2020 \cite{Banan2020DeepLA}
+Ogunlana 2015 \cite{Ogunlana2015FCU},
+Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
+Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
+Shah 2019 \cite{Shah2019FishPakFS},
 

### 2021-03-29 paper/paper.tex
Updates from Overleaf
Wrapped up first pass on Fish Image Analysis section.

--- 2021-03-28 paper/paper.tex
@@
 \usepackage{comment}
+\usepackage{wrapfig}
 %%
@@
 
-Fish Classification\newline
-Alsmadi 2010 \cite{Alsmadi2010FishRB},
-Alsmadi 2019 \cite{Alsmadi2019RFE},
-Hasija 2017 \cite{Hasija2017FishSC},
-Hu 2012 \cite{HuJing2012Fscb},
-Iqbal 2021 \cite{Iqbal2021AutomaticFS},
-Iscimen 2014 \cite{Iscimen2014ImageAM},
-Iscimen 2015 \cite{Iscimen2015ClassificationOF},
-Kinjo 2014 \cite{KinjoAtsushi2014Scoi},
-Li 2014 \cite{Li2014IdentificationOF}
-
-Orientation, Size and Weight and Shape\newline
-Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
-Balaban 2010 \cite{Balaban2010UsingIA},
-Wang 2015 \cite{Huihui2015StudyOT},
-Hao 2015 \cite{Hao2015TheMO},
-Konovalov 2018 \cite{Konovalov2018AutomaticSO},
-Konovalov 2019 \cite{Konovalov2019AutomaticWE},
-
-Ruler Detection\newline
-Konovalov 2017 \cite{KonovalovD2017RDfA},
-
-Fish Quality\newline
-Bernardo 2020 \cite{Bernardo2020FishQI},
-Dowlati 2012 \cite{Dowlati2012ApplicationOM},
-Lalabadi 2020 \cite{Lalabadi2020FishFC},
-
-3D Segmentation from microCT\newline
-Bock 2018 \cite{BockAlexander2018TITE},
-
-Computer Vision Overviews Related to Fish\newline
-G{\"u}m{\"u}\c{s} 2011 \cite{Gm2011MachineVA},
-
-Williams 2020 \cite{Williams:2020:UIF},
-Saberioon 2017 \cite{Saberioon2017ApplicationOM},
-Tappi 2017 \cite{Tappi2017ComputerVS},
-Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
-Lugatiman 2019 \cite{Lugatiman2019TunaMF},
-Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
-Petrov 2020 \cite{Petrov2020Overview},
-Miranda 2017 \cite{MIRANDA201741},
-Zion 2000 \cite{Zion2000InvivoFS},
-Zion 2012 \cite{Zion2012ReviewTU},
-Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
-Sung 2017 \cite{Sung2017VisionBR},
-Sharmin 2019 \cite{Sharmin2019MVB},
-Salman 2016 \cite{Salman2016FishSC},
-Sung 2020 \cite{Sung2020AutomaticGF},
-Xu 2021 \cite{Xu2021TransferLA},
-Banan 2020 \cite{Banan2020DeepLA}
-Ogunlana 2015 \cite{Ogunlana2015FCU},
-Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
-Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
-Shah 2019 \cite{Shah2019FishPakFS},
+Image analysis has been utilized to examine and process images of fish
+for well over two decades \cite{Zion2000InvivoFS,Saberioon2017ApplicationOM}. It is an important
+application of technology both for marine science, in the study of aquatic
+species, habitats and ecosystems, and for food the industry, in the
+development of automated fish sorting and grading systems, as well as
+fisheries management. Many of these computational analyses focus on
+the recognition and classification 
+of the fish present in an image.  The computational methods employed for
+fish image analysis followed the general trends in the field.
+Hu et al.~\cite{HuJing2012Fscb} presented a method of classifying species
+of fish based on color and texture features and used a multi-class support
+vector machine (MSVM) \cite{Vapnik1999AOS}.
+Li and Hong \cite{Li2014IdentificationOF} computed eleven shape and color
+features from fish images that were distilled down to four, using Principal
+Component Analysis, and derived a linear model from these four features
+that could discriminate between four different fishes.
+%  Kinda unimpressive. Let's leave out.
+% Saitoh \cite{Saitoh2015ImagebasedFR}
+% utilized a Random Forest method \cite{Breiman2001RF} on manually-derived
+% geometric, Bag of visual words (BoVW) and color features 
+Rodrigues et al.~\cite{RodriguesMarcoT.A2015Ecda} explored several
+combinations of features extraction, input classifiers and clustering
+algorithms to produce a method that could distinguish between 10 different
+types of fish with a 92\% accuracy.
+%  Again, not too impressive. Let's leave out.
+% Ogunlana 2015 \cite{Ogunlana2015FCU},
+% In this paper, a Support Vector Machine (SVM)-based technique for the elimination of the limitations of some existing techniques and improved classification of fish species is proposed.
+The technique is based on the shape features of fish that was divided into two subsets with the first comprising 76 fish as training set while the second comprises of 74 fish as testing set.
+The body and the five fin lengths; namely anal, caudal, dorsal, pelvic and pectoral were extracted in centimeter (cm).
+Results based on the new technique show a classification accuracy of 78.59%, which is significantly higher than what obtained for ANN, KNN and K-mean clustering-based algorithms.
+Salman et al.~\cite{Salman2016FishSC} employed a deep Convolution Neural
+Networks (CNN) \cite{LeCun2004LMG} together with classification based on
+K-Nearest Neighbor and Support Vector Machines trained on the features
+extracted by the CNN in supervised deep learning. They achieved 90\%
+accuracy when identifying 15 different fish in challenging underwater
+digital images.
+% Unimpressive. Do not include.
+% Sung 2017 \cite{Sung2017VisionBR},
+% Underwater vision has specific characteristics such as high attenuation of lights, severe noise and haze in the images.
+For real-time fish detection using underwater vision, this paper proposes convolutional neural network based techniques based on You Only Look Once algorithm.
+Actual fish video images were used to evaluate the reliability and accuracy of the proposed method.
+As a result, the network recorded 93% classification accuracy, 0.634 intersection over union between predicted bounding box and ground truth, and 16.7 frames per second of fish detection.
+It also outperforms another fish detector using sliding window algorithm and classifier trained with histogram of oriented gradient features and support vector machine.
+% Not digging it.
+% Hasija 2017 \cite{Hasija2017FishSC},
+% This paper proposes a novel method based on an improved image-set matching approach, which makes use of Graph-Embedding Discriminant Analysis.
+In contrast to the state-of-the-art methods, which operate on single input images, our method makes, use of explicit image set matching which renders it robust computationally.
+% Not this one either
+% Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
+% This paper proposed an automated fish species identification system based on a modified crow search optimization algorithm.
+Median filtering is applied for image smoothing and removing noise through reducing the variation of intensities between the neighbors.
+Then, a k-mean clustering algorithm is used to segment the fish image into multiple segments.
+Shape-based and texture-based feature extraction process for classification is presented.
+A new modified binary version of crow search algorithm is proposed to reduce the data dimensionality of the extracted features.
+Finally, support vector machine and decision trees are implemented for classification and the fish species are classified based on either their class including Actinopterygii and Chondrichthyes or based on their order.
+Total of 270 images with different species, classes and orders are used for evaluation of the proposed system.
+The experimental results show that the proposed system achieves the highest classification accuracy compared to state-of-the-art algorithms.
+Also, the results show that the overall fish species identification system obtains on average of 10 folds, 96% classification accuracy for classification based on class and 74% for classification based on fish order.
+Utilizing texture, anchor points, and statistical measurements,
+Alsmadi et al.~\cite{Alsmadi2019RFE} implemented fish
+classification through a meta-heuristic algorithm known as Memetic Algorithm (Genetic Algorithm with Simulated Annealing) with back-propagation algorithm (MA-B Classifier).
+They were able to classify 24 fish families with 90\%
+accuracy.
+% Nope
+% Sharmin 2019 \cite{Sharmin2019MVB},
+% the new generation people of Bangladesh lacks the knowledge of local freshwater fish.
+For this problem, a solution has been found with the collaboration of vision-based technology.
+As a solution, a machine-vision based local freshwater fish recognition system is presented that can be proceed with an image of fish captured with a mobile or handheld device and recognize the fish in order to introduce the fish.
+To demonstrate the utility of the proposed expert system, several experiments are performed.
+At first, a set of fourteen features, which consists of four types of features, are presented.
+Then the color image has been converted into gray-scale image and the gray-scale histogram is formed.
+Image segmentation takes place using histogram-based method and then the features are extracted.
+PCA is used for decreasing the feature numbers.
+Three classifiers are used for recognizing fish, where SVM gives the highest accuracy showing a value of 94.2%.
+%  I want to see the paper before I cite it.
+% Banan 2020 \cite{Banan2020DeepLA}
+% Hence, in this study, a deep learning neural network as a smart, real-time and non-destructive method was developed and applied to automate the identification of four economically important carp species namely common carp (Cyprinus carpio), grass carp (Ctenopharingodon idella), bighead carp (Hypophtalmichthys nobilis) and silver carp (Hypophthalmichthys molitrix).
+The obtained results proved that our approach, evaluated through 5-fold cross-validation, achieved the highest possible accuracy of 100 %.
+The achieved high level of classification accuracy was due to the ability of the suggested deep model to build a hierarchy of self-learned features, which was in accordance with the hierarchy of these fish’s identification keys.
+In conclusion, the proposed convolutional neural network (CNN)-based method has a single and generic trained architecture with promising performance for fish species identification.
+Iqbal et al.~\cite{Iqbal2021AutomaticFS} used a modified
+AlexNet \cite{AlexNet2012} model to classify six different fish species
+with 90\% accuracy.
+% In this paper, we presented an automated system for identification and classification of fish species.
+It helps the marine biologists to have greater understanding of the fish species and their habitats.
+The proposed model is based on deep convolutional neural networks.
+It uses a reduced version of AlexNet model comprises of four convolutional layers and two fully connected layers.
+A comparison is presented against the other deep learning models such as AlexNet and VGGNet.
+The four parameters are considered that is number of convolu- tional layers and number of fully-connected layers, number of iterations to achieve 100% accuracy on training data, batch size and dropout layer.
+The results show that the proposed and modified AlexNet model with less number of layers has achieved the testing accuracy of 90.48% while the original AlexNet model achieved 86.65% over the untrained bench- mark fish dataset.
+The inclusion of dropout layer has enhanced the overall performance of our proposed model.
+It contain less training images, less memory and it is also less compu- tational complex.
+%  No paper. No reference
+% Xu 2021 \cite{Xu2021TransferLA},
+% Scientific studies on species identification in fish have considerable significance in aquatic ecosystems and quality evaluation.
+The morphological differences between different fish species are obvious.
+Machine learning methods use artificial prior knowledge to extract fish features, which is time-consuming, laborious, and subjective.
+Recently, deep learning-based identification of fish species has been widely used.
+However, fish species identification still faces many challenges due to the small scale of fish samples and the imbalance of the number of categories.
+For example, the model is prone to being overfitted, and the performance of the classifier is biased to the fish species of most samples.
+To solve the above problems, this paper proposes a fish species identification approach based on SE-ResNet152 and class-balanced focal loss.
+First, visualization analysis and image preprocessing of fish datasets are carried out.
+Second, the SE-ResNet152 model is constructed as a generalized feature extractor and is migrated to the target dataset.
+Finally, we apply the class-balanced focal loss function to train the SE-ResNet152 model, and realize fish species identification on three fish image views (body, head, and scale).
+The proposed method was tested on the Fish-Pak public dataset and achieved 98.80%, 96.67%, and 91.25% accuracy on the three fish image views, respectively.
+To ensure the superior performance of the proposed method, we performed an experimental comparison with other methods involving SENet154, DenseNet121, ResNet18, ResNet152, VGG16, cross-entropy, and focal loss.
+Comprehensive empirical analyses reveal that the proposed method achieves good performance on the three fish image views and outperforms common methods.
+
+% \textbf{Orientation, Length, Size, Weight and Shape}\newline
+Especially in industrial settings it is necessary to automatically
+detect the orientation, length and weight of fish during handling
+and processing.
+In some instances it is necessary to computationally straighten the
+fish in the images \cite{MuozBenavent2018EnhancedFB} before further
+processing can be attempted.
+Balaban et al.~\cite{Balaban2010UsingIA} demonstrated that image analysis
+and data fitting may be used to predict the weight of salmons with high
+accuracy.
+% After harvesting , salmon is sorted by species, size, and quality.
+This is generally manually done by op-erators.
+Automation would bring repeatability, objectivity, and record-keeping capabilities to these tasks.
+Machinevision (MV) and image analysis have been used in sorting many agricultural products.
+Four salmon species weretested: pink (Oncorhynchus gorbuscha), red (Oncorhynchus nerka), silver (Oncorhynchus kisutch), and chum (On-corhynchus keta).
+A total of 60 whole fish from each species were first weighed, then placed in a light box to taketheir picture.
+Weight compared with view area as well as length and width correlations were developed.
+In additionthe effect of “hump” development (see text) of pink salmon on this correlation was investigated.
+It was possible topredict the weight of a salmon by view area, regardless of species, and regardless of the development of a humpfor pinks.
+Within pink salmon there was a small but insignificant difference between predictive equations for theweight of “regular” fish and “humpy” fish.
+Machine vision can accurately predict the weight of whole salmon forsorting.
+% Konovalov 2017 \cite{KonovalovD2017RDfA},
+% Fast and low cost image collection and processing is often required in aquaculture farms for quality/size attributes and breeding programs.
+For example, the absolute physical dimensions of fish (in millimeters or inches) could be estimated from electronic images.
+The absolute scale of the photographed fish is often unknown or requires additional hardware, data- collection and/or management overheads.
+One cost and time effective solution is to capture the absolute scale (in pixels-per- millimeter or dots-per-inch) by including a measuring ruler in the photographed scene.
+To assist that type of workflow, we designed a relatively simple image-processing algorithm that automatically located a sufficiently large section of the ruler in a given image.
+The algorithm utilized the Fast Fourier Transform and was designed to be free from adjustable parameters and therefore did not require training or calibration.
+The algorithm was tested on 445 images of Barramundi (Asian sea bass, Lates calcarifer), where a millimeter-graded ruler was included in each image.
+The algorithm achieved precision of 98% (on the original, 10, 20, 70, 80 90 degree rotated images) and 95-96% on 40, 50, 60 degree rotated images.
+\newline
+% Konovalov 2018 \cite{Konovalov2018AutomaticSO},
+% In aquaculture breeding programs where large numbers of fish need to be rapidly phenotyped, the absolute physical dimensions of fish (in millimeters or inches) are often required to be extracted from electronic images in order to measure the size of the fish.
+While it is possible to infer the length of the fish in pixels, the absolute scale of the image (in pixels-per-millimeter or dots-per- inch) is largely unknown without a reference grid, or requires additional hardware, data collection and/or record-keeping management overheads.
+One cost and time effective solution is to capture the absolute scale by including a measuring ruler in the photographed scene and from which a computer program can automatically identify the scale of the photo and calculate fish morphometric measurements.
+To assist such workflow, this study developed an algorithm that automatically detects a ruler in a given image, and automatically extracts its scale as distance (in fractional number of pixels) betw.
+The algorithm was applied to 445 publicly available images of barramundi or Asian seabass (Lates calcarifer), where a millimeter-graded ruler was included in each image.
+Convolutional Neural Network (CNN) was trained to segment the images into ruler, background, fish and label sections.
+Then the distance-extraction algorithm was applied to the ruler section of the images.
+The false-negative rate was less than 2%, where the ruler graduation distances could not be extracted in only 2-6 (out of 445) images even when the test images were rotated up to 90 degrees.
+The mean absolute relative error (MARE) of the inferred distances was 1-2%.\newline
+Konovalov et al.~\cite{Konovalov2019AutomaticWE} presented a method for
+accurate automatic weight estimation of fish using a Convolutional Neural
+Network (CNN), data fitting, and ruler detection/measurement
+method \cite{Konovalov2018AutomaticSO}.
+% Approximately 2,500 weights and corresponding images of harvested Lates calcarifer (Asian seabass or barra- mundi) were collected at three different locations in Queensland, Australia.
+Two instances of the LinkNet-34 segmentation Convo- lutional Neural Network (CNN) were trained.
+The first one was trained on 200 manually segmented fish masks with excluded fins and tails.
+The second was trained on 100 whole-fish masks.
+The two CNNs were applied to the rest of the images and yielded automatically segmented masks.
+The one-factor and two-factor simple mathematical weight-from-area models were fitted on 1072 area-weight pairs from the first two locations, where area values were extracted from the automatically segmented masks.
+When applied to 1,400 test images (from the third location), the one- factor whole-fish mask model achieved the best mean absolute percentage error (MAPE), MAPE = 4.36%.
+Direct weight-from- image regression CNNs were also trained, where the no-fins based CNN performed best on the test images with MAPE = 4.28%.
+Hao et al.~\cite{Hao2015TheMO} provide an excellent review of fish
+measurement by machine visions efforts.
+% This study reviewed the methods of fish size measurement through machine vision.
+Length and area are important information that can help fishers manage fish scientifically and conveniently.
+This information could be used to calculate the volume and weight according to their relation; other information could also be calculated.
+Machine vision is more effective, economical and faster than traditional methods.
+Azarmdel et al.~\cite{Azarmdel2019DevelopingAO} developed a system
+capable of determining the orientation of a trout and segmenting its fins,
+which are used as cutting points, with an accuracy over 99\%.
+% Fish processing in small and medium fish supplying centers requires an intelligent system to operate on different sizes.
+Therefore, an image processing algorithm was developed to extract the proper head and belly cutting points according to the trout dimensions.
+The algorithm detects the fish orientation and location of pectoral, anal, pelvic, and caudal fins.
+In this study, each of the trout images was divided into slices along its length in order to segment the fins and extract cutting points.
+The channel ‘B’ of RGB color space was considered in both initial segmentation and fin detection stages among the examined channels of RGB, HSV, and L*a*b* color spaces.
+The back-belly and head-tail sides were detected with an accuracy of 100% based on gray intensity values and head to tail ratio, respectively.
+Furthermore, performing an analysis of variance (ANOVA) resulted in an F-value of 64.82 among the fins.
+Conducting a t-test among the mean intensity values of the fins and non-fin regions of channel ‘B’ resulted in the highest distinction with t-values of 90.30, 78.07, 74.28, and 86.01 with p < 0.01 for the pectoral, pelvic, anal, and caudal fins paired with the corresponding non-fin region, respectively.
+The results showed that the selected ‘B’ channel is the adequate one for fin segmentation.
+The fin detection process showed an overall sensitivity, specificity, and accuracy of 86.05%, 99.97%, and 99.87%, respectively.
+By solving the line determination error in 8.24% and the extra object error in 4.12% of the samples, the overall fin identification accuracy was 100%.
+Finally, after extracting the fin regions, the start point of the pectoral fin and the end point of the anal fin will be applied in the trout processing system as the head and belly cutting points, respectively.
+
+Another application of image analysis to fish images is the evaluation
+fish freshness, a computation usually performed on the color features of
+the images.
+Tappi et al.~\cite{Tappi2017ComputerVS} assees the freshness of frozen
+fish by computing a change of color and an eye concavity index.
+% The evaluation of fish freshness can be per- formed using chemical, sensory and physical methods.
+Besides sensory methods, several instrumental techniques have been applied with the objective of replacing sensory assessment.
+The aim of this study was to set up and test objective physical methods mainly based on computer vision system (CVS) to assess red mullet (Mullus barba- tus) freshness evolution during 10 days of storage, at two different storage temperatures (0 and 4 °C).
+To check the effectiveness of the purposed physical methods, CVS fea- tures (loss in the epidermis pigmentation, development of gill mucus and eye concavity index) and firmness have been compared with chemical trimethylamine content and sensory (QIM) attribute scores.
+As expected, fish degrada- tion was faster at the higher temperature.
+Instrumental tex- ture evaluation of fish by penetration test enabled to detect distinctive firmness changes due to onset and resolution of rigor mortis, and the successive tenderization phenomenon.
+Among CVS parameters, the epidermis pigmentation loss, and particularly the eye shape modification (eye concavity index) evidenced a high sensibility for the estimation of fresh red mullet quality loss, as a function of the two differ- ent storage conditions, and a good agreement with trimeth- ylamine content and QIM response evolution.
+Taheri-Garavand et al.~\cite{TaheriGaravand2019RealtimeNM} diagnosed the 
+freshness of common carp during ice storage. They utilize color feature
+extraction and Artificial Neural Networks (ANN) to place fish in four
+freshness categories with 93\% accuracy.
+% In the current research, the potential of a novel method based on the artificial neural network was investigated to diagnose the freshness of common carp (Cyprinus carpio) during ice storage.
+Fish as an aquaculture product has high nutrients and low-fat content.
+So, people have consumed it as a safe and high-value foodstuff in their daily diet.
+Investigation of fish freshness is proposed as a significant issue in the aquaculture industry since fish spoils rapidly.
+The applied system of this study is comprised of the following steps: First, images of samples were captured and the pre-processing operation was done on the images.
+Then, particular channels including R, G, B, H, S, I, L*, a*, and b* were computed.
+Next, feature extraction was performed to obtain 6 types of texture features from each channel.
+Afterward, the hybrid Artificial Bee Colony-Artificial Neural Network (ABC-ANN) algorithm was applied to select the best features.
+Finally, the Support Vector Machine (SVM), K-Nearest Neighbor (K-NN) and Artificial Neural Network (ANN) algorithms as the most common methods were used to classify fish images.
+The best performance of the K-NN classifier was calculated in the k = 8 neighborhood size with the accuracy of 90.48.
+The best kernel function for the SVM algorithm was polynomial with C, sigma, and accuracy of 1, 2 and 91.52 percent, respectively.
+In this system, the input layer has consisted of 22 neurons based on the feature selection operation and 4 classes including most fresh, fresh, fairly fresh and spoiled have been used as the number of output layer.
+At the end, the best results of the MLP networks were achieved by LM learning algorithm and 6 neurons in the hidden layer with the 22–10–4 topology and accuracy of 93.01 percent.
+% The achieved results demonstrate the high performance of the ANN classifier for evaluation of common carp freshness during ice storage as a rapid, accurate, non-destructive, real-time and automated method.
+It shows the potential of computer vision method in combination with artificial neural networks as an intelligent technique for evaluation of fish freshness.
+A similar approach was developed by Lalabadi et al.~\cite{Lalabadi2020FishFC}.
+% Developing new techniques to determine fish freshness and quality can enhance nutritional value of the overall household food basket.
+In this research, digital image analysis was utilized to assess the freshness of rainbow trout fish by tracing the color attributes of its eyes and gills.
+The image data were collected from left and right eyes and gills in a 10-day ice-storage duration, and color components were extracted in RGB, HSV, and L*a*b* color spaces.
+Analysis of variance revealed that the RGB components of both eyes and gills had a significant change towards getting brighter during the ice-storage.
+Feature extraction was fulfilled from the color spaces, and then artificial neural networks (ANNs) and support vector machines (SVMs) were applied for classification of the ice-storage durations.
+The overall accuracies of the developed models demonstrated that the ANN somewhat outperformed the SVM for both the extracted features from the eyes and gills.
+Moreover, the gills’ features could describe the variance in the storage durations more efficiently than those extracted from the eyes.
+Finally, it was concluded that the applied colorimetric system along with the developing models could be employed as a successful non-destructive approach for evaluation of fish freshness.
+
+\begin{comment}
+\textbf{Not Used}\newline
+(Kinda vague. More about food, then fish, G{\"u}m{\"u} 2011 \cite{Gm2011MachineVA}),
+(In Turkish, Iscimen 2014 \cite{Iscimen2014ImageAM},
+Iscimen 2015 \cite{Iscimen2015ClassificationOF}),
+(Not based on images (sonar?) Kinjo 2014 \cite{KinjoAtsushi2014Scoi}),
+(Too basic, Wang 2015 \cite{Huihui2015StudyOT}),
+(Not so interesting, a very engineered, constrained imaging set up, Miranda 2017 \cite{MIRANDA201741}),
+
+(A review of all types of sensing systems for quality checkin, Bernardo 2020 \cite{Bernardo2020FishQI}),
+(Another review, but in Trends in Analytical Chemistry. I think we can 
+skip it. Not so technical, Dowlati 2012 \cite{Dowlati2012ApplicationOM}),
+
+(Simple industrial system. Computing length, Sung 2020 \cite{Sung2020AutomaticGF}),
+
+(These are 3D. Don't want to go there, Bock 2018 \cite{BockAlexander2018TITE},
+Williams 2020 \cite{Williams:2020:UIF})
+
+(A review that is not quite focused enough, Petrov 2020 \cite{Petrov2020Overview}),
+(Don't have access to it, and I have a newer review, Zion 2012 \cite{Zion2012ReviewTU}),
+\end{comment}
 
@@
 
-\begin{table}[H]
+\begin{wraptable}{r}{5.5cm}
     \centering
@@
     \end{tabular}
-\end{table}
+\end{wraptable}
 

### 2021-03-29 paper/paper.tex
Tweaked Intro
Started Goals and Objectives section

@@
 associated with the image collections.
-Poor quality images, e.g. with low contrast, inadequate lighting, out of
-focus, cluttered visual arrangements, provide inadequate input for automated
+Poor quality images, e.g. with low contrast, inadequate lighting,
+out-of-focus or cluttered visual arrangements, provide inadequate input
+for automated
 image analysis and machine learning algorithms and lead to inferior
@@
 to determine if, for instance, a specific fish grows to different lengths
-in different ecosystems.
+in different habitats.
 
@@
 Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
-As a step towards improving metadata in specimen research image collections, members of the Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
+As a step towards improving metadata in specimen research image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
 extract a set of data features that provide important metadata about the
-digital specimen.
+digitized specimen.
 The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
@@
 application of technology both for marine science, in the study of aquatic
-species, habitats and ecosystems, and for food the industry, in the
+species, habitats and ecosystems, and for the seafood industry, in the
 development of automated fish sorting and grading systems, as well as
@@
 of the fish present in an image.  The computational methods employed for
-fish image analysis followed the general trends in the field.
+fish image analysis have followed the general trends in the AI field.
 Hu et al.~\cite{HuJing2012Fscb} presented a method of classifying species
-of fish based on color and texture features and used a multi-class support
+of fish based on color and texture features and a multi-class support
 vector machine (MSVM) \cite{Vapnik1999AOS}.
@@
 features from fish images that were distilled down to four, using Principal
-Component Analysis, and derived a linear model from these four features
+Component Analysis, and derived a linear model
 that could discriminate between four different fishes.
@@
 K-Nearest Neighbor and Support Vector Machines trained on the features
-extracted by the CNN in supervised deep learning. They achieved 90\%
+extracted by the CNN. They achieved 90\%
 accuracy when identifying 15 different fish in challenging underwater
@@
 accurate automatic weight estimation of fish using a Convolutional Neural
-Network (CNN), data fitting, and ruler detection/measurement
+Network (CNN), data fitting, and a ruler detection/measurement
 method \cite{Konovalov2018AutomaticSO}.
@@
 Hao et al.~\cite{Hao2015TheMO} provide an excellent review of fish
-measurement by machine visions efforts.
+measurement efforts that utilize machine vision.
 % This study reviewed the methods of fish size measurement through machine vision.
@@
 the images.
-Tappi et al.~\cite{Tappi2017ComputerVS} assees the freshness of frozen
+Tappi et al.~\cite{Tappi2017ComputerVS} assess the freshness of frozen
 fish by computing a change of color and an eye concavity index.
@@
 
+Digitized specimen collections offer numerous outstanding opportunities
+for new scientific studies and discoveries.
+
+The amount of data is immense, with image collections containing 10,000's
+of entries. These discoveries will only be possible
+with computational techniques that can process this vast amount of data.
+
+These image-based computational techniques are hindered by both poor
+image quality and the lack of high-quality and pertinent metadata.
+
+For example, a study may require images that contain only one fish with a
+given level of lighting and contrast. Additionally, performing quantitative
+investiations into the morphology of the specimens requires knowing
+the physical scale of the images, i.e.~pixels/inch.
+
+Given the many thousands of images that have and will be acquired of
+biological specimens, it is infeasible to generate the needed metadata
+via manual, i.e. via human input, methods.  It is critical to deploy
+computational techniques that will automate the process of generating
+the pertinent metatdata that is essential for downstream analyses and
+studies.
+
+In order to address the need for fish specimen image metadata that can
+support scientific investigations we have begun the deployment of
+both off-the-shelf and custom-written software that automatically
+generates a variety of metadata from a publicly-available biological
+image repository.  The types of metadata being produced are related
+to image quality, content and scale, and should provide the information
+necessary for quantitative studies of the digitized specimens.
+
 \section{Methods}

### 2021-03-29 paper/paper.tex
Small tweak in Sect. 3

@@
 computational techniques that will automate the process of generating
-the pertinent metatdata that is essential for downstream analyses and
-studies.
+the metatdata that is essential for downstream analyses and studies.
 

### 2021-03-30 paper/paper.tex
Reworked Sections 4.1 and 4.2

@@
   \Description{Fish predictions}
-  \label{fig:fish}
+  \label{fig:teaser}
 \end{teaserfigure}
@@
 
-Over the last several decades, given the trends towards open science,
-advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections.
+Over the last several decades advances in computing, imaging, and
+cyberinfrastructure have supported the growth of digital natural history collections; thus supporting the trends towards open scienc.
 In the U.S., programs, such as the National Science Foundation’s former
@@
 
-These image-based computational techniques are hindered by both poor
-image quality and the lack of high-quality and pertinent metadata.
+These image-based computational techniques are hampered by both poor
+image quality and the lack of high-quality and pertinent metadata
+associated with collections.
 
@@
 to image quality, content and scale, and should provide the information
-necessary for quantitative studies of the digitized specimens.
+necessary for advanced quantitative studies of the digitized specimens.
+
+The automated metadata generation methods for our project were developed
+to work on a specific set of images, the INHS\ Fish
+Collection~\cite{INHS}.  Most of these images have been configured,
+produced and acquired with a standard procedure.  The images used for
+our study contain one fish placed on a bright, white background and
+contain an information tag and the same ruler.  See 
+Figure \ref{fig:teaser} for two example images from the collection.
+While training and focusing our system on images with very similar
+compositions and visual properties may limit its immediate applicability,
+our efforts do demonstrate the potential that machine learning and
+image informatics techniques have for automatically generating metadata
+for biological specimen image collections.
 
 \section{Methods}
-Our process for metadata generation can be broken into 3 steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image informatics analysis at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.\todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images.
-Not sure where I want to put it yet so just leaving it as a todo}
+Our process for metadata generation can be broken into three steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image informatics analysis at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.
+% \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}
 
 \subsection{Detectron}
-A prerequisite task to addressing any more advanced metadata property determination is finding specimens (and other relevant objects) within collection images.
-Object detection has been an incredibly active field of study in recent years,~\cite{zou2019object} and has resulted in a number of well tested, purpose built architectures.
-We elected to use Facebook AI Research's \verb|detectron| tool,~\cite{wu2019detectron2} and specifically its implementation of the Mask R-CNN architecture,~\cite{he2018mask} for object detection in our project.
-
+A prerequisite task to performing any advanced metadata property generation
+is finding the specimens (and other relevant objects) within the collection
+images. Object detection has been a broadly active field of study in recent
+years \cite{zou2019object}, and has resulted in a number of well-tested, purpose-built architectures.
+We elected to use Facebook AI Research's \verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project.
 \verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format datasets.
@@
 For our project, we are currently using it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers.
-
-Our training dataset consisted of the following number of instances for each class:
 
@@
 
-All of the training data was labeled by hand using \verb|makesense.ai|.~\cite{make-sense} While the ultimate goal of the project is to generalize to images from a variety of specimen collections, we have thus far focused only on images from the INHS\ Fish Collection.~\cite{INHS} Using \verb|detectron|'s default training scheme, the model was trained for \(100,000\) epochs.
+Table \ref{tab:dataset} lists the number of instances for each class 
+used in our training dataset.
+All of the training data was labeled by hand using \verb|makesense.ai| \cite{make-sense}
+% While the ultimate goal of the project is to generalize to images from a variety of specimen collections, we have thus far focused only
+on images from the INHS\ Fish Collection \cite{INHS}.
+Using \verb|detectron|'s default training scheme, the model was trained for \(100,000\) epochs.
 All instance types were included in a single object detection model.
@@
 \subsection{Pixel Analysis}
-The masks and bounding boxes produced by \verb|detectron| are generally quite good, although they are almost never perfect.
-They almost always either include additional background as part of the fish, or clip part(s) of the fish outside the bounding box.
-To solve this shortcoming, we utilize pixel analysis methods commonly found in image informatics.
-
-The first calculation in the pixel analysis process is determining the cutoff intensity between what constitutes the foreground (i.e.\ the fish) and background of the image.
-Initially, we base this off the bounding box and mask generated by \verb|detectron|.
-Specimen images are read in as gray scale, and pixels in the image are treated as unsigned integers between 0 and 255.
-Otsu thresholding is used to get an initial cutoff value between foreground and background.
-\todo{Put in another sentence or two about Otsu} While this value occasionally generates an accurate mask as is, most of the time the contrast between foreground and background is not great enough and much of the lighter parts of the fish (such as its tail fin) are marked as background.
-
-To overcome this, the threshold value needs either scaled up or down depending on if the background is lighter or darker than the fish.
-For our current dataset, the background is always lighter (i.e.\ closer to 255), so the threshold value needs scaled up to include more of the image as foreground.
-Precisely how much to scale this value by is difficult to determine.
-For optimal results it is dependent on the level of contrast between the background and foreground, which can be affected by both how washed out the image is and how light or dark the pigmentation of the fish is.
-To take this into account, we measure the mean intensity of the foreground and background, then use these intensity values and the difference between them to scale the threshold value.
-Even with these values in hand it is not entirely clear how to scale the threshold.
-We scaled the threshold value by 50\% of the difference between the mean of the background and the original threshold value, which captures most of fish's fins in most cases without also masking parts of the background.
-
+The masks and bounding boxes produced by \verb|detectron| are generally quite good, although they almost never completely or tightly enclose the
+detected objects.
+This is problematic for the detected fish objects in our analyzed images,
+where the most accurate segmentation is desired.
+The mask may include additional background as part of the fish, or the
+bounding box may clip away part(s) of the fish. To solve these
+shortcomings, we utilize pixel analysis methods commonly found in image
+informatics to produce more accurate objects masks and bounding boxes.
+
+\subsubsection{Threshold Adjustment}
+The first calculation in the pixel analysis process determines the cutoff intensity between what constitutes the foreground (i.e.~the fish) and background of the image.
+Initially, the calculation is based on the bounding box and mask generated by
+\verb|detectron|. Specimen images are read in as gray scale, and pixels in the image are treated as unsigned integers between 0 and 255.
+Otsu thresholding, a technique that maximizes the variance between the 
+foreground and background intensities, is used to compute an initial cutoff value between foreground and background. 
+While the Otsu value occasionally generates an accurate mask as is, usually
+the contrast between foreground and background is low and much of the lighter parts of the fish (such as its tail fin) are marked as background.
+
+To overcome this under-segmentation, the threshold value should be
+either adjusted up or down, depending on if the background is lighter or darker than the fish.
+For our current dataset, the background is always lighter (i.e.~closer to 255), so the threshold value needs to be scaled up to include more of the
+foreground image.
+% Precisely how much to scale this value by is difficult to determine.
+For optimal results the scaling should be dependent on the
+contrast between the background and foreground,
+which can be affected by
+% both how washed out the image is and
+the level of pigmentation of the fish.
+% To take this into account, we compute the mean intensity of the foreground and background pixels, then use these intensity values and the difference between them to scale the threshold value.
+% Even with these values in hand it is not entirely clear how to scale the threshold.
+We found that an improved threshold value can be computed as the halfway
+point between the Otsu threshold value and the
+mean of the background intensities.
+This adjusted threshold value
+% by 50\% of the difference between the mean of the background and the original threshold value, which 
+captures most of fish's fins in most cases, without also masking parts of the background.
+
+\subsubsection{Consolidating the Foreground}
 While thresholding has the potential to generate better masks than a neural network (when provided an initial approximate bounding box), it also introduces considerable noise.
@@
 
+\subsubsection{Adjusting the Bounding Box}
 With an accurate mask generated, it is then necessary to check whether the bounding box needs expanded or shrunk along any edges.
@@
 
-\begin{table}[H]
+\begin{table}[t]
     \centering
@@
 The other 6 were values of 3 instead of 9 or vice versa that resulted from a mislabeled eye as discussed in the previous section.
-A small number of images (such as on the right in Figure~\ref{fig:fish}) have tags that overlap with the fish.
+A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.
 These tags were light enough that they were correctly labeled as background by the pixel analysis.

### 2021-03-30 paper/paper.tex
Added names
Updates from Overleaf

@@
 Over the last several decades advances in computing, imaging, and
-cyberinfrastructure have supported the growth of digital natural history collections; thus supporting the trends towards open scienc.
-In the U.S., programs, such as the National Science Foundation’s former
-Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
-nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of
-data and images for millions of biological specimens.
-These resources are globally available through a wide range of portals and digital libraries for researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
+cyberinfrastructure have supported the growth of digital natural history collections.
+In the U.S., programs, such as the National Science Foundation’s former Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
+nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of data and images for millions of biological specimens.
+These resources are globally available through a wide range of open access repositories, enabling researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
 Significant challenges surface, however, when researchers seek to apply computational methods to these data items,

### 2021-03-30 paper/paper_new.tex
2 columns in as paper_new.tex

--- 2021-03-30 paper/paper.tex
@@
-%\documentclass[acmsmall,screen,review]{acmart}
-%\documentclass[acmconf,screen,review]{acmart}
-\documentclass[screen,review]{acmart}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{comment}
 \usepackage{todonotes}
-\usepackage{comment}
 \usepackage{wrapfig}
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2021}
-\acmYear{2021}
-\acmDOI{}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[JCDL '21]{JCDL '21: Joint Conference on
-  Digital Libraries, September 27--30, 2021, Urbana--Champaign, Illinois, USA}
-%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  %June 03--05, 2018, Woodstock, NY}
-%\acmPrice{15.00}
-%\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
+\usepackage{hyperref}
+\usepackage{xurl}
+\usepackage{booktabs}
+\usepackage{float}
+\usepackage[noadjust]{cite}
+
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 \begin{document}
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-\title{Automated Metadata Generation for Fish Specimen Image Collections}
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{Joel Pepper}
-\email{jcp353@drexel.edu}
-\orcid{0002-1601-8729}
-\author{Jane Greenberg}
-\orcid{0001-7819-5360}
-\affiliation{%
-  \institution{Drexel University}
-  \streetaddress{3675 Market St}
-  \city{Philadelphia}
-  \state{Pennsylvania}
-  \country{USA}
-  \postcode{19104}
+\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
+    {\footnotesize \thanks{NSF Grant ???} }}
+
+\author{
+\IEEEauthorblockN{Joel Pepper}
+\IEEEauthorblockA{\textit{Department of Computer Science} \\
+\textit{Drexel University}\\
+Philadelphia, USA\\
+0000-0002-1601-8729}
+\and
+\IEEEauthorblockN{Jane Greenberg}
+\IEEEauthorblockA{\textit{Department of Information Science} \\
+\textit{Drexel University}\\
+Philadelphia, USA\\
+0000-0001-7819-5360}
+\and
+\IEEEauthorblockN{Yasin Baki\c{s}}
+\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
+\textit{Tulane University}\\
+New Orleans, USA\\
+0000-0001-6144-9440}
+\and
+\IEEEauthorblockN{Xiaojun Wang}
+\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
+\textit{Tulane University}\\
+New Orleans, USA\\
+0000-0001-8639-6795}
+\and
+\IEEEauthorblockN{Henry Bart Jr.}
+\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
+\textit{Tulane University}\\
+New Orleans, USA\\
+0000-0002-5662-9444}
+\and
+\IEEEauthorblockN{David Breen}
+\IEEEauthorblockA{\textit{Department of Information Science} \\
+\textit{Drexel University}\\
+Philadelphia, USA\\
+0000-0002-1376-5008}
 }
-\author{Yasin Baki\c{s}}
-\orcid{0001-6144-9440}
-\author{Henry Bart Jr.}
-\orcid{0002-5662-9444}
-\affiliation{
-  \institution{Tulane University}
-  \city{New Orleans}
-  \state{Louisiana}
-  \country{USA}
-}
-\author{David Breen}
-\orcid{0002-1376-5008}
-\affiliation{%
-  \institution{Drexel University}
-  \streetaddress{3675 Market St}
-  \city{Philadelphia}
-  \state{Pennsylvania}
-  \country{USA}
-  \postcode{19104}
-}
-
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Pepper, Greenberg, Baki\c{s}, Bart and Breen}
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
+%\and
+%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address or ORCID}
+%}
+
+\maketitle
+
 \begin{abstract}
-%%    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down. Also, we need to decide what to do for the ``teaser image''.} 
-%    Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
-One area of considerable activity is the digitization of the biological specimens that have been collected worldwide by museums and other research institutions.
-The scanning of these specimen collections and the placement of the resulting images into easily accessible repositories on the Internet is enabling new scientific studies based on the previously unavailable data.
-Unfortunately, potential scientific advances are hindered by the lack of high-quality and pertinent metadata associated with the image collections.
-Metadata is required to search the repositories for the imaged specimens needed for a particular study.
-Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
-Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
-
      Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
@@
 A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
-
-% Metadata is often unavailable, sparse or incorrect within specimen image repositories, but is vital for subsequent machine learning, analysis and scientific discovery.
-Our goal is to develop image metadata generation methods that both support the novel machine learning research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
-A longer term goal is to extend the image analysis methods for computing specific quantitative features in support of specific biological investigations.
-For example, we are able to automatically measure the length of a fish specimen.
-Associating these measurements with location and acquisition date may provide insights into the influence of habitat factors on fish development/health.
-Since it is prohibitively expensive for scientists to manually gather this data, we are also interested in applying our tools to images of other species stored in a variety of repositories (e.g.
-iDigBio).
-The technical challenges in achieving a broader usage of our approach mostly involve training new classifiers for different types of species, learning to segment and read annotation tags, and generalizing our classifier to find and interpret different types of rulers.
-This presentation will report on our current efforts to automatically generate metadata for fish specimen images and offer thoughts on how to extend these techniques for other specimen image collections.
 \end{abstract}
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
-   <concept>
-       <concept_id>10002951.10002952.10003219.10003215</concept_id>
-       <concept_desc>Information systems~Extraction, transformation and loading</concept_desc>
-       <concept_significance>500</concept_significance>
-   </concept>
-   <concept>
-        <concept_id>10010147.10010178</concept_id>
-	<concept_desc>Computing methodologies~Artificial intelligence~Computer Vision</concept_desc>
-	<concept_significance>500</concept_significance>
-    </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Information systems~Extraction, transformation and loading}
-\ccsdesc[500]{Computing methodologies~Artificial intelligence}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{bioinformatics, metadata, image analysis, applied machine learning}
-
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-\begin{teaserfigure}
+\begin{IEEEkeywords}
+bioinformatics, metadata, image analysis, applied machine learning
+\end{IEEEkeywords}
+
+\section{Introduction}
+\begin{figure}[H]
   \centering
@@
   \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
-  \Description{Fish predictions}
   \label{fig:teaser}
-\end{teaserfigure}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-
-\section{Introduction}
-
+\end{figure}
 \todo{Sentences I didn't use: Over the last few decades, cyberinfrastructure development, advances in digitization, and the open science tenor, have helped support global access to natural history. OR
@@
 % Konovalov 2018 \cite{Konovalov2018AutomaticSO},
-% In aquaculture breeding programs where large numbers of fish need to be rapidly phenotyped, the absolute physical dimensions of fish (in millimeters or inches) are often required to be extracted from electronic images in order to measure the size of the fish.
-While it is possible to infer the length of the fish in pixels, the absolute scale of the image (in pixels-per-millimeter or dots-per- inch) is largely unknown without a reference grid, or requires additional hardware, data collection and/or record-keeping management overheads.
-One cost and time effective solution is to capture the absolute scale by including a measuring ruler in the photographed scene and from which a computer program can automatically identify the scale of the photo and calculate fish morphometric measurements.
-To assist such workflow, this study developed an algorithm that automatically detects a ruler in a given image, and automatically extracts its scale as distance (in fractional number of pixels) betw.
-The algorithm was applied to 445 publicly available images of barramundi or Asian seabass (Lates calcarifer), where a millimeter-graded ruler was included in each image.
-Convolutional Neural Network (CNN) was trained to segment the images into ruler, background, fish and label sections.
-Then the distance-extraction algorithm was applied to the ruler section of the images.
-The false-negative rate was less than 2%, where the ruler graduation distances could not be extracted in only 2-6 (out of 445) images even when the test images were rotated up to 90 degrees.
-The mean absolute relative error (MARE) of the inferred distances was 1-2%.\newline
-Konovalov et al.~\cite{Konovalov2019AutomaticWE} presented a method for
-accurate automatic weight estimation of fish using a Convolutional Neural
-Network (CNN), data fitting, and a ruler detection/measurement
-method \cite{Konovalov2018AutomaticSO}.
 % Approximately 2,500 weights and corresponding images of harvested Lates calcarifer (Asian seabass or barra- mundi) were collected at three different locations in Queensland, Australia.
@@
 Finally, after extracting the fin regions, the start point of the pectoral fin and the end point of the anal fin will be applied in the trout processing system as the head and belly cutting points, respectively.
-
 Another application of image analysis to fish images is the evaluation
@@
   \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}
-  \Description{Bounding box and mask examples}
 \end{figure}
@@
   \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
-  \Description{Mislabeled eye on a catfish}
 \end{figure}
@@
   \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
-  \Description{Mislabeled eye on a catfish}
 \end{figure}
@@
   \caption{An example of a heavily curved specimen.}
-  \Description{Mislabeled eye on a catfish}
 \end{figure}
@@
 
-\bibliographystyle{ACM-Reference-Format}
+\section*{Acknowledgment}
+
+The preferred spelling of the word ``acknowledgment'' in America is without 
+an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+acknowledgments in the unnumbered footnote on the first page.
+
+\bibliographystyle{IEEEtran}
 \bibliography{paper}
 
-%\begin{figure}[H]
-%  \centering
-%  \includegraphics[width=\linewidth]{images/}
-%  \caption{}
-%  \Description{}
+\end{document}
+
+%\begin{thebibliography}{00}
+%\bibitem{b1} G.
+Eason, B.
+Noble, and I.
+N.
+Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
+Trans.
+Roy.
+Soc.
+London, vol.
+A247, pp.
+529--551, April 1955.
+%\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+%\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+%\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+%\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+%\bibitem{b6} Y.
+Yorozu, M.
+Hirano, K.
+Oka, and Y.
+Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
+J.
+Magn.
+Japan, vol.
+2, pp.
+740--741, August 1987 [Digests 9th Annual Conf.
+Magnetics Japan, p.
+301, 1982].
+%\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+%\end{thebibliography}
+%\vspace{12pt}
+
+%\begin{table}[htbp]
+%\caption{Table Type Styles}
+%\begin{center}
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+%\cline{2-4} 
+%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+%\hline
+%copy& More table copy$^{\mathrm{a}}$& &  \\
+%\hline
+%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+%\end{tabular}
+%\label{tab1}
+%\end{center}
+%\end{table}
+
+%\begin{figure}[htbp]
+%\centerline{\includegraphics{fig1.png}}
+%\caption{Example of a figure caption.}
+%\label{fig}
 %\end{figure}
-
-\begin{comment}
-\pagebreak{}
-\section{Introduction}~\label{demo-intro}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
-
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
-
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
-
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
-
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[acmsmall]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-Always use midrule to separate table header rows from data rows, and
-use it only for this purpose. This enables assistive technologies to
-recognise table headers and support their users in navigating tables
-more easily.
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  %\includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader.
-
-Figure captions are placed {\itshape below} the figure.
-
-Every figure should also have a figure description unless it is purely
-decorative. These descriptions convey what’s in the image to someone
-who cannot see it. They are also used by search engine crawlers for
-indexing images, and when images cannot be loaded.
-
-A figure description must be unformatted plain text less than 2000
-characters long (including spaces).  {\bfseries Figure descriptions
-  should not repeat the figure caption – their purpose is to capture
-  important information that is not already provided in the caption or
-  the main text of the paper.} For figures that convey important and
-complex new information, a short text description may not be
-adequate. More complex alternative descriptions can be placed in an
-appendix and referenced in a short figure description. For example,
-provide a data table capturing the information in a bar chart, or a
-structured list representing a graph.  For additional information
-regarding how best to write figure descriptions and why doing this is
-so important, please see
-\url{https://www.acm.org/publications/taps/describing-figures/}.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{paper}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
-\end{comment}
-
-\end{document}
-\endinput
-%%
-%% End of file `sample-acmsmall-conf.tex'.

### 2021-03-30 paper/paper.tex
Updates from Overleaf

@@
   Digital Libraries, September 27--30, 2021, Urbana--Champaign, Illinois, USA}
+  \acmBooktitle{Joint Conference on Digital Libraries}
+  %\acmPrice{1.00}
+  %\acmISBN{911}
 %\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
   %June 03--05, 2018, Woodstock, NY}
-%\acmPrice{15.00}
-%\acmISBN{978-1-4503-XXXX-X/18/06}
 
@@
 \orcid{0001-6144-9440}
+\author{Xiaojun Wang}
+\orcid{0001-8639-6795}
 \author{Henry Bart Jr.}
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Pepper, Greenberg, Baki\c{s}, Bart and Breen}
+\renewcommand{\shortauthors}{Pepper, Greenberg, Baki\c{s}, Wang, Bart and Breen}
 
@@
 \section{Introduction}
-
-\todo{Sentences I didn't use: Over the last few decades, cyberinfrastructure development, advances in digitization, and the open science tenor, have helped support global access to natural history. OR
-Global access to natural history collections has accelerated over the last few decades to advances in cyberinfrastructure, digitization, and the general open science tenor}
-
-Over the last several decades advances in computing, imaging, and
-cyberinfrastructure have supported the growth of digital natural history collections.
-In the U.S., programs, such as the National Science Foundation’s former Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
+Over the last several decades advances in computing and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain digital specimens.
+The U.
+S.
+National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
 nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of data and images for millions of biological specimens.

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

@@
 
-Over the last several decades advances in computing, imaging, and
-cyberinfrastructure have supported the growth of digital natural history collections; thus supporting the trends towards open scienc.
-In the U.S., programs, such as the National Science Foundation’s former
-Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
-nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of
-data and images for millions of biological specimens.
-These resources are globally available through a wide range of portals and digital libraries for researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
+Over the last several decades advances in computing and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens.
+Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-better to say hundreds of thousands, or is millions appropriate?} of biological specimens.
+These resources are globally available through a range of open access repositories, enabling esearchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
 Significant challenges surface, however, when researchers seek to apply computational methods to these data items,
@@
 
-\begin{table}[t]
+\begin{table*}[t]
     \centering
@@
 \end{tabular}
-\end{table}
+\end{table*}
 

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

@@
 \end{figure}
-\todo{Sentences I didn't use: Over the last few decades, cyberinfrastructure development, advances in digitization, and the open science tenor, have helped support global access to natural history. OR
-Global access to natural history collections has accelerated over the last few decades to advances in cyberinfrastructure, digitization, and the general open science tenor}
-
-Over the last several decades advances in computing and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens.
-Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-better to say hundreds of thousands, or is millions appropriate?} of biological specimens.
-These resources are globally available through a range of open access repositories, enabling esearchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
-Significant challenges surface, however, when researchers seek to apply computational methods to these data items,
-due to both image quality and metadata issues.
-% (As researchers seek to apply computational methods, and explore AI, significant challenges surface..)
+Over the last several decades advances in computing, imagine, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens.
+Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-is millions appropriate?} of biological specimens.
+These digital specimen images globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
+Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
+%{jane} not sure this note is mine? should we integrate machine learning into intro. As researchers seek to apply computational methods, and explore AI, significant challenges surface..)
 
@@
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+Vishal? Hank's undergrads? Other team members?
 

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

@@
 \end{figure}
-Over the last several decades advances in computing, imagine, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens.
-Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-is millions appropriate?} of biological specimens.
-These digital specimen images globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens.
+Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-millions?} of biological specimens.
+These digital specimen images are globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
 Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
-%{jane} not sure this note is mine? should we integrate machine learning into intro. As researchers seek to apply computational methods, and explore AI, significant challenges surface..)
+%{jane} not sure this following mine: "As researchers seek to apply computational methods, and explore AI, significant challenges surface..)" 
+%should we try to insert machine learning here?
 

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

@@
 Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens.
-Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-millions?} of biological specimens.
+Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.
 These digital specimen images are globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

@@
 \usepackage{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%% REMOVE FOLLOWING LINE BEFORE SUBMITTING %%%%%%%%%
+\setlength {\marginparwidth }{2cm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{todonotes}
@@
 \IEEEauthorblockN{David Breen}
-\IEEEauthorblockA{\textit{Department of Information Science} \\
+\IEEEauthorblockA{\textit{Department of Computer Science} \\
 \textit{Drexel University}\\
@@
 \end{figure}
-Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens.
-Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.\cite{page2015digitization,}.
 These digital specimen images are globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
 Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
-%{jane} not sure this following mine: "As researchers seek to apply computational methods, and explore AI, significant challenges surface..)" 
-%should we try to insert machine learning here?
+%{jane}should we try to insert machine learning here, last sentence, or computation methods ok?
 

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

@@
 \end{figure}
-Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.\cite{page2015digitization,}.
-These digital specimen images are globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.~\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.~\cite{page2015digitization} These digital specimen accessible through global, open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
 Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
@@
 requiring the ability to identify and measure rulers in the images.
-Many specimen collections do include Darwin Core metadata, detailing
+Many specimen collections do include Darwin Core metadata,~\cite{biodiv_info_standards} detailing
 specimen taxon, geographic location, and several other descriptive aspects.
@@
 \subsection{Metadata for Image Collection}
-\todo{Wasn't looking for a citation but stumbled upon this paper: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0207636}, might be worth a skim}
-Metadata development is intertwined with the development of digital technology.
 A wide range of metadata standards are applicable to metadata supporting image description as well as technical aspects, and have been used in a range of image repositories.

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

@@
 \textbf{Todo}
-\subsection{Metadata for Image Collection}
-A wide range of metadata standards are applicable to metadata supporting image description as well as technical aspects, and have been used in a range of image repositories.
-Examples of Descriptive schemes include X, y, z...
-Examples of technical schemes include...
-The use varies across communities, and application technique is primarily manual.
-Research evaluating such schemes XXX, show XXX.
+\subsection{Metadata for Natural History Image Collection}
+%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.
+A number of different metadata standards have been applied to support the description and access of digitized scientific images.
+Darwin Core developed specifically for digital museum projects is one of the most frequently used standards.
+Other popular standards include the Dublin Core, particularly application profiles, drawing from other namespaces such as the Ecological Metadata Language (EML) and ISO-geo [jane add]; and there is also the recent Audubon Core, designed to support the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.
+These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
+In other words, their application anticipates that a curator or data entry staff person will manually enter data from the original acquisition logs, or historical labels.
+As a result, the metadata associated with each digital rendering seems somewhat limited, particularly to researchers seeking to apply machine learning, and leverage both the image and the metadata.
+%will add cites above, depending on paper length.
 
-Natural history collections generally use a sub-set of such standards.
-Darwin Core, a globally adopted standard overseen by the Taxonomic Data Working Group (TDWG).
-[Jane continue here on some of this, and then with preservation/image quality less]
+%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS},
 
-Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS},
-
-\subsection{Metadata generation?}
+\subsection{Automatic Metadata Generation}
+Metadata researchers are aware of challenges posted by manual metadata generation, both in terms of time, 
+%jane working here, i figured out how to scope this, I think! I need to get outside now, but back later.
 

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf
Have at least something in all results and discuss sections I think

@@
 }
-%\and
-%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address or ORCID}
-%}
 
@@
 We ran the metadata extraction program on these \(7,244\) images.
+These properties did not include information on image scale, fish length, or fish bounding boxes.
+For these properties, a random sample of 50 specimens from the set of \(7,244\) were analyzed by hand for comparison.
 
@@
 All but 263 of these were generated via pixel analysis, with those 263 falling back to the original \verb|detectron| bounding box.
-\textbf{Todo}: Anything more than this is going to need hand checked.
+Of the 50 images reviewed manually for these properties, all mask and bounding boxes were correctly placed on/around the location of the fish.
+However, a number of them lacked portions of lightly colored tails and/or fins.
+Specifically, 22 mask and bounding boxes covered the entire fish, 16 missed some of the tail, and 12 missed most or all of the tail.
 
-\subsection{Length}
-Fish lengths were calculated for \(7,179\) of the images. \textbf{Todo}: Anything more than this is going to need hand checked.
-\begin{comment}
-\begin{verbatim}
-What I think should be the final results:
-
-Right: 6956
-Errored: 0
-No eye: 246
-No fish: 10
-Wrong wrong: 35
-Total: 7247
-Percent right: 0.959845453291017
-Percent right that didn't error: 0.9949935631526248
-
------------------------
-
-Pixel analysis failed: 0.036336004421110804
-
------------------------
-
-My hand checking of the ''wrong wrong'' fish:
-               My guess, Yasin spreadsheet
-INHS_FISH_101109.jpg: 9, 11, I'm wrong although it's fairly curved
-INHS_FISH_56818.jpg: 4, 2, I'm wrong although there's a tag that is likely messing things up
-INHS_FISH_57607.jpg: 3, 9, I'm wrong
-INHS_FISH_57001.jpg: 4, 2, I'm wrong although there's a tag that is likely messing things up
-INHS_FISH_63953.jpg: 3, 9, I'm wrong
-INHS_FISH_51100.jpg: 3, 9, I'm wrong
-INHS_FISH_80528.jpg: 3, 8, I'm wrong
-INHS_FISH_6370.jpg: 3, 9, I'm wrong
-INHS_FISH_54157.jpg: 9, 7, I'm arguably wrong although it's very curved
-INHS_FISH_80987.jpg: 9, 3, I'm wrong although this one is a fairly atypical image
-
-INHS_FISH_58647.jpg: 9, 7, I'm right
-INHS_FISH_8415.jpg: 9, 6, I'm right
-INHS_FISH_5041.jpg: 9, 11, very curved averages to about 9
-INHS_FISH_52821.jpg: 9, 7, I'm arguably right although the fish is damaged and its head points to ~7
-INHS_FISH_6696.jpg: 9, 7, I'm right
-INHS_FISH_75252.jpg: 9, 6, I'm right
-INHS_FISH_79498.jpg: 9, 6, I'm right
-INHS_FISH_45744.jpg: 9, 5, I'm right
-INHS_FISH_47579.jpg: 9, 6, I'm right
-INHS_FISH_64599.jpg: 9, 6, I'm right
-INHS_FISH_74550.jpg: 9, 5, I'm right
-INHS_FISH_101664.jpg: 9, 6, I'm right
-INHS_FISH_100861.jpg: 9, 6, I'm right
-INHS_FISH_60589.jpg: 3, 9, I'm right
-INHS_FISH_53469.jpg: 9, 1, I'm right
-INHS_FISH_44694.jpg: 9, 6, I'm right
-INHS_FISH_54921.jpg: 9, 6, I'm right
-INHS_FISH_44645.jpg: 10, 8, I'm right
-INHS_FISH_50459.jpg: 9, 11, I'm right although the fish is damaged and its head points to ~11
-INHS_FISH_68061.jpg: 9, 6, I'm right
-INHS_FISH_74716.jpg: 9, 6, I'm right
-INHS_FISH_80976.jpg: 9, 6, I'm right
-INHS_FISH_57977.jpg: 9, 6, I'm right
-INHS_FISH_45377.jpg: 9, 6, I'm right
-INHS_FISH_47142.jpg: 9, 6, I'm right
-
-Verdict: For only 10 of the 35 am I actually wrong and all of those are either curved, atypical
-images with tags, or something on the wrong side was detected as an eye (so the clock value is backwards).
-
-\end{verbatim}
-\end{comment}
+\subsection{Scale and Length}
+Image scale and fish lengths were calculated for \(7,179\) of the images.
+50 of these images were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ.~\cite{imagejCite} The average error for the scale calculation was \(0.911\%\), and the average error for the fish length calculation was \(5.87\%\).
 
@@
 \subsubsection{Mask and Bounding Box}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/61631}
+  \includegraphics[width=0.49\linewidth]{images/61631_mask}
+  \caption{An example of a light colored tail being missed during the pixel analysis process.}
+\end{figure}
+Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work?
+Or both?}
 
 \subsubsection{Brightness?}
+\textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
+I still have to look into the dark normal bright calculations in the new way we discussed.}
 
-\subsubsection{Length}
+\subsubsection{Scale and Length}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/54172}
+  \includegraphics[width=0.49\linewidth]{images/54172_mask}
+  \caption{An example of a light colored tail being missed during the pixel analysis process.}
+  \label{fig:scale_len}
+\end{figure}
+Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler.
+When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well.
+An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm).
+Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
 
@@
     \item Fitting a ``spine'' to specimen.
+    \item Check for color channel inequality when masking fish
 \end{itemize}
@@
 \end{document}
-
-%\begin{thebibliography}{00}
-%\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-%\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-%\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-%\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-%\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-%\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-%\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-%\end{thebibliography}
-%\vspace{12pt}
 

### 2021-03-31 paper/paper_new.tex
Mostly formatting changes

@@
 \section{Introduction}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=.45\textwidth]{images/teaser1_crop}
-  \hspace{4mm}
-  \includegraphics[width=.45\textwidth]{images/teaser2_crop}
-  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
-  \label{fig:teaser}
-\end{figure}
+% Moving teaser since this template doesn't actually ask for one
 Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.~\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.~\cite{page2015digitization} These digital specimen accessible through global, open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=.49\linewidth]{images/teaser1_crop}
+  %\hspace{4mm}
+  \includegraphics[width=.49\linewidth]{images/teaser2_crop}
+  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
+  \label{fig:teaser}
+\end{figure}
 \subsection{Detectron}
@@
 
-\begin{wraptable}{r}{5.5cm}
+% Not sure wrapping this is really getting us much after the 2 column switch
+
+%\begin{wraptable}{r}{5.5cm}
+\begin{table}[H]
     \centering
@@
     \end{tabular}
-\end{wraptable}
+\end{table}
+%\end{wraptable}
 
@@
   \includegraphics[width=0.49\linewidth]{images/curved1}
-  %\includegraphics[width=0.49\linewidth]{images/}
   \caption{An example of a heavily curved specimen.}

### 2021-03-31 paper/paper_new.tex
Updates from Overleaf

@@
     {\footnotesize \thanks{NSF Grant ???} }}
+%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., e.g., bgnn, and even mention of metadata research center. 
+%for the record: Research supported by NSF OAC #1940233 and #1940322.
 
@@
 \section{Related Work}
-\textbf{Todo}
 \subsection{Metadata for Natural History Image Collection}
@@
 A number of different metadata standards have been applied to support the description and access of digitized scientific images.
-Darwin Core developed specifically for digital museum projects is one of the most frequently used standards.
-Other popular standards include the Dublin Core, particularly application profiles, drawing from other namespaces such as the Ecological Metadata Language (EML) and ISO-geo [jane add]; and there is also the recent Audubon Core, designed to support the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.
-These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
-In other words, their application anticipates that a curator or data entry staff person will manually enter data from the original acquisition logs, or historical labels.
-As a result, the metadata associated with each digital rendering seems somewhat limited, particularly to researchers seeking to apply machine learning, and leverage both the image and the metadata.
+Darwin Core~\cite{biodiv_info_standards} developed specifically for digital museum projects is one of the most frequently used standards.
+Another approach is to create a metadata application profile by integrating properties from Dublin Core's DCMI Metadata Terms \cite{dc_terms}, the Ecological Metadata Language (EML) \cite{EML_2019} and other namespaces.
+There is also the recent Audubon Core supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.\cite{audub_core} These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
+In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels.
+This task is labor intensive, and the metadata associated with each digital rendering is limited, particularly for researchers seeking to apply machine learning, and leverage both the image and the metadata for scientific research.
+
+This limitation is magnified, when trying get a handle on the actual quality of the digitized specimen.
+Descriptive oriented standards support search and retrieval, but metadata properties used to record image quality is severely limited and generally missing.
+This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bio-generated neural network.
 %will add cites above, depending on paper length.
@@
 \subsection{Automatic Metadata Generation}
-Metadata researchers are aware of challenges posted by manual metadata generation, both in terms of time, 
+Metadata researchers are aware of challenges posted by manual metadata generation, both in terms of time,  //Technical metadata capturing image lighting, camera, date of digitization and other information are automatically generated, but
 %jane working here, i figured out how to scope this, I think! I need to get outside now, but back later.

### 2021-03-31 paper/paper_DEB.tex
Edited Sections 4 & 5.

--- 2021-03-30 paper/paper.tex
@@
 \verb|detectron|. Specimen images are read in as gray scale, and pixels in the image are treated as unsigned integers between 0 and 255.
-Otsu thresholding, a technique that maximizes the variance between the 
+Otsu thresholding \cite{Otsu1979ATS}, a technique that maximizes the variance between the 
 foreground and background intensities, is used to compute an initial cutoff value between foreground and background. 
@@
 
-\subsubsection{Fallback} The pixel analysis process occasionally fails.
+\subsubsection{Fallback} The pixel analysis process occasionally fails,
+e.g.~ flood-filling does not produce a large enough blob or
+the bounding box adjustment does not terminate.
 This can occur if certain flood fill operations behave unexpectedly, or if the image is too washed out or otherwise atypical for the thresholding process to work correctly.
 In the event this happens, the original mask and bounding box generated by \verb|detectron| is used for metadata generation.
+
 \subsection{Metadata Generation}

### 2021-03-31 paper/paper_new.tex
Updates from Overleaf

@@
     {\footnotesize \thanks{NSF Grant ???} }}
-%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., e.g., bgnn, and even mention of metadata research center. 
+%do we add grant now, or wait til acceptance.
+i think we need to ultimately remove any identifying info., i think bgnn is likely okay; but, perhaps mention metadata research center (MRC) need to be removed?.
+if so, i kind of like to put it back in for final version, if accepted.
+it helps with getting funding ...
+you are both listed on the MRC page.
+we should check on the identifying info.
+removed, or not.
 %for the record: Research supported by NSF OAC #1940233 and #1940322.
@@
 
-This limitation is magnified, when trying get a handle on the actual quality of the digitized specimen.
-Descriptive oriented standards support search and retrieval, but metadata properties used to record image quality is severely limited and generally missing.
-This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bio-generated neural network.
+This limitation is magnified when trying get a handle on the actual quality of the digitized specimen.
+Descriptive oriented standards support search and retrieval, and the biodiversity community advocated for data fitness standards \cite{chapman2020developing}.
+Even so, metadata properties used to record image quality is severely limited and generally missing.
+This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bgnn.
+Although, the manual generation of this metadata is costly in terms of labor and time.
 %will add cites above, depending on paper length.
@@
 \subsection{Automatic Metadata Generation}
-Metadata researchers are aware of challenges posted by manual metadata generation, both in terms of time,  //Technical metadata capturing image lighting, camera, date of digitization and other information are automatically generated, but
-%jane working here, i figured out how to scope this, I think! I need to get outside now, but back later.
+Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX.
+Some of this metadata may be useful in for selecting a machine learning sample.
+A researcher may desire images captured chiefly with a certain aperture setting.
+Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to reply on manually generated descriptive metadata, which itself is sparse.
+
+Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating}.
+Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.
+
+%\cite{heidorn2008automatic} speciment labels \cite{manso2004automatic} carteogrpahic info.
 

### 2021-03-31 paper/paper_new.tex
Wrote future work, added a bit more results

--- 2021-03-31 paper/paper_new.tex
@@
 \subsection{Brightness/Uniformity Results?}
-\textbf{Todo}: I can try to do this but I need to set up the infrastructure, we probably need to discuss a plan of action for this.
+\begin{verbatim}
+Mean intensity in bounding box | Count
+
+dark: 153.94935240158551 | 1800
+normal: 168.2924981358199 | 5186
+bright: 177.68854540643943 | 242
+\end{verbatim}
+\begin{verbatim}
+Standard Deviations for:
+    Uniform: 12.554834863869324
+    Not Uniform: 11.312181711328828
+\end{verbatim}
 
@@
 \textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
-I still have to look into the dark normal bright calculations in the new way we discussed.}
+Brightness results are are in previous section.
+Need to think about what is worth noting since it's a fairly trivial result.}
 
@@
 \subsection{Future Work}
-\begin{itemize}
-    \item Further fine tuning of pixel analysis (e.g.\ thresholding on different regions of the bbox).
-    \item Generalizing ruler reading.
-    \item Training on a progressively larger number of image collections to hopefully gain reasonable generality for the whole class of fish specimen images.
-    \item Adding things like seahorses and eels.
-    \item Fitting a ``spine'' to specimen.
-    \item Check for color channel inequality when masking fish
-\end{itemize}
+The most pressing next step is to refine the pixel analysis thresholding process so that the entirety of even light colored fish are marked as foreground in the mask.
+A deficiency of the current process is that it only operates on single channel intensity.
+Some of the lightest tails appear yellow in hue to the human eye and easily distinguishable, but when compressed to a single intensity value they are almost identical in value to the white background.
+Considering when the RGB channels of a pixel are not equal in value may be able to improve masking of such features.
+Another possible approach to solving this is to threshold an mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.
+
+Our ultimate goal is to create a generalized process to work on classes of specimen images (specifically all fish images for BGNN), not only the INHS collection.
+To accomplish this, a much larger training dataset full of more diverse images will be required.
+Another requirement will be to generalize the ruler reading process beyond the INHS specific reading of digits on the ruler.\todo{Suggest way(s) to do this?}
+% Todo: Are these worth mentioning?
+%Adding things like seahorses and eels.
+%Fitting a ``spine'' to specimen.
 \section{Conclusion}

### 2021-03-31 paper/paper_new.tex

--- 2021-03-31 paper/paper_new.tex
@@
     {\footnotesize \thanks{NSF Grant ???} }}
-%do we add grant now, or wait til acceptance.
-i think we need to ultimately remove any identifying info., i think bgnn is likely okay; but, perhaps mention metadata research center (MRC) need to be removed?.
-if so, i kind of like to put it back in for final version, if accepted.
-it helps with getting funding ...
-you are both listed on the MRC page.
-we should check on the identifying info.
-removed, or not.
+%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., e.g., bgnn, and even mention of metadata research center. 
 %for the record: Research supported by NSF OAC #1940233 and #1940322.
@@
 
-This limitation is magnified when trying get a handle on the actual quality of the digitized specimen.
-Descriptive oriented standards support search and retrieval, and the biodiversity community advocated for data fitness standards \cite{chapman2020developing}.
-Even so, metadata properties used to record image quality is severely limited and generally missing.
-This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bgnn.
-Although, the manual generation of this metadata is costly in terms of labor and time.
+This limitation is magnified, when trying get a handle on the actual quality of the digitized specimen.
+Descriptive oriented standards support search and retrieval, but metadata properties used to record image quality is severely limited and generally missing.
+This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bio-generated neural network.
 %will add cites above, depending on paper length.
@@
 \subsection{Automatic Metadata Generation}
-Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX.
-Some of this metadata may be useful in for selecting a machine learning sample.
-A researcher may desire images captured chiefly with a certain aperture setting.
-Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to reply on manually generated descriptive metadata, which itself is sparse.
-
-Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating}.
-Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.
-
-%\cite{heidorn2008automatic} speciment labels \cite{manso2004automatic} carteogrpahic info.
+Metadata researchers are aware of challenges posted by manual metadata generation, both in terms of time,  //Technical metadata capturing image lighting, camera, date of digitization and other information are automatically generated, but
+%jane working here, i figured out how to scope this, I think! I need to get outside now, but back later.
 
@@
 
+\begin{table*}[t]
+    \centering
+    \caption{Metadata properties}
+    \label{tab:properties}
+    \begin{tabular}{cccp{0.5\linewidth}}
+        \toprule
+        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
+        \midrule
+        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
+        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
+        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
+        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
+        \verb|scale| & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of the bounding box for a fish.\\
+        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
+        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
+        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
+        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
+        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
+        \verb|primary_axis| & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
+        \verb|clock_value| & Per Fish & Integer & Fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
+        \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
+        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish.
+If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
+        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
+        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
+        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
+        \verb|side| & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
+      \bottomrule
+\end{tabular}
+\end{table*}
+
 \subsubsection{Threshold Adjustment}
@@
 
-\subsubsection{Fallback} The pixel analysis process occasionally fails.
+\subsubsection{Fallback} The pixel analysis process occasionally fails,
+e.g.~ flood-filling does not produce a large enough blob or
+the bounding box adjustment does not terminate.
 This can occur if certain flood fill operations behave unexpectedly, or if the image is too washed out or otherwise atypical for the thresholding process to work correctly.
 In the event this happens, the original mask and bounding box generated by \verb|detectron| is used for metadata generation.
+
 \subsection{Metadata Generation}
-Including what has already been discussed, the following metadata properties are being currently being generated:
 
-\begin{table*}[t]
-    \centering
-    \caption{Metadata properties}
-    \label{tab:properties}
-    \begin{tabular}{cccp{0.5\linewidth}}
-        \toprule
-        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
-        \midrule
-        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
-        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
-        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
-        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
-        \verb|scale| & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
-        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of what define the bounding box for a fish.\\
-        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
-        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
-        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
-        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
-        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
-        \verb|primary_axis| & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
-        \verb|clock_value| & Per Fish & Integer & A fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
-        \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
-        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
-        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish.
-If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
-        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
-        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
-        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
-        \verb|side| & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
-      \bottomrule
-\end{tabular}
-\end{table*}
+The following metadata properties are generated from the methods
+described above:
+\verb|has_fish|, \verb|fish_count|, \verb|has_ruler|, \verb|ruler_bbox|, \verb|background.{mean,std}|, \verb|foreground.{mean,std}|, \verb|bbox|, \verb|mask|, \verb|score|, and \verb|has_eye|.
+The remaining properties are computed as described below, with all the
+metadata properties listed in Table \ref{tab:properties}.
 
-\verb|has_fish|, \verb|fish_count|, \verb|has_ruler|, \verb|ruler_bbox|, \verb|background.*|, \verb|foreground.*|, \verb|bbox|, \verb|mask|, \verb|score|, and \verb|has_eye| have already been discussed.
-The remaining properties are determined as follows:
 \subsubsection{centroid and eye\_center}
-Centroids are provided for masks/bounding boxes generated by \verb|detectron|, and since we do not recalculate the mask of fish eyes we can use that value directly for \verb|eye_center|.
+Centroids are provided for the masks and bounding boxes generated by \verb|detectron|, and since we do not recalculate the mask of fish eyes we can use that value directly for \verb|eye_center|.
 
@@
 \begin{equation}
-    (\bar{x}, \bar{y}) = (\mathrm{round}(\frac{M_{10}}{M_{00}}), \mathrm{round}(\frac{M_{01}}{M_{00}}))
+    (\bar{x}, \bar{y}) = (\mathrm{round}(\frac{M_{10}}{M_{00}}), \mathrm{round}(\frac{M_{01}}{M_{00}})),
 \end{equation}
@@
 \subsubsection{primary\_axis and clock\_value}
-The \verb|primary_axis| of a fish can be calculated by taking the covariance\todo{I could explain this in more detail if necessary} of its blob in \(x\) and \(y\), which yields its principle eigenvector.
-This can be directly assigned to the property.
-If an eye is present, we specify this axis in the direction of the eye in relation to the fish's centroid.
+The \verb|primary_axis| of a fish can be calculated by taking the covariance\todo{I could explain this in more detail if necessary.
+(DEB No, that's OK.} of its blob in \(x\) and \(y\), which yields its principle eigenvector.
+The eigenvector can be directly assigned to the property. If an eye is
+present, we ensure that \verb|primary_axis| points in the direction of the
+eye in relation to the fish's centroid.
 
-Our team encoded this information as a ``clock value'' between 1 and 12 when recording it by hand.
-To convert \verb|principal_axis| to \verb|clock_value|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish is angles into relative to its centroid.
-Depending on this quadrant, we then dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\) which correspond to 9, 6, 3 and ``0'' o'clock respectively.
+Our team encoded this information as a ``clock value'' between 1 and 12 when manually recording it.
+To convert \verb|principal_axis| to \verb|clock_value|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish angles into relative to its centroid.
+Depending on this quadrant, we dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\), which correspond to 9, 6, 3 and ``0'' o'clock respectively.
 The resulting radian value is then converted to a polar displacement in clock value space, and added to the comparative clock value used in the dot product.
-This then gives the fish's clock value from 0 to \(11.\overline{9}\).
-Before recording as \verb|clock_value| in the output, the value is rounded to the nearest integer, and in the event of a 0 final result it is replaced with 12.
+This gives the fish's clock value from
+0 to \(11.\overline{9}\). Before recording \verb|clock_value| in the output,
+the value is rounded to the nearest integer, with a 0 final result replaced with 12.
 \subsubsection{scale and length}
-\(\frac{\mathrm{pixels}}{\mathrm{inch}}\) can be calculated by measuring the distance between the digits 2 and 3 found on the ruler by \verb|detectron|.
+\(\frac{\mathrm{pixels}}{\mathrm{inch}}\) can be calculated by measuring the distance in pixels between the digits 2 and 3 (a 1 inch separation) found on the ruler by \verb|detectron|.
 Converting this to \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) gives the \verb|scale| metadata property as reported in the output.
 
-For the fish \verb|length| property, it is necessary to determine the furthest points from the centroid of the fish in each direction.
-Since fish are normally measured in a straight line from their snout down the middle of their trunk, we project every pixel onto the major axis of the fish (as a line through its centroid) before checking the distance.
-This projection is done by intersecting the line through the point along the tangent of the principal axis and the aforementioned centroid--principal axis line.
-After checking every pixel, measuring the distance between the two furthest projected points gives the length of the fish in pixels.
-Multiplying this by \verb|scale| gives the fish \verb|length| in centimeters.
+For the fish \verb|length| property, it is necessary to determine the furthest points from the centroid of the fish in each direction along its major
+axis. Since fish are normally measured in a straight line from their snout down the middle of their trunk, every pixel of the fish blob is projected
+onto the fish's major axis (as a line through its centroid).
+The projection is done by finding the closest point on the
+centroid--principal axis line from the pixel's location.
+% intersecting the line through the point along the tangent of the principal axis and the aforementioned centroid--principal axis line.
+After processing every pixel in the fish blob, computing the distance
+between the two furthest projected points gives the length of the fish in pixels. Multiplying this distance by \verb|scale| gives the fish \verb|length| in centimeters.
 \begin{comment}
@@
 \(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images.
-Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and meet our current admissibility criteria for what \verb|detectron| and the pixel analysis process can reliably handle.
+Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and met our current admissibility criteria for \verb|detectron| and pixel analysis processing.
 We ran the metadata extraction program on these \(7,244\) images.
-These properties did not include information on image scale, fish length, or fish bounding boxes.
-For these properties, a random sample of 50 specimens from the set of \(7,244\) were analyzed by hand for comparison.
+For the properties of image scale, fish length, and fish bounding boxes
+(properties not manually generated),
+a random sample of 50 specimens from the set of \(7,244\) were analyzed by
+hand for comparison.
 
@@
 \subsection{Fish Detection}
-All images in the INHS dataset contain exactly one fish.
-For \(7,209\) of the specimen images, one fish was detected.
+All images in the INHS dataset contain exactly one fish. For \(7,209\) of the specimen images, one fish was detected, a 99.5\% correct rate.
 For 25 of the images, 2 fish were detected, 3 fish were detected for 3 images, and for 7 images no fish were found.
@@
 \subsection{Ruler Detection}
-For all but 2 of the \(7,244\) images \verb|detectron| was able to find the ruler.\todo{Not sure if I can phrase it that way or not since I haven't looked at all the images to see if the ruler itself was found or something else was labeled a ruler} For an additional 56 images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed.
+For all but 2 of the \(7,244\) images \verb|detectron| was able to find the ruler, a nearly perfect correct rate.
+\todo{Not sure if I can phrase it that way or not since I haven't looked at all the images to see if the ruler itself was found or something else was labeled a ruler} In 56 of the images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed, producing a 99.2\% success rate for being able to compute
+\verb|scale|.
 
@@
 
+\subsection{Foreground/Background Contrast Results?}
+\textbf{Todo}: It would be great to compute a histogram of foreground.mean -
+bakground.mean for the all our samples.
+Perhaps it would then be obvious how to break the images into low, medium
+and high F/B contrast.  We could show a representative image from each
+group.
+
 \subsection{Brightness/Uniformity Results?}
@@
 
-\subsection{Mask and Bounding Box}
 \begin{figure}[H]

### 2021-03-31 paper/paper_new.tex
Updates from Overleaf
Finished a pass through Section 5.

@@
 
+%abstract can be shortened a good bit.
+%can offer an alternative manana..
 \begin{abstract}
@@
 Although, the manual generation of this metadata is costly in terms of labor and time.
-%will add cites above, depending on paper length.
 
@@
 
-%\cite{heidorn2008automatic} speciment labels \cite{manso2004automatic} carteogrpahic info.
+%\cite{heidorn2008automatic} speciment labels \cite{manso2004automatic} cartographic info.
+%above paragraph..need to finesse a couple of sentences w/results, weave in these 2 citations, and then say we can look to image analysis.
 
@@
 for new scientific studies and discoveries.
-
+%I think we can go from the above, statement, directly to the paragraph that starts with "Given the many..." Then, specifically state the goal of this paper is to XXXX address the need, or the goal is to investigate, test, (pick your verb) an approach automatically generating metadata, combining off-the-shelf software and custom written, or is it simply test off-the-shelf software, and later the realization that customization happens.
 The amount of data is immense, with image collections containing 10,000's
@@
 For all but 2 of the \(7,244\) images \verb|detectron| was able to find the ruler, a nearly perfect correct rate.
-\todo{Not sure if I can phrase it that way or not since I haven't looked at all the images to see if the ruler itself was found or something else was labeled a ruler} In 56 of the images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed, producing a 99.2\% success rate for being able to compute
-\verb|scale|.
+% \todo{Not sure if I can phrase it that way or not since I haven't looked at all the images to see if the ruler itself was found or something else was labeled a ruler}
+In 56 of the images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed, producing a 99.2\% success rate for
+the \verb|scale| computation.
 
 \subsection{Side Detection}
-For 246 of the images \verb|detectron| was unable to find a fish eye. Of the remaining \(6,998\) images where it did, the correct side (\verb|left| or \verb|right|) was detected in all but 6 cases.
+\verb|detectron| was unable to find a fish eye
+in 246 of the images. Of the remaining \(6,998\) images, the correct side
+(\verb|left| or \verb|right|) was detected in all but 6 cases, producing
+a 96.5\% correct rate.
+\todo{Comment on the 6 cases. What failed?}
 
 \subsection{Clock Value}
-Clock position values were successfully generated for \(6,991\) of the images. Of those, all but 8 were within \(\pm{}1\) of the correct result.
+Clock position values were successfully generated for \(6,991\) of the images. Of those, all but 8 were within \(\pm{}1\) of the correct result,
+our definition of a correct/acceptable result. The correct rate for this
+computation is 96.4\%.
+\todo{Comment on the cases where we were unable to compute clock value. What failed?}
 
@@
 \subsection{Brightness/Uniformity Results?}
+\textbf{Todo}: Need standard deviations here, too. To show that the
+differences are significant and meaningful. Clearly the trend is there.\newline
+It looks like we should leave out Uniformity.
+
 \begin{verbatim}
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
   \centering
@@
 \end{figure}
+
+\subsection{Mask and Bounding Box}
 Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found.
 All but 263 of these were generated via pixel analysis, with those 263 falling back to the original \verb|detectron| bounding box.
-Of the 50 images reviewed manually for these properties, all mask and bounding boxes were correctly placed on/around the location of the fish.
-However, a number of them lacked portions of lightly colored tails and/or fins.
-Specifically, 22 mask and bounding boxes covered the entire fish, 16 missed some of the tail, and 12 missed most or all of the tail.
+50 randomly-chosen images were reviewed manually to evaluate the
+calculation.  All 50 masks and bounding boxes were correctly placed
+on/around the location of the fish. However, a number of them lacked portions of lightly colored tails and/or fins.
+Specifically, 22 masks and bounding boxes covered the entire fish,
+16 missed some of the tail, and 12 missed most or all of the tail.
 
@@
 Image scale and fish lengths were calculated for \(7,179\) of the images.
-50 of these images were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ.~\cite{imagejCite} The average error for the scale calculation was \(0.911\%\), and the average error for the fish length calculation was \(5.87\%\).
+\todo{What happened the excluded images?}
+Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
+measured, using ImageJ~\cite{imagejCite}, in the same(?) 50 test images.
+% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ.~\cite{imagejCite}
+In this subset of images the average error for the scale calculation
+was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
 
@@
 \textbf{Todo}: Will need some sort of intro/framing paragraph
+%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation.
+Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
+%Discussion needed to weave in at least a couple of citations. Happy to discuss
 \subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
@@
 \section*{Acknowledgment}
-
-Vishal? Hank's undergrads? Other team members?
+%can make possible note about larger BGNN team, and/or general note to Tulane data in-putters for giving us data to compare, and/or INHS collection. [we can discuss]
 

### 2021-03-31 paper/paper_new.tex
Edited Section 6.

@@
   \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}
+  \label{fig:bbox_mask}
 \end{figure}
@@
 50 randomly-chosen images were reviewed manually to evaluate the
-calculation.  All 50 masks and bounding boxes were correctly placed
+calculation, a representative sample are presented in
+Figure \ref{fig:bbox_mask}.
+All 50 masks and bounding boxes were correctly placed
 on/around the location of the fish. However, a number of them lacked portions of lightly colored tails and/or fins.
@@
 %Discussion needed to weave in at least a couple of citations. Happy to discuss
-\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
-\subsubsection{Object Detection}
 \begin{figure}[H]
@@
 \end{figure}
+\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
+\subsubsection{Object Detection}
 
@@
 \end{itemize}
-\subsubsection{Side Detection}
 \begin{figure}[H]
@@
 \end{figure}
-For all 6 of the cases where an eye was detected but the \verb|side| value was wrong, a spot on the wrong side of the fish was labeled as the most likely eye within the bounding box of the fish.
+\subsubsection{Side Detection}
+There were six cases where an eye was detected but the \verb|side| value
+was wrong. Here, a spot on the wrong side of the fish was labeled as the
+most likely eye within the bounding box of the fish, i.e.~eye detection 
+was incorrect.
 There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
-For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than than the human error rate.
+For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
+This result highlights the additional utility of automated methods to
+double-check and verify human-generated metadata.
 
@@
   \caption{An example of a heavily curved specimen.}
+  \label{fig:curvedFish}
 \end{figure}
-Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).For 25 of those the human generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
-Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value.
-The other 6 were values of 3 instead of 9 or vice versa that resulted from a mislabeled eye as discussed in the previous section.
+Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
+For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
+Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
+seen in Figure \ref{fig:curvedFish}.
+The other 6 were values of 3 instead of 9 or vice versa, which resulted from
+a mislabeled eye as discussed in the previous section.
+\todo{Why is the following sentence here? What does it have to do with
+Clock Value?}
 A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.

### 2021-03-31 paper/paper_DEB.tex

@@
-%\documentclass[acmsmall,screen,review]{acmart}
-%\documentclass[acmconf,screen,review]{acmart}
-\documentclass[screen,review]{acmart}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%% REMOVE FOLLOWING LINE BEFORE SUBMITTING %%%%%%%%%
+\setlength {\marginparwidth }{2cm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{todonotes}
-\usepackage{comment}
 \usepackage{wrapfig}
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2021}
-\acmYear{2021}
-\acmDOI{}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[JCDL '21]{JCDL '21: Joint Conference on
-  Digital Libraries, September 27--30, 2021, Urbana--Champaign, Illinois, USA}
-%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  %June 03--05, 2018, Woodstock, NY}
-%\acmPrice{15.00}
-%\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
+\usepackage{hyperref}
+\usepackage{xurl}
+\usepackage{booktabs}
+\usepackage{float}
+\usepackage[noadjust]{cite}
+
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 \begin{document}
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-\title{Automated Metadata Generation for Fish Specimen Image Collections}
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{Joel Pepper}
-\email{jcp353@drexel.edu}
-\orcid{0002-1601-8729}
-\author{Jane Greenberg}
-\orcid{0001-7819-5360}
-\affiliation{%
-  \institution{Drexel University}
-  \streetaddress{3675 Market St}
-  \city{Philadelphia}
-  \state{Pennsylvania}
-  \country{USA}
-  \postcode{19104}
+\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
+    {\footnotesize \thanks{NSF Grant ???} }}
+%do we add grant now, or wait til acceptance.
+i think we need to ultimately remove any identifying info., i think bgnn is likely okay; but, perhaps mention metadata research center (MRC) need to be removed?.
+if so, i kind of like to put it back in for final version, if accepted.
+it helps with getting funding ...
+you are both listed on the MRC page.
+we should check on the identifying info.
+removed, or not.
+%for the record: Research supported by NSF OAC #1940233 and #1940322.
+
+\author{
+\IEEEauthorblockN{Joel Pepper}
+\IEEEauthorblockA{\textit{Department of Computer Science} \\
+\textit{Drexel University}\\
+Philadelphia, USA\\
+0000-0002-1601-8729}
+\and
+\IEEEauthorblockN{Jane Greenberg}
+\IEEEauthorblockA{\textit{Department of Information Science} \\
+\textit{Drexel University}\\
+Philadelphia, USA\\
+0000-0001-7819-5360}
+\and
+\IEEEauthorblockN{Yasin Baki\c{s}}
+\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
+\textit{Tulane University}\\
+New Orleans, USA\\
+0000-0001-6144-9440}
+\and
+\IEEEauthorblockN{Xiaojun Wang}
+\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
+\textit{Tulane University}\\
+New Orleans, USA\\
+0000-0001-8639-6795}
+\and
+\IEEEauthorblockN{Henry Bart Jr.}
+\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
+\textit{Tulane University}\\
+New Orleans, USA\\
+0000-0002-5662-9444}
+\and
+\IEEEauthorblockN{David Breen}
+\IEEEauthorblockA{\textit{Department of Computer Science} \\
+\textit{Drexel University}\\
+Philadelphia, USA\\
+0000-0002-1376-5008}
 }
-\author{Yasin Baki\c{s}}
-\orcid{0001-6144-9440}
-\author{Henry Bart Jr.}
-\orcid{0002-5662-9444}
-\affiliation{
-  \institution{Tulane University}
-  \city{New Orleans}
-  \state{Louisiana}
-  \country{USA}
-}
-\author{David Breen}
-\orcid{0002-1376-5008}
-\affiliation{%
-  \institution{Drexel University}
-  \streetaddress{3675 Market St}
-  \city{Philadelphia}
-  \state{Pennsylvania}
-  \country{USA}
-  \postcode{19104}
-}
-
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Pepper, Greenberg, Baki\c{s}, Bart and Breen}
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
+
+\maketitle
+
+%abstract can be shortened a good bit.
+%can offer an alternative manana..
 \begin{abstract}
-%%    \todo{Just throwing the Hank conference abstract in here for us to work off of and pare down. Also, we need to decide what to do for the ``teaser image''.} 
-%    Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
-One area of considerable activity is the digitization of the biological specimens that have been collected worldwide by museums and other research institutions.
-The scanning of these specimen collections and the placement of the resulting images into easily accessible repositories on the Internet is enabling new scientific studies based on the previously unavailable data.
-Unfortunately, potential scientific advances are hindered by the lack of high-quality and pertinent metadata associated with the image collections.
-Metadata is required to search the repositories for the imaged specimens needed for a particular study.
-Since the collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
-Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
-
      Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
@@
 A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
-
-% Metadata is often unavailable, sparse or incorrect within specimen image repositories, but is vital for subsequent machine learning, analysis and scientific discovery.
-Our goal is to develop image metadata generation methods that both support the novel machine learning research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
-A longer term goal is to extend the image analysis methods for computing specific quantitative features in support of specific biological investigations.
-For example, we are able to automatically measure the length of a fish specimen.
-Associating these measurements with location and acquisition date may provide insights into the influence of habitat factors on fish development/health.
-Since it is prohibitively expensive for scientists to manually gather this data, we are also interested in applying our tools to images of other species stored in a variety of repositories (e.g.
-iDigBio).
-The technical challenges in achieving a broader usage of our approach mostly involve training new classifiers for different types of species, learning to segment and read annotation tags, and generalizing our classifier to find and interpret different types of rulers.
-This presentation will report on our current efforts to automatically generate metadata for fish specimen images and offer thoughts on how to extend these techniques for other specimen image collections.
 \end{abstract}
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
-   <concept>
-       <concept_id>10002951.10002952.10003219.10003215</concept_id>
-       <concept_desc>Information systems~Extraction, transformation and loading</concept_desc>
-       <concept_significance>500</concept_significance>
-   </concept>
-   <concept>
-        <concept_id>10010147.10010178</concept_id>
-	<concept_desc>Computing methodologies~Artificial intelligence~Computer Vision</concept_desc>
-	<concept_significance>500</concept_significance>
-    </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Information systems~Extraction, transformation and loading}
-\ccsdesc[500]{Computing methodologies~Artificial intelligence}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{bioinformatics, metadata, image analysis, applied machine learning}
-
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-\begin{teaserfigure}
-  \centering
-  \includegraphics[width=.45\textwidth]{images/teaser1_crop}
-  \hspace{4mm}
-  \includegraphics[width=.45\textwidth]{images/teaser2_crop}
-  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
-  \Description{Fish predictions}
-  \label{fig:teaser}
-\end{teaserfigure}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
+\begin{IEEEkeywords}
+bioinformatics, metadata, image analysis, applied machine learning
+\end{IEEEkeywords}
 
 \section{Introduction}
-
-\todo{Sentences I didn't use: Over the last few decades, cyberinfrastructure development, advances in digitization, and the open science tenor, have helped support global access to natural history. OR
-Global access to natural history collections has accelerated over the last few decades to advances in cyberinfrastructure, digitization, and the general open science tenor}
-
-Over the last several decades advances in computing, imaging, and
-cyberinfrastructure have supported the growth of digital natural history collections; thus supporting the trends towards open scienc.
-In the U.S., programs, such as the National Science Foundation’s former
-Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for
-nearly a decade, and the current Infrastructure Capacity for Biological Research program have supported the digital acquisition and dissemination of
-data and images for millions of biological specimens.
-These resources are globally available through a wide range of portals and digital libraries for researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
-Significant challenges surface, however, when researchers seek to apply computational methods to these data items,
-due to both image quality and metadata issues.
-% (As researchers seek to apply computational methods, and explore AI, significant challenges surface..)
+% Moving teaser since this template doesn't actually ask for one
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.~\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.~\cite{page2015digitization} These digital specimen accessible through global, open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
+Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
+%{jane}should we try to insert machine learning here, last sentence, or computation methods ok?
 
@@
 \section{Related Work}
-\textbf{Todo}
-\subsection{Metadata for Image Collection}
-\todo{Wasn't looking for a citation but stumbled upon this paper: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0207636}, might be worth a skim}
-Metadata development is intertwined with the development of digital technology.
-A wide range of metadata standards are applicable to metadata supporting image description as well as technical aspects, and have been used in a range of image repositories.
-Examples of Descriptive schemes include X, y, z...
-Examples of technical schemes include...
-The use varies across communities, and application technique is primarily manual.
-Research evaluating such schemes XXX, show XXX.
-
-Natural history collections generally use a sub-set of such standards.
-Darwin Core, a globally adopted standard overseen by the Taxonomic Data Working Group (TDWG).
-[Jane continue here on some of this, and then with preservation/image quality less]
-
-Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS},
-
-\subsection{Metadata generation?}
+\subsection{Metadata for Natural History Image Collection}
+%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.
+A number of different metadata standards have been applied to support the description and access of digitized scientific images.
+Darwin Core~\cite{biodiv_info_standards} developed specifically for digital museum projects is one of the most frequently used standards.
+Another approach is to create a metadata application profile by integrating properties from Dublin Core's DCMI Metadata Terms \cite{dc_terms}, the Ecological Metadata Language (EML) \cite{EML_2019} and other namespaces.
+There is also the recent Audubon Core supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.\cite{audub_core} These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
+In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels.
+This task is labor intensive, and the metadata associated with each digital rendering is limited, particularly for researchers seeking to apply machine learning, and leverage both the image and the metadata for scientific research.
+
+This limitation is magnified when trying get a handle on the actual quality of the digitized specimen.
+Descriptive oriented standards support search and retrieval, and the biodiversity community advocated for data fitness standards \cite{chapman2020developing}.
+Even so, metadata properties used to record image quality is severely limited and generally missing.
+This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bgnn.
+Although, the manual generation of this metadata is costly in terms of labor and time.
+
+%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS},
+
+\subsection{Automatic Metadata Generation}
+Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX.
+Some of this metadata may be useful in for selecting a machine learning sample.
+A researcher may desire images captured chiefly with a certain aperture setting.
+Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to reply on manually generated descriptive metadata, which itself is sparse.
+
+Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating}.
+Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.
+
+%\cite{heidorn2008automatic} speciment labels \cite{manso2004automatic} cartographic info.
+%above paragraph..need to finesse a couple of sentences w/results, weave in these 2 citations, and then say we can look to image analysis.
 
@@
 \subsection{Metadata Generation}
-Including what has already been discussed, the following metadata properties are being currently being generated:
-
-\begin{table}[t]
-    \centering
-    \caption{Metadata properties}
-    \label{tab:properties}
-    \begin{tabular}{cccp{0.5\linewidth}}
-        \toprule
-        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
-        \midrule
-        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
-        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
-        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
-        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
-        \verb|scale| & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
-        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of what define the bounding box for a fish.\\
-        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
-        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
-        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
-        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
-        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
-        \verb|primary_axis| & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
-        \verb|clock_value| & Per Fish & Integer & A fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
-        \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
-        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
-        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish.
-If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
-        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
-        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
-        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
-        \verb|side| & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
-      \bottomrule
-\end{tabular}
-\end{table}
-
-\verb|has_fish|, \verb|fish_count|, \verb|has_ruler|, \verb|ruler_bbox|, \verb|background.*|, \verb|foreground.*|, \verb|bbox|, \verb|mask|, \verb|score|, and \verb|has_eye| have already been discussed.
-The remaining properties are determined as follows:
+
+The following metadata properties are generated from the methods
+described above:
+\verb|has_fish|, \verb|fish_count|, \verb|has_ruler|, \verb|ruler_bbox|, \verb|background.{mean,std}|, \verb|foreground.{mean,std}|, \verb|bbox|, \verb|mask|, \verb|score|, and \verb|has_eye|.
+The remaining properties are computed as described below, with all the
+metadata properties listed in Table \ref{tab:properties}.
+
 \subsubsection{centroid and eye\_center}
-Centroids are provided for masks/bounding boxes generated by \verb|detectron|, and since we do not recalculate the mask of fish eyes we can use that value directly for \verb|eye_center|.
+Centroids are provided for the masks and bounding boxes generated by \verb|detectron|, and since we do not recalculate the mask of fish eyes we can use that value directly for \verb|eye_center|.
 
@@
 \subsubsection{primary\_axis and clock\_value}
-The \verb|primary_axis| of a fish can be calculated by taking the covariance\todo{I could explain this in more detail if necessary} of its blob in \(x\) and \(y\), which yields its principle eigenvector.
-This can be directly assigned to the property.
-If an eye is present, we specify this axis in the direction of the eye in relation to the fish's centroid.
-
-Our team encoded this information as a ``clock value'' between 1 and 12 when recording it by hand.
-To convert \verb|principal_axis| to \verb|clock_value|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish is angles into relative to its centroid.
-Depending on this quadrant, we then dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\) which correspond to 9, 6, 3 and ``0'' o'clock respectively.
+The \verb|primary_axis| of a fish can be calculated by taking the covariance\todo{I could explain this in more detail if necessary.
+(DEB No, that's OK.} of its blob in \(x\) and \(y\), which yields its principle eigenvector.
+The eigenvector can be directly assigned to the property. If an eye is
+present, we ensure that \verb|primary_axis| points in the direction of the
+eye in relation to the fish's centroid.
+
+Our team encoded this information as a ``clock value'' between 1 and 12 when manually recording it.
+To convert \verb|principal_axis| to \verb|clock_value|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish angles into relative to its centroid.
+Depending on this quadrant, we dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\), which correspond to 9, 6, 3 and ``0'' o'clock respectively.
 The resulting radian value is then converted to a polar displacement in clock value space, and added to the comparative clock value used in the dot product.
-This then gives the fish's clock value from 0 to \(11.\overline{9}\).
-Before recording as \verb|clock_value| in the output, the value is rounded to the nearest integer, and in the event of a 0 final result it is replaced with 12.
+This gives the fish's clock value from
+0 to \(11.\overline{9}\). Before recording \verb|clock_value| in the output,
+the value is rounded to the nearest integer, with a 0 final result replaced with 12.
 \subsubsection{scale and length}
-\(\frac{\mathrm{pixels}}{\mathrm{inch}}\) can be calculated by measuring the distance between the digits 2 and 3 found on the ruler by \verb|detectron|.
+\(\frac{\mathrm{pixels}}{\mathrm{inch}}\) can be calculated by measuring the distance in pixels between the digits 2 and 3 (a 1 inch separation) found on the ruler by \verb|detectron|.
 Converting this to \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) gives the \verb|scale| metadata property as reported in the output.
 
-For the fish \verb|length| property, it is necessary to determine the furthest points from the centroid of the fish in each direction.
-Since fish are normally measured in a straight line from their snout down the middle of their trunk, we project every pixel onto the major axis of the fish (as a line through its centroid) before checking the distance.
-This projection is done by intersecting the line through the point along the tangent of the principal axis and the aforementioned centroid--principal axis line.
-After checking every pixel, measuring the distance between the two furthest projected points gives the length of the fish in pixels.
-Multiplying this by \verb|scale| gives the fish \verb|length| in centimeters.
+For the fish \verb|length| property, it is necessary to determine the furthest points from the centroid of the fish in each direction along its major
+axis. Since fish are normally measured in a straight line from their snout down the middle of their trunk, every pixel of the fish blob is projected
+onto the fish's major axis (as a line through its centroid).
+The projection is done by finding the closest point on the
+centroid--principal axis line from the pixel's location.
+% intersecting the line through the point along the tangent of the principal axis and the aforementioned centroid--principal axis line.
+After processing every pixel in the fish blob, computing the distance
+between the two furthest projected points gives the length of the fish in pixels. Multiplying this distance by \verb|scale| gives the fish \verb|length| in centimeters.
 \begin{comment}
@@
 \(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images.
-Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and meet our current admissibility criteria for what \verb|detectron| and the pixel analysis process can reliably handle.
+Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and met our current admissibility criteria for \verb|detectron| and pixel analysis processing.
 We ran the metadata extraction program on these \(7,244\) images.
+For the properties of image scale, fish length, and fish bounding boxes
+(properties not manually generated),
+a random sample of 50 specimens from the set of \(7,244\) were analyzed by
+hand for comparison.
 
@@
 \subsection{Ruler Detection}
-For all but 2 of the \(7,244\) images \verb|detectron| was able to find the ruler.\todo{Not sure if I can phrase it that way or not since I haven't looked at all the images to see if the ruler itself was found or something else was labeled a ruler} For an additional 56 images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed.
+For all but 2 of the \(7,244\) images \verb|detectron| was able to find the ruler, a nearly perfect correct rate.
+% \todo{Not sure if I can phrase it that way or not since I haven't looked at all the images to see if the ruler itself was found or something else was labeled a ruler}
+In 56 of the images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed, producing a 99.2\% success rate for
+the \verb|scale| computation.
 
 \subsection{Side Detection}
-For 246 of the images \verb|detectron| was unable to find a fish eye. Of the remaining \(6,998\) images where it did, the correct side (\verb|left| or \verb|right|) was detected in all but 6 cases.
+\verb|detectron| was unable to find a fish eye
+in 246 of the images. Of the remaining \(6,998\) images, the correct side
+(\verb|left| or \verb|right|) was detected in all but 6 cases, producing
+a 96.5\% correct rate.
+\todo{Comment on the 6 cases. What failed?}
 
 \subsection{Clock Value}
-Clock position values were successfully generated for \(6,991\) of the images. Of those, all but 8 were within \(\pm{}1\) of the correct result.
+Clock position values were successfully generated for \(6,991\) of the images. Of those, all but 8 were within \(\pm{}1\) of the correct result,
+our definition of a correct/acceptable result. The correct rate for this
+computation is 96.4\%.
+\todo{Comment on the cases where we were unable to compute clock value. What failed?}
+
+\subsection{Foreground/Background Contrast Results?}
+\textbf{Todo}: It would be great to compute a histogram of foreground.mean -
+bakground.mean for the all our samples.
+Perhaps it would then be obvious how to break the images into low, medium
+and high F/B contrast.  We could show a representative image from each
+group.
 
 \subsection{Brightness/Uniformity Results?}
-\textbf{Todo}: I can try to do this but I need to set up the infrastructure, we probably need to discuss a plan of action for this.
-
-\subsection{Mask and Bounding Box}
-\begin{figure}[H]
+\textbf{Todo}: Need standard deviations here, too. To show that the
+differences are significant and meaningful. Clearly the trend is there.\newline
+It looks like we should leave out Uniformity.
+
+\begin{verbatim}
+Mean intensity in bounding box | Count
+
+dark: 153.94935240158551 | 1800
+normal: 168.2924981358199 | 5186
+bright: 177.68854540643943 | 242
+\end{verbatim}
+\begin{verbatim}
+Standard Deviations for:
+    Uniform: 12.554834863869324
+    Not Uniform: 11.312181711328828
+\end{verbatim}
+
+\begin{figure}[t]
   \centering
@@
   \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}
-  \Description{Bounding box and mask examples}
+  \label{fig:bbox_mask}
 \end{figure}
+
+\subsection{Mask and Bounding Box}
 Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found.
 All but 263 of these were generated via pixel analysis, with those 263 falling back to the original \verb|detectron| bounding box.
-\textbf{Todo}: Anything more than this is going to need hand checked.
-
-\subsection{Length}
-Fish lengths were calculated for \(7,179\) of the images. \textbf{Todo}: Anything more than this is going to need hand checked.
-\begin{comment}
-\begin{verbatim}
-What I think should be the final results:
-
-Right: 6956
-Errored: 0
-No eye: 246
-No fish: 10
-Wrong wrong: 35
-Total: 7247
-Percent right: 0.959845453291017
-Percent right that didn't error: 0.9949935631526248
-
------------------------
-
-Pixel analysis failed: 0.036336004421110804
-
------------------------
-
-My hand checking of the ''wrong wrong'' fish:
-               My guess, Yasin spreadsheet
-INHS_FISH_101109.jpg: 9, 11, I'm wrong although it's fairly curved
-INHS_FISH_56818.jpg: 4, 2, I'm wrong although there's a tag that is likely messing things up
-INHS_FISH_57607.jpg: 3, 9, I'm wrong
-INHS_FISH_57001.jpg: 4, 2, I'm wrong although there's a tag that is likely messing things up
-INHS_FISH_63953.jpg: 3, 9, I'm wrong
-INHS_FISH_51100.jpg: 3, 9, I'm wrong
-INHS_FISH_80528.jpg: 3, 8, I'm wrong
-INHS_FISH_6370.jpg: 3, 9, I'm wrong
-INHS_FISH_54157.jpg: 9, 7, I'm arguably wrong although it's very curved
-INHS_FISH_80987.jpg: 9, 3, I'm wrong although this one is a fairly atypical image
-
-INHS_FISH_58647.jpg: 9, 7, I'm right
-INHS_FISH_8415.jpg: 9, 6, I'm right
-INHS_FISH_5041.jpg: 9, 11, very curved averages to about 9
-INHS_FISH_52821.jpg: 9, 7, I'm arguably right although the fish is damaged and its head points to ~7
-INHS_FISH_6696.jpg: 9, 7, I'm right
-INHS_FISH_75252.jpg: 9, 6, I'm right
-INHS_FISH_79498.jpg: 9, 6, I'm right
-INHS_FISH_45744.jpg: 9, 5, I'm right
-INHS_FISH_47579.jpg: 9, 6, I'm right
-INHS_FISH_64599.jpg: 9, 6, I'm right
-INHS_FISH_74550.jpg: 9, 5, I'm right
-INHS_FISH_101664.jpg: 9, 6, I'm right
-INHS_FISH_100861.jpg: 9, 6, I'm right
-INHS_FISH_60589.jpg: 3, 9, I'm right
-INHS_FISH_53469.jpg: 9, 1, I'm right
-INHS_FISH_44694.jpg: 9, 6, I'm right
-INHS_FISH_54921.jpg: 9, 6, I'm right
-INHS_FISH_44645.jpg: 10, 8, I'm right
-INHS_FISH_50459.jpg: 9, 11, I'm right although the fish is damaged and its head points to ~11
-INHS_FISH_68061.jpg: 9, 6, I'm right
-INHS_FISH_74716.jpg: 9, 6, I'm right
-INHS_FISH_80976.jpg: 9, 6, I'm right
-INHS_FISH_57977.jpg: 9, 6, I'm right
-INHS_FISH_45377.jpg: 9, 6, I'm right
-INHS_FISH_47142.jpg: 9, 6, I'm right
-
-Verdict: For only 10 of the 35 am I actually wrong and all of those are either curved, atypical
-images with tags, or something on the wrong side was detected as an eye (so the clock value is backwards).
-
-\end{verbatim}
-\end{comment}
+50 randomly-chosen images were reviewed manually to evaluate the
+calculation, a representative sample are presented in
+Figure \ref{fig:bbox_mask}.
+All 50 masks and bounding boxes were correctly placed
+on/around the location of the fish. However, a number of them lacked portions of lightly colored tails and/or fins.
+Specifically, 22 masks and bounding boxes covered the entire fish,
+16 missed some of the tail, and 12 missed most or all of the tail.
+
+\subsection{Scale and Length}
+Image scale and fish lengths were calculated for \(7,179\) of the images.
+\todo{What happened the excluded images?}
+Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
+measured, using ImageJ~\cite{imagejCite}, in the same(?) 50 test images.
+% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ.~\cite{imagejCite}
+In this subset of images the average error for the scale calculation
+was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
 
@@
   \includegraphics[width=0.49\linewidth]{images/curved1}
-  %\includegraphics[width=0.49\linewidth]{images/}
   \caption{An example of a heavily curved specimen.}
-  \Description{Mislabeled eye on a catfish}
 \end{figure}
@@
 \subsubsection{Mask and Bounding Box}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/61631}
+  \includegraphics[width=0.49\linewidth]{images/61631_mask}
+  \caption{An example of a light colored tail being missed during the pixel analysis process.}
+\end{figure}
+Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work?
+Or both?}
 
 \subsubsection{Brightness?}
-
-\subsubsection{Length}
+\textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
+Brightness results are are in previous section.
+Need to think about what is worth noting since it's a fairly trivial result.}
+
+\subsubsection{Scale and Length}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/54172}
+  \includegraphics[width=0.49\linewidth]{images/54172_mask}
+  \caption{An example of a light colored tail being missed during the pixel analysis process.}
+  \label{fig:scale_len}
+\end{figure}
+Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler.
+When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well.
+An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm).
+Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
 
 \subsection{Future Work}
-\begin{itemize}
-    \item Further fine tuning of pixel analysis (e.g.\ thresholding on different regions of the bbox).
-    \item Generalizing ruler reading.
-    \item Training on a progressively larger number of image collections to hopefully gain reasonable generality for the whole class of fish specimen images.
-    \item Adding things like seahorses and eels.
-    \item Fitting a ``spine'' to specimen.
-\end{itemize}
+The most pressing next step is to refine the pixel analysis thresholding process so that the entirety of even light colored fish are marked as foreground in the mask.
+A deficiency of the current process is that it only operates on single channel intensity.
+Some of the lightest tails appear yellow in hue to the human eye and easily distinguishable, but when compressed to a single intensity value they are almost identical in value to the white background.
+Considering when the RGB channels of a pixel are not equal in value may be able to improve masking of such features.
+Another possible approach to solving this is to threshold an mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.
+
+Our ultimate goal is to create a generalized process to work on classes of specimen images (specifically all fish images for BGNN), not only the INHS collection.
+To accomplish this, a much larger training dataset full of more diverse images will be required.
+Another requirement will be to generalize the ruler reading process beyond the INHS specific reading of digits on the ruler.\todo{Suggest way(s) to do this?}
+% Todo: Are these worth mentioning?
+%Adding things like seahorses and eels.
+%Fitting a ``spine'' to specimen.
 \section{Conclusion}
@@
 
-\bibliographystyle{ACM-Reference-Format}
+\section*{Acknowledgment}
+%can make possible note about larger BGNN team, and/or general note to Tulane data in-putters for giving us data to compare, and/or INHS collection. [we can discuss]
+
+\bibliographystyle{IEEEtran}
 \bibliography{paper}
 
-%\begin{figure}[H]
-%  \centering
-%  \includegraphics[width=\linewidth]{images/}
-%  \caption{}
-%  \Description{}
+\end{document}
+
+%\begin{table}[htbp]
+%\caption{Table Type Styles}
+%\begin{center}
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+%\cline{2-4} 
+%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+%\hline
+%copy& More table copy$^{\mathrm{a}}$& &  \\
+%\hline
+%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+%\end{tabular}
+%\label{tab1}
+%\end{center}
+%\end{table}
+
+%\begin{figure}[htbp]
+%\centerline{\includegraphics{fig1.png}}
+%\caption{Example of a figure caption.}
+%\label{fig}
 %\end{figure}
-
-\begin{comment}
-\pagebreak{}
-\section{Introduction}~\label{demo-intro}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
-
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
-
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
-
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
-
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[acmsmall]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-Always use midrule to separate table header rows from data rows, and
-use it only for this purpose. This enables assistive technologies to
-recognise table headers and support their users in navigating tables
-more easily.
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  %\includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader.
-
-Figure captions are placed {\itshape below} the figure.
-
-Every figure should also have a figure description unless it is purely
-decorative. These descriptions convey what’s in the image to someone
-who cannot see it. They are also used by search engine crawlers for
-indexing images, and when images cannot be loaded.
-
-A figure description must be unformatted plain text less than 2000
-characters long (including spaces).  {\bfseries Figure descriptions
-  should not repeat the figure caption – their purpose is to capture
-  important information that is not already provided in the caption or
-  the main text of the paper.} For figures that convey important and
-complex new information, a short text description may not be
-adequate. More complex alternative descriptions can be placed in an
-appendix and referenced in a short figure description. For example,
-provide a data table capturing the information in a bar chart, or a
-structured list representing a graph.  For additional information
-regarding how best to write figure descriptions and why doing this is
-so important, please see
-\url{https://www.acm.org/publications/taps/describing-figures/}.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{paper}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
-\end{comment}
-
-\end{document}
-\endinput
-%%
-%% End of file `sample-acmsmall-conf.tex'.

### 2021-03-31 paper/paper_new.tex
Committing to pull
Added histogram (without labels yet)

@@
 \subsection{Brightness/Uniformity Results?}
-\textbf{Todo}: Need standard deviations here, too. To show that the
-differences are significant and meaningful. Clearly the trend is there.\newline
-It looks like we should leave out Uniformity.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\linewidth]{images/histo}
+  \caption{Histogram for brightness.}
+\end{figure}
+\textbf{Todo}: It looks like we should leave out Uniformity.
 
 \begin{verbatim}
-Mean intensity in bounding box | Count
+Mean intensity in bounding box | Std
+        | Count
 
-dark: 153.94935240158551 | 1800
-normal: 168.2924981358199 | 5186
-bright: 177.68854540643943 | 242
+dark: 153.94935240158566 |
+        15.526143315470392 | 1800
+normal: 168.2924981358199 |
+        14.214506494349248 | 5186
+bright: 177.68854540643952 |
+        12.401282979349904 | 242
 \end{verbatim}

### 2021-03-31 paper/paper_DEB.tex
Got rid of duplicate Leipzig refs.  Correct .bib entry for it.

@@
 \section{Results}
-Technicians employed by our team have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{Leipzig2021.01.28.428644} for a large number of INHS images.
+Technicians employed by our team have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{leipzig2021biodiversity} for a large number of INHS images.
 \(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images.

### 2021-03-31 paper/paper_new.tex
Added images
Updates from Overleaf
Merged most of Sect. 6 into Sect. 5.

@@
 
+\begin{itemize}
+    \item Worked fairly well all things considered
+    \item Talk about which fish failed
+    \item Talk about which rulers failed
+\end{itemize}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
+  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
+  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
+\end{figure}
+
 \subsection{Side Detection}
@@
 
+There were six cases where an eye was detected but the \verb|side| value
+was wrong. Here, a spot on the wrong side of the fish was labeled as the
+most likely eye within the bounding box of the fish, i.e.~eye detection 
+was incorrect.
+There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
+For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
+This result highlights the additional utility of automated methods to
+double-check and verify human-generated metadata.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/none1}
+  \includegraphics[width=0.49\linewidth]{images/double1}
+  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
+\end{figure}
+
 \subsection{Clock Value}
@@
 \todo{Comment on the cases where we were unable to compute clock value. What failed?}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/curved1}
+  \caption{An example of a heavily curved specimen.}
+  \label{fig:curvedFish}
+\end{figure}
+Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
+For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
+Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
+seen in Figure \ref{fig:curvedFish}.
+The other 6 were values of 3 instead of 9 or vice versa, which resulted from
+a mislabeled eye as discussed in the previous section.
+\todo{Why is the following sentence here? What does it have to do with
+Clock Value?}
+A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.
+These tags were light enough that they were correctly labeled as background by the pixel analysis.
 
@@
   \centering
+  \includegraphics[width=0.49\linewidth]{images/dark}
+  \includegraphics[width=0.49\linewidth]{images/normal}
+  \includegraphics[width=0.49\linewidth]{images/bright}
+  \caption{Examples of low, normal and high contrast fish images.}
+\end{figure}
+\begin{figure}[H]
+  \centering
   \includegraphics[width=\linewidth]{images/histo}
-  \caption{Histogram for brightness.}
+  \caption{Histogram for difference in brightness between foreground an background.}
 \end{figure}
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/61631}
+  \includegraphics[width=0.49\linewidth]{images/61631_mask}
+  \caption{A fish for which the masking and measurement process was highly accurate.}
+\end{figure}
+Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work?
+Or both?}
+
 \subsection{Scale and Length}
@@
 
-\section{Discussion}
-\textbf{Todo}: Will need some sort of intro/framing paragraph
-%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation.
-Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
-%Discussion needed to weave in at least a couple of citations. Happy to discuss
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/none1}
-  \includegraphics[width=0.49\linewidth]{images/double1}
-  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
-\end{figure}
-\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
-\subsubsection{Object Detection}
-
-\begin{itemize}
-    \item Worked fairly well all things considered
-    \item Talk about which fish failed
-    \item Talk about which rulers failed
-\end{itemize}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
-  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
-  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
-\end{figure}
-\subsubsection{Side Detection}
-There were six cases where an eye was detected but the \verb|side| value
-was wrong. Here, a spot on the wrong side of the fish was labeled as the
-most likely eye within the bounding box of the fish, i.e.~eye detection 
-was incorrect.
-There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
-For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
-This result highlights the additional utility of automated methods to
-double-check and verify human-generated metadata.
-
-\subsubsection{Clock Value}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/curved1}
-  \caption{An example of a heavily curved specimen.}
-  \label{fig:curvedFish}
-\end{figure}
-Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
-For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
-Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
-seen in Figure \ref{fig:curvedFish}.
-The other 6 were values of 3 instead of 9 or vice versa, which resulted from
-a mislabeled eye as discussed in the previous section.
-\todo{Why is the following sentence here? What does it have to do with
-Clock Value?}
-A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.
-These tags were light enough that they were correctly labeled as background by the pixel analysis.
-
-\subsubsection{Mask and Bounding Box}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/61631}
-  \includegraphics[width=0.49\linewidth]{images/61631_mask}
-  \caption{An example of a light colored tail being missed during the pixel analysis process.}
-\end{figure}
-Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work?
-Or both?}
-
-\subsubsection{Brightness?}
-\textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
-Brightness results are are in previous section.
-Need to think about what is worth noting since it's a fairly trivial result.}
-
-\subsubsection{Scale and Length}
 \begin{figure}[H]
@@
 Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
+
+\section{Discussion}
+\textbf{Todo}: Will need some sort of intro/framing paragraph
+%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation.
+Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
+%Discussion needed to weave in at least a couple of citations. Happy to discuss
+
+\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
+
+\subsubsection{Brightness?}
+\textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
+Brightness results are are in previous section.
+Need to think about what is worth noting since it's a fairly trivial result.}
 

### 2021-03-31 paper/paper_new.tex
Cropped images and other minor tweaks

@@
 
-\begin{itemize}
-    \item Worked fairly well all things considered
-    \item Talk about which fish failed
-    \item Talk about which rulers failed
-\end{itemize}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
-  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
-  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
-\end{figure}
-
 \subsection{Side Detection}
@@
 
-There were six cases where an eye was detected but the \verb|side| value
-was wrong. Here, a spot on the wrong side of the fish was labeled as the
-most likely eye within the bounding box of the fish, i.e.~eye detection 
-was incorrect.
-There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
-For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
-This result highlights the additional utility of automated methods to
-double-check and verify human-generated metadata.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/none1}
-  \includegraphics[width=0.49\linewidth]{images/double1}
-  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
-\end{figure}
-
 \subsection{Clock Value}
@@
 
+\subsection{Foreground/Background Contrast Results?}
 \begin{figure}[H]
   \centering
-  \includegraphics[width=0.49\linewidth]{images/curved1}
-  \caption{An example of a heavily curved specimen.}
-  \label{fig:curvedFish}
+  \includegraphics[width=\linewidth]{images/histo}
+  \caption{Histogram for difference in brightness between foreground an background.}
 \end{figure}
-Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
-For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
-Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
-seen in Figure \ref{fig:curvedFish}.
-The other 6 were values of 3 instead of 9 or vice versa, which resulted from
-a mislabeled eye as discussed in the previous section.
-\todo{Why is the following sentence here? What does it have to do with
-Clock Value?}
-A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.
-These tags were light enough that they were correctly labeled as background by the pixel analysis.
-
-\subsection{Foreground/Background Contrast Results?}
-\textbf{Todo}: It would be great to compute a histogram of foreground.mean -
-bakground.mean for the all our samples.
-Perhaps it would then be obvious how to break the images into low, medium
-and high F/B contrast.  We could show a representative image from each
-group.
 
@@
 \end{figure}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=\linewidth]{images/histo}
-  \caption{Histogram for difference in brightness between foreground an background.}
-\end{figure}
 \textbf{Todo}: It looks like we should leave out Uniformity.
@@
 \begin{verbatim}
+This is for average foreground intensity
+(i.e. the fish pixels)
 Mean intensity in bounding box | Std
@@
 
-dark: 153.94935240158566 |
-        15.526143315470392 | 1800
-normal: 168.2924981358199 |
-        14.214506494349248 | 5186
-bright: 177.68854540643952 |
-        12.401282979349904 | 242
+dark: 75.14548320341247 | 13.491022754871715
+        | 1800
+normal: 93.63755945070938 | 14.781004083081378
+        | 5186
+bright: 108.39315328695254 | 15.210726241270661
+        | 242
 \end{verbatim}
@@
 
+\subsection{Scale and Length}
+Image scale and fish lengths were calculated for \(7,179\) of the images.
+\todo{What happened the excluded images?}
+Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
+measured, using ImageJ,~\cite{imagejCite} in the same(?) 50 test images.
+% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ.~\cite{imagejCite}
+In this subset of images the average error for the scale calculation
+was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
+
+\section{Discussion}
+\textbf{Todo}: Will need some sort of intro/framing paragraph
+%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation.
+Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
+%Discussion needed to weave in at least a couple of citations. Happy to discuss
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/none1}
+  \includegraphics[width=0.49\linewidth]{images/double1}
+  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
+\end{figure}
+\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
+\subsubsection{Object Detection}
+
+\begin{itemize}
+    \item Worked fairly well all things considered
+    \item Talk about which fish failed
+    \item Talk about which rulers failed
+\end{itemize}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
+  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
+  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
+\end{figure}
+\subsubsection{Side Detection}
+There were six cases where an eye was detected but the \verb|side| value
+was wrong. Here, a spot on the wrong side of the fish was labeled as the
+most likely eye within the bounding box of the fish, i.e.~eye detection 
+was incorrect.
+There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
+For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
+This result highlights the additional utility of automated methods to
+double-check and verify human-generated metadata.
+
+\subsubsection{Clock Value}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/curved1}
+  \caption{An example of a heavily curved specimen.}
+  \label{fig:curvedFish}
+\end{figure}
+Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
+For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
+Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
+seen in Figure \ref{fig:curvedFish}.
+The other 6 were values of 3 instead of 9 or vice versa, which resulted from
+a mislabeled eye as discussed in the previous section.
+\todo{Why is the following sentence here? What does it have to do with
+Clock Value?}
+A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.
+These tags were light enough that they were correctly labeled as background by the pixel analysis.
+
+\subsubsection{Mask and Bounding Box}
 \begin{figure}[H]
@@
   \includegraphics[width=0.49\linewidth]{images/61631_mask}
-  \caption{A fish for which the masking and measurement process was highly accurate.}
+  \caption{An example of a light colored tail being missed during the pixel analysis process.}
 \end{figure}
@@
 
-\subsection{Scale and Length}
-Image scale and fish lengths were calculated for \(7,179\) of the images.
-\todo{What happened the excluded images?}
-Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
-measured, using ImageJ~\cite{imagejCite}, in the same(?) 50 test images.
-% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ.~\cite{imagejCite}
-In this subset of images the average error for the scale calculation
-was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
+\subsubsection{Brightness?}
+\textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
+Brightness results are are in previous section.
+Need to think about what is worth noting since it's a fairly trivial result.}
 
+\subsubsection{Scale and Length}
 \begin{figure}[H]
@@
   \includegraphics[width=0.49\linewidth]{images/54172_mask}
-  \caption{An example of a light colored tail being missed during the pixel analysis process.}
+  \caption{A fish for which the masking and measurement process was highly accurate.}
   \label{fig:scale_len}
@@
 Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
-
-\section{Discussion}
-\textbf{Todo}: Will need some sort of intro/framing paragraph
-%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation.
-Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
-%Discussion needed to weave in at least a couple of citations. Happy to discuss
-
-\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
-
-\subsubsection{Brightness?}
-\textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
-Brightness results are are in previous section.
-Need to think about what is worth noting since it's a fairly trivial result.}
 

### 2021-03-31 paper/paper_new.tex
Fixed formatting in author list.
Added states in addresses.

--- 2021-03-31 paper/paper_new.tex
@@
 \textit{Drexel University}\\
-Philadelphia, USA\\
-0000-0002-1601-8729}
+Philadelphia, PA\hspace{3mm}USA\\
+0000-0002-1601-8729}\\
+\IEEEauthorblockN{Xiaojun Wang}
+\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
+\textit{Tulane University}\\
+New Orleans, LA\hspace{3mm}USA\\
+0000-0001-8639-6795}
 \and
@@
 \textit{Drexel University}\\
-Philadelphia, USA\\
-0000-0001-7819-5360}
+Philadelphia, PA\hspace{3mm}USA\\
+0000-0001-7819-5360}\\
+\IEEEauthorblockN{Henry Bart Jr.}
+\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
+\textit{Tulane University}\\
+New Orleans, LA\hspace{3mm}USA\\
+0000-0002-5662-9444}
 \and
@@
 \textit{Tulane University}\\
-New Orleans, USA\\
-0000-0001-6144-9440}
-\and
-\IEEEauthorblockN{Xiaojun Wang}
-\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
-\textit{Tulane University}\\
-New Orleans, USA\\
-0000-0001-8639-6795}
-\and
-\IEEEauthorblockN{Henry Bart Jr.}
-\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
-\textit{Tulane University}\\
-New Orleans, USA\\
-0000-0002-5662-9444}
-\and
+New Orleans, LA\hspace{3mm}USA\\
+0000-0001-6144-9440}\\
 \IEEEauthorblockN{David Breen}
@@
 \textit{Drexel University}\\
-Philadelphia, USA\\
+Philadelphia, PA\hspace{3mm}USA\\
 0000-0002-1376-5008}

### 2021-03-31 paper/paper_new.tex

--- 2021-03-31 paper/paper_new.tex
@@
 \end{comment}
-\section{Results}
+\section{Results and Discussion}
 Technicians employed by our team have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{leipzig2021biodiversity} for a large number of INHS images.
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/none1}
+  \includegraphics[width=0.49\linewidth]{images/double1}
+  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
+\end{figure}
+
 \subsection{Ruler Detection}
@@
 the \verb|scale| computation.
+\todo{Missed ruler stuff}
+
+%\begin{itemize}
+    %\item Worked fairly well all things considered
+    %\item Talk about which fish failed
+    %\item Talk about which rulers failed
+%\end{itemize}
 
@@
 
+There were six cases where an eye was detected but the \verb|side| value
+was wrong. Here, a spot on the wrong side of the fish was labeled as the
+most likely eye within the bounding box of the fish, i.e.~eye detection 
+was incorrect.
+There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
+For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
+This result highlights the additional utility of automated methods to
+double-check and verify human-generated metadata.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
+  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
+  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
+\end{figure}
+
 \subsection{Clock Value}
@@
 \todo{Comment on the cases where we were unable to compute clock value. What failed?}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/curved1}
+  \caption{An example of a heavily curved specimen.}
+  \label{fig:curvedFish}
+\end{figure}
+Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
+For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
+Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
+seen in Figure \ref{fig:curvedFish}.
+The other 6 were values of 3 instead of 9 or vice versa, which resulted from
+a mislabeled eye as discussed in the previous section.
+%\todo{Why is the following sentence here? What does it have to do with
+%Clock Value?}
+%A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.
+These tags were light enough that they were correctly labeled as background by the pixel analysis.
 
@@
 
-dark: 75.14548320341247 | 13.491022754871715
-        | 1800
-normal: 93.63755945070938 | 14.781004083081378
-        | 5186
-bright: 108.39315328695254 | 15.210726241270661
-        | 242
+dark: 75.14548320341247 |
+        13.491022754871715 | 1800
+normal: 93.63755945070938 |
+        14.781004083081378 | 5186
+bright: 108.39315328695254 |
+        15.210726241270661 | 242
 \end{verbatim}
@@
 
-\begin{figure}[t]
+\subsection{Mask and Bounding Box}
+
+\begin{figure}[H]
   \centering
@@
 
-\subsection{Mask and Bounding Box}
 Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found.
@@
 16 missed some of the tail, and 12 missed most or all of the tail.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/61631}
+  \includegraphics[width=0.49\linewidth]{images/61631_mask}
+  \caption{An example of a light colored tail being missed during the pixel analysis process.}
+\end{figure}
+Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work?
+Or both?}
 
@@
 was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
-
-\section{Discussion}
-\textbf{Todo}: Will need some sort of intro/framing paragraph
-%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation.
-Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
-%Discussion needed to weave in at least a couple of citations. Happy to discuss
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/none1}
-  \includegraphics[width=0.49\linewidth]{images/double1}
-  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
-\end{figure}
-\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
-\subsubsection{Object Detection}
-
-\begin{itemize}
-    \item Worked fairly well all things considered
-    \item Talk about which fish failed
-    \item Talk about which rulers failed
-\end{itemize}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
-  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
-  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
-\end{figure}
-\subsubsection{Side Detection}
-There were six cases where an eye was detected but the \verb|side| value
-was wrong. Here, a spot on the wrong side of the fish was labeled as the
-most likely eye within the bounding box of the fish, i.e.~eye detection 
-was incorrect.
-There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
-For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
-This result highlights the additional utility of automated methods to
-double-check and verify human-generated metadata.
-
-\subsubsection{Clock Value}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/curved1}
-  \caption{An example of a heavily curved specimen.}
-  \label{fig:curvedFish}
-\end{figure}
-Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
-For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
-Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
-seen in Figure \ref{fig:curvedFish}.
-The other 6 were values of 3 instead of 9 or vice versa, which resulted from
-a mislabeled eye as discussed in the previous section.
-\todo{Why is the following sentence here? What does it have to do with
-Clock Value?}
-A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.
-These tags were light enough that they were correctly labeled as background by the pixel analysis.
-
-\subsubsection{Mask and Bounding Box}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/61631}
-  \includegraphics[width=0.49\linewidth]{images/61631_mask}
-  \caption{An example of a light colored tail being missed during the pixel analysis process.}
-\end{figure}
-Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work?
-Or both?}
-
-\subsubsection{Brightness?}
-\textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
-Brightness results are are in previous section.
-Need to think about what is worth noting since it's a fairly trivial result.}
-
-\subsubsection{Scale and Length}
 \begin{figure}[H]
@@
 
+%\section{Discussion}
+%\textbf{Todo}: Will need some sort of intro/framing paragraph
+%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation.
+Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
+%Discussion needed to weave in at least a couple of citations. Happy to discuss
+%\begin{figure}[H]
+  %\centering
+  %\includegraphics[width=0.49\linewidth]{images/none1}
+  %\includegraphics[width=0.49\linewidth]{images/double1}
+  %\caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
+%\end{figure}
+%\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
+%\subsubsection{Object Detection}
+
+%\begin{itemize}
+    %\item Worked fairly well all things considered
+    %\item Talk about which fish failed
+    %\item Talk about which rulers failed
+%\end{itemize}
+%\begin{figure}[H]
+  %\centering
+  %\includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
+  %\includegraphics[width=0.49\linewidth]{images/wrong_side1}
+  %\caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
+%\end{figure}
+%\subsubsection{Side Detection}
+%There were six cases where an eye was detected but the \verb|side| value
+%was wrong. Here, a spot on the wrong side of the fish was labeled as the
+%most likely eye within the bounding box of the fish, i.e.~eye detection 
+%was incorrect.
+%There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
+For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
+%This result highlights the additional utility of automated methods to
+%double-check and verify human-generated metadata.
+
+%\subsubsection{Clock Value}
+%\begin{figure}[H]
+  %\centering
+  %\includegraphics[width=0.49\linewidth]{images/curved1}
+  %\caption{An example of a heavily curved specimen.}
+  %\label{fig:curvedFish}
+%\end{figure}
+%Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
+%For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
+Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
+%seen in Figure \ref{fig:curvedFish}.
+%The other 6 were values of 3 instead of 9 or vice versa, which resulted from
+%a mislabeled eye as discussed in the previous section.
+%\todo{Why is the following sentence here? What does it have to do with
+%Clock Value?}
+%A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish.
+These tags were light enough that they were correctly labeled as background by the pixel analysis.
+
+%\subsubsection{Mask and Bounding Box}
+
+%\subsection{Scale and Length}
+%Image scale and fish lengths were calculated for \(7,179\) of the images.
+%\todo{What happened the excluded images?}
+%Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
+%measured, using ImageJ~\cite{imagejCite}, in the same(?) 50 test images.
+% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ.~\cite{imagejCite}
+%In this subset of images the average error for the scale calculation
+%was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
+
+%\section{Discussion}
+%\textbf{Todo}: Will need some sort of intro/framing paragraph
+%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation.
+Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
+%Discussion needed to weave in at least a couple of citations. Happy to discuss
+
+%\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
+
+%\subsubsection{Brightness?}
+%\textit{Like I said in slack, the standard deviation of background does not currently correlate with the is\_background\_uniform property.
+Brightness results are are in previous section.
+Need to think about what is worth noting since it's a fairly trivial result.}
+
+\section{Conclusions}
+\textbf{Todo}
 \subsection{Future Work}
@@
 %Fitting a ``spine'' to specimen.
-\section{Conclusion}
-\textbf{Todo}
+%\section{Conclusion}
+%\textbf{Todo}
 

### 2021-03-31 paper/paper_new.tex
Ruler section

@@
 the \verb|scale| computation.
-\todo{Missed ruler stuff}
+
+Images where one of these three objects were not detected generally had some form of coloration issue.
+They were either washed out, very dark or yellow in hue.
+Some of the rulers for which ``2'' and/or ``3'' were not detected were particularly scratched and damaged.
+Only ``3'' was missed in 45 of the 56 cases, only ``2'' was missed in 2 cases, and both were missed in 9 cases.
+This may indicate that more training samples for ``3'' are required.
+Many of the rulers where both numerals were missed were particularly small within the image, which again may be solvable through bolstering the training dataset.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/no_ruler1}
+  \includegraphics[width=0.49\linewidth]{images/no_ruler2}
+  \caption{The two images where the ruler was not found. The left image exhibits a yellow hue, and the right is quite washed out with poor contrast.}
+\end{figure}
 

### 2021-04-01 paper/paper_new.tex
Brightness section

@@
 \title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
-    {\footnotesize \thanks{NSF Grant ???} }}
+    {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }}
 %do we add grant now, or wait til acceptance.
@@
     \label{tab:dataset}
-    \begin{tabular}{cc}
+    \begin{tabular}{cccc}
         \toprule
@@
 
-\subsection{Foreground/Background Contrast Results?}
+\subsection{Image Contrast}
 \begin{figure}[H]
@@
   \caption{Histogram for difference in brightness between foreground an background.}
+  \label{fig:histo}
 \end{figure}
 
-\subsection{Brightness/Uniformity Results?}
+The contrast of an image is an important aspect of the image quality for the BGNN study.
+Ideally, for INHS images the fish should be well lit and vibrant, and the background should also be as light and white as possible.
+Figure~\ref{fig:histo} shows the distribution of the difference between the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box.
+The overall mean of the distribution is \(144.26\), with a standard deviation of \(15.79\).
+Images on the low end of this distribution exhibit poor foreground--background contrast, and images on the high end likely contain poorly lit specimens.
+Examples of each type of image (low, normal, and high contrast) can be seen in Figure~\ref{fig:contrast}.
+The top left image has a mean intensity of 103 (low), the top right 144 (normal), and the bottom 186 (high).
+
 \begin{figure}[H]
@@
   \caption{Examples of low, normal and high contrast fish images.}
+  \label{fig:contrast}
 \end{figure}
-\textbf{Todo}: It looks like we should leave out Uniformity.
 
-\begin{verbatim}
-This is for average foreground intensity
-(i.e. the fish pixels)
-Mean intensity in bounding box | Std
-        | Count
+\subsection{Brightness}
+Specimen brightness is one of the 22 hand recorded properties.
+It is encoded as \verb|dark|, \verb|normal| or \verb|bright|.
+These values correspond to the measurement of mean foreground intensity by the automated system.
+The correlation between the two measurements can be seen in Table~\ref{tab:bright} below.
+\begin{table}[H]
+    \centering
+    \caption{Brightness measurements}
+    \label{tab:bright}
+    \begin{tabular}{cccc}
+        \toprule
+        \textbf{Class} & \textbf{Mean Intensity} & \textbf{Standard Deviation} & \textbf{Instances}\\
+        \midrule
+        Dark & 75.15 & 13.49 & 1800\\
+        Normal & 93.64 & 14.78 & 5186\\
+        Bright & 108.39 & 15.21 & 242\\
+        \bottomrule
+    \end{tabular}
+\end{table}
 
-dark: 75.14548320341247 |
-        13.491022754871715 | 1800
-normal: 93.63755945070938 |
-        14.781004083081378 | 5186
-bright: 108.39315328695254 |
-        15.210726241270661 | 242
-\end{verbatim}
-\begin{verbatim}
-Standard Deviations for:
-    Uniform: 12.554834863869324
-    Not Uniform: 11.312181711328828
-\end{verbatim}
+\textbf{Todo}: I suppose more should be said here.
+
+%\begin{verbatim}
+%Standard Deviations for:
+    %Uniform: 12.554834863869324
+    %Not Uniform: 11.312181711328828
+%\end{verbatim}
 

### 2021-04-01 paper/paper_new.tex
Explained why fish were missed

@@
 Of the remaining 17, \verb|detectron| erroneously labeled the fish as two separate fish objects, or labeled a subsection of the fish a second time.
+The 7 fish that were not detected were quite small, which is something that is a type of specimen that is currently lacking from the training set.
+See the left image in Figure~\ref{fig:fish_detect_wrong} for an example of this.
+Fish that were double labeled were generally quite large and/or dissimilar from the fish found in the training set, such as the right image in Figure~\ref{fig:fish_detect_wrong}.
 
@@
   \includegraphics[width=0.49\linewidth]{images/double1}
-  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
+  \caption{A fish that was not detected (left) and a fish that was detected twice (right).}
+  \label{fig:fish_detect_wrong}
 \end{figure}

### 2021-04-01 paper/paper_new.tex
Cleaned up all the todo things

@@
 \usepackage{comment}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%% REMOVE FOLLOWING LINE BEFORE SUBMITTING %%%%%%%%%
-\setlength {\marginparwidth }{2cm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{todonotes}
@@
 All instance types were included in a single object detection model.
-The total loss\todo{Find and specify which loss function was used} began at \(2.948\) and ended at \(0.158\) for the training data.
+The total cross--entropy loss began at \(2.948\) and ended at \(0.158\) for the training data.
 
@@
 \subsubsection{primary\_axis and clock\_value}
-The \verb|primary_axis| of a fish can be calculated by taking the covariance\todo{I could explain this in more detail if necessary.
-(DEB No, that's OK.} of its blob in \(x\) and \(y\), which yields its principle eigenvector.
+The \verb|primary_axis| of a fish can be calculated by taking the covariance of its blob in \(x\) and \(y\), which yields its principle eigenvector.
 The eigenvector can be directly assigned to the property. If an eye is
@@
 Our automated process currently generates 7 of the 22 core metadata properties: \verb|if_fish| (\verb|has_fish|), \verb|fish_number| (\verb|fish_count|), \verb|if_ruler| (\verb|has_ruler|), \verb|specimen_angled| (\verb|clock_value|), \verb|specimen_view| (\verb|side|), \verb|brightness| (derived from \verb|background.mean| and \verb|foreground.mean|), and \verb|if_background_uniform| (\verb|background.std|).
-In addition, our process also calculates bounding boxes and fish lengths in centimeters.\todo{Talk more about what we can and can't verify and how.}
+In addition, our process also calculates bounding boxes and fish lengths in centimeters.
 
@@
 For all but 2 of the \(7,244\) images \verb|detectron| was able to find the ruler, a nearly perfect correct rate.
-% \todo{Not sure if I can phrase it that way or not since I haven't looked at all the images to see if the ruler itself was found or something else was labeled a ruler}
 In 56 of the images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed, producing a 99.2\% success rate for
@@
 a 96.5\% correct rate.
-\todo{Comment on the 6 cases. What failed?}
 
@@
 computation is 96.4\%.
-\todo{Comment on the cases where we were unable to compute clock value. What failed?}
 
@@
 \end{figure}
-Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work?
-Or both?}
+Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.
 
@@
 Image scale and fish lengths were calculated for \(7,179\) of the images.
-\todo{What happened the excluded images?}
+For the remaining 65 images, either the fish, the ``2'' and/or the ``3'' on the ruler were not detected.
 Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
@@
 To accomplish this, a much larger training dataset full of more diverse images will be required.
-Another requirement will be to generalize the ruler reading process beyond the INHS specific reading of digits on the ruler.\todo{Suggest way(s) to do this?}
+Another requirement will be to generalize the ruler reading process beyond the INHS specific reading of digits on the ruler.
+\textbf{Todo}: Suggest way(s) to do this?
 % Todo: Are these worth mentioning?

### 2021-04-01 paper/paper_new.tex
Updates from Overleaf

@@
 \begin{abstract}
-     Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
-One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.
-The metadata that is vital for subsequent machine learning, analysis and
-scientific discovery based on these specimen image repositories
-is often unavailable, sparse or incorrect.
+Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens.
+Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means.
+This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features.
+The digitized fish specimen are being analyzed as part of the XXX project [*Biology Guided Neural Networks (BGNN)], where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
+The paper reports on research combining machine  learning  and  image  informatics  tools and techniques.
+A sample 7247 images from the INHS (write-out) were examined via automatic processes; and results show we can  accurately determine metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
+Results also indicate that automatic approaches "can outperform humans" and/or "expedite" the creation of metadata that's critical to leveraging digitized specimens for machine learning.
+The sections that follow cover background context, reviews the research design, reports results Next,  the  results  are presented, followed by a discussion.
+%something about implications above
+%something about comparison to human results.
+
+% Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent machine learning, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect.
 As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features.
 These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies.
-Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.
-Our goal is to develop image metadata generation methods that both support
-the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
+Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
 A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.

### 2021-04-01 paper/paper_new.tex
Updates from Overleaf

@@
 A sample 7247 images from the INHS (write-out) were examined via automatic processes; and results show we can  accurately determine metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
-Results also indicate that automatic approaches "can outperform humans" and/or "expedite" the creation of metadata that's critical to leveraging digitized specimens for machine learning.
+Results also indicate that automatic approaches "can outperform humans" [and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
 The sections that follow cover background context, reviews the research design, reports results Next,  the  results  are presented, followed by a discussion.
+%items in square brackets are just other suggested words, e.g., select one or the other, or .... 
 %something about implications above

### 2021-04-01 paper/paper_new.tex
Further editing/refinement of Section 5.

--- 2021-04-01 paper/paper_new.tex
@@
 in different habitats.
+\begin{figure*}
+  \centering
+  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
+  \hspace{1mm}
+  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100682}
+  \hspace{1mm}
+  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
+  \caption{Three example images from the Illinois Natural History Survey (INHS) collection.}
+  \label{fig:INHS_examples}
+\end{figure*}
 
@@
 images drawn from the Illinois Natural History Survey (INHS) Collection.
+Figure \ref{fig:INHS_examples} presents three typical images used in our
+study.
 The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods.
@@
 \section{Methods}
-Our process for metadata generation can be broken into three steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image informatics analysis at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.
+Our process for metadata generation can be broken into three steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image processing at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.
 % \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=.49\linewidth]{images/teaser1_crop}
+\begin{figure}[b]
+  \centering
+%  \includegraphics[width=.49\linewidth]{images/teaser1_crop}
   %\hspace{4mm}
-  \includegraphics[width=.49\linewidth]{images/teaser2_crop}
-  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
+  \includegraphics[width=.90\linewidth]{images/teaser2_crop}
+  \caption{Initial object detection on a specimen image using Detectron2~\cite{wu2019detectron2}.}
   \label{fig:teaser}
 \end{figure}
+
 \subsection{Detectron}
@@
 It is able to handle an arbitrary number of object classes, and can classify an arbitrary number of object within a given image.
-For our project, we are currently using it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers.
+For our project, we use it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers,
+as shown in Figure \ref{fig:teaser}.
 
@@
         \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
+        \verb|contrast| & Per Fish & Float & The contrast between foreground and background intensities within a given fish's bounding box.\\
         \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
@@
 
+\subsubsection{contrast}
+The contrast between the intensities of the foreground and background
+pixels is computed as \verb|background.mean| - \verb|foreground.mean|.
+
 \subsubsection{centroid and eye\_center}
@@
 
-Since we recalculate the mask of the fish, we must recalculate its centroid as well. This can be done via
+Since we recalculate the mask of the fish, its centroid must be recalculated
+as well. This can be done via
 \begin{equation}
@@
 \(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images.
-Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and met our current admissibility criteria for \verb|detectron| and pixel analysis processing.
+Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and met our current admissibility criteria for \verb|detectron| and pixel processing.
 We ran the metadata extraction program on these \(7,244\) images.
@@
 
-Our automated process currently generates 7 of the 22 core metadata properties: \verb|if_fish| (\verb|has_fish|), \verb|fish_number| (\verb|fish_count|), \verb|if_ruler| (\verb|has_ruler|), \verb|specimen_angled| (\verb|clock_value|), \verb|specimen_view| (\verb|side|), \verb|brightness| (derived from \verb|background.mean| and \verb|foreground.mean|), and \verb|if_background_uniform| (\verb|background.std|).
-In addition, our process also calculates bounding boxes and fish lengths in centimeters.
+Our automated process currently generates 6 of the 22 core metadata properties: \verb|if_fish| (\verb|has_fish|), \verb|fish_number| (\verb|fish_count|), \verb|if_ruler| (\verb|has_ruler|), \verb|specimen_angled| (\verb|clock_value|), \verb|specimen_view| (\verb|side|), and \verb|brightness| (\verb|foreground.mean|).
+% and \verb|if_background_uniform| (\verb|background.std|).
+In addition, our process also calculates contrast, bounding boxes and
+fish lengths in centimeters.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\linewidth]{images/none1_crop} \\
+  \vspace{3mm}
+  \includegraphics[width=0.9\linewidth]{images/double1_crop}
+  \caption{A fish that was not detected (top) and a fish that was detected twice (bottom).}
+  \label{fig:fish_detect_wrong}
+\end{figure}
 
@@
 For 25 of the images, 2 fish were detected, 3 fish were detected for 3 images, and for 7 images no fish were found.
-In the case of greater than 1 fish, 9 of the 28 contained tags which overlapped the fish and were themselves labeled as a second fish.
+The 7 fish that were not detected were quite small. This type of specimen 
+is currently lacking from the training set.
+See the top image in Figure~\ref{fig:fish_detect_wrong} for an example.
+In the case of greater than 1 fish, 9 of the 28 contained tags that
+overlapped the fish and were themselves labeled as a second fish.
 Of the remaining 17, \verb|detectron| erroneously labeled the fish as two separate fish objects, or labeled a subsection of the fish a second time.
-The 7 fish that were not detected were quite small, which is something that is a type of specimen that is currently lacking from the training set.
-See the left image in Figure~\ref{fig:fish_detect_wrong} for an example of this.
-Fish that were double labeled were generally quite large and/or dissimilar from the fish found in the training set, such as the right image in Figure~\ref{fig:fish_detect_wrong}.
+Fish that were double labeled were generally quite large and/or dissimilar from the fish found in the training set, such as the bottom image in
+Figure~\ref{fig:fish_detect_wrong}.
 
@@
   \centering
-  \includegraphics[width=0.49\linewidth]{images/none1}
-  \includegraphics[width=0.49\linewidth]{images/double1}
-  \caption{A fish that was not detected (left) and a fish that was detected twice (right).}
-  \label{fig:fish_detect_wrong}
+  \includegraphics[width=0.49\linewidth]{images/no_ruler1}
+  \includegraphics[width=0.49\linewidth]{images/no_ruler2}
+  \caption{The two images where the ruler was not found. The left image exhibits a yellow hue, and the right is quite washed out with poor contrast.}
+  \label{fig:no_ruler}
 \end{figure}
@@
 For all but 2 of the \(7,244\) images \verb|detectron| was able to find the ruler, a nearly perfect correct rate.
-In 56 of the images, the ruler itself was found but the ``2'' and/or the ``3'' on it was not, so a scale calculation could not be performed, producing a 99.2\% success rate for
+In 56 of the images, the ruler itself was found, but the numbers ``2''
+and/or the ``3'' on the ruler were not. Therefore a scale calculation could
+not be performed, producing a 99.2\% success rate for
 the \verb|scale| computation.
 
-Images where one of these three objects were not detected generally had some form of coloration issue.
-They were either washed out, very dark or yellow in hue.
+Images where one of these objects were not detected generally had some form of coloration issue. They were either washed out, very dark or yellow in hue.
+See Figure \ref{fig:no_ruler} two such examples.
 Some of the rulers for which ``2'' and/or ``3'' were not detected were particularly scratched and damaged.
@@
 This may indicate that more training samples for ``3'' are required.
-Many of the rulers where both numerals were missed were particularly small within the image, which again may be solvable through bolstering the training dataset.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/no_ruler1}
-  \includegraphics[width=0.49\linewidth]{images/no_ruler2}
-  \caption{The two images where the ruler was not found. The left image exhibits a yellow hue, and the right is quite washed out with poor contrast.}
-\end{figure}
+Many of the rulers where both numerals were missed were particularly small within the image, which again may be solvable through expanding the training dataset.
 
@@
 
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=0.31\linewidth]{images/dark}
+  \includegraphics[width=0.31\linewidth]{images/normal}
+  \includegraphics[width=0.31\linewidth]{images/bright}
+  \caption{Examples of low, medium and high contrast fish images.}
+  \label{fig:contrast}
+\end{figure*}
+
 \subsection{Side Detection}
@@
 
-There were six cases where an eye was detected but the \verb|side| value
-was wrong. Here, a spot on the wrong side of the fish was labeled as the
+% There were six cases where an eye was detected but the \verb|side| value
+% was wrong.
+For these 6 cases, a spot on the wrong side of the fish was labeled as the
 most likely eye within the bounding box of the fish, i.e.~eye detection 
-was incorrect.
+was incorrect. Figure \ref{fig:wrong_eye} presents one such example.
 There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
   \centering
@@
   \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
+  \label{fig:wrong_eye}
 \end{figure}
@@
 Clock position values were successfully generated for \(6,991\) of the images. Of those, all but 8 were within \(\pm{}1\) of the correct result,
-our definition of a correct/acceptable result. The correct rate for this
-computation is 96.4\%.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/curved1}
-  \caption{An example of a heavily curved specimen.}
-  \label{fig:curvedFish}
-\end{figure}
+our definition of a correct/acceptable result, making the correct rate for
+this computation 96.4\%.
+
 Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
-For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate.
-Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
+For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate. Of the 8 that were
+computationally classified incorrectly,
+two specimens were quite curved making it difficult to assign a clear angle value, as
 seen in Figure \ref{fig:curvedFish}.
-The other 6 were values of 3 instead of 9 or vice versa, which resulted from
+The other 6 were values of ``3'' instead of ``9'' or vice versa, which resulted from
 a mislabeled eye as discussed in the previous section.
@@
 
-\subsection{Image Contrast}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=\linewidth]{images/histo}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.7\linewidth]{images/curved1}
+  \caption{An example of a heavily curved specimen.}
+  \label{fig:curvedFish}
+\end{figure}
+
+\begin{comment}
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\linewidth]{images/histo}
   \caption{Histogram for difference in brightness between foreground an background.}
@@
 \end{figure}
-
-The contrast of an image is an important aspect of the image quality for the BGNN study.
-Ideally, for INHS images the fish should be well lit and vibrant, and the background should also be as light and white as possible.
-Figure~\ref{fig:histo} shows the distribution of the difference between the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box.
-The overall mean of the distribution is \(144.26\), with a standard deviation of \(15.79\).
-Images on the low end of this distribution exhibit poor foreground--background contrast, and images on the high end likely contain poorly lit specimens.
-Examples of each type of image (low, normal, and high contrast) can be seen in Figure~\ref{fig:contrast}.
-The top left image has a mean intensity of 103 (low), the top right 144 (normal), and the bottom 186 (high).
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/dark}
-  \includegraphics[width=0.49\linewidth]{images/normal}
-  \includegraphics[width=0.49\linewidth]{images/bright}
-  \caption{Examples of low, normal and high contrast fish images.}
-  \label{fig:contrast}
-\end{figure}
-
-\subsection{Brightness}
-Specimen brightness is one of the 22 hand recorded properties.
-It is encoded as \verb|dark|, \verb|normal| or \verb|bright|.
-These values correspond to the measurement of mean foreground intensity by the automated system.
-The correlation between the two measurements can be seen in Table~\ref{tab:bright} below.
+\end{comment}
+
+\subsection{Image Contrast}
+The contrast of an image is an important image property needed
+for the analyses of the BGNN study. Ideally, for INHS images the fish should be well lit and clearly displayed, and the background should also be as light and white as possible.
+% Figure~\ref{fig:histo} shows the distribution of
+The difference between
+the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box
+was computed for all 7,244 images.
+The overall mean of the differences is \(144.3\), with a standard deviation of \(15.8\).
+Images on the low end of the distribution exhibit poor foreground--background contrast, and images on the high end likely contain poorly lit specimens.
+Images are considered to have ``low'' and
+``high'' contrast if their background-foreground difference is greater than
+one standard deviation away from the mean; otherwise they are classified as
+``medium''.
+Examples of each type of image (low, medium, and high contrast) can be seen in Figure~\ref{fig:contrast}.
+The left image has a mean intensity of 103 (low), the middle image 144
+(medium), and the right 186 (high).
+
 \begin{table}[H]
     \centering
-    \caption{Brightness measurements}
+%    \caption{\verb|foreground.mean| statistics for the three Brightness classes}
+    \caption{foreground.mean statistics for the three Brightness classes}
     \label{tab:bright}
@@
         \midrule
-        Dark & 75.15 & 13.49 & 1800\\
-        Normal & 93.64 & 14.78 & 5186\\
-        Bright & 108.39 & 15.21 & 242\\
+        Dark & 75.2 & 13.5 & 1800\\
+        Normal & 93.6 & 14.8 & 5186\\
+        Bright & 108.4 & 15.2 & 242\\
         \bottomrule
@@
 \end{table}
-
-\textbf{Todo}: I suppose more should be said here.
+\subsection{Brightness}
+Specimen brightness is one of the 22 hand-recorded metadata properties. It is encoded as \verb|dark|, \verb|normal| or \verb|bright|. These values
+correspond to the mean foreground intensity computed by the automated system.
+The mean and standard deviation of the mean foreground intensities were
+computed for the images in the three human-specified classes.
+Table~\ref{tab:bright} contains the resulting values and shows that
+automated intensities values provide objective measures that may be used to break images into groups that correlate with human-defined brightness
+classifications.
+The mean of \verb|foreground.mean| over all 7,244 images is 89.5, with a
+standard deviation of 16.9. These numbers suggest, for example, that
+\verb|foreground.mean| $\pm$ one-half a standard deviation could define 
+\verb|normal| brightness, with values outside this range being classified
+as \verb|dark| or \verb|bright|.
 
@@
 Specifically, 22 masks and bounding boxes covered the entire fish,
-16 missed some of the tail, and 12 missed most or all of the tail.
+16 missed some of the tail, and 12 missed most or all of the tail, as
+seen in Figure \ref{fig:missedTail}.
 \begin{figure}[H]
@@
   \caption{An example of a light colored tail being missed during the pixel analysis process.}
+  \label{fig:missedTail}
 \end{figure}
-Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.
+Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but further refinement of our algoriths will be needed
+to ensure that light fins and tails are masked consistently and accurately.
 
@@
 Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
-measured, using ImageJ,~\cite{imagejCite} in the same(?) 50 test images.
-% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ.~\cite{imagejCite}
+measured, using ImageJ~\cite{imagejCite}, in the same 50 test images.
+% 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ~\cite{imagejCite}.
 In this subset of images the average error for the scale calculation
 was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
+Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler.
+When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well.
+An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm).
+Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
 \begin{figure}[H]
@@
 \end{figure}
-Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler.
-When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well.
-An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm).
-Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
 

### 2021-04-01 paper/paper_new.tex

@@
 \begin{abstract}
-     Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
-One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.
-The metadata that is vital for subsequent machine learning, analysis and
-scientific discovery based on these specimen image repositories
-is often unavailable, sparse or incorrect.
+Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens.
+Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means.
+This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features.
+The digitized fish specimen are being analyzed as part of the XXX project [*Biology Guided Neural Networks (BGNN)], where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
+The paper reports on research combining machine  learning  and  image  informatics  tools and techniques.
+A sample 7247 images from the INHS (write-out) were examined via automatic processes; and results show we can  accurately determine metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
+Results also indicate that automatic approaches "can outperform humans" [and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
+The sections that follow cover background context, reviews the research design, reports results Next,  the  results  are presented, followed by a discussion.
+%items in square brackets are just other suggested words, e.g., select one or the other, or .... 
+%something about implications above
+%something about comparison to human results.
+
+% Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent machine learning, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect.
 As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features.
 These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies.
-Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.
-Our goal is to develop image metadata generation methods that both support
-the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
+Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
 A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.

### 2021-04-01 paper/paper_new.tex
Minor number tweak.
Grammar

--- 2021-04-01 paper/paper_new.tex
@@
 \begin{abstract}
-Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens.
-Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means.
-This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features.
-The digitized fish specimen are being analyzed as part of the XXX project [*Biology Guided Neural Networks (BGNN)], where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
-The paper reports on research combining machine  learning  and  image  informatics  tools and techniques.
-A sample 7247 images from the INHS (write-out) were examined via automatic processes; and results show we can  accurately determine metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
-Results also indicate that automatic approaches "can outperform humans" [and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
-The sections that follow cover background context, reviews the research design, reports results Next,  the  results  are presented, followed by a discussion.
-%items in square brackets are just other suggested words, e.g., select one or the other, or .... 
-%something about implications above
-%something about comparison to human results.
-
-% Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
-One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent machine learning, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect.
+     Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.
+The metadata that is vital for subsequent machine learning, analysis and
+scientific discovery based on these specimen image repositories
+is often unavailable, sparse or incorrect.
 As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features.
 These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies.
-Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
+Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.
+Our goal is to develop image metadata generation methods that both support
+the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
 A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
@@
 % Moving teaser since this template doesn't actually ask for one
-Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.~\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.~\cite{page2015digitization} These digital specimen accessible through global, open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
-Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain specimen images.~\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.~\cite{page2015digitization} These digital specimen images are accessible through global, open access repositories; they enable researchers, educators, students, and the general public to examine and compare collections in ways previously unimaginable.
+Significant challenges surface, however, when researchers seek to apply computational methods to these repositories, due to both image quality and metadata issues.
 %{jane}should we try to insert machine learning here, last sentence, or computation methods ok?
@@
 associated with the image collections.
-Poor quality images, e.g. with low contrast, inadequate lighting,
-out-of-focus or cluttered visual arrangements, provide inadequate input
+Poor quality images---e.g.\ those with low contrast, inadequate lighting,
+out-of-focus or cluttered visual arrangements---provide inadequate input
 for automated
-image analysis and machine learning algorithms and lead to inferior
+image analysis and machine learning algorithms, and lead to inferior
 computational results.
 In order to perform quantitative morphometric analysis of the specimens,
-the physical scale of the images (pixels/inch) is needed; thus
+the physical scale of the images (pixels/cm) is needed; thus
 requiring the ability to identify and measure rulers in the images.
@@
 as their length and area.  In order to test and validate our methods, they
-were  applied to a set of 7,247
+were  applied to a set of \(7,244\)
 images drawn from the Illinois Natural History Survey (INHS) Collection.
@@
 Darwin Core~\cite{biodiv_info_standards} developed specifically for digital museum projects is one of the most frequently used standards.
-Another approach is to create a metadata application profile by integrating properties from Dublin Core's DCMI Metadata Terms \cite{dc_terms}, the Ecological Metadata Language (EML) \cite{EML_2019} and other namespaces.
-There is also the recent Audubon Core supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.\cite{audub_core} These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
+Another approach is to create a metadata application profile by integrating properties from Dublin Core's DCMI Metadata Terms~\cite{dc_terms}, the Ecological Metadata Language (EML)~\cite{EML_2019} and other namespaces.
+There is also the recent Audubon Core supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.~\cite{audub_core} These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
 In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels.

### 2021-04-01 paper/paper_new.tex

--- 2021-04-01 paper/paper_new.tex
@@
 The mean of \verb|foreground.mean| over all 7,244 images is 89.5, with a
-standard deviation of 16.9. These numbers suggest, for example, that
+standard deviation of 16.6. These numbers suggest, for example, that
 \verb|foreground.mean| $\pm$ one-half a standard deviation could define 

### 2021-04-01 paper/paper_new.tex

--- 2021-04-01 paper/paper_new.tex
@@
 This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features.
-The digitized fish specimen are being analyzed as part of the XXX project [*Biology Guided Neural Networks (BGNN)], where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
+The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
 The paper reports on research combining machine  learning  and  image  informatics tools and techniques.
-A sample 7247 images from the INHS (write-out) were examined via automatic processes; and results show we can  accurately determine metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
-Results also indicate that automatic approaches "can outperform humans" [and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
+A sample 7247 images from the Illionois Natural History Survey (INHS) were examined via automatic processes [*<--needs help].
+Results show we can  accurately determine metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
+Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
 The sections that follow cover background context, reviews the research design, reports results Next,  the  results  are presented, followed by a discussion.
-%items in square brackets are just other suggested words, e.g., select one or the other, or .... 
-%something about implications above
-%something about comparison to human results.
+%items in square brackets [*xxx] are just other suggested words, e.g., select one or the other, or ....
+%let's give a few data results, e.g., percentages, numbers..what will be emphasize in conclusion, key findings.
+%abstract could say something about comparison to human results.
 
@@
 A number of different metadata standards have been applied to support the description and access of digitized scientific images.
-Darwin Core~\cite{biodiv_info_standards} developed specifically for digital museum projects is one of the most frequently used standards.
-Another approach is to create a metadata application profile by integrating properties from Dublin Core's DCMI Metadata Terms \cite{dc_terms}, the Ecological Metadata Language (EML) \cite{EML_2019} and other namespaces.
-There is also the recent Audubon Core supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.\cite{audub_core} These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
+The Darwin Core (DwC~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data is among the most popular standard for such efforts.
+It is an extension of the Dublin Core's DCMI Metadata Terms \cite{dc_terms}.
+There is also the recent Audubon Core\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.
+These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
 In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels.
-This task is labor intensive, and the metadata associated with each digital rendering is limited, particularly for researchers seeking to apply machine learning, and leverage both the image and the metadata for scientific research.
+This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply machine learning to the image and the metadata for scientific research.
 
@@
 Even so, metadata properties used to record image quality is severely limited and generally missing.
-This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bgnn.
-Although, the manual generation of this metadata is costly in terms of labor and time.
+This point is addressed in detail in \cite{leipzig2021biodiversity}, and serves to justify a new initiative at Tulane University, where staff are manually capturing content for 22 metadata properties, to get a handle on the quality of digitized specimens drawn from the INHS collection and iDigBio.
+This current process is costly in terms of labor and time, and underscores the need to explore automatic metadata generation [*extraction].
 

### 2021-04-02 paper/paper_new.tex
Started to write transition out of the Related Work section.

@@
 
-This limitation is magnified when trying get a handle on the actual quality of the digitized specimen.
-Descriptive oriented standards support search and retrieval, and the biodiversity community advocated for data fitness standards \cite{chapman2020developing}.
+This limitation is magnified when trying to assess the actual quality of the digitized specimen.
+Descriptive oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}.
 Even so, metadata properties used to record image quality is severely limited and generally missing.
-This point is addressed in detail in \cite{leipzig2021biodiversity}, and serves to justify a new initiative at Tulane University, where staff are manually capturing content for 22 metadata properties, to get a handle on the quality of digitized specimens drawn from the INHS collection and iDigBio.
-This current process is costly in terms of labor and time, and underscores the need to explore automatic metadata generation [*extraction].
+This point is addressed in detail in \cite{leipzig2021biodiversity}, and serves to justify a new initiative at Tulane University, where staff are manually capturing content for 22 metadata properties, to characterize the quality of digitized specimens drawn from the INHS collection and iDigBio.
+This current process is costly in terms of labor and time, error-prone, and underscores the need to
+explore automatic metadata generation methods.
 
@@
 Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX.
-Some of this metadata may be useful in for selecting a machine learning sample.
+Some of this metadata may be useful when selecting a machine learning sample.
 A researcher may desire images captured chiefly with a certain aperture setting.
-Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to reply on manually generated descriptive metadata, which itself is sparse.
+Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse.
 
@@
 Li and Hong \cite{Li2014IdentificationOF} computed eleven shape and color
-features from fish images that were distilled down to four, using Principal
-Component Analysis, and derived a linear model
+features from fish images and derived a linear model
 that could discriminate between four different fishes.
@@
 and processing.
-In some instances it is necessary to computationally straighten the
-fish in the images \cite{MuozBenavent2018EnhancedFB} before further
-processing can be attempted.
+In some instances fish in the images need to be computationally straightened
+before further processing can be attempted \cite{MuozBenavent2018EnhancedFB}.
 Balaban et al.~\cite{Balaban2010UsingIA} demonstrated that image analysis
@@
 A similar approach was developed by Lalabadi et al.~\cite{Lalabadi2020FishFC}.
+
+Our work stands apart from previous work in that we are
+addressing a different need. Lack of metadata is impeding scientific studies.
+Our focus and motivation are different.
+Effectively doing the computational pre-processing
+that will enable further downstream analyses.
+
+We are applying a variety of machine learning, image processing and
+image informatics techniques to extract critical properties from the
+images.  The properties will allow follow-on studies to identify
+the specific images needed for a particular analysis, ensuring that
+the specimen images meet both scientific and technical requirements.
+
 % Developing new techniques to determine fish freshness and quality can enhance nutritional value of the overall household food basket.

### 2021-04-03 paper/paper_new.tex
Updates from Overleaf

--- 2021-04-01 paper/paper_new.tex
@@
 The paper reports on research combining machine  learning  and  image  informatics tools and techniques.
-A sample 7247 images from the Illionois Natural History Survey (INHS) were examined via automatic processes [*<--needs help].
-Results show we can  accurately determine metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
+A sample 7244 images from the Illinois Natural History Survey (INHS) were examined via automatic processes [*<--needs help].
+Results show we can  accurately extract metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
 Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
@@
 \end{figure}
-Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but further refinement of our algoriths will be needed
+Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but further refinement of our algorithms will be needed
 to ensure that light fins and tails are masked consistently and accurately.

### 2021-04-03 paper/paper_new.tex
Updates from Overleaf

@@
     {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }}
-%do we add grant now, or wait til acceptance.
-i think we need to ultimately remove any identifying info., i think bgnn is likely okay; but, perhaps mention metadata research center (MRC) need to be removed?.
-if so, i kind of like to put it back in for final version, if accepted.
-it helps with getting funding ...
-you are both listed on the MRC page.
-we should check on the identifying info.
-removed, or not.
-%for the record: Research supported by NSF OAC #1940233 and #1940322.
 
@@
 The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
-The paper reports on research combining machine  learning  and  image  informatics tools and techniques.
+The automatically generated metadata is crucial for identifying high-quality images for the neural network, and, further support empirical [*predicative] analysis [analytics?].
+This paper reports specifically on research combining machine learning  and  image  informatics tools and techniques.
 A sample 7244 images from the Illinois Natural History Survey (INHS) were examined via automatic processes [*<--needs help].
+Key findings indicate z, y, z.
+%for x, y, z, can we give some numbers? thinking on this.
 Results show we can  accurately extract metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
 Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
-The sections that follow cover background context, reviews the research design, reports results Next,  the  results  are presented, followed by a discussion.
-%items in square brackets [*xxx] are just other suggested words, e.g., select one or the other, or ....
-%let's give a few data results, e.g., percentages, numbers..what will be emphasize in conclusion, key findings.
-%abstract could say something about comparison to human results.
-
-% Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
+This research has implications for leveraging the extensive collection of digitized scientific images stored in globally, accessible open repositories.
+%[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.
+
+% OLD text - Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
 One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent machine learning, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect.

### 2021-04-03 paper/paper_new.tex
Updates from Overleaf

@@
 Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
-This research has implications for leveraging the extensive collection of digitized scientific images stored in globally, accessible open repositories.
+This research has implications for tens of thousands of digitized specimens stored in globally, accessible open repositories.
 %[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.
@@
 \subsection{Automatic Metadata Generation}
-Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX.
+Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)\cite{Exif}, the camera's technical metadata that is automatically captured and inserted into digital image files at the time of digitization.
 Some of this metadata may be useful when selecting a machine learning sample.

### 2021-04-04 paper/paper_new.tex
Updates from Overleaf

@@
 
-\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
+\title{Automatic Metadata Generation for Fish Specimen Image Collections%*\\
     {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }}
@@
 \begin{abstract}
-Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens.
-Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means.
-This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features.
+Metadata is a key data source particularly for researchers seeking use apply achine learning to the vast collections of digitized specimens.
+Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual means.
+This paper reports on a research applying machine-driven approaches to analyze digitized fish images and extract a variety of important features.
 The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
-The automatically generated metadata is crucial for identifying high-quality images for the neural network, and, further support empirical [*predicative] analysis [analytics?].
-This paper reports specifically on research combining machine learning  and  image  informatics tools and techniques.
-A sample 7244 images from the Illinois Natural History Survey (INHS) were examined via automatic processes [*<--needs help].
-Key findings indicate z, y, z.
-%for x, y, z, can we give some numbers? thinking on this.
-Results show we can  accurately extract metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics.
-Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning.
-This research has implications for tens of thousands of digitized specimens stored in globally, accessible open repositories.
+The automatically generated metadata is crucial for identifying high-quality images for the neural network to support predictive analyses.%predictive analytics?
+Research combining machine learning  and  image  informatics tools and techniques allow us to rapidly enrich the metadata currently associated with the digitized specimens.
+The study focuses on a sample of 7244 images from the Illinois Natural History Survey (INHS), which also included additional, manually generated image-quality metadata Results show we can  accurately generate metadata for six key %6?
+metadata properties: fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also show can also x, y, z.
+%to confirm list
+%jg to add note about x, y, z, unless someone else does first
+The automatic process out-performs humans in terms and cost, and provides a solution for leveraging digitized specimens for machine learning.
+This research has implications for harnessing the tens of thousands of digitized specimens stored in globally, accessible open repositories.
 %[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 The automatically generated metadata is crucial for identifying high-quality images for the neural network to support predictive analyses.%predictive analytics?
-Research combining machine learning  and  image  informatics tools and techniques allow us to rapidly enrich the metadata currently associated with the digitized specimens.
-The study focuses on a sample of 7244 images from the Illinois Natural History Survey (INHS), which also included additional, manually generated image-quality metadata Results show we can  accurately generate metadata for six key %6?
+Research combining machine learning  and  image  informatics techniques allow us to rapidly enrich existing metadata associated for a sample of 7244 images from the Illinois Natural History Survey (INHS).
+The sample also includes 22 manually generated image-quality metadata properties, aiding our comparsion.
+Results show we can  accurately generate metadata for six key %6?
 metadata properties: fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also show can also x, y, z.
-%to confirm list
-%jg to add note about x, y, z, unless someone else does first
-The automatic process out-performs humans in terms and cost, and provides a solution for leveraging digitized specimens for machine learning.
+%to confirm list of six properties.
+%x, y, z = any other key results. jg will add from results sectin, unless someone else does first. 
+The automatic process out-performs humans in terms and cost, and provides a novel solution for leveraging digitized specimens for machine learning.
 This research has implications for harnessing the tens of thousands of digitized specimens stored in globally, accessible open repositories.
-%[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.
 

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 Research combining machine learning  and  image  informatics techniques allow us to rapidly enrich existing metadata associated for a sample of 7244 images from the Illinois Natural History Survey (INHS).
-The sample also includes 22 manually generated image-quality metadata properties, aiding our comparsion.
+The sample also includes 22 manually generated image-quality metadata properties, aiding our comparison.
 Results show we can  accurately generate metadata for six key %6?
@@
 %to confirm list of six properties.
-%x, y, z = any other key results. jg will add from results sectin, unless someone else does first. 
-The automatic process out-performs humans in terms and cost, and provides a novel solution for leveraging digitized specimens for machine learning.
-This research has implications for harnessing the tens of thousands of digitized specimens stored in globally, accessible open repositories.
+%x, y, z = any other key results. jg will add from results section, unless someone else does first. 
+The automatic process out-performs humans in terms time and labor cost, and provides a novel solution for leveraging digitized specimens for machine learning.
+This research has implications for harnessing the tens of thousands of digitized specimens stored in open access repositories found wold-wide.
+%world wide [*across the globe] or we may not even need this part as open access is global access
 
@@
 % Moving teaser since this template doesn't actually ask for one
-Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.~\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.~\cite{page2015digitization} These digital specimen accessible through global, open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable.
-Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
-%{jane}should we try to insert machine learning here, last sentence, or computation methods ok?
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.~\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.~\cite{page2015digitization} These digitized specimen are generally accessible through global, open access repositories supporting digital library services, such as browsing, search and retrieval, and preservation.
+These digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine collections on a previously unattainable scale.
+Moreover, the digitized instantiations present a pathway for applying machine learning and making new scientific discoveries.
 
@@
 associated with the image collections.
-Poor quality images, e.g. with low contrast, inadequate lighting,
-out-of-focus or cluttered visual arrangements, provide inadequate input
+Poor quality images (e.g. low contrast, inadequate lighting,
+out-of-focus or cluttered visual arrangements) provide inadequate input
 for automated
@@
 Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
-human examining several images at a time, they are insufficient for researchers seeking to apply computational methods to examine thousands of images
-to determine if, for instance, a specific fish grows to different lengths
-in different habitats.
+human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %machine learning? or okay here
+to examine thousands of images
+to determine if, for example, a specific fish grows to different lengths
+in different habitats, or the impact of temporal factors the size of a dorsal fin.
 \begin{figure*}
@@
 
-Since the digital collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible.
-Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
+Since the digital collections may each contain tens of thousands of images, manually producing additional image quality metadata for each digitized specimen is both labor-and time intensive and prohibitively expensive.
+Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
+%we are both extracting and calculating.
+Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.
 As a step towards improving metadata in specimen research image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
@@
 The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
-Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
+Using a combination of machine learning and image informatics 
+techniques,
+%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
+we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
 image scaling based on ruler identification and measurement. Image scaling

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 study.
+%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results.
+I guess it's okay to give this in introduction.
+Just wanted to raise this point.
+I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both.
+I think it's okay as I re-read it, but good to have someone check.
 The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods.
@@
 A number of different metadata standards have been applied to support the description and access of digitized scientific images.
-The Darwin Core (DwC~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data is among the most popular standard for such efforts.
+The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data is among the most popular standard for such efforts.
 It is an extension of the Dublin Core's DCMI Metadata Terms \cite{dc_terms}.
-There is also the recent Audubon Core\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.
-These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
+The Audubon Core\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including 3-D digitized specimens, is an DwC extension that has become more popular.
+All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
 In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels.
@@
 Descriptive oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}.
-Even so, metadata properties used to record image quality is severely limited and generally missing.
-This point is addressed in detail in \cite{leipzig2021biodiversity}, and serves to justify a new initiative at Tulane University, where staff are manually capturing content for 22 metadata properties, to characterize the quality of digitized specimens drawn from the INHS collection and iDigBio.
-This current process is costly in terms of labor and time, error-prone, and underscores the need to
+This point is also emphasized by Wieczorek\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions to meet growing community concerns and needs, including data quality and fitness.
+Even so, metadata describing image quality is severely limited and generally missing.
+This point is addressed in detail in \cite{leipzig2021biodiversity}, serves as the rationale for Tulane University's effort to manually capturing content for 22 metadata properties characterizing digitized specimen image quality.
+Their work is being conducted in connection with the lager BGNN initiative, and the current process is costly in terms of labor and time, prone to human error and inconsistencies, and underscores the need to
 explore automatic metadata generation methods.
-
-%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS},
-
+%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS}
 \subsection{Automatic Metadata Generation}
+Automatic metadata generation advance covering both descriptive and technical metadata are relevant to the research presented in this paper.
+Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating,paynter2005developing}.
+Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.
+Heidorn, et al,\cite{heidorn2008automatic} demonstrated the use optical character recognition (OCR) to extract specimen information from the original typed and often hand-annotated labels that are digitized along with herbarium collection holdings.
+The extracted information was  encoded in the DwC metadata associated with the specimen's digitized rendering.
+There's also been some success with extracting descriptive cartographic information from maps \cite{manso2004automatic}.
+While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; extensive use of automatic processes are still limited.
+More significantly, descriptive metadata does not not sufficiently addressed data quality.
+
 Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)\cite{Exif}, the camera's technical metadata that is automatically captured and inserted into digital image files at the time of digitization.
@@
 A researcher may desire images captured chiefly with a certain aperture setting.
-Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse.
-
-Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating}.
-Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.
-
-%\cite{heidorn2008automatic} speciment labels \cite{manso2004automatic} cartographic info.
-%above paragraph..need to finesse a couple of sentences w/results, weave in these 2 citations, and then say we can look to image analysis.
+Even so, the majority of automatically captured technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error.
+Fish image analysis research, as reviewed below, provides an opportunity to address current metadata shortcomings and needs specific to the selection of high-quality images for neural networks and the application of machine learning.
 
@@
 \section{Methods}
-Our process for metadata generation can be broken into three steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image processing at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.
+Our process for metadata generation can be broken into three steps: 1) object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), 2) image processing at the pixel level, and 3) calculations on the results of the previous steps to determine higher level metadata properties.
 % \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 Even so, the majority of automatically captured technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error.
-Fish image analysis research, as reviewed below, provides an opportunity to address current metadata shortcomings and needs specific to the selection of high-quality images for neural networks and the application of machine learning.
+Fish image analysis research, as reviewed below, provides an opportunity to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for neural networks and the application of machine learning.
 

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 \usepackage{comment}
-\usepackage{todonotes}
+%\usepackage{todonotes}
 \usepackage{wrapfig}
@@
 that will enable further downstream analyses.
-
-We are applying a variety of machine learning, image processing and
-image informatics techniques to extract critical properties from the
-images.  The properties will allow follow-on studies to identify
-the specific images needed for a particular analysis, ensuring that
-the specimen images meet both scientific and technical requirements.
+%RE: paragraph directly above, DAVE/JOEL - thinking we should we shift message a little bit to something like, e.g., The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories.
+Our research addresses this need by applying machine learning and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results.
+Our goals and objectives our presented below.
+
+%I think this paragraph could be deleted then, or moves elsewhere, we say this a lot already: We are applying a variety of machine learning, image processing and image informatics techniques to extract key metadata properties from the images.
+These properties a critical for selecting high-quality, usable digitized specimens for further computational analysis, and and ensuring that the specimen images meet both scientific and technical requirements.
 
@@
 
-Digitized specimen collections offer numerous outstanding opportunities
-for new scientific studies and discoveries.
-%I think we can go from the above, statement, directly to the paragraph that starts with "Given the many..." Then, specifically state the goal of this paper is to XXXX address the need, or the goal is to investigate, test, (pick your verb) an approach automatically generating metadata, combining off-the-shelf software and custom written, or is it simply test off-the-shelf software, and later the realization that customization happens.
-The amount of data is immense, with image collections containing 10,000's
-of entries. These discoveries will only be possible
-with computational techniques that can process this vast amount of data.
-
-These image-based computational techniques are hampered by both poor
-image quality and the lack of high-quality and pertinent metadata
-associated with collections.
-
-For example, a study may require images that contain only one fish with a
-given level of lighting and contrast. Additionally, performing quantitative
-investiations into the morphology of the specimens requires knowing
-the physical scale of the images, i.e.~pixels/inch.
-
-Given the many thousands of images that have and will be acquired of
-biological specimens, it is infeasible to generate the needed metadata
-via manual, i.e. via human input, methods.  It is critical to deploy
-computational techniques that will automate the process of generating
-the metatdata that is essential for downstream analyses and studies.
-
-In order to address the need for fish specimen image metadata that can
-support scientific investigations we have begun the deployment of
-both off-the-shelf and custom-written software that automatically
-generates a variety of metadata from a publicly-available biological
-image repository.  The types of metadata being produced are related
-to image quality, content and scale, and should provide the information
-necessary for advanced quantitative studies of the digitized specimens.
-
-The automated metadata generation methods for our project were developed
-to work on a specific set of images, the INHS\ Fish
-Collection~\cite{INHS}.  Most of these images have been configured,
-produced and acquired with a standard procedure.  The images used for
-our study contain one fish placed on a bright, white background and
-contain an information tag and the same ruler.  See
-Figure \ref{fig:teaser} for two example images from the collection.
-While training and focusing our system on images with very similar
-compositions and visual properties may limit its immediate applicability,
-our efforts do demonstrate the potential that machine learning and
-image informatics techniques have for automatically generating metadata
-for biological specimen image collections.
+Digitized specimen accessible in open access repositories provide a rich, extensive data source machine-learning and scientific discovery, however, these resources remain largely untapped due image quality and metadata limitations.
+We are addressing this need by combining machine-learning and image informatics technqiues.
+The overall goal of our
+
+%Following is original Goals/objectives text: The amount of data is immense, with image collections containing 10,000's of entries.
+These discoveries will only be possible with computational techniques that can process this vast amount of data.
+
+%These image-based computational techniques are hampered by both poor image quality and the lack of high-quality and pertinent metadata associated with collections.
+
+%For example, a study may require images that contain only one fish with a given level of lighting and contrast.
+Additionally, performing quantitative investiations into the morphology of the specimens requires knowing the physical scale of the images, i.e.~pixels/inch.
+
+%Given the many thousands of images that have and will be acquired of biological specimens, it is infeasible to generate the needed metadata via manual, i.e.
+via human input, methods.
+It is critical to deploy computational techniques that will automate the process of generating the metatdata that is essential for downstream analyses and studies.
+
+%In order to address the need for fish specimen image metadata that can support scientific investigations we have begun the deployment of both off-the-shelf and custom-written software that automatically generates a variety of metadata from a publicly-available biological image repository.
+The types of metadata being produced are related to image quality, content and scale, and should provide the information necessary for advanced quantitative studies of the digitized specimens.
+
+%The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.
+Most of these images have been configured, produced and acquired with a standard procedure.
+The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.
+See Figure \ref{fig:teaser} for two example images from the collection.
+While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts do demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
   \centering

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 were  applied to a set of \(7,244\)
-images drawn from the Illinois Natural History Survey (INHS) Collection.
+images drawn from the Illinois Natural History Survey (INHS) Collection.~\cite{INHS}
 Figure \ref{fig:INHS_examples} presents three typical images used in our
@@
 that will enable further downstream analyses.
-%RE: paragraph directly above, DAVE/JOEL - thinking we should we shift message a little bit to something like, e.g., The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories.
+NOTE-NOTE-NOTE DAVE/JOEL/ALL - RE: above paragraph, I'm thinking we should we shift message a little bit to something like, e.g., "The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories.
 Our research addresses this need by applying machine learning and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results.
-Our goals and objectives our presented below.
+Our goals and objectives are presented in the following section.
 

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 were  applied to a set of \(7,244\)
-images drawn from the Illinois Natural History Survey (INHS) Collection.~\cite{INHS}
+images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
 Figure \ref{fig:INHS_examples} presents three typical images used in our
@@
 that will enable further downstream analyses.
-NOTE-NOTE-NOTE DAVE/JOEL/ALL - RE: above paragraph, I'm thinking we should we shift message a little bit to something like, e.g., "The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories.
+
+<--NOTE-NOTE-NOTE DAVE/JOEL/ALL - RE: above paragraph, I'm thinking we should we shift message a little bit to something like, e.g., "The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories.
 Our research addresses this need by applying machine learning and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results.

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 % Moving teaser since this template doesn't actually ask for one
-Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images.~\cite{beaman2012mass} Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens.~\cite{page2015digitization} These digitized specimen are generally accessible through global, open access repositories supporting digital library services, such as browsing, search and retrieval, and preservation.
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images~\cite{beaman2012mass}.
+Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}.
+These digitized specimen are generally accessible through global, open access repositories supporting digital library services, such as browsing, search and retrieval, and preservation.
 These digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine collections on a previously unattainable scale.
@@
 requiring the ability to identify and measure rulers in the images.
-Many specimen collections do include Darwin Core metadata,~\cite{biodiv_info_standards} detailing
+Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
 specimen taxon, geographic location, and several other descriptive aspects.
@@
 The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data is among the most popular standard for such efforts.
-It is an extension of the Dublin Core's DCMI Metadata Terms \cite{dc_terms}.
-The Audubon Core\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including 3-D digitized specimens, is an DwC extension that has become more popular.
-All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator.
+It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}.
+The Audubon Core~\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including 3--D digitized specimens, is an DwC extension that has become more popular.
+All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the lens of a human curator.
 In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels.
@@
 Descriptive oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}.
-This point is also emphasized by Wieczorek\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions to meet growing community concerns and needs, including data quality and fitness.
+This point is also emphasized by Wieczorek~\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions to meet growing community concerns and needs, including data quality and fitness.
 Even so, metadata describing image quality is severely limited and generally missing.
@@
 \subsection{Automatic Metadata Generation}
-Automatic metadata generation advance covering both descriptive and technical metadata are relevant to the research presented in this paper.
+Automatic metadata generation advances covering both descriptive and technical metadata are relevant to the research presented in this paper.
 Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating,paynter2005developing}.
-Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.
-Heidorn, et al,\cite{heidorn2008automatic} demonstrated the use optical character recognition (OCR) to extract specimen information from the original typed and often hand-annotated labels that are digitized along with herbarium collection holdings.
+Researchers have applied support vector machine (SVM) approaches~\cite{han2003automatic}, and associated networks to address sparse and incomplete metadata~\cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.
+Heidorn, et al.~\cite{heidorn2008automatic} demonstrated the use of optical character recognition (OCR) to extract specimen information from the original typed and often hand-annotated labels that are digitized along with herbarium collection holdings.
 The extracted information was encoded in the DwC metadata associated with the specimen's digitized rendering.
-There's also been some success with extracting descriptive cartographic information from maps \cite{manso2004automatic}.
+There has also been some success with extracting descriptive cartographic information from maps~\cite{manso2004automatic}.
 While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; extensive use of automatic processes are still limited.
@@
 
-Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)\cite{Exif}, the camera's technical metadata that is automatically captured and inserted into digital image files at the time of digitization.
+Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)~\cite{Exif}.
+The camera's technical metadata that is automatically captured and inserted into digital image files at the time of capture.
 Some of this metadata may be useful when selecting a machine learning sample.
-A researcher may desire images captured chiefly with a certain aperture setting.
+A researcher may desire images with specific properties, such as being captured chiefly with a certain aperture setting.
 Even so, the majority of automatically captured technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error.
@@
 Image analysis has been utilized to examine and process images of fish
-for well over two decades \cite{Zion2000InvivoFS,Saberioon2017ApplicationOM}. It is an important
+for well over two decades~\cite{Zion2000InvivoFS,Saberioon2017ApplicationOM}. It is an important
 application of technology both for marine science, in the study of aquatic
@@
 of fish based on color and texture features and a multi-class support
-vector machine (MSVM) \cite{Vapnik1999AOS}.
-Li and Hong \cite{Li2014IdentificationOF} computed eleven shape and color
+vector machine (MSVM)~\cite{Vapnik1999AOS}.
+Li and Hong~\cite{Li2014IdentificationOF} computed eleven shape and color
 features from fish images and derived a linear model
@@
 Our work stands apart from previous work in that we are
-addressing a different need. Lack of metadata is impeding scientific studies.
+addressing a different need: lack of metadata is impeding scientific studies.
 Our focus and motivation are different.
@@
 Digitized specimen accessible in open access repositories provide a rich, extensive data source machine-learning and scientific discovery, however, these resources remain largely untapped due image quality and metadata limitations.
-We are addressing this need by combining machine-learning and image informatics technqiues.
+The overall goal is addressing this need by combining machine-learning and image informatics techniques.
 The overall goal of our
@@
 years \cite{zou2019object}, and has resulted in a number of well-tested, purpose-built architectures.
-We elected to use Facebook AI Research's \verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project.
+We elected to use Facebook AI Research's (FAIR) \verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project.
 \verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format datasets.
 It is able to handle an arbitrary number of object classes, and can classify an arbitrary number of object within a given image.
+We chose \verb|detectron| for its relative ease of use compared to lower level libraries, and its implementations of powerful architectures developed by FAIR.
 For our project, we use it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers,

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 The overall goal is addressing this need by combining machine-learning and image informatics techniques.
-The overall goal of our
-
+The overall goal of our research is to offer a machine-driven [*novel/innovative??
+blah...] approach to current manual metadata generation that is prohibitively costly in both terms of labor and time, and to further offer a [*novel] approach to computing higher-level metadata that supports scientific inquiry.
+Three key objectives are to:
+1) Test [*Explore, Demonstrate the us of] Facebook's AI Research's dectectron tool
+Specific aims are to use dectectron to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers, as shown in Figure 2.
+2) Pursue [*Investigate] image processing at the pixel level.
+Pilot testing found the dectectron bounding boxes could be more tightly enclosed the detected objects. We will see if additional masking background as part of the fish, or the
+bounding box may clip away part(s) of the fish with pixel analysis methods commonly
+found in image informatics. Specific aim [*objectives] of our research are to:
+%not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with 
+1.
+Identify the appropriate threshold.
+We will compute optimal scaling between [*or is it Otsu thresholding] to identify an improved threshold value.
+[Or we will determine is we can computed as the halfway point between the Otsu threshold value and the mean of the background intensities.]
+2. Consolidate the foreground
+3. Adjusting the bounding box. [We will use computational methods for masking [calcuate a mask?] to determine if bounding box needs to be shrunk or expanded]
+% Jane confused here, if this belongs here, or below
+4. Developing a fallback approach for when flood fill operations behave unexpectedly the image is too washed out.
+3) Compute [Test our ability to calculate] the following higher-level metadata properties: 
+1) contrast (intensities of
+the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.
 %Following is original Goals/objectives text: The amount of data is immense, with image collections containing 10,000's of entries.
@@
 
-%The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.
+The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.
 Most of these images have been configured, produced and acquired with a standard procedure.
@@
 All instance types were included in a single object detection model.
-The total cross--entropy loss began at \(2.948\) and ended at \(0.158\) for the training data.
+The total cross-entropy loss began at \(2.948\) and ended at \(0.158\) for the training data.
 
@@
 shortcomings, we utilize pixel analysis methods commonly found in image
-informatics to produce more accurate objects masks and bounding boxes.
+informatics to produce more accurate object masks and bounding boxes.
 
@@
 With an accurate mask generated, it is then necessary to check whether the bounding box needs expanded or shrunk along any edges.
-Expansion is done first, buy checking whether any edge intersects with any of the foreground mask pixels.
+Expansion is done first, by checking whether any edge intersects with any of the foreground mask pixels.
 If one does, it is expanded out by 1 pixel.
-If any edges are expanded, the whole the process, masking and expansion process is repeated to account for any changes in average intensities.
-Once no edges contain foreground pixels, the mask is the shrunk.
+If any edges are expanded, the whole process of masking and expansion process is repeated to account for any changes in average intensities.
+Once no edges contain foreground pixels, the mask is then shrunk.
 This process is more efficient as all that is required is to shrink each edge by one up until the point they contain one or more foreground pixels.
@@
 \subsubsection{Fallback} The pixel analysis process occasionally fails,
-e.g.~ flood-filling does not produce a large enough blob or
+e.g.\ when flood-filling does not produce a large enough blob or
 the bounding box adjustment does not terminate.

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 Three key objectives are to:
-1) Test [*Explore, Demonstrate the us of] Facebook's AI Research's dectectron tool
-Specific aims are to use dectectron to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers, as shown in Figure 2.
-2) Pursue [*Investigate] image processing at the pixel level.
+
+GOAL 1) Test [*Explore, Demonstrate the us of] Facebook's AI Research's dectectron tool
+Specific aims are to use dectectron to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers, as shown in Figure
+
+GOAL 2) Pursue [*Investigate] image processing at the pixel level.
 Pilot testing found the dectectron bounding boxes could be more tightly enclosed the detected objects. We will see if additional masking background as part of the fish, or the
@@
 %not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with
+
 1.
@@
 [Or we will determine is we can computed as the halfway point between the Otsu threshold value and the mean of the background intensities.]
+
 2. Consolidate the foreground
+
 3. Adjusting the bounding box. [We will use computational methods for masking [calcuate a mask?] to determine if bounding box needs to be shrunk or expanded]
 % Jane confused here, if this belongs here, or below
+
 4. Developing a fallback approach for when flood fill operations behave unexpectedly the image is too washed out.
-3) Compute [Test our ability to calculate] the following higher-level metadata properties: 
-1) contrast (intensities of
-the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.
+
+GOAL 3) Compute [*Test our ability to calculate] the following set of higher-level metadata properties: 1) contrast (intensities of the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.
+
 %Following is original Goals/objectives text: The amount of data is immense, with image collections containing 10,000's of entries.
@@
 For our project, we use it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers,
-as shown in Figure \ref{fig:teaser}.
+as shown in Figure \ref{fig:teaser}. Objects with a 30\% confidence score or higher are maintained for analysis.
 
@@
 % by 50\% of the difference between the mean of the background and the original threshold value, which 
-captures most of fish's fins in most cases, without also masking parts of the background.
+struck a fairly optimal balance between capturing most of fish's fins in most cases, without also masking parts of the background.
 
@@
 If an eye is found, the sign of the \(x\) component of the vector from the centroid of the fish to the centroid of the eye specifies which side is up: negative for left and positive for right.
-This assumes the fish was photographed vertically, which is essentially always the case for all image collections our group has worked on.
+This assumes the fish was photographed vertically (i.e.\ dorsal fin on top), which is essentially always the case for all image collections our group has worked on.
 \subsubsection{primary\_axis and clock\_value}
@@
 In 56 of the images, the ruler itself was found, but the numbers ``2''
-and/or the ``3'' on the ruler were not. Therefore a scale calculation could
+and/or ``3'' on the ruler were not. Therefore, a scale calculation could
 not be performed, producing a 99.2\% success rate for
@@
 \verb|detectron| was unable to find a fish eye
-in 246 of the images. Of the remaining \(6,998\) images, the correct side
+in 246 of the images. These eyes were generally extremely dark, small, or looked nothing like those found in the training set. Of the remaining \(6,998\) images, the correct side
 (\verb|left| or \verb|right|) was detected in all but 6 cases, producing
@@
 For these 6 cases, a spot on the wrong side of the fish was labeled as the
-most likely eye within the bounding box of the fish, i.e.~eye detection 
+most likely eye within the bounding box of the fish, i.e.\ eye detection 
 was incorrect. Figure \ref{fig:wrong_eye} presents one such example.
@@
 correspond to the mean foreground intensity computed by the automated system.
-The mean and standard deviation of the mean foreground intensities were
+The mean and standard deviation of the foreground intensities were
 computed for the images in the three human-specified classes.
@@
 \section{Conclusions}
-\textbf{Todo}
+The BGNN project demonstrates a clear need for improved metadata for specimen image collections.
+Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and machine learning is limited.
+Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are needed to generate this missing metadata at scale.
+
+In this paper we presented such a metadata generation program.
+It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes and scale and length information.
+Testing this program on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation metadata.
+Through further refinement and generalizing beyond only INHS images, we aim to create a tool that can be distributed to specimen image collection curators to correct the metadata sparsity that precipitated this work.
 \subsection{Future Work}
@@
 Considering when the RGB channels of a pixel are not equal in value may be able to improve masking of such features.
-Another possible approach to solving this is to threshold an mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.
+Another possible approach to solving this is to threshold and mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.
 
@@
 To accomplish this, a much larger training dataset full of more diverse images will be required.
-Another requirement will be to generalize the ruler reading process beyond the INHS specific reading of digits on the ruler.
-\textbf{Todo}: Suggest way(s) to do this?
+Another requirement will be to generalize the ruler reading process beyond the INHS specific reading of digits on the ruler, which will likely involve an automated method of reading ruler ticks instead of digits.
 % Todo: Are these worth mentioning?

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

@@
 Philadelphia, PA\hspace{3mm}USA\\
-0000-0002-1601-8729}\\
+\href{https://orcid.org/0000-0002-1601-8729}{0000-0002-1601-8729}}\\
 \IEEEauthorblockN{Xiaojun Wang}
@@
 New Orleans, LA\hspace{3mm}USA\\
-0000-0001-8639-6795}
+\href{https://orcid.org/0000-0002-2995-9050}{0000-0002-2995-9050}}
 \and
@@
 Philadelphia, PA\hspace{3mm}USA\\
-0000-0001-7819-5360}\\
+\href{https://orcid.org/0000-0001-7819-5360}{0000-0001-7819-5360}}\\
 \IEEEauthorblockN{Henry Bart Jr.}
@@
 New Orleans, LA\hspace{3mm}USA\\
-0000-0002-5662-9444}
+\href{https://orcid.org/0000-0002-5662-9444}{0000-0002-5662-9444}}
 \and
@@
 New Orleans, LA\hspace{3mm}USA\\
-0000-0001-6144-9440}\\
+\href{https://orcid.org/0000-0001-6144-9440}{0000-0001-6144-9440}}\\
 \IEEEauthorblockN{David Breen}
@@
 Philadelphia, PA\hspace{3mm}USA\\
-0000-0002-1376-5008}
+\href{https://orcid.org/0000-0002-1376-5008}{0000-0002-1376-5008}}
 }

### 2021-04-06 paper/paper_new.tex
Updates from Overleaf

@@
     \centering
-    \caption{Metadata properties}
+    \caption{Metadata properties (* indicates higher order properties)}
     \label{tab:properties}
@@
         \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
-        \verb|scale| & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|scale|* & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
         \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of the bounding box for a fish.\\
@@
         \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
-        \verb|contrast| & Per Fish & Float & The contrast between foreground and background intensities within a given fish's bounding box.\\
+        \verb|contrast|* & Per Fish & Float & The contrast between foreground and background intensities within a given fish's bounding box.\\
         \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
-        \verb|primary_axis| & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
-        \verb|clock_value| & Per Fish & Integer & Fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
-        \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|primary_axis|* & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
+        \verb|clock_value|* & Per Fish & Integer & Fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
+        \verb|length|* & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
         \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
@@
         \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
-        \verb|side| & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
+        \verb|side|* & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
       \bottomrule

### 2021-04-06 paper/paper_new.tex
Reworked Section III.

--- 2021-04-05 paper/paper_new.tex
@@
 The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods.
-Next, the results are presented, followed by a discussion.
+Next, the results, along with discussion, are presented.
 The conclusion highlights key findings and identifies next steps.
@@
 
+The research reviewed above involves image features extraction and
+artificial intelligence; although the researchers have not applied these
+approaches to the burgeoning collections of digitized specimens
+accessible in open repositories. Our research addresses this need by
+applying machine learning and image informatics techniques to extract key
+metadata properties from fish specimen images and computing
+higher-level metadata based on these initial results.
+Our goals and objectives our presented below.
+
+\begin{comment}
 Our work stands apart from previous work in that we are
@@
 Our goals and objectives are presented in the following section.
+\end{comment}
 
@@
 
-Digitized specimen accessible in open access repositories provide a rich, extensive data source machine-learning and scientific discovery, however, these resources remain largely untapped due image quality and metadata limitations.
-The overall goal is addressing this need by combining machine-learning and image informatics techniques.
-The overall goal of our research is to offer a machine-driven [*novel/innovative??
-blah...] approach to current manual metadata generation that is prohibitively costly in both terms of labor and time, and to further offer a [*novel] approach to computing higher-level metadata that supports scientific inquiry.
-Three key objectives are to:
-
-GOAL 1) Test [*Explore, Demonstrate the us of] Facebook's AI Research's dectectron tool
-Specific aims are to use dectectron to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers, as shown in Figure
-
-GOAL 2) Pursue [*Investigate] image processing at the pixel level.
-Pilot testing found the dectectron bounding boxes could be more tightly enclosed the detected objects. We will see if additional masking background as part of the fish, or the
-bounding box may clip away part(s) of the fish with pixel analysis methods commonly
-found in image informatics. Specific aim [*objectives] of our research are to:
+Digitized specimen accessible in open access repositories provide a rich,
+extensive data source for machine-learning and scientific discovery.
+These resources, however, remain largely untapped due to image quality
+issues and metadata limitations.
+The overall goal of our work addresses this need by combining
+machine-learning and image informatics techniques to produce a computational
+% . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
+alternative to the current manual metadata generation process, one that is
+prohibitively costly in both terms of labor and time. Additionally, our
+methods collectively provide a novel approach to computing higher-level
+metadata that will support further scientific inquiry.
+
+% [WHAT'S THE DIFFERENCE BETWEEN A GOAL AND AN OBJECTIVE?]
+
+Four key objectives are to:
+
+1) Explore use of Facebook AI Research's \verb|detectron| tool.  Specific
+aims are to use \verb|detectron| to identify study-specific objects.
+% classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers, as shown in
+% Figure \ref{fig:teaser}.
+
+2) Investigate image processing at the pixel level.
+Pilot testing found the detectron under-segmented the detected objects
+with tightly enclosing bounding boxes. We will determine if
+pixel analysis methods commonly found in image informatics may produce
+more accurate bounding boxes and object masks.
+% background as part of the fish, or the
+% bounding box may clip away part(s) of the fish with
+The specific aims of this objective are to:
 %not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with
 
-1.
-Identify the appropriate threshold.
-We will compute optimal scaling between [*or is it Otsu thresholding] to identify an improved threshold value.
+\renewcommand{\labelenumi}{\alph{enumi}.}
+\begin{enumerate}
+\item
+Identify the appropriate threshold value for more accurate mask.
+% We will compute optimal scaling between [*or is it Otsu thresholding] to identify an improved threshold value.
 [Or we will determine is we can computed as the halfway point between the Otsu threshold value and the mean of the background intensities.]
 
-2. Consolidate the foreground
-
-3. Adjusting the bounding box. [We will use computational methods for masking [calcuate a mask?] to determine if bounding box needs to be shrunk or expanded]
+\item
+Remove noise to produce a single, solid mask.
+
+\item
+Compute more accurate bounding box from updated mask.
+% Adjusting the bounding box. [We will use computational methods for masking [calcuate a mask?] to determine if bounding box needs to be shrunk or expanded]
 % Jane confused here, if this belongs here, or below
 
-4. Developing a fallback approach for when flood fill operations behave unexpectedly the image is too washed out.
-
-GOAL 3) Compute [*Test our ability to calculate] the following set of higher-level metadata properties: 1) contrast (intensities of the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.
+\item
+Automatically determine when modified methods fail and detectron values
+should be used as is.
+% Developing a fallback approach for when flood fill operations behave unexpectedly the image is too washed out.
+\end{enumerate}
+
+\begin{figure*}[t]
+  \centering
+ \includegraphics[width=.45\linewidth]{images/teaser1_crop}
+  \hspace{5mm}
+  \includegraphics[width=.45\linewidth]{images/teaser2_crop}
+  \caption{Initial object detection on two specimen images using Detectron2~\cite{wu2019detectron2}.}
+  \label{fig:teaser}
+\end{figure*}
+
+3) Compute a number of high-level metadata properties from the detected objects and image quality metrics.
+% [*Test our ability to calculate] the following set of
+% : 1) contrast (intensities of the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.
+
+4) Compare computed metadata properties with manually generated properties
+when possible to assess the accuracy and effectiveness of automated 
+methods.
 
@@
 The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.
-See Figure \ref{fig:teaser} for two example images from the collection.
+See Figure \ref{fig:INHS_examples} for three example images from the collection.
 While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts do demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections.
@@
 % \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}
-
-\begin{figure}[b]
-  \centering
-%  \includegraphics[width=.49\linewidth]{images/teaser1_crop}
-  %\hspace{4mm}
-  \includegraphics[width=.90\linewidth]{images/teaser2_crop}
-  \caption{Initial object detection on a specimen image using Detectron2~\cite{wu2019detectron2}.}
-  \label{fig:teaser}
-\end{figure}
 
@@
 images. Object detection has been a broadly active field of study in recent
-years \cite{zou2019object}, and has resulted in a number of well-tested, purpose-built architectures.
-We elected to use Facebook AI Research's (FAIR) \verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project.
+years \cite{zou2019object}, and has resulted in a number of well-tested, purpose-built architectures. We elected to use Facebook AI Research's (FAIR)
+\verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project.
 \verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format datasets.

### 2021-04-06 paper/paper_new.tex
Updates from Overleaf
Edited the abstract and Intro.

@@
 \begin{abstract}
-Metadata is a key data source particularly for researchers seeking use apply achine learning to the vast collections of digitized specimens.
-Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual means.
-This paper reports on a research applying machine-driven approaches to analyze digitized fish images and extract a variety of important features.
-The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
-The automatically generated metadata is crucial for identifying high-quality images for the neural network to support predictive analyses.%predictive analytics?
-Research combining machine learning  and  image  informatics techniques allow us to rapidly enrich existing metadata associated for a sample of 7244 images from the Illinois Natural History Survey (INHS).
-The sample also includes 22 manually generated image-quality metadata properties, aiding our comparison.
-Results show we can  accurately generate metadata for six key %6?
-metadata properties: fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also show can also x, y, z.
+Metadata is a key data source, particularly for researchers seeking to apply machine learning to the vast collections of digitized specimens.
+Unfortunately, the available metadata is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual means.
+This paper reports on research that applies machine-driven approaches to
+analyzing digitized fish images and extracting various of important
+features from them.
+The digitized fish specimens are being analyzed as part of the Biology Guided Neural Networks (BGNN) initiative, which is developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
+Automatically generated metadata is crucial for identifying
+the high-quality images needed for the neural network's predictive
+analyses.
+%predictive analytics?
+Methods that  combine machine learning  and  image  informatics techniques allow us to rapidly enrich the existing metadata associated with each of the
+7,244 images from the Illinois Natural History Survey (INHS). The sample
+images each include 22 manually generated metadata properties, which
+aid our study.  Results show we can  accurately generate metadata for
+twenty key %6? 
+metadata properties, for example: fish quantity, fish orientation,
+image scaling based on
+ruler identification and measurement, and general image quality metrics
+(brightness and contrast). Results also show can also x, y, z.
 %to confirm list of six properties.
 %x, y, z = any other key results. jg will add from results section, unless someone else does first. 
-The automatic process out-performs humans in terms time and labor cost, and provides a novel solution for leveraging digitized specimens for machine learning.
-This research has implications for harnessing the tens of thousands of digitized specimens stored in open access repositories found wold-wide.
+The automatic process out-performs humans in terms of time and labor cost,
+as well as accuracy, and provides a novel solution for leveraging digitized
+specimens for machine learning. This research has implications for harnessing the tens of thousands of digitized specimens stored in open-access repositories found wold-wide.
 %world wide [*across the globe] or we may not even need this part as open access is global access
@@
 Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images~\cite{beaman2012mass}.
-Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}.
-These digitized specimen are generally accessible through global, open access repositories supporting digital library services, such as browsing, search and retrieval, and preservation.
-These digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine collections on a previously unattainable scale.
-Moreover, the digitized instantiations present a pathway for applying machine learning and making new scientific discoveries.
+Additionally, initiatives, such as the National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program,
+% (which ran for nearly a decade),
+have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}.
+These digitized specimens are generally accessible through global, open-access repositories that support digital library services, such as browsing, search and retrieval, and preservation.
+The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
+on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying machine learning and making new scientific discoveries.
 
@@
 to determine if, for example, a specific fish grows to different lengths
-in different habitats, or the impact of temporal factors the size of a dorsal fin.
+in different habitats, or the temporal evolution of an anatomical feature,
+e.g.~the size of a dorsal fin.
 \begin{figure*}
@@
 
-Since the digital collections may each contain tens of thousands of images, manually producing additional image quality metadata for each digitized specimen is both labor-and time intensive and prohibitively expensive.
+Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is both labor- and time-intensive and prohibitively expensive.
 Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
@@
 Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.
-As a step towards improving metadata in specimen research image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
+As a step towards improving metadata in research specimen image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
 extract a set of data features that provide important metadata about the
-digitized specimen.
-The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
+digitized specimens.
+The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which is developing a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
 Using a combination of machine learning and image informatics 
@@
 as their length and area.  In order to test and validate our methods, they
-were  applied to a set of \(7,244\)
+have been  applied to a set of \(7,244\)
 images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
@@
     \centering
-    \caption{Metadata properties (* indicates higher order properties)}
+    \caption{Metadata properties (* indicates higher order derived properties)}
     \label{tab:properties}

### 2021-04-07 paper/paper_new.tex
Edited Sections 2 & 3.

@@
 A number of different metadata standards have been applied to support the description and access of digitized scientific images.
-The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data is among the most popular standard for such efforts.
+The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data, is one of the most popular standards for such efforts.
 It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}.
-The Audubon Core~\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including 3--D digitized specimens, is an DwC extension that has become more popular.
-All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the lens of a human curator.
-In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels.
+The Audubon Core~\cite{audub_core}, which supports the discoverability, dissemination, and use of data related to biological organisms (including 3--D digitized specimens), is a DwC extension that has become more popular.
+All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the perspective of a human curator.
+In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawn from acquisition logs or original specimen labels.
 This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply machine learning to the image and the metadata for scientific research.
@@
 This limitation is magnified when trying to assess the actual quality of the digitized specimen.
-Descriptive oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}.
-This point is also emphasized by Wieczorek~\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions to meet growing community concerns and needs, including data quality and fitness.
+Descriptive-oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}.
+This point is also emphasized by
+Wieczorek et al.~\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions needed to meet growing community concerns and
+requirements, including data quality and fitness.
 Even so, metadata describing image quality is severely limited and generally missing.
-This point is addressed in detail in \cite{leipzig2021biodiversity}, serves as the rationale for Tulane University's effort to manually capturing content for 22 metadata properties characterizing digitized specimen image quality.
-Their work is being conducted in connection with the lager BGNN initiative, and the current process is costly in terms of labor and time, prone to human error and inconsistencies, and underscores the need to
+This point is addressed in detail by Leipzig et al.~\cite{leipzig2021biodiversity} and serves as the rationale for Tulane University's effort to manually capture
+content for 22 metadata properties that characterize digitized specimen image quality.
+Their work is being conducted in connection with the larger BGNN initiative, and the current process is costly in terms of labor and time, prone to human error and inconsistencies, and underscores the need to
 explore automatic metadata generation methods.
@@
 While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; extensive use of automatic processes are still limited.
-More significantly, descriptive metadata does not not sufficiently addressed data quality.
+More significantly, descriptive metadata does not sufficiently addressed data quality.
 
 Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)~\cite{Exif}.
-The camera's technical metadata that is automatically captured and inserted into digital image files at the time of capture.
+The camera's technical metadata is automatically captured and inserted into digital image files at the time of acquisition.
 Some of this metadata may be useful when selecting a machine learning sample.
 A researcher may desire images with specific properties, such as being captured chiefly with a certain aperture setting.
-Even so, the majority of automatically captured technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error.
-Fish image analysis research, as reviewed below, provides an opportunity to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for neural networks and the application of machine learning.
+Even so, the majority of automatically registered technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error.
+Fish image analysis research, as reviewed below, demonstrates the
+potential of automated computational methods to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for the application of machine learning.
 
@@
 Utilizing texture, anchor points, and statistical measurements,
-Alsmadi et al.~\cite{Alsmadi2019RFE} implemented fish
-classification through a meta-heuristic algorithm known as Memetic Algorithm (Genetic Algorithm with Simulated Annealing) with back-propagation algorithm (MA-B Classifier).
-They were able to classify 24 fish families with 90\%
-accuracy.
+Alsmadi et al.~\cite{Alsmadi2019RFE} implemented fish classification
+through a meta-heuristic algorithm known as the Memetic Algorithm.
+% (Genetic Algorithm with Simulated Annealing) with back-propagation algorithm (MA-B Classifier).
+They were able to classify 24 fish families with 90\% accuracy.
 % Nope
@@
 % \textbf{Orientation, Length, Size, Weight and Shape}\newline
-Especially in industrial settings it is necessary to automatically
+Especially in industrial settings, it is necessary to automatically
 detect the orientation, length and weight of fish during handling
@@
 Finally, after extracting the fin regions, the start point of the pectoral fin and the end point of the anal fin will be applied in the trout processing system as the head and belly cutting points, respectively.
-Another application of image analysis to fish images is the evaluation
+Another application of image analysis to fish images is the evaluation of
 fish freshness, a computation usually performed on the color features of
@@
 
-Digitized specimen accessible in open access repositories provide a rich,
-extensive data source for machine-learning and scientific discovery.
+Digitized specimens accessible in open-access repositories provide a rich,
+extensive data source for machine learning and scientific discovery.
 These resources, however, remain largely untapped due to image quality
 issues and metadata limitations.
-The overall goal of our work addresses this need by combining
-machine-learning and image informatics techniques to produce a computational
+The overall goal of our work addresses this need by
+% combining machine learning and image informatics techniques to produce
+developing a computational
 % . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
@@
 prohibitively costly in both terms of labor and time. Additionally, our
-methods collectively provide a novel approach to computing higher-level
-metadata that will support further scientific inquiry.
+methods collectively provide a novel and general approach to computing
+higher-level metadata that will support scientific inquiry based
+on the analysis of specimen image collections.
 
@@
 
-Four key objectives are to:
+Our four key objectives are to:
 
@@
 2) Investigate image processing at the pixel level.
-Pilot testing found the detectron under-segmented the detected objects
+Pilot testing found that \verb|detectron| under-segmented the detected objects
 with tightly enclosing bounding boxes. We will determine if
@@
 \item
-Identify the appropriate threshold value for more accurate mask.
+Identify the appropriate threshold value for a more accurate mask.
 % We will compute optimal scaling between [*or is it Otsu thresholding] to identify an improved threshold value.
@@
 \item
-Compute more accurate bounding box from updated mask.
+Compute a more accurate bounding box from the updated mask.
 % Adjusting the bounding box. [We will use computational methods for masking [calcuate a mask?] to determine if bounding box needs to be shrunk or expanded]
@@
 See Figure \ref{fig:INHS_examples} for three example images from the collection.
-While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts do demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections.
+While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.
 

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

--- 2021-04-06 paper/paper_new.tex
@@
 (properties not manually generated),
-a random sample of 50 specimens from the set of \(7,244\) were analyzed by
+a random sample of 100 specimens from the set of \(7,244\) were analyzed by
 hand for comparison.
@@
 All but 263 of these were generated via pixel analysis, with those 263 falling back to the original \verb|detectron| bounding box.
-50 randomly-chosen images were reviewed manually to evaluate the
+100 randomly-chosen images were reviewed manually to evaluate the
 calculation, a representative sample are presented in
 Figure \ref{fig:bbox_mask}.
-All 50 masks and bounding boxes were correctly placed
+All 100 masks and bounding boxes were correctly placed
 on/around the location of the fish. However, a number of them lacked portions of lightly colored tails and/or fins.
-Specifically, 22 masks and bounding boxes covered the entire fish,
-16 missed some of the tail, and 12 missed most or all of the tail, as
+Specifically, 41 masks and bounding boxes covered the entire fish,
+36 missed some of the tail, and 23 missed most or all of the tail, as
 seen in Figure \ref{fig:missedTail}.
@@
 Image scale ($\frac{\mathrm{pixels}}{\mathrm{cm}}$) and fish length were
-measured, using ImageJ~\cite{imagejCite}, in the same 50 test images.
+measured, using ImageJ~\cite{imagejCite}, in the same 100  test images.
 % 50 of these images \todo{The same 50 as before?} were measured by hand to get \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) and fish length in centimeters with ImageJ~\cite{imagejCite}.
@@
 \section{Conclusions}
-The BGNN project demonstrates a clear need for improved metadata for specimen image collections.
+The BGNN project demonstrates a clear need for improved metadata associated with specimen image collections.
 Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and machine learning is limited.
@@
 In this paper we presented such a metadata generation program.
+Using machine learning and image informatics tools and techniques, it is able to locate, bitmask and analyze specimen (currently limited to fish) in collection images with a high degree of accuracy.
 It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes and scale and length information.
-Testing this program on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation metadata.
+Testing this program on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation data.
 Through further refinement and generalizing beyond only INHS images, we aim to create a tool that can be distributed to specimen image collection curators to correct the metadata sparsity that precipitated this work.
@@
 
-Our ultimate goal is to create a generalized process to work on classes of specimen images (specifically all fish images for BGNN), not only the INHS collection.
+Our ultimate goal is to create a generalized process that works on classes of specimen images.
+For the BGNN project we are beginning with fish images, but we are designing the metadata generation system such that it can eventually operate on other species if trained that way.
 To accomplish this, a much larger training dataset full of more diverse images will be required.
+The first step towards greater generality will be to operate on other fish collections besides INHS, which is something our program has already show itself capable of doing during initial testing.
 Another requirement will be to generalize the ruler reading process beyond the INHS specific reading of digits on the ruler, which will likely involve an automated method of reading ruler ticks instead of digits.

### 2021-04-07 paper/paper_new.tex
Edited Section IV.

--- 2021-04-07 paper/paper_new.tex
@@
 \section{Methods}
-Our process for metadata generation can be broken into three steps: 1) object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), 2) image processing at the pixel level, and 3) calculations on the results of the previous steps to determine higher level metadata properties.
+Our process for metadata generation can be divided into three steps: 1) object detection with Facebook's Detectron2 machine learning library (referred to as \verb|detectron|), 2) image processing at the pixel level, and 3) calculations on the results of the previous steps to determine higher level metadata properties.
 % \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}
@@
 years \cite{zou2019object}, and has resulted in a number of well-tested, purpose-built architectures. We elected to use Facebook AI Research's (FAIR)
-\verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project.
+\verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project, given its many flexible and robust capabilities.
 \verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format datasets.
-It is able to handle an arbitrary number of object classes, and can classify an arbitrary number of object within a given image.
-We chose \verb|detectron| for its relative ease of use compared to lower level libraries, and its implementations of powerful architectures developed by FAIR.
+It is able to handle any number of object classes, and can classify an arbitrary number of objects within a given image.
+We chose \verb|detectron| for its relative ease of use compared to lower level libraries, and its implementation of powerful architectures developed by FAIR.
 For our project, we use it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers,
@@
 on images from the INHS\ Fish Collection \cite{INHS}.
-Using \verb|detectron|'s default training scheme, the model was trained for \(100,000\) epochs.
-All instance types were included in a single object detection model.
-The total cross-entropy loss began at \(2.948\) and ended at \(0.158\) for the training data.
+Using \verb|detectron|'s default training scheme, the model was trained for \(100,000\) epochs. All instance types were included in a single object detection model.
+% The total cross-entropy loss began at \(2.948\) and ended at \(0.158\) for the training data.
 
@@
 
-To overcome this under-segmentation, the threshold value should be
+To overcome this improper segmentation, the threshold value should be
 either adjusted up or down, depending on if the background is lighter or darker than the fish.
@@
 % by 50\% of the difference between the mean of the background and the original threshold value, which 
-struck a fairly optimal balance between capturing most of fish's fins in most cases, without also masking parts of the background.
+usually produced an acceptable balance between capturing most of the
+fish's fins, without also masking parts of the background.
 
@@
 Single or small groups of errant pixels can be marked as foreground depending on the consistency of the background, and interior pixels of the fish (especially around the fins) can be marked as background.
-To be useful for generating an accurate bounding box and for subsequent computational analysis, the mask must consist of one single ``blob'' over the fish the contains no holes, and no other pixels disconnected from this blob can be marked as foreground.
+To be useful for generating an accurate bounding box and for subsequent computational analysis, the mask must consist of one single ``blob'' over the fish, i.e.~containing no holes, and no other pixels disconnected from this blob can be marked as foreground.
 
 To accomplish this, we apply an iterative process of flood filling from all the foreground pixels in the image until a blob is generated that is large enough to constitute the fish.
-This is another metaparameter, but greater than 10\% of the current bounding box has masked the specimen in all observed cases.
-Once the fish's blob is found, noise then needs removed.
-This is done by flood filling from each of the corner of the bounding box where the specimen is not present (all four corners in the overwhelming majority of cases), then taking the inverse of the result.
-The fish mask is excluded from these corner flood fills, so this process removes all noise from both the background and foreground of the image leaving only a close mask over the fish itself.
+This leads to another metaparameter, but
+using greater than 10\% of the current bounding box has masked the specimen in all observed cases. Once the fish's blob is found, noise then needs 
+to be removed.
+This is done by flood filling from each of the corners of the bounding box, where the specimen is not present (all four corners in the overwhelming majority of cases), then taking the inverse of the result.
+The fish mask is excluded from these corner flood fills, so this process removes all noise from both the background and foreground of the image, leaving only a single
+mask over the fish itself.
 
 \subsubsection{Adjusting the Bounding Box}
-With an accurate mask generated, it is then necessary to check whether the bounding box needs expanded or shrunk along any edges.
+With an accurate mask generated, it is then necessary to check whether the bounding box needs to be expanded or shrunk along any of its edges.
 Expansion is done first, by checking whether any edge intersects with any of the foreground mask pixels.
 If one does, it is expanded out by 1 pixel.
-If any edges are expanded, the whole process of masking and expansion process is repeated to account for any changes in average intensities.
-Once no edges contain foreground pixels, the mask is then shrunk.
-This process is more efficient as all that is required is to shrink each edge by one up until the point they contain one or more foreground pixels.
-Once the shrinkage step is accomplished, the final mask and bounding box have been generated.
+If any edges are expanded, the whole process of masking and expansion is repeated to account for any changes in average intensities.
+Once no edges contain foreground pixels, the bounding box is then shrunk.
+% This process is more efficient as all that is required is to shrink
+Each edge is contacted by one pixel up until it contain one or more foreground pixels. Once the shrinkage step is accomplished, the final mask and bounding box have been generated.
 
@@
 present, we ensure that \verb|primary_axis| points in the direction of the
-eye in relation to the fish's centroid.
+eye relative to the fish's centroid.
 
@@
 To convert \verb|principal_axis| to \verb|clock_value|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish angles into relative to its centroid.
-Depending on this quadrant, we dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\), which correspond to 9, 6, 3 and ``0'' o'clock respectively.
+Depending on the quadrant, we dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\), which correspond to 9, 6, 3 and ``0'' o'clock respectively.
 The resulting radian value is then converted to a polar displacement in clock value space, and added to the comparative clock value used in the dot product.
@@
 \end{comment}
-\section{Results and Discussion}
+\section{Results}
 Technicians employed by our team have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{leipzig2021biodiversity} for a large number of INHS images.

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

@@
 % Moving teaser since this template doesn't actually ask for one
-Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images~\cite{beaman2012mass}.
+Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain specimen images~\cite{beaman2012mass}.
 Additionally, initiatives, such as the National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program,
@@
 associated with the image collections.
-Poor quality images (e.g. low contrast, inadequate lighting,
+Poor quality images (e.g.\ low contrast, inadequate lighting,
 out-of-focus or cluttered visual arrangements) provide inadequate input
@@
 In order to perform quantitative morphometric analysis of the specimens,
-the physical scale of the images (pixels/inch) is needed; thus
+the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
 requiring the ability to identify and measure rulers in the images.
@@
 the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box
-was computed for all 7,244 images.
+was computed for all \(7,244\) images.
 The overall mean of the differences is \(144.3\), with a standard deviation of \(15.8\).
@@
 classifications.
-The mean of \verb|foreground.mean| over all 7,244 images is 89.5, with a
+The mean of \verb|foreground.mean| over all \(7,244\) images is 89.5, with a
 standard deviation of 16.6. These numbers suggest, for example, that

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

@@
 In this subset of images the average error for the scale calculation
-was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
+was \(0.89\%\), and the average error for the fish length calculation was \(5.55\%\).
 Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler.

### 2021-04-07 paper/paper_new.tex
Edited Section 5.

--- 2021-04-07 paper/paper_new.tex
@@
 \end{comment}
+
+\begin{figure}[b]
+  \centering
+  \includegraphics[width=0.9\linewidth]{images/none1_crop} \\
+  \vspace{3mm}
+  \includegraphics[width=0.9\linewidth]{images/double1_crop}
+  \caption{A fish that was not detected (top) and a fish that was detected twice (bottom).}
+  \label{fig:fish_detect_wrong}
+\end{figure}
+
 \section{Results}
@@
 % and \verb|if_background_uniform| (\verb|background.std|).
-In addition, our process also calculates contrast, bounding boxes and
+In addition, our approach also calculates contrast, bounding boxes and
 fish lengths in centimeters.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.9\linewidth]{images/none1_crop} \\
-  \vspace{3mm}
-  \includegraphics[width=0.9\linewidth]{images/double1_crop}
-  \caption{A fish that was not detected (top) and a fish that was detected twice (bottom).}
-  \label{fig:fish_detect_wrong}
-\end{figure}
 
@@
 Images where one of these objects were not detected generally had some form of coloration issue. They were either washed out, very dark or yellow in hue.
-See Figure \ref{fig:no_ruler} two such examples.
+See Figure \ref{fig:no_ruler} for two such examples.
 Some of the rulers for which ``2'' and/or ``3'' were not detected were particularly scratched and damaged.
@@
 % was wrong.
-For these 6 cases, a spot on the wrong side of the fish was labeled as the
-most likely eye within the bounding box of the fish, i.e.\ eye detection 
-was incorrect. Figure \ref{fig:wrong_eye} presents one such example.
+For these 6 incorrect cases, a spot on the wrong side of the fish was
+labeled as the most likely eye within the bounding box of the fish.
+% , i.e.\ eye detection was incorrect.
+Figure \ref{fig:wrong_eye} presents one such example.
 There were an additional 17 images for which the automated process generated a result that did not match the manually created data.
@@
 This result highlights the additional utility of automated methods to
-double-check and verify human-generated metadata.
+double-check and verify manually generated metadata.
 
@@
 Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
-For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate. Of the 8 that were
+For 25 of those, the manually generated data was incorrect, giving the automated process a \(3.1\) times lower error rate. Of the 8 that were
 computationally classified incorrectly,
@@
 Examples of each type of image (low, medium, and high contrast) can be seen in Figure~\ref{fig:contrast}.
-The left image has a mean intensity of 103 (low), the middle image 144
+The left image has a contrast of 103 (low), the middle image 144
 (medium), and the right 186 (high).
@@
 The mean and standard deviation of the foreground intensities were
-computed for the images in the three human-specified classes.
+computed for the images in the three manually specified classes.
 Table~\ref{tab:bright} contains the resulting values and shows that
-automated intensities values provide objective measures that may be used to break images into groups that correlate with human-defined brightness
-classifications.
+automated intensities values provide objective measures that may be used to break images into groups that correlate with manually generated
+brightness classifications.
 The mean of \verb|foreground.mean| over all 7,244 images is 89.5, with a
-standard deviation of 16.6. These numbers suggest, for example, that
-\verb|foreground.mean| $\pm$ one-half a standard deviation could define 
-\verb|normal| brightness, with values outside this range being classified
-as \verb|dark| or \verb|bright|.
+standard deviation of 16.6.
+Given that human perception of brightness is quite subjective and
+highly variable, we found it problematic to use specific threshold
+values to define \verb|dark|, \verb|normal| or \verb|bright| specimens
+in concordance with the manually generated metadata.  The technicians
+showed little consistency when classifying \verb|normal| or \verb|bright|
+specimens. We did find that an 81.2\% accuracy rate could be achieved by
+classifying \verb|dark|, as those with a \verb|foreground.mean| of 75
+or lower; thus demonstrating that this computed metadata property does 
+offer some value when assessing image quality.
+% These numbers suggest, for example, that
+% \verb|foreground.mean| $\pm$ one-half a standard deviation could define 
+% \verb|normal| brightness, with values outside this range being classified
+% as \verb|dark| or \verb|bright|.
 
@@
 
-Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found.
-All but 263 of these were generated via pixel analysis, with those 263 falling back to the original \verb|detectron| bounding box.
+Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found. All but 263 of these were generated via pixel analysis, with
+the 263 falling back to the original \verb|detectron| bounding box.
 100 randomly-chosen images were reviewed manually to evaluate the
@@
 seen in Figure \ref{fig:missedTail}.
-\begin{figure}[H]
+Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but further refinement of our algorithms will be needed
+to ensure that light fins and tails are masked consistently and accurately.
+\begin{figure}[t]
   \centering
@@
 \end{figure}
-Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but further refinement of our algorithms will be needed
-to ensure that light fins and tails are masked consistently and accurately.
 
@@
 When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well.
-An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm).
+An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand-measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm).
 Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.

### 2021-04-07 paper/paper_new.tex

@@
 In this subset of images the average error for the scale calculation
-was \(0.91\%\), and the average error for the fish length calculation was \(5.87\%\).
+was \(0.89\%\), and the average error for the fish length calculation was \(5.55\%\).
 Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler.
 When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well.
-An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand-measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm).
+An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm).
 Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

--- 2021-04-07 paper/paper_new.tex
@@
 
-1) Explore use of Facebook AI Research's \verb|detectron| tool.  Specific
+\begin{enumerate}
+\item Explore use of Facebook AI Research's \verb|detectron| tool.  Specific
 aims are to use \verb|detectron| to identify study-specific objects.
@@
 
-2) Investigate image processing at the pixel level.
+\item Investigate image processing at the pixel level.
 Pilot testing found that \verb|detectron| under-segmented the detected objects
@@
 
-\renewcommand{\labelenumi}{\alph{enumi}.}
+%\renewcommand{\labelenumi}{\alph{enumi}.}
 \begin{enumerate}
@@
 
-3) Compute a number of high-level metadata properties from the detected objects and image quality metrics.
+\item Compute a number of high-level metadata properties from the detected objects and image quality metrics.
 % [*Test our ability to calculate] the following set of
@@
 
-4) Compare computed metadata properties with manually generated properties
+\item Compare computed metadata properties with manually generated properties
 when possible to assess the accuracy and effectiveness of automated 
 methods.
+\end{enumerate}
 

### 2021-04-07 paper/paper_new.tex
Changed example images
Fixed figure numbering. (Fig. 7)
Tweaked language in Sect. V.F .

@@
 
-\begin{figure*}[t]
-  \centering
-  \includegraphics[width=0.31\linewidth]{images/dark}
-  \includegraphics[width=0.31\linewidth]{images/normal}
-  \includegraphics[width=0.31\linewidth]{images/bright}
-  \caption{Examples of low, medium and high contrast fish images.}
-  \label{fig:contrast}
-\end{figure*}
-
 \subsection{Side Detection}
@@
 \end{comment}
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=0.31\linewidth]{images/dark}
+  \includegraphics[width=0.31\linewidth]{images/normal}
+  \includegraphics[width=0.31\linewidth]{images/bright}
+  \caption{Examples of low, medium and high contrast fish images.}
+  \label{fig:contrast}
+\end{figure*}
 
@@
 in concordance with the manually generated metadata.  The technicians
-showed little consistency when classifying \verb|normal| or \verb|bright|
+showed little consistency when classifying \verb|normal| versus \verb|bright|
 specimens. We did find that an 81.2\% accuracy rate could be achieved by
-classifying \verb|dark|, as those with a \verb|foreground.mean| of 75
-or lower; thus demonstrating that this computed metadata property does 
+classifying \verb|dark| images as those with a \verb|foreground.mean| of 75
+or less; thus demonstrating that this computed metadata property does 
 offer some value when assessing image quality.
@@
   \centering
-  \includegraphics[width=0.49\linewidth]{images/011196_pred}
-  \includegraphics[width=0.49\linewidth]{images/011196_mask}
+  %\includegraphics[width=0.49\linewidth]{images/011196_pred}
+  %\includegraphics[width=0.49\linewidth]{images/011196_mask}
+  \includegraphics[width=0.49\linewidth]{images/6703_pred}
+  \includegraphics[width=0.49\linewidth]{images/6703_mask}
   \includegraphics[width=0.49\linewidth]{images/52399_pred}
   \includegraphics[width=0.49\linewidth]{images/52399_mask}
-  \includegraphics[width=0.49\linewidth]{images/56885_pred}
-  \includegraphics[width=0.49\linewidth]{images/56885_mask}
+  %\includegraphics[width=0.49\linewidth]{images/56885_pred}
+  %\includegraphics[width=0.49\linewidth]{images/56885_mask}
   \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

@@
 
-\section{Conclusions}
-The BGNN project demonstrates a clear need for improved metadata associated with specimen image collections.
+\section{Discussion}
+Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, particularly pixel analysis to improve and enrich metadata that enables researchers to apply machine learning to investigate scientific research questions on a scale that has never been pursued before.
+Our investigation focused on fish in general.
+Fish are vertebrate animals (phylum Chordata), with current knowledge of there being over 34,000 fish species\cite{fishbase}, and this figure does not include the world of unidentified species.
+Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype.
+The ability to analyze thousands of images of of a single fish species computationally can lead to new discoveries that are impossible to manually pursue.
+Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress \cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity.
+Efforts to integrate such methods in digital libraries, particularly for digitized specimens, appear to be still somewhat limited, likely due to the diversity of image shapes and sizes.
+Object detection as explored in our research, working with existing software, is applicable the the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research.
+
+Digital libraries serve to collect, provide access to, and archive rich collections, of a wide array of materials.
+Many digital libraries interconnect with open repository, supporting FAIR (Findable, Accessible, Interoperable, and Reuseable)\cite{wilkinson2016fair}.
+In discussing the future of digitial library services \cite{fox2021building} underscores the need to prepare for and test AI applications.
+The work presented here, with BGNN project demonstrates a clear need for improved metadata associated with specimen image collections.
 Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and machine learning is limited.
@@
 
+\section{Conclusion}
 In this paper we presented such a metadata generation program.
@@
 
-\section*{Acknowledgment}
+%\section*{Acknowledgment}
 %can make possible note about larger BGNN team, and/or general note to Tulane data in-putters for giving us data to compare, and/or INHS collection. [we can discuss]

### 2021-04-08 paper/paper_new.tex

@@
 \section{Discussion}
-Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, particularly pixel analysis to improve and enrich metadata that enables researchers to apply machine learning to investigate scientific research questions on a scale that has never been pursued before.
+Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, to improve and enrich metadata that enables researchers to pursue advanced specimen image analysis and investigate scientific research questions on a scale that has never been pursued before.
 Our investigation focused on fish in general.
@@
 Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype.
-The ability to analyze thousands of images of of a single fish species computationally can lead to new discoveries that are impossible to manually pursue.
-Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress \cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity.
-Efforts to integrate such methods in digital libraries, particularly for digitized specimens, appear to be still somewhat limited, likely due to the diversity of image shapes and sizes.
+The ability to analyze thousands of images of a single fish species computationally can lead to new discoveries that are impossible to manually pursue.
+Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress \cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity for useful metadata.
+Efforts to integrate such methods in digital libraries as a means of automatic metadata generation, particularly for digitized specimens, appear to be still somewhat limited, likely due to the diversity of image shapes and sizes.
 Object detection as explored in our research, working with existing software, is applicable the the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research.
+And following object verification, one can apply pixel analysis to computer XXX
+%can we say something here.
 

### 2021-04-08 paper/paper_new.tex
Updates from Overleaf

--- 2021-04-07 paper/paper_new.tex
@@
 \begin{abstract}
-Metadata is a key data source, particularly for researchers seeking to apply machine learning to the vast collections of digitized specimens.
-Unfortunately, the available metadata is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual means.
+Metadata is a key data source, particularly for researchers seeking to apply machine learning (ML) to the vast collections of digitized specimens.
+Unfortunately, the available metadata is often sparse and, at times, erroneous.
+Additionally, it is prohibitively expensive to address these limitations through traditional, manual means.
 This paper reports on research that applies machine-driven approaches to
-analyzing digitized fish images and extracting various of important
+analyzing digitized fish images and extracting various important
 features from them.
@@
 Automatically generated metadata is crucial for identifying
-the high-quality images needed for the neural network's predictive
-analyses.
+the high-quality images needed for the neural network's predictive analytics.
 %predictive analytics?
-Methods that  combine machine learning  and  image  informatics techniques allow us to rapidly enrich the existing metadata associated with each of the
+Methods that  combine ML and image informatics techniques allow us to rapidly enrich the existing metadata associated with each of 
 7,244 images from the Illinois Natural History Survey (INHS). The sample
-images each include 22 manually generated metadata properties, which
-aid our study.  Results show we can  accurately generate metadata for
-twenty key %6? 
-metadata properties, for example: fish quantity, fish orientation,
-image scaling based on
+images all have 22 manually generated metadata properties associated with them, which
+aid our study.  Results show we can accurately generate many key metadata properties relevant to the
+BGNN project such as: fish quantity and orientation,  image scaling based on
 ruler identification and measurement, and general image quality metrics
-(brightness and contrast). Results also show can also x, y, z.
+(e.g.\ brightness and contrast). Results also show we can also accurately generate bounding boxes and segmentation masks for fish, which are needed for subsequent machine learning analysis.
 %to confirm list of six properties.
@@
 as well as accuracy, and provides a novel solution for leveraging digitized
-specimens for machine learning. This research has implications for harnessing the tens of thousands of digitized specimens stored in open-access repositories found wold-wide.
+specimens in ML. This research has implications for harnessing the tens of thousands of digitized specimens stored in open-access repositories found wold-wide.
 %world wide [*across the globe] or we may not even need this part as open access is global access
@@
 % OLD text - Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
-One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent machine learning, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect.
+One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent ML, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect.
 As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features.
 These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies.
-Using a combination of machine learning and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
+Using a combination of ML and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images.
 A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
@@
 The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
-on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying machine learning and making new scientific discoveries.
+on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying ML and making new scientific discoveries.
 
@@
 for automated
-image analysis and machine learning algorithms and lead to inferior
+image analysis and ML algorithms and lead to inferior
 computational results.
@@
 Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
-human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %machine learning? or okay here
+human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %ML? or okay here
 to examine thousands of images
@@
 The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which is developing a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
-Using a combination of machine learning and image informatics 
+Using a combination of ML and image informatics 
 techniques,
@@
 In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawn from acquisition logs or original specimen labels.
-This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply machine learning to the image and the metadata for scientific research.
+This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply ML to the image and the metadata for scientific research.
 
@@
 The camera's technical metadata is automatically captured and inserted into digital image files at the time of acquisition.
-Some of this metadata may be useful when selecting a machine learning sample.
+Some of this metadata may be useful when selecting a ML sample.
 A researcher may desire images with specific properties, such as being captured chiefly with a certain aperture setting.
@@
 Fish image analysis research, as reviewed below, demonstrates the
-potential of automated computational methods to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for the application of machine learning.
+potential of automated computational methods to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for the application of ML.
 
@@
 The morphological differences between different fish species are obvious.
-Machine learning methods use artificial prior knowledge to extract fish features, which is time-consuming, laborious, and subjective.
+ML methods use artificial prior knowledge to extract fish features, which is time-consuming, laborious, and subjective.
 Recently, deep learning-based identification of fish species has been widely used.
@@
 accessible in open repositories. Our research addresses this need by
-applying machine learning and image informatics techniques to extract key
+applying ML and image informatics techniques to extract key
 metadata properties from fish specimen images and computing
@@
 <--NOTE-NOTE-NOTE DAVE/JOEL/ALL - RE: above paragraph, I'm thinking we should we shift message a little bit to something like, e.g., "The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories.
-Our research addresses this need by applying machine learning and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results.
+Our research addresses this need by applying ML and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results.
 Our goals and objectives are presented in the following section.
@@
 
-%I think this paragraph could be deleted then, or moves elsewhere, we say this a lot already: We are applying a variety of machine learning, image processing and image informatics techniques to extract key metadata properties from the images.
+%I think this paragraph could be deleted then, or moves elsewhere, we say this a lot already: We are applying a variety of ML, image processing and image informatics techniques to extract key metadata properties from the images.
 These properties a critical for selecting high-quality, usable digitized specimens for further computational analysis, and and ensuring that the specimen images meet both scientific and technical requirements.
@@
 Digitized specimens accessible in open-access repositories provide a rich,
-extensive data source for machine learning and scientific discovery.
+extensive data source for ML and scientific discovery.
 These resources, however, remain largely untapped due to image quality
@@
 The overall goal of our work addresses this need by
-% combining machine learning and image informatics techniques to produce
+% combining ML and image informatics techniques to produce
 developing a computational
@@
 See Figure \ref{fig:INHS_examples} for three example images from the collection.
-While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.
+While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that ML and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.
 
 \section{Methods}
-Our process for metadata generation can be divided into three steps: 1) object detection with Facebook's Detectron2 machine learning library (referred to as \verb|detectron|), 2) image processing at the pixel level, and 3) calculations on the results of the previous steps to determine higher level metadata properties.
+Our process for metadata generation can be divided into three steps: 1) object detection with Facebook's Detectron2 ML library (referred to as \verb|detectron|), 2) image processing at the pixel level, and 3) calculations on the results of the previous steps to determine higher level metadata properties.
 % \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}
@@
 
-\section{Conclusions}
-The BGNN project demonstrates a clear need for improved metadata associated with specimen image collections.
-Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and machine learning is limited.
+\section{Discussion}
+Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, to improve and enrich metadata that enables researchers to perform advanced specimen image analysis and investigate scientific research questions on a scale that has never been pursued before.
+Our investigation has thus far focused on fish as the specimen of study.
+Fish are vertebrate animals (phylum Chordata), with over \(34,000\) known unique species~\cite{fishbase}, and likely many more undiscovered.
+Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype information.
+The ability to analyze thousands of images of a single fish species computationally can lead to new discoveries that are impossible to pursue manually.
+Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity for useful metadata.
+Efforts to integrate such methods in digital libraries as a means of automatic metadata generation, particularly for digitized specimens, appear to still be somewhat limited.
+This is likely due to the diversity of image shapes, sizes and the inconsistent configurations of specimens, labels, rulers, etc.\ within them.
+Object detection as explored in our research, working with an established architecture, is applicable the the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research.
+And following object detection, one can apply pixel analysis to computer many more higher order properties from the initial segmentation information.
+%can we say something here.
+
+Digital libraries serve to collect, provide access to, and archive rich collections of a wide array of materials.
+Many digital libraries interconnect with open repository, supporting FAIR (Findable, Accessible, Interoperable, and Reuseable)~\cite{wilkinson2016fair}.
+In discussing the future of digital library services \cite{fox2021building} underscores the need to prepare for and test ML applications.
+The work presented here, within the context of the BGNN project, demonstrates a clear need for improved metadata associated with specimen image collections.
+Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and ML is limited.
 Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are needed to generate this missing metadata at scale.
 
+\section{Conclusion}
 In this paper we presented such a metadata generation program.
-Using machine learning and image informatics tools and techniques, it is able to locate, bitmask and analyze specimen (currently limited to fish) in collection images with a high degree of accuracy.
+Using ML and image informatics tools and techniques, it is able to locate, bitmask and analyze specimen (currently limited to fish) in collection images with a high degree of accuracy.
 It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes and scale and length information.

### 2021-04-08 paper/paper_new.tex
Updates from Overleaf

@@
 
-%\begin{wraptable}{r}{5.5cm}
+%\begin{wraptable}{r}{5.0cm}
 \begin{table}[H]
@@
 This is likely due to the diversity of image shapes, sizes and the inconsistent configurations of specimens, labels, rulers, etc.\ within them.
-Object detection as explored in our research, working with an established architecture, is applicable the the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research.
+Object detection as explored in our research, working with an established architecture, is applicable the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research.
 And following object detection, one can apply pixel analysis to computer many more higher order properties from the initial segmentation information.

### 2021-04-08 paper/paper_new.tex
Updates from Overleaf

@@
 The ability to analyze thousands of images of a single fish species computationally can lead to new discoveries that are impossible to pursue manually.
-Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity for useful metadata.
-Efforts to integrate such methods in digital libraries as a means of automatic metadata generation, particularly for digitized specimens, appear to still be somewhat limited.
+Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity to automatically generate useful metadata.
+Efforts to integrate such automatic metadata generation methods into digital library workflows and architectures still seem limited.
+%content based information retrieval (CBIR) for digital library images\cite{ivanova2011content}
+%Link above is from the EU counterpart to JCDL, and trying to weave in, just focuses on color semantics, if we want to get another citation in there.
 This is likely due to the diversity of image shapes, sizes and the inconsistent configurations of specimens, labels, rulers, etc.\ within them.

### 2021-04-08 paper/paper_new.tex
Tweaking images and such.

--- 2021-04-08 paper/paper_new.tex
@@
 e.g.~the size of a dorsal fin.
-\begin{figure*}
-  \centering
-  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
-  \hspace{1mm}
-  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100682}
-  \hspace{1mm}
-  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
-  \caption{Three example images from the Illinois Natural History Survey (INHS) collection.}
+\begin{figure}[t]
+  \centering
+  % \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
+  % \hspace{1mm}
+  \includegraphics[width=.95\linewidth]{images/INHS_FISH_100682}
+  % \hspace{1mm}
+  % \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
+  \caption{An image from the Illinois Natural History Survey (INHS) collection.}
   \label{fig:INHS_examples}
-\end{figure*}
+\end{figure}
 
@@
 images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
-Figure \ref{fig:INHS_examples} presents three typical images used in our
+Figure \ref{fig:INHS_examples} presents a typical image used in our
 study.
@@
 In conclusion, the proposed convolutional neural network (CNN)-based method has a single and generic trained architecture with promising performance for fish species identification.
-Iqbal et al.~\cite{Iqbal2021AutomaticFS} used a modified
-AlexNet \cite{AlexNet2012} model to classify six different fish species
-with 90\% accuracy.
+Iqbal et al.~\cite{Iqbal2021AutomaticFS} used a
+deep learning
+% modified AlexNet \cite{AlexNet2012}
+model to classify six different fish species with 90\% accuracy.
 % In this paper, we presented an automated system for identification and classification of fish species.
@@
 
-\begin{figure*}[t]
-  \centering
- \includegraphics[width=.45\linewidth]{images/teaser1_crop}
-  \hspace{5mm}
-  \includegraphics[width=.45\linewidth]{images/teaser2_crop}
-  \caption{Initial object detection on two specimen images using Detectron2~\cite{wu2019detectron2}.}
+\begin{figure}[t]
+  \centering
+ % \includegraphics[width=.45\linewidth]{images/teaser1_crop}
+  % \hspace{5mm}
+  \includegraphics[width=.95\linewidth]{images/teaser2_crop}
+  \caption{Initial object detection on a specimen image using Detectron2~\cite{wu2019detectron2}.}
   \label{fig:teaser}
-\end{figure*}
+\end{figure}
 
@@
 The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.
-See Figure \ref{fig:INHS_examples} for three example images from the collection.
+See Figure \ref{fig:INHS_examples} for an example image from the collection.
 While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that ML and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.

### 2021-04-08 paper/paper_new.tex
Tweaked Fig. 10 placement.
Edited abstract.

@@
 %predictive analytics?
-Methods that  combine ML and image informatics techniques allow us to rapidly enrich the existing metadata associated with each of 
-7,244 images from the Illinois Natural History Survey (INHS). The sample
-images all have 22 manually generated metadata properties associated with them, which
-aid our study.  Results show we can accurately generate many key metadata properties relevant to the
+Methods that  combine ML and image informatics techniques allow us to rapidly enrich the existing metadata associated with the
+7,244 images from the Illinois Natural History Survey (INHS) used in our
+study. The sample
+images also have 22 manually generated metadata properties, which
+can be used for comparison.  Results show we can accurately generate many key metadata properties relevant to the
 BGNN project such as: fish quantity and orientation,  image scaling based on
@@
 as well as accuracy, and provides a novel solution for leveraging digitized
-specimens in ML. This research has implications for harnessing the tens of thousands of digitized specimens stored in open-access repositories found wold-wide.
+specimens in ML. This research demonstrates the ability of computational
+methods to enhance the digital library services associated with
+the tens of thousands of digitized specimens stored in open-access
+repositories world-wide.
 %world wide [*across the globe] or we may not even need this part as open access is global access
@@
 Iqbal et al.~\cite{Iqbal2021AutomaticFS} used a
-deep learning
-% modified AlexNet \cite{AlexNet2012}
+% deep learning
+modified AlexNet \cite{AlexNet2012}
 model to classify six different fish species with 90\% accuracy.
@@
 
+\begin{figure}[b]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/54172}
+  \includegraphics[width=0.49\linewidth]{images/54172_mask}
+  \caption{A fish for which the masking and measurement process was highly accurate.}
+  \label{fig:scale_len}
+\end{figure}
+
 \subsection{Scale and Length}
@@
 Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/54172}
-  \includegraphics[width=0.49\linewidth]{images/54172_mask}
-  \caption{A fish for which the masking and measurement process was highly accurate.}
-  \label{fig:scale_len}
-\end{figure}
 

### 2021-04-08 paper/paper_new.tex
Edited Sections 6 & 7

@@
 
-\begin{figure}[b]
+\begin{figure}[t]
   \centering
   \includegraphics[width=0.9\linewidth]{images/none1_crop} \\
-  \vspace{3mm}
+  \vspace{5mm}
   \includegraphics[width=0.9\linewidth]{images/double1_crop}
@@
 \section{Discussion}
-Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, to improve and enrich metadata that enables researchers to perform advanced specimen image analysis and investigate scientific research questions on a scale that has never been pursued before.
-Our investigation has thus far focused on fish as the specimen of study.
-Fish are vertebrate animals (phylum Chordata), with over \(34,000\) known unique species~\cite{fishbase}, and likely many more undiscovered.
+Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, to improve and enrich metadata that enables advanced specimen image analysis and investigations of scientific research questions on an unprecedented
+scale. Our investigation has thus far focused on fish as the specimen of study. Fish are vertebrate animals (phylum Chordata), with over \(34,000\) known unique species~\cite{fishbase},
+with many more likely undiscovered.
 Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype information.
-The ability to analyze thousands of images of a single fish species computationally can lead to new discoveries that are impossible to pursue manually.
-Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity to automatically generate useful metadata.
+The ability to computationally analyze thousands of images of a single fish species, from different habitats and time periods, can lead to new discoveries that are impossible to pursue with manual methods.
+Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods.
+The work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunities to automatically generating useful metadata.
 Efforts to integrate such automatic metadata generation methods into digital library workflows and architectures still seem limited.
@@
 This is likely due to the diversity of image shapes, sizes and the inconsistent configurations of specimens, labels, rulers, etc.\ within them.
-Object detection as explored in our research, working with an established architecture, is applicable the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research.
-And following object detection, one can apply pixel analysis to computer many more higher order properties from the initial segmentation information.
+Object detection as explored in our research, working with an established architecture, is applicable to the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized objects made accessible for scientific and scholarly research.
+Following object
+detection, one can apply pixel analysis and informatics methods to compute
+many more higher order properties from the initial segmentations.
 %can we say something here.
@@
 Digital libraries serve to collect, provide access to, and archive rich collections of a wide array of materials.
-Many digital libraries interconnect with open repository, supporting FAIR (Findable, Accessible, Interoperable, and Reuseable)~\cite{wilkinson2016fair}.
-In discussing the future of digital library services \cite{fox2021building} underscores the need to prepare for and test ML applications.
+Many digital libraries interconnect with open repositories, supporting FAIR (Findable, Accessible, Interoperable, and Reuseable)~\cite{wilkinson2016fair}.
+In discussing the future of digital library services, Fox \cite{fox2021building} underscores the need to prepare for and test ML applications.
 The work presented here, within the context of the BGNN project, demonstrates a clear need for improved metadata associated with specimen image collections.
-Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and ML is limited.
-Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are needed to generate this missing metadata at scale.
+Much effort, time and money have been put into photographing and digitizing physical specimens, but without detailed and complete metadata properties the utility of these repositories for advanced computational analysis and ML is limited.
+Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are essential to generating the missing metadata at scale.
 
 \section{Conclusion}
-In this paper we presented such a metadata generation program.
-Using ML and image informatics tools and techniques, it is able to locate, bitmask and analyze specimen (currently limited to fish) in collection images with a high degree of accuracy.
-It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes and scale and length information.
-Testing this program on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation data.
-Through further refinement and generalizing beyond only INHS images, we aim to create a tool that can be distributed to specimen image collection curators to correct the metadata sparsity that precipitated this work.
+In this paper we presented an automatic metadata generation approach. 
+Using ML and image informatics algorithms, it is able to locate, mask and analyze specimens (currently limited to fish) in collection images with a high degree of accuracy.
+It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes, scale and length information.
+Testing this approach on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation data.
+Through further refinement and generalization beyond only INHS images, we aim to create a tool that can be distributed to specimen image collection curators to correct the metadata sparsity that precipitated this work.
 \subsection{Future Work}
@@
 Some of the lightest tails appear yellow in hue to the human eye and easily distinguishable, but when compressed to a single intensity value they are almost identical in value to the white background.
-Considering when the RGB channels of a pixel are not equal in value may be able to improve masking of such features.
-Another possible approach to solving this is to threshold and mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.
+Considering when the RGB channels of a pixel are not equal in value may improve masking of such features.
+Another possible approach to solving this
+problem is to threshold and mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.
 
 Our ultimate goal is to create a generalized process that works on classes of specimen images.
-For the BGNN project we are beginning with fish images, but we are designing the metadata generation system such that it can eventually operate on other species if trained that way.
-To accomplish this, a much larger training dataset full of more diverse images will be required.
-The first step towards greater generality will be to operate on other fish collections besides INHS, which is something our program has already show itself capable of doing during initial testing.
-Another requirement will be to generalize the ruler reading process beyond the INHS specific reading of digits on the ruler, which will likely involve an automated method of reading ruler ticks instead of digits.
+For the BGNN project we are beginning with fish images, but we are designing the metadata generation system so that it can eventually operate on other species if appropriately  trained.
+To accomplish this, a much larger training dataset consisting of more diverse images will be required.
+The first step towards greater generality will be to operate on other fish collections besides INHS, which is something our program has already
+shown itself capable of doing during initial testing.
+Another requirement will be to generalize the ruler reading process beyond the INHS-specific reading of digits on the ruler, which will likely involve an automated method of reading ruler ticks instead of digits.
 % Todo: Are these worth mentioning?

### 2021-04-08 paper/paper_new.tex
Updates from Overleaf

@@
 
-Our ultimate goal is to create a generalized process that works on classes of specimen images.
+Our longer-term goal is to create a generalized process that works on classes of specimen images.
 For the BGNN project we are beginning with fish images, but we are designing the metadata generation system so that it can eventually operate on other species if appropriately  trained.
@@
 Another requirement will be to generalize the ruler reading process beyond the INHS-specific reading of digits on the ruler, which will likely involve an automated method of reading ruler ticks instead of digits.
+Overall, the  research reported in this paper will improve our BGNN workflow, and at the same time demonstrates an innovative approach that may greatly enhance digital  library  services for the tens of thousands of digitized specimens and images for other types of objects.
 % Todo: Are these worth mentioning?

### 2022-09-15 legacy_code/paper/jcdl.tex
Create legacy-code folder with initial code

--- 2021-04-08 paper/paper_new.tex
@@
 \begin{abstract}
-Metadata is a key data source, particularly for researchers seeking to apply machine learning (ML) to the vast collections of digitized specimens.
+Metadata are key descriptors of research data, particularly for researchers seeking to apply machine learning (ML) to the vast collections of digitized specimens.
 Unfortunately, the available metadata is often sparse and, at times, erroneous.
 Additionally, it is prohibitively expensive to address these limitations through traditional, manual means.
-This paper reports on research that applies machine-driven approaches to
-analyzing digitized fish images and extracting various important
-features from them.
+This paper reports on research that applies machine-driven approaches to analyzing digitized fish images and extracting various important features from them.
 The digitized fish specimens are being analyzed as part of the Biology Guided Neural Networks (BGNN) initiative, which is developing a novel class of artificial neural networks using phylogenies and anatomy ontologies.
-Automatically generated metadata is crucial for identifying
-the high-quality images needed for the neural network's predictive analytics.
-%predictive analytics?
-Methods that  combine ML and image informatics techniques allow us to rapidly enrich the existing metadata associated with the
-7,244 images from the Illinois Natural History Survey (INHS) used in our
-study. The sample
-images also have 22 manually generated metadata properties, which
-can be used for comparison.  Results show we can accurately generate many key metadata properties relevant to the
-BGNN project such as: fish quantity and orientation,  image scaling based on
-ruler identification and measurement, and general image quality metrics
-(e.g.\ brightness and contrast). Results also show we can also accurately generate bounding boxes and segmentation masks for fish, which are needed for subsequent machine learning analysis.
-%to confirm list of six properties.
-%x, y, z = any other key results. jg will add from results section, unless someone else does first. 
-The automatic process out-performs humans in terms of time and labor cost,
-as well as accuracy, and provides a novel solution for leveraging digitized
-specimens in ML. This research demonstrates the ability of computational
-methods to enhance the digital library services associated with
-the tens of thousands of digitized specimens stored in open-access
-repositories world-wide.
-%world wide [*across the globe] or we may not even need this part as open access is global access
-
+Automatically generated metadata is crucial for identifying the high-quality images needed for the neural network's predictive analytics.
+Methods that combine ML and image informatics techniques allow us to rapidly enrich the existing metadata associated with the 7,244 images from the Illinois Natural History Survey (INHS) used in our study.
+Results show we can accurately generate many key metadata properties relevant to the BGNN project, as well as general image quality metrics (e.g.\ brightness and contrast).
+Results also show that we can accurately generate bounding boxes and segmentation masks for fish, which are needed for subsequent machine learning analyses.
+The automatic process outperforms humans in terms of time and accuracy, and provides a novel solution for leveraging digitized specimens in ML.
+This research demonstrates the ability of computational methods to enhance the digital library services associated with the tens of thousands of digitized specimens stored in open-access repositories world-wide.
 % OLD text - Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery.
@@
 The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
-on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying ML and making new scientific discoveries.
+on a previously unattainable scale. Moreover, the digitized instantiations present a pathway  for making new scientific discoveries via the application of machine learning (ML).
 
@@
 Poor quality images (e.g.\ low contrast, inadequate lighting,
-out-of-focus or cluttered visual arrangements) provide inadequate input
+out-of-focus or cluttered visual arrangements) are inadequate
 for automated
-image analysis and ML algorithms and lead to inferior
+image analysis by ML algorithms and lead to inferior
 computational results.
@@
 the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
-requiring the ability to identify and measure rulers in the images.
+requiring the ability to identify and take measurements using rulers in the images.
 Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
-specimen taxon, geographic location, and several other descriptive aspects.
+specimen taxon, geographic location, and several other specimen-related aspects.
 Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
@@
 to determine if, for example, a specific fish grows to different lengths
-in different habitats, or the temporal evolution of an anatomical feature,
+in different habitats, or to study differences in the size of a particular anatomical feature,
 e.g.~the size of a dorsal fin.
@@
 
-Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is both labor- and time-intensive and prohibitively expensive.
+Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is prohibitively expensive.
 Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
@@
 %tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
-we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
+we can accurately determine general image quality and metadata, such as fish quantity, location and orientation, and
 image scaling based on ruler identification and measurement. Image scaling
@@
 have been  applied to a set of \(7,244\)
-images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
+images drawn from the Illinois Natural History Survey (INHS) Collection of fish specimens~\cite{INHS}.
 Figure \ref{fig:INHS_examples} presents a typical image used in our
@@
 %question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.
-A number of different metadata standards have been applied to support the description and access of digitized scientific images.
+A number of different metadata standards have been applied to support the description and access of digital images of scientific specimens.
 The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data, is one of the most popular standards for such efforts.
 It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}.
-The Audubon Core~\cite{audub_core}, which supports the discoverability, dissemination, and use of data related to biological organisms (including 3--D digitized specimens), is a DwC extension that has become more popular.
+The Audubon Core~\cite{audub_core}, which supports the discoverability, dissemination, and use of data related to biological organisms (including 3--D digitized specimens), is a DwC extension that has become the popular metadata standard for biodiversity multimedia resources and collections.
 All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the perspective of a human curator.
 In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawn from acquisition logs or original specimen labels.
-This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply ML to the image and the metadata for scientific research.
+The generated metadata associated with each digital rendering is generally sparse and prone to human error, placing limitations on a researcher seeking to apply ML to the image and the metadata for scientific research.
 
@@
 content for 22 metadata properties that characterize digitized specimen image quality.
-Their work is being conducted in connection with the larger BGNN initiative, and the current process is costly in terms of labor and time, prone to human error and inconsistencies, and underscores the need to
-explore automatic metadata generation methods.
+Their work is being conducted in connection with the larger BGNN initiative, and the difficulties encountered during the process underscore the need to explore automatic metadata generation methods.
 %Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS}
 \subsection{Automatic Metadata Generation}
-Automatic metadata generation advances covering both descriptive and technical metadata are relevant to the research presented in this paper.
+Advances in automatic metadata generation of both descriptive and technical metadata are relevant to the research presented in this paper.
 Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating,paynter2005developing}.
@@
 There has also been some success with extracting descriptive cartographic information from maps~\cite{manso2004automatic}.
-While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; extensive use of automatic processes are still limited.
+While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; uses of automatic processes are still limited.
 More significantly, descriptive metadata does not sufficiently addressed data quality.
@@
 for well over two decades~\cite{Zion2000InvivoFS,Saberioon2017ApplicationOM}. It is an important
-application of technology both for marine science, in the study of aquatic
+application of technology for marine science, in the study of aquatic
 species, habitats and ecosystems, and for the seafood industry, in the
@@
 Rodrigues et al.~\cite{RodriguesMarcoT.A2015Ecda} explored several
-combinations of features extraction, input classifiers and clustering
+combinations of feature extractions, input classifiers and clustering
 algorithms to produce a method that could distinguish between 10 different
-types of fish with a 92\% accuracy.
+types of fish with 92\% accuracy.
 %  Again, not too impressive. Let's leave out.
@@
 extracted by the CNN. They achieved 90\%
-accuracy when identifying 15 different fish in challenging underwater
+accuracy when identifying 15 different fish species in challenging underwater
 digital images.
@@
 Finally, after extracting the fin regions, the start point of the pectoral fin and the end point of the anal fin will be applied in the trout processing system as the head and belly cutting points, respectively.
+\begin{comment}
 Another application of image analysis to fish images is the evaluation of
@@
 A similar approach was developed by Lalabadi et al.~\cite{Lalabadi2020FishFC}.
-
+\end{comment}
+
+The research reviewed above demonstrates the application of image feature extraction and
+machine learning algorithms to fish images; although researchers have not applied these approaches to the numerous collections of digitized specimens accessible in open repositories.
+Our research addresses this need by applying ML and informatics techniques to extract key metadata properties from the images.
+% further computing higher-level metadata based on these initial results.
+The availability of general and powerful
+off-the-shelf ML tools make the usage of previous special-purpose techniques unnecessary.
+% Our goals and objectives are presented in the following section.
+
+\begin{comment}
 The research reviewed above involves image features extraction and
@@
 
-\begin{comment}
 Our work stands apart from previous work in that we are
@@
 % . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
-alternative to the current manual metadata generation process, one that is
-prohibitively costly in both terms of labor and time. Additionally, our
+alternative to the current manual metadata generation process, which is
+prohibitively costly both in terms of labor and time. Additionally, our
 methods collectively provide a novel and general approach to computing
@@
 \item Investigate image processing at the pixel level.
-Pilot testing found that \verb|detectron| under-segmented the detected objects
+Pilot testing found that \verb|detectron| undersegmented the detected objects
 with tightly enclosing bounding boxes. We will determine if
@@
 \item
-Automatically determine when modified methods fail and detectron values
+Automatically determine when modified methods fail and \verb|detectron| values
 should be used as is.
@@
 
+\item Compute a number of high-level metadata properties from the detected objects and image quality metrics.
+% [*Test our ability to calculate] the following set of
+% : 1) contrast (intensities of the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.
+
+\item Compare computed metadata properties with manually generated properties
+when possible to assess the accuracy and effectiveness of automated 
+methods.
+\end{enumerate}
+
+%Following is original Goals/objectives text: The amount of data is immense, with image collections containing 10,000's of entries.
+These discoveries will only be possible with computational techniques that can process this vast amount of data.
+
+%These image-based computational techniques are hampered by both poor image quality and the lack of high-quality and pertinent metadata associated with collections.
+
+%For example, a study may require images that contain only one fish with a given level of lighting and contrast.
+Additionally, performing quantitative investiations into the morphology of the specimens requires knowing the physical scale of the images, i.e.~pixels/inch.
+
+%Given the many thousands of images that have and will be acquired of biological specimens, it is infeasible to generate the needed metadata via manual, i.e.
+via human input, methods.
+It is critical to deploy computational techniques that will automate the process of generating the metatdata that is essential for downstream analyses and studies.
+
+%In order to address the need for fish specimen image metadata that can support scientific investigations we have begun the deployment of both off-the-shelf and custom-written software that automatically generates a variety of metadata from a publicly-available biological image repository.
+The types of metadata being produced are related to image quality, content and scale, and should provide the information necessary for advanced quantitative studies of the digitized specimens.
 \begin{figure}[t]
@@
 
-\item Compute a number of high-level metadata properties from the detected objects and image quality metrics.
-% [*Test our ability to calculate] the following set of
-% : 1) contrast (intensities of the foreground and background, 2) centroid and eye center, and if eye is found, the fish 3) side 4) primary axis and clock value, finally the 5) scale and length.
-
-\item Compare computed metadata properties with manually generated properties
-when possible to assess the accuracy and effectiveness of automated 
-methods.
-\end{enumerate}
-
-%Following is original Goals/objectives text: The amount of data is immense, with image collections containing 10,000's of entries.
-These discoveries will only be possible with computational techniques that can process this vast amount of data.
-
-%These image-based computational techniques are hampered by both poor image quality and the lack of high-quality and pertinent metadata associated with collections.
-
-%For example, a study may require images that contain only one fish with a given level of lighting and contrast.
-Additionally, performing quantitative investiations into the morphology of the specimens requires knowing the physical scale of the images, i.e.~pixels/inch.
-
-%Given the many thousands of images that have and will be acquired of biological specimens, it is infeasible to generate the needed metadata via manual, i.e.
-via human input, methods.
-It is critical to deploy computational techniques that will automate the process of generating the metatdata that is essential for downstream analyses and studies.
-
-%In order to address the need for fish specimen image metadata that can support scientific investigations we have begun the deployment of both off-the-shelf and custom-written software that automatically generates a variety of metadata from a publicly-available biological image repository.
-The types of metadata being produced are related to image quality, content and scale, and should provide the information necessary for advanced quantitative studies of the digitized specimens.
-
-The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.
+The automated metadata generation methods for our project were developed to work on a specific set of images from the INHS\ Fish Collection~\cite{INHS}.
 Most of these images have been configured, produced and acquired with a standard procedure.
@@
 \verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project, given its many flexible and robust capabilities.
+Most importantly, following a review of the literature and available tools, we determined that there were no other machine learning packages that returned pixel by pixel masks over detected objects in a comparable fashion.
+
 \verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format datasets.
@@
         \verb|clock_value|* & Per Fish & Integer & Fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
-        \verb|length|* & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
+        \verb|length|* & Per Fish & Float & The length of a fish in centimeters.\\
         \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
@@
 To overcome this improper segmentation, the threshold value should be
-either adjusted up or down, depending on if the background is lighter or darker than the fish.
+either adjusted up or down, depending on whether the background is lighter or darker than the fish.
 For our current dataset, the background is always lighter (i.e.~closer to 255), so the threshold value needs to be scaled up to include more of the
@@
 % This process is more efficient as all that is required is to shrink
-Each edge is contacted by one pixel up until it contain one or more foreground pixels. Once the shrinkage step is accomplished, the final mask and bounding box have been generated.
+Each edge is contacted by one pixel until it contains one or more foreground pixels. Once the shrinkage step is accomplished, the final mask and bounding box have been generated.
 
@@
 \begin{itemize}
-    \item Program falls back to using detectron mask and bbox for metadata generation in the event the mask generation/pixel analysis fails.
-Failure is defined as never finding a cohesive flood filled mask that covers more than 10\% of the detectron bbox initially.
+    \item Program falls back to using \verb|detectron| mask and bbox for metadata generation in the event the mask generation/pixel analysis fails.
+Failure is defined as never finding a cohesive flood filled mask that covers more than 10\% of the \verb|detectron| bbox initially.
 Can provide a statistic on how often this occurs.
@@
 \section{Results}
-Technicians employed by our team have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{leipzig2021biodiversity} for a large number of INHS images.
-\(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images.
-Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and met our current admissibility criteria for \verb|detectron| and pixel processing.
+Technicians employed by Tulane University have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{leipzig2021biodiversity} for a large number of INHS images.
+\(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images, of which \(7,244\) were both not part of the \verb|detectron| training set and met our current admissibility criteria for \verb|detectron| and pixel processing.
 We ran the metadata extraction program on these \(7,244\) images.
@@
 
-\begin{figure}[H]
+\begin{figure}[b]
   \centering
@@
 %\end{itemize}
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
+  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
+  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
+  \label{fig:wrong_eye}
+\end{figure}
 
@@
 double-check and verify manually generated metadata.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
-  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
-  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
-  \label{fig:wrong_eye}
-\end{figure}
 
@@
 
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=0.32\linewidth]{images/dark}
+  \includegraphics[width=0.32\linewidth]{images/normal}
+  \includegraphics[width=0.32\linewidth]{images/bright}
+  \caption{Examples of low, medium and high contrast fish images.}
+  \label{fig:contrast}
+\end{figure*}
+
 \begin{comment}
@@
 \end{figure}
-\end{comment}
 
@@
 \end{figure*}
+\end{comment}
 
@@
   \label{fig:missedTail}
-\end{figure}
-
-\begin{figure}[b]
+%\end{figure}
+%
+%\begin{figure}[b]
+\vspace{10mm}
   \centering
@@
 The ability to computationally analyze thousands of images of a single fish species, from different habitats and time periods, can lead to new discoveries that are impossible to pursue with manual methods.
-Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods.
+Digital library researchers have been concerned with computationally extracting image features, using content-based image retrieval methods.
 The work by Toress~\cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunities to automatically generating useful metadata.
@@
 Much effort, time and money have been put into photographing and digitizing physical specimens, but without detailed and complete metadata properties the utility of these repositories for advanced computational analysis and ML is limited.
-Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are essential to generating the missing metadata at scale.
+Since it is very time intensive to generate all the pertinent properties by hand, automated techniques are essential to generating the missing metadata at scale.
 
@@
 
-%\section*{Acknowledgment}
-%can make possible note about larger BGNN team, and/or general note to Tulane data in-putters for giving us data to compare, and/or INHS collection. [we can discuss]
+\section{Acknowledgment}
+We thank the full BGNN team for support, the data curation team at the Tulane University Biodiversity Research Institute, and Chris A.
+Taylor, Curator of Fishes and Crustaceans at the Illinois Natural History Survey (INHS).
+INHS is one of six fish collections participating in the Great Lakes Invasives Network (GLIN).
 

### 2022-09-16 gen_metadata_mini/scripts/dataverse_download.py
In Dockerfile Download the model from dataverse

@@ -1,0 +1,67 @@
+# Script to download a dataset from a Dataverse (https://dataverse.org/)
+# originated from John Bradley
+# modified by Thibault Tabarin
+
+import os
+import sys
+import hashlib
+from pyDataverse.api import NativeApi, DataAccessApi
+
+
+def download_dataset(base_url, api_token, doi, directory_output):
+    api = NativeApi(base_url, api_token)
+    data_api = DataAccessApi(base_url, api_token)
+    dataset = api.get_dataset(doi)
+    files_list = dataset.json()['data']['latestVersion']['files']
+    for dv_file in files_list:
+        filepath = download_file(data_api, dv_file, directory_output)
+        verify_checksum(dv_file, filepath)
+
+
+def download_file(data_api, dv_file, directory_output):
+    filepath = dv_file["dataFile"]["filename"]
+    directory_label = dv_file["directoryLabel"]
+    os.makedirs(directory_output, exist_ok=True)
+    filepath = os.path.join(directory_output, filepath)
+    file_id = dv_file["dataFile"]["id"]
+    print("Downloading file {}, id {}".format(filepath, file_id))
+    response = data_api.get_datafile(file_id)
+    with open(filepath, "wb") as f:
+        f.write(response.content)
+    return filepath
+
+
+def verify_checksum(dv_file, filepath):
+    checksum = dv_file["dataFile"]["checksum"]
+    checksum_type = checksum["type"]
+    checksum_value = checksum["value"]
+    if checksum_type != "MD5":
+        raise ValueError(f"Unsupported checksum type {checksum_type}")
+
+    with open(filepath, 'rb') as infile:
+        hash = hashlib.md5(infile.read()).hexdigest()
+        if checksum_value == hash:
+            print("Verified file checksum for {filepath}.")
+        else:
+            raise ValueError(f"Hash value mismatch for {filepath}: {checksum_value} vs {hash} ")
+
+
+def show_usage():
+   print()
+   print(f"Usage: python {sys.argv[0]} <dataverse_base_url> <doi> <directory_output>\n")
+   print("To specify a API token set the DATAVERSE_API_TOKEN environment variable.\n")
+   print("To set the environment variable : export DATAVERSE_API_TOKEN=<my_token>")
+   print()
+
+
+if __name__ == '__main__':
+    if len(sys.argv) != 4:
+         show_usage()
+         sys.exit(1)
+    else:
[…]
